### 2016-06-12 Macro Impacts.tex
Uploading my end of the document

\documentclass{article}

% Packages

\usepackage{fullpage}
\usepackage{amsmath, amsthm, amsfonts, amssymb, mathtools, calrsfs, tensor, physics, MnSymbol,tikz-cd}
\usepackage[mathscr]{euscript}
\usepackage{graphicx}
\graphicspath{ {images/} }
\usepackage{enumitem}
\setlist[description]{font=\normalfont}

% Custom Commands

\newcommand*\diff{\mathop{}\!\mathrm{d}}
\newcommand*\Diff[1]{\mathop{}\!\mathrm{d^#1}}
\newcommand*\nrml{\vartriangleleft}
\newcommand*\scr[1]{\mathscr{#1}}
\newcommand*\bb[1]{\mathbb{#1}}
\newcommand*\la{\langle}
\newcommand*\ra{\rangle}
\newcommand*\gen[1]{\langle #1 \rangle}
\newcommand*\x{\times}
\newcommand*\st{\text{ s.t. }}
\newcommand*\ord[1]{\left\vert#1\right\vert}
\newcommand*\aut{\text{Aut}}
\newcommand*\lcm{\text{lcm}}
\newcommand*\mcal{\mathcal}
\newcommand*\es{\emptyset}
\newcommand*\im{\text{ Im }}
\newcommand*\N{\mathbb N}
\newcommand*\Z{\mathbb Z}
\newcommand*\R{\mathbb R}
\newcommand*\Q{\mathbb Q}
\newcommand*\C{\mathbb C}
\newcommand*\te[1]{\text{#1}}
\newcommand*\en[1]{\begin{enumerate}#1\end{enumerate}}
\newcommand*\e{\varepsilon}
\newcommand*\p[1]{\left(#1\right)}
\newcommand*\ps[1]{\left[#1\right]}
\newcommand*\pc[1]{\left\{#1\right\}}
\newcommand*\f[2]{\frac{#1}{#2}}
\newcommand*\mat[2]{\left(\begin{array}{#1}#2\end{array}\right)}
\newcommand*\ocross{\otimes}
\newcommand*\I{\te{i}}
\newcommand*\pd[3]{\frac{\partial^{#3} #1}{\partial {#2}^{#3}}}
\newcommand*\td[3]{\frac{d^{#3}#1}{d #2^{#3}}}
\newcommand*\m{\te{Mat}}
\newcommand*\End{\te{End}}
\newcommand*\irr{\te{Irr}}
\newcommand*\sgn{\te{sgn}}
\newcommand*\pn[2]{\left\|#1\right\|_{#2}}
\newcommand*\esssup{\te{ess sup}}
\newcommand*\essinf{\te{ess inf}}

% Miscellaneous

\newtheorem{theorem}{Theorem}
\usetikzlibrary{matrix,arrows,decorations.pathmorphing}

% Title
\title{Macro Impacts}
\author{David Cyncynates \\ dcc57@case.edu}
\date{\today}

\begin{document}
\maketitle
The linearized elastic wave equations are (Hemmann)
\begin{align}
0&=(\lambda+2\mu)\nabla^2\phi-\rho\ddot\phi+f\,,\\
0&=\mu\nabla(\nabla\cdot A)-\mu\nabla\times(\nabla\times A)-\rho\ddot A+G\,,
\end{align}
where $u=\nabla\phi+\nabla\times A$ is the displacement and $F=\nabla f+\nabla\times G$ is the body force. Hence, we see to first order that shear waves and compressional waves decouple in the linear regime. If we assume that displacements due to the impact are very small (as we would expect for a very dense macro impact), then we may assume hydrostatic equilibrium, in which case the stress tensor takes the form
\begin{align}
-p\delta_{ij}&=\tau_{ij}=\lambda g_{ij} u^s_{,s}+\mu(u_{i,j}+u_{j,i})\,.
\end{align}
Note, the commas denote covariant differentiation. We now transform into cylindrical coordinates. In the case that we are interested in, the only important component is the radial one, for which we have
\begin{align}
-p&=\tau_{rr}\,,\\
&=\lambda u^s_{,s}+2\mu u_{r,r}\,,\\
&=\lambda \nabla_{s}g^{ss}u_s+2\mu u_{r,r}\,.
\end{align}
The metric of cylindrical coordinates is
\begin{align}
\diff s^2&=\diff r^2+r^2\diff\theta^2+\diff z^2\,,
\end{align}
leading to the Christoffel symbols
\begin{align}
\Gamma^r_{\theta\theta}&=-r\,,\\
\Gamma^r_{r\theta}&=\f1r\,.
\end{align}
Thus, assuming only the radial component has non-zero derivatives (which will be the case for a cylindrically symmetric source),
\begin{align}
\nabla u&=\partial_r u_r+\f1r u_r\,,\\
&=\f1r\partial_r(ru_r)\,.
\end{align}
Hence
\begin{align}
-p&=\tau_{rr}=\lambda\f1r\partial_r(ru_r)+2\mu\partial_r u_r\,,\\
&=\lambda\f1r\partial_r(ru_r)+2\mu\f1r(\partial_r ru_r)-2\mu\f1r(u_r)\,,\\
&=(\lambda+2\mu)\f1r\partial_r(ru_r)-2\mu\f1ru_r\,,\\
&=(\lambda+2\mu)\f1r\partial_r(r\partial_r\phi)-2\mu\f1r\partial_r\phi
\end{align}
With $f=0$, this and the scalar equation of motion yield
\begin{align}
0&=(\lambda+2\mu)\nabla^2\phi-\rho\ddot\phi\,,\\
&=(\lambda+2\mu)\p{\f1r\partial_r\p{r\partial_r\phi}}-\rho\ddot\phi\,,\\
&=-p+2\mu\f1r\partial_r\phi-\rho\ddot\phi\,,
\end{align}
Thus, observe that all the solutions from Hemmann apply with small modification (compare 19 with his equation 9).
Assuming only outgoing modes are generated, we may write $\phi=F(t-r/\alpha)$ where $\alpha=\sqrt{(\lambda+2\mu)/\rho}$ is the compressional wave velocity. We can, for the sake of reusing Hemmann's work, assume that the cavity produced by the macro existed prior to the generation of compressional modes. This is actually somewhat convenient, since it is the production of the cavity that generates shear modes. Denote differentiation with respect to the retarded time $t'=t-\f r\alpha$ by a prime. I can't figure out how to get the following from equation 11 in Hemmann, but the evolution equation is
\begin{align}
-r^3\alpha p&=\alpha\rho r^2 F''+2\mu r F'+2\mu\alpha F\,.
\end{align}
After some guessing and checking, it seems that one can arrive at this equation by the substitution $\phi=\f1rF(t-r/\alpha)$. Either way, this simply confirms that we can use Hemmann directly with only slight modification.
\end{document}

### 2016-06-12 Macro Impacts.tex
Slight Update

@@
 &=\lambda u^s_{,s}+2\mu u_{r,r}\,,\\
-&=\lambda \nabla_{s}g^{ss}u_s+2\mu u_{r,r}\,.
+&=\lambda \nabla u+2\mu u_{r,r}\,.
 \end{align}
@@
 Thus, observe that all the solutions from Hemmann apply with small modification (compare 19 with his equation 9).
+\\\\
 Assuming only outgoing modes are generated, we may write $\phi=F(t-r/\alpha)$ where $\alpha=\sqrt{(\lambda+2\mu)/\rho}$ is the compressional wave velocity.
@@
 Either way, this simply confirms that we can use Hemmann directly with only slight modification.
+In particular, replace $\mu$ in Hemmann's paper with $\mu/2$.
 \end{document}

### 2016-06-13 Macro Impacts.tex
Up to the total energy radiated.

--- 2016-06-12 Macro Impacts.tex
@@
 Either way, this simply confirms that we can use Hemmann directly with only slight modification.
+In particular, replace $\mu$ in Hemmann's paper with $\mu/2$.
+\\\\
+The equation between 43 and 44 provides that
+\begin{align}
+S_r&=-\lambda \dot u_r \nabla u -2\mu u_r \partial_r u_r\,,\\
+&=-\lambda \dot u_r\partial_r u_r-\f{\lambda}{r} \dot u_r u_r -2\mu u_r \partial_r u_r\,,\\
+&=-(\lambda+2\mu) \dot u_r\partial_r u_r-\f{\lambda}{r} \dot u_r u_r\,.
+\end{align}
+Again, this only differs from his work by a factor of two on the right-most term.
+However, in this case, it is not so simple as substituting $\mu/2$ for $\mu$.
+In this case, we may need to follow through some calculations with the modification unless there is another simple change we can make.
+However, he appears to drop the problem term in the following steps...
+\\\\
+Now, the obvious modification to calculate $Q$, the total energy radiated from the source, is that instead of integrating over a spherical shell, we must integrate over the length of the explosion and the circle of radius $r$.
+This yields
+\begin{align}
+Q&=2\pi rL\int_{-\infty}^{\infty}S_r\diff t\,.
+\end{align}
+Dropping the terms as in Hemmann, we find that
+\begin{align}
+Q&=-2\pi rL(\lambda+2\mu)\int_{-\infty}^{\infty}u_r\partial_r u_r\diff t\,.
+\end{align}
+Observe, our version of equation 34 will be different by factors of $r$ since he had to undo the spherical gradient while we have to undo only the polar gradient. I will go through this tomorrow.
 \end{document}

### 2016-06-29 Macro Impacts.tex
This had better work
OR ELSE

--- 2016-06-12 Macro Impacts.tex
@@
 % Title
-\title{Macro Impacts}
+\title{Homework}
 \author{David Cyncynates \\ dcc57@case.edu}
@@
 \maketitle
-The linearized elastic wave equations are (Hemmann)
+In the following, lower case denotes a quantity in position space while capital letters denote their components in Fourier space.
+\\\\
+Denote the displacement field $u(\vec x,t)=\nabla\phi(\vec x,t)+\nabla\times a(\vec x,t)$\,. The linearized (acoustic) wave equation for $\phi$ is then
 \begin{align}
-0&=(\lambda+2\mu)\nabla^2\phi-\rho\ddot\phi+f\,,\\
-0&=\mu\nabla(\nabla\cdot A)-\mu\nabla\times(\nabla\times A)-\rho\ddot A+G\,,
+\alpha^2\nabla^2\phi&=\partial_t^2\phi\,,
 \end{align}
-where $u=\nabla\phi+\nabla\times A$ is the displacement and $F=\nabla f+\nabla\times G$ is the body force.
-Hence, we see to first order that shear waves and compressional waves decouple in the linear regime.
-If we assume that displacements due to the impact are very small (as we would expect for a very dense macro impact), then we may assume hydrostatic equilibrium, in which case the stress tensor takes the form
+where $\alpha^2=\f{\lambda+2\mu}{\rho}$. We may write
 \begin{align}
--p\delta_{ij}&=\tau_{ij}=\lambda g_{ij} u^s_{,s}+\mu(u_{i,j}+u_{j,i})\,.
+\phi(\vec x,t)=\int\f{\diff^3 k}{(2\pi)^3}\Phi(\vec k,\omega)e^{\I(\vec k\cdot\vec x-\omega t)}\,,
 \end{align}
-Note, the commas denote covariant differentiation.
-We now transform into cylindrical coordinates.
-In the case that we are interested in, the only important component is the radial one, for which we have
+from which we obtain the dispersion relation $\alpha k=\omega$, and hence the solution
 \begin{align}
--p&=\tau_{rr}\,,\\
-&=\lambda u^s_{,s}+2\mu u_{r,r}\,,\\
-&=\lambda \nabla_{s}g^{ss}u_s+2\mu u_{r,r}\,.
+\phi(\vec x,t)=\int\f{\diff^3 k}{(2\pi)^3}\Phi(\vec k,\omega)e^{\I(\vec k\cdot\vec x-\alpha k t)}\,.
 \end{align}
-The metric of cylindrical coordinates is
+We now impose the constraint equation
 \begin{align}
-\diff s^2&=\diff r^2+r^2\diff\theta^2+\diff z^2\,,
+\sigma_{ij}&=\delta_{ij}\lambda\nabla\cdot u+\mu(u_{i,j}+u_{j,i})
 \end{align}
-leading to the Christoffel symbols
+which, for the scalar modes becomes
 \begin{align}
-\Gamma^r_{\theta\theta}&=-r\,,\\
-\Gamma^r_{r\theta}&=\f1r\,.
+\sigma_{ij}&=\delta_{ij}\lambda\nabla^2\phi+2\mu\partial_i\partial_j\phi
 \end{align}
-Thus, assuming only the radial component has non-zero derivatives (which will be the case for a cylindrically symmetric source),
+and whose trace is
 \begin{align}
-\nabla u&=\partial_r u_r+\f1r u_r\,,\\
-&=\f1r\partial_r(ru_r)\,.
+-p=K\nabla^2\phi\,,
 \end{align}
-Hence
+where $K=\lambda+\f23\mu$ is the bulk modulus and $p=-\f13\tr\sigma_{ij}$. We take this constraint as an initial condition at $t=0$. In Fourier space
 \begin{align}
--p&=\tau_{rr}=\lambda\f1r\partial_r(ru_r)+2\mu\partial_r u_r\,,\\
-&=\lambda\f1r\partial_r(ru_r)+2\mu\f1r(\partial_r ru_r)-2\mu\f1r(u_r)\,,\\
-&=(\lambda+2\mu)\f1r\partial_r(ru_r)-2\mu\f1ru_r\,,\\
-&=(\lambda+2\mu)\f1r\partial_r(r\partial_r\phi)-2\mu\f1r\partial_r\phi
+P(\vec k)=Kk^2\Phi(\vec K)\,,
 \end{align}
-With $f=0$, this and the scalar equation of motion yield
+from which we obtain the displacement field components
 \begin{align}
-0&=(\lambda+2\mu)\nabla^2\phi-\rho\ddot\phi\,,\\
-&=(\lambda+2\mu)\p{\f1r\partial_r\p{r\partial_r\phi}}-\rho\ddot\phi\,,\\
-&=-p+2\mu\f1r\partial_r\phi-\rho\ddot\phi\,,
+U(\vec k)&=\I\f{P(\vec k)}{K}\f{\vec k}{k^2}\,,
 \end{align}
-Thus, observe that all the solutions from Hemmann apply with small modification (compare 19 with his equation 9).
-Assuming only outgoing modes are generated, we may write $\phi=F(t-r/\alpha)$ where $\alpha=\sqrt{(\lambda+2\mu)/\rho}$ is the compressional wave velocity.
-We can, for the sake of reusing Hemmann's work, assume that the cavity produced by the macro existed prior to the generation of compressional modes.
-This is actually somewhat convenient, since it is the production of the cavity that generates shear modes.
-Denote differentiation with respect to the retarded time $t'=t-\f r\alpha$ by a prime.
-I can't figure out how to get the following from equation 11 in Hemmann, but the evolution equation is
+and hence
 \begin{align}
--r^3\alpha p&=\alpha\rho r^2 F''+2\mu r F'+2\mu\alpha F\,.
+u(\vec x,t)=\int\f{\diff^3 k}{(2\pi)^3}\I\f{P(\vec k)}{K}\f{\vec k}{k^2}e^{\I(\vec k\cdot\vec x-\alpha k t)}\,,
 \end{align}
-After some guessing and checking, it seems that one can arrive at this equation by the substitution $\phi=\f1rF(t-r/\alpha)$.
-Either way, this simply confirms that we can use Hemmann directly with only slight modification.
+The equation for the energy of the compressional modes is
+\begin{align}
+E&=\f12\int_V\diff^3x\p{\rho\abs{\partial_t u}^2+(\lambda+2\mu)\abs{\nabla\cdot u}^2}\,,\\
+&=\f{\lambda+2\mu}{K^2}\int\f{\diff^3 k}{(2\pi)^3}\abs{P(\vec k)}^2
+\end{align}
+In the case that $P$ depends only on the frequency
+\begin{align}
+E&=4\pi\f{\lambda+2\mu}{K^2}\int\f{\diff\tilde\lambda}{\tilde\lambda^4}\abs{P(\tilde\lambda)}^2\,.
+\end{align}
+Now consider the case of a step function type pressure source - a cylinder of height $h$ and radius $r_X$
+\begin{align}
+p(\vec x,0)&=p_0\theta(r_X-r)\ps{\theta(z+h/2)-\theta(z-h/2)}\,,
+\end{align}
+whose Fourier components are
+\begin{align}
+P(\vec k)&=\f{4\pi r_X p_0}{\sqrt{k_x^2+k_y^2}k_z}J_1\p{\sqrt{k_x^2+k_y^2}r_X}\sin\p{\f{h}{2}k_z}\,,
+\end{align}
+which, in polar $k$-space is
+\begin{align}
+P(k,\varphi,\theta)&=\f{4\pi r_X p_0}{k^2\sin\theta\cos\theta}J_1\p{r_Xk\sin\theta}\sin\p{\f{h}{2}k\cos\theta}\,,
+\end{align}
+Directly integrating in Mathematica (over $\theta$ first) yields
+\begin{align}
+E_{\te{total}}&=\f{\lambda+2\mu}{K^2}4\pi^2p_0^2\sigma_Xh
+\end{align}
+where $\sigma_X=\pi r_X^2$. To calculate the energy deposition into the low frequency spectrum, we integrate $k$ from $0$ to $k_0$. Observe, we can make the following approximation
+\begin{align}
+P(\vec k)&\approx_{k\ll r_X}\f{2\pi r_Xp_0}{k^2\cos\theta\sin\theta}r_X k\sin\theta\sin\p{\f{h}{2}k\cos\theta}\,,\\
+&=\f{2\pi r_X^2 p_0}{k\cos\theta}\sin\p{\f{h}{2}k\cos\theta}\,.
+\end{align}
+From this we obtain the portion of the energy relegated to the long wavelength spectrum
+\begin{align}
+E_{\te{propagated}}&=\f{\lambda+2\mu}{K^2}\int\f{\diff^3 k}{(2\pi)^3}\abs{\f{2\pi r_X^2 p_0}{k\cos\theta}\sin\p{\f{h}{2}k\cos\theta}}^2\,,\\
+&=\ps{\f{1}{2h}(r_X^2p_0)^2\f{\lambda+2\mu}{K^2}}\ps{hk_0\cos(hk_0)+\sin(hk_0)+hk_0\p{-2+hk_0\te{Si}(hk_0)}}\,,\\
+&=\ps{(r_X^2p_0)^2\f{\lambda+2\mu}{K^2}}\ps{\f{\pi}{\lambda_0}\cos\p{\f{2\pi h}{\lambda_0}}+\sin\p{\f{2\pi h}{\lambda_0}}+\p{\f{\pi}{\lambda_0}}\p{-2+\p{\f{2\pi h}{\lambda_0}}\te{Si}\p{\f{2\pi h}{\lambda_0}}}}\,,\\
+&\approx_{h\gg\lambda_0\gg1}\ps{(r_X^2p_0)^2\f{\lambda+2\mu}{K^2}}\ps{\f{\pi^3 h}{\lambda_0^2}}\,,\\
+&=\ps{(\sigma_Xp_0)^2\f{\lambda+2\mu}{K^2}}\ps{\f{\pi h}{\lambda_0^2}}\,.
+\end{align}
+From this we obtain the fractional energy deposition into the unattenuated wavelengths
+\begin{align}
+\Xi&=\f{\sigma_X}{4\pi\lambda_0^2}\,.
+\end{align}
+This approximation holds for $\lambda_0^2\gg\sigma_X$, which is appropriate for the case that $\lambda_0$ is on the order of kilometers and $\sigma_X$ is on the order of centimeters squared.
 \end{document}

### 2016-06-29 Macro Impacts.tex
More Stuff
Butts
Vector modes
some more to come

@@
 \usepackage{fullpage}
-\usepackage{amsmath, amsthm, amsfonts, amssymb, mathtools, calrsfs, tensor, physics, MnSymbol,tikz-cd}
+\usepackage{amsmath, amsthm, amsfonts, amssymb, mathtools, calrsfs, tensor, physics,tikz-cd}
 \usepackage[mathscr]{euscript}
@@
 \maketitle
+\section{Scalar Modes}
 In the following, lower case denotes a quantity in position space while capital letters denote their components in Fourier space.
@@
 This approximation holds for $\lambda_0^2\gg\sigma_X$, which is appropriate for the case that $\lambda_0$ is on the order of kilometers and $\sigma_X$ is on the order of centimeters squared.
+\pagebreak
+\section{Vector Modes}
+The following is the equation of motion for the vector potential $a$ without body force:
+\begin{align}
+\mu\nabla^2a-\rho\ddot a=\mu\nabla(\nabla\cdot a)-\mu\nabla\times(\nabla\times a)-\rho\ddot a=0\,,
+\end{align}
+where the leftmost term is the vector laplacian. This gives us three wave equations for the three components of $a$. The constraint equation takes the form
+\begin{align}
+\sigma_{ij}&=\lambda\delta_{ij}\nabla\cdot \nabla\times a+\mu(\partial_j (\nabla\times a)_i+\partial_i (\nabla\times a)_j)\,,\\
+&=\mu(\partial_j (\nabla\times a)_i+\partial_i (\nabla\times a)_j)\,,\\
+&=\mu\mat{ccc}{2\partial_x(\partial_ya_z-\partial_za_y)&(\partial_y^2-\partial_x^2)a_z+\partial_z(\partial_x a_x-\partial_y a_y)&(\partial_x^2-\partial_z^2)a_y+\partial_y(\partial_z a_z-\partial_x a_x)\\
+&2\partial_y(\partial_z a_x-\partial_x a_z)&(\partial_z^2-\partial_y^2)a_x+\partial_x(\partial_ya_y-\partial_za_z)\\
+&&2\partial_z(\partial_xa_y-\partial_ya_x)}\,.
+\end{align}
 \end{document}

### 2016-06-29 Macro Impacts.tex
Everything relevant is up

@@
 \end{align}
+We now write $a_i$ in terms of its Fourier components
+\begin{align}
+a_i(\vec x,t)&=\int\f{\diff^3k}{(2\pi)^3}A_i(\vec k,\omega)e^{\I(\vec k\cdot\vec x-\omega t)}\,.
+\end{align}
+Observe the dispersion relation $\beta k=\omega$, which holds for each component $a_i$, and that $\beta=\f\mu\rho$. Thus, the solutions to the wave equation are
+\begin{align}
+a_i(\vec x,t)&=\int\f{\diff^3k}{(2\pi)^3}A_i(\vec k,\omega)e^{\I(\vec k\cdot\vec x-\beta k t)}\,.
+\end{align}
+We now use the constraint equation to write down the initial vector potential in terms of the initial stress.
+Note, we will obtain three equations constraining the possible initial stresses (i.e., we will be able to eliminate three components of $\sigma$ from the equations), and three equations writing $A_i$ in terms of $\Sigma_{ij}$.
 \end{document}

### 2016-06-30 Macro Impacts.tex
Added some incorrect work.
Some new stuff. Almost there...
Got it. Neat stuff happens

@@
 Note, we will obtain three equations constraining the possible initial stresses (i.e., we will be able to eliminate three components of $\sigma$ from the equations), and three equations writing $A_i$ in terms of $\Sigma_{ij}$.
+\\\\
+In Fourier space we have
+\begin{align}
+-\Sigma_{xx}&=2k_x(k_y A_z-k_z A_y)\,,\\
+-\Sigma_{yy}&=2k_y(k_z A_x-k_x A_z)\,,\\
+-\Sigma_{zz}&=2k_z(k_x A_y-k_y A_x)\,,\\
+-\Sigma_{xy}&=(k_y^2-k_x^2) A_z+k_z(k_x A_x-k_y A_y)\,,\\
+-\Sigma_{yz}&=(k_z^2-k_y^2) A_x+k_x(k_y A_y-k_z A_z)\,,\\
+-\Sigma_{zx}&=(k_x^2-k_z^2) A_y+k_y(k_z A_z-k_x A_x)\,.
+\end{align}
+First observe that any three of these equations together forms a singular linear system.
+\\\\
+Taking the sum of 31-33 yields
+\begin{align}
+0&=\Sigma_{xx}+\Sigma_{yy}+\Sigma_{zz}\,.
+\end{align}
+Observe that
+\begin{align}
+\f{-\Sigma_{xx}k_y}{2k_xk_z}&=\f{k_y^2}{k_z}A_z-k_yA_y\,,\\
+\f{-\Sigma_{yy}k_x}{2k_yk_z}&=k_xA_x-\f{k_x^2}{k_z}A_z\,,\\
+\f{-\Sigma_{xy}}{k_z}&=\ps{\f{k_y^2-k_z^2}{k_z}}A_z+k_xA_x-k_yA_y\,.
+\end{align}
+Taking the sum of the first two reveals that
+\begin{align}
+2k_xk_y\Sigma_{xy}&=k_y^2\Sigma_{xx}+k_x^2\Sigma_{yy}\,.
+\end{align}
+If you want to be silly, we find
+\begin{align}
+0&=(\Sigma_xk_y-\Sigma_yk_x)^2\,.
+\end{align}
+Anyway, we then have the system of three equations
+\begin{align}
+2k_xk_y\Sigma_{xy}&=k_y^2\Sigma_{xx}+k_x^2\Sigma_{yy}\,,\\
+2k_yk_z\Sigma_{yz}&=k_z^2\Sigma_{yy}+k_y^2\Sigma_{zz}\,,\\
+2k_zk_x\Sigma_{zx}&=k_x^2\Sigma_{zz}+k_z^2\Sigma_{xx}\,.
+\end{align}
+which are non-singular. They yield
+\begin{align}
+\Sigma_{xx}&=\f{k_x}{k_yk_z}\p{k_z\Sigma_{xy}-k_x\Sigma_{yz}+k_y\Sigma_{zx}}\,,\\
+\Sigma_{yy}&=\f{k_y}{k_zk_x}\p{k_z\Sigma_{xy}+k_x\Sigma_{yz}-k_y\Sigma_{zx}}\,,\\
+\Sigma_{zz}&=\f{k_z}{k_xk_y}\p{-k_z\Sigma_{xy}+k_x\Sigma_{yz}+k_y\Sigma_{zx}}\,.
+\end{align}
+This reveals two facts. The first fact is that the only relevant equations are 34-36. The second is that 37 implies that
+\begin{align}
+0&=k^2\ps{\f{\Sigma_{yz}}{k_yk_z}+\f{\Sigma_{zx}}{k_zk_x}+\f{\Sigma_{xy}}{k_xk_y}}\,.
+\end{align}
 \end{document}

### 2016-06-30 Macro Impacts.tex
small update

@@
 \begin{align}
-0&=k^2\ps{\f{\Sigma_{yz}}{k_yk_z}+\f{\Sigma_{zx}}{k_zk_x}+\f{\Sigma_{xy}}{k_xk_y}}\,.
+0&=k^2\ps{\f{\Sigma_{yz}}{k_yk_z}+\f{\Sigma_{zx}}{k_zk_x}+\f{\Sigma_{xy}}{k_xk_y}}\,,
 \end{align}
+i.e.
+\begin{align}
+0&=k_x\Sigma_{yz}+k_y\Sigma_{zx}+k_z\Sigma_{xy}\,.
+\end{align}
+That is to say $(\Sigma_{yz},\Sigma_{zx},\Sigma_{xy})$ is transverse.
+Because the only three relevant components are those of this vector, denote $\Sigma=(\Sigma_{yz},\Sigma_{zx},\Sigma_{xy}):=(\Sigma_x,\Sigma_y,\Sigma_z)$.
 \end{document}

### 2016-06-30 Macro Impacts.tex
We need to solve for A_i in terms of Sigma_i
This shouldn’t be hard. It’ll just take some playing around with the
equations.
For shocks, check the laser physics book
Corrected Things

--- 2016-06-30 Macro Impacts.tex
@@
 \end{align}
-which are non-singular. They yield
+which is non-singular. They yield
 \begin{align}
@@
 \end{align}
-This reveals two facts. The first fact is that the only relevant equations are 34-36. The second is that 37 implies that
-\begin{align}
-0&=k^2\ps{\f{\Sigma_{yz}}{k_yk_z}+\f{\Sigma_{zx}}{k_zk_x}+\f{\Sigma_{xy}}{k_xk_y}}\,.
-\end{align}
+This, along with being traceless, shows that the shear only has two independent degrees of freedom: the polarizations. In other words, we have shown that you can always diagonalize the stress tensor.
+\\\\
+We now solve for $A_i$ in terms of $\Sigma_i$.
+\\\\
+We still have a gauge degree of freedom...
+\\\\
+For shocks, check the laser physics book.
 \end{document}

### 2016-07-02 Macro Impacts.tex
Gauge invariance -- yay!
Just clarified one thing
Nevermind...
Imposed divergenceless gauge - obtained A_i
The important technique I used was to maintain proper symmetry of my
substitutions.

@@
 \end{align}
-First observe that any three of these equations together forms a singular linear system.
+First observe that any three of these equations together forms a singular linear system in $A_i$. Thus we cannot invert to solve for $A_i$. However, we can get some information about the $\Sigma$'s.
 \\\\
@@
 \end{align}
-Taking the sum of the first two reveals that
+Taking the sum of the first two reveals that`
 \begin{align}
@@
 \end{align}
-This, along with being traceless, shows that the shear only has two independent degrees of freedom: the polarizations. In other words, we have shown that you can always diagonalize the stress tensor.
+This, along with being traceless, shows that the shear only has two independent degrees of freedom: the polarizations.
 \\\\
-We now solve for $A_i$ in terms of $\Sigma_i$.
-\\\\
-We still have a gauge degree of freedom...
+It is impossible to solve for $A_i$ in terms of the stress as is, hence we must fix a gauge. To do this, we fix $\nabla\cdot a=0$, whence
+\begin{align}
+0=k_xA_x+k_yA_y+k_zA_z\,.
+\end{align}
+From earlier, we have
+\begin{align}
+-\Sigma_{yy}&=2k_y(k_z A_x-k_x A_z)\,,\\
+-\Sigma_{zz}&=2k_z(k_x A_y-k_y A_x)\,,
+\end{align}
+which becomes
+\begin{align}
+-\Sigma_{yy}&=2k_y\ps{-\f{k_z}{k_x} \p{k_yA_y+k_zA_z}-k_x A_z}\,,\\
+-\Sigma_{zz}&=2k_z\ps{k_x A_y+\f{k_y}{k_x} \p{k_yA_y+k_zA_z}}\,,
+\end{align}
+which simplifies to
+\begin{align}
+-\Sigma_{yy}&=-\f{2k_y}{k_x}\ps{k_y k_z A_y+\p{k_z^2+k_x^2} A_z}\,,\\
+-\Sigma_{zz}&=\f{2k_z}{k_x}\ps{\p{k_x^2 + k_y^2}A_y+k_yk_zA_z}\,,
+\end{align}
+Hence
+\begin{align}
+A_x&=\f{(k_y^2-k_z^2)(\Sigma_{yy}-\Sigma_{zz})+k_x^2(\Sigma_{yy}+\Sigma_{zz})}{2k_x^2k^2}\,,\\
+&=\f{(k_y^2-k_z^2)(\Sigma_{yy}-\Sigma_{zz})-k_x^2\Sigma_{xx}}{2k_x^2k^2}\,,\\
+&=\f{(k_y^2-k_z^2)}{k_x^2}\f{(\Sigma_{yy}-\Sigma_{zz})}{2k^2}-\f{\Sigma_{xx}}{2k^2}\,,\\
+\end{align}
+By symmetry, we have
+\begin{align}
+A_x&=\f{(k_y^2-k_z^2)}{k_x^2}\f{(\Sigma_{yy}-\Sigma_{zz})}{2k^2}-\f{\Sigma_{xx}}{2k^2}\,,\\
+A_y&=\f{(k_z^2-k_x^2)}{k_y^2}\f{(\Sigma_{zz}-\Sigma_{xx})}{2k^2}-\f{\Sigma_{yy}}{2k^2}\,,\\
+A_z&=\f{(k_x^2-k_y^2)}{k_z^2}\f{(\Sigma_{xx}-\Sigma_{yy})}{2k^2}-\f{\Sigma_{zz}}{2k^2}\,.
+\end{align}
+Observe, in the case that all stresses are equal, we obtain that $A_x=A_y=A_z=0$, as we should.
 \\\\

### 2016-07-02 Macro Impacts.tex
Trying this again
Displacements

@@
 \begin{align}
-0&=(\Sigma_xk_y-\Sigma_yk_x)^2\,.
+0&=(\Sigma_{x}k_y-\Sigma_{y}k_x)^2\,.
 \end{align}
@@
 Observe, in the case that all stresses are equal, we obtain that $A_x=A_y=A_z=0$, as we should.
+We now solve for $A_i$ in terms of $\Sigma_{i}$.
+\\\\
+Now we take the curl of $A$ to find the shear mode displacement
+\begin{align}
+U_x&=ky A_z-kz A_y\,,\\
+&=\f{1}{2k^2k_y^2k_z^2}\ps{-k_z^3\p{-k_y^2\Sigma_{yy}+(k_x^2-k_z^2)(\Sigma_{xx}-\Sigma_{zz})}+k_y^3\p{(k_x^2-k_y^2)(\Sigma_{xx}-\Sigma_{yy})-k_z^2\Sigma_{zz}}}
+\end{align}
+Just cyclically permute the indices to obtain the expressions for $U_y$ and $U_z$.
 \\\\

### 2016-07-02 Macro Impacts.tex
Stuff

@@
 For shocks, check the laser physics book.
+
+\pagebreak
+\section{Comparison to ``Passage of Small BH...''}
+Their considerations in the acoustic limit account for a body force generated by the gravitational pull of the miniature black hole.
+They discover that only supersonic blackholes would generate this type of radiation.
+Our calculations, on the other hand, seem independent of these considerations.
+In our case, the gravitational pull of something as dense as a Macro is not negligible, but should not generate as significant an effect this way.
+The principal mechanism for energy deposition is the scattering of matter off the macro.
+However, their methods do bring into question whether the free wave equation is appropriate.
+They also consider the transfer of energy due to pressure from the black hole to matter along its path.
+This is a different calculation from ours since black hole radiation is very weak, as opposed to collisions between baryonic matter.
+\\\\
+However, one key point is that they do neglect shear by using a scalar displacement potential $\psi$ below their equation (3).
+Moreover, they neglect the subtlety of the behavior of the collision near the boundary of the Earth.
+
+\pagebreak
+\section{Our Argument}
+As a Macro passes through the earth, there are several phases to its journey.
+The first is its passage through the atmosphere.
+The second is its crossing the boundary from air to earth, which we suspect will be relatively uneventful, since the air is 1000$\times$ lower density than earth, and thus would displace relatively little of it.
+The third is the transit of the macro through the earth.
+The shockwave it produces should be generated primarily by elastic and inelastic scattering of baryonic matter off the Macro.
+If we estimate that the macro produces an initial overpressure in a tube of its own radius, we can calculate the initial overpressure from the total energy deposition and its cross section.
+Given that the macro is dense enough, its loss of momentum will be approximately linear, and we can approximate its energy loss as being approximately constant.
+Estimates have already been made of the stopping power, so the total energy deposition will just be the
+\begin{align}
+\abs{\td{E}{x}{}}h=E_{\te{total}}=\f{\lambda+2\mu}{K^2}4\pi^2p_0^2\sigma_Xh
+\end{align}
+whence the initial overpressure is
+\begin{align}
+p_0=\f{K}{2\pi}\sqrt{\abs{\td{E}{x}{}}\f{1}{\sigma_X(\lambda+2\mu)}}
+\end{align}
+It is not appropriate to use the linear regime until the overpressure is close to 0 compared to some pressure, which we suspect may be $p_{\te{non-linear}}\approx60\te{GPa}$.
+It is reasonable to assume that the elastic limit holds when the pressures are an order of magnitude smaller than $p_{\te{non-linear}}$, denoted $p_{\te{linear}}\approx6\te{GPa}$.
+(This stuff needs to be checked).
+Note that energy losses due to heating, i.e.
+anelastic frequency attenuation, will dilute the energy density of the shock.
+However, for a conservative  estimate, we only consider the geometric attenuation, which will dilute the energy density as $r^{-1}$, where $r$ is the radial distance from the Macro's trajectory to the shock front.
+The shape of the shockwave will rapidly achieve a right-triangular profile.
+Geometric considerations show that the overpressure will go as $r^{-1}$.
+Thus, suppose that the average pressure in the shock is $\bar p$.
+Then the average pressure at radius $r$ is given
+\begin{align}
+\bar p(r)=p_0\f{r_0+l}{r}\,.
+\end{align}
+The overpressure is then given by
+\begin{align}
+p=\bar p_{\te{linear}}\f{r-r_0}{\ell}\ps{\theta(r_0+\ell-r)-\theta(r+\ell)}\ps{\theta(z+h/2)-\theta(z-h/2)}
+\end{align}
+where $\ell$ is the radial length of the shock and $r_0$ is its base. We now calculate the total energy contained in this shock. Fourier transforming reveals
+\begin{align}
+\notag P&=\f{\bar p_{\te{linear}}}{k_r^2k_z\ell}\pi\sin\p{\f{h}{2}k_z}\ps{(\ell+r_0)(2\sqrt{2} k_r\ell-\pi H_0(\sqrt{2} k_r(\ell+r_0))J_1(\sqrt{2}k_r(\ell+r_0))\right.\\&\left.+\pi(\ell+r_0)H_1(\sqrt{2}k_r(\ell+r_0))J_0(\sqrt{2}k_r(\ell+r_0))+\pi r_0 H_0(\sqrt{2}k_r r_0)J_1(\sqrt{2}k_r r_0)-\pi r_0 H_1(\sqrt{2} k_r r_0)J_0(\sqrt{2}k_r r_0)}
+\end{align}
+This reduces to, for the limit that $r_0\ll\lambda_{\te{attenuation}}$ 
+\pagebreak
+\section{What we still need to do}
+What we've calculated is the the pressure from the total energy deposition.
+We need to figure out the total energy, pressure, and shape of the shock after it becomes sufficiently acoustic.
+It would also be good to know the velocity of the shock.
+From this, we can calculate the energy deposited in the measurable range.
+\\\\
+It appears as though *nobody* considers the shear waves... Should we?
+\\\\
+The gravitational effects can be taken into account as in the Black Hole paper.
 \end{document}

### 2016-07-03 Macro Impacts.tex
Did some stuff. Estimates and whatnot.

@@
 \begin{align}
--\Sigma_{xx}&=2k_x(k_y A_z-k_z A_y)\,,\\
--\Sigma_{yy}&=2k_y(k_z A_x-k_x A_z)\,,\\
--\Sigma_{zz}&=2k_z(k_x A_y-k_y A_x)\,,\\
--\Sigma_{xy}&=(k_y^2-k_x^2) A_z+k_z(k_x A_x-k_y A_y)\,,\\
--\Sigma_{yz}&=(k_z^2-k_y^2) A_x+k_x(k_y A_y-k_z A_z)\,,\\
--\Sigma_{zx}&=(k_x^2-k_z^2) A_y+k_y(k_z A_z-k_x A_x)\,.
+-\Sigma_{xx}&=\mu2k_x(k_y A_z-k_z A_y)\,,\\
+-\Sigma_{yy}&=\mu2k_y(k_z A_x-k_x A_z)\,,\\
+-\Sigma_{zz}&=\mu2k_z(k_x A_y-k_y A_x)\,,\\
+-\Sigma_{xy}&=\mu\ps{(k_y^2-k_x^2) A_z+k_z(k_x A_x-k_y A_y)}\,,\\
+-\Sigma_{yz}&=\mu\ps{(k_z^2-k_y^2) A_x+k_x(k_y A_y-k_z A_z)}\,,\\
+-\Sigma_{zx}&=\mu\ps{(k_x^2-k_z^2) A_y+k_y(k_z A_z-k_x A_x)}\,.
 \end{align}
@@
 \begin{align}
-\f{-\Sigma_{xx}k_y}{2k_xk_z}&=\f{k_y^2}{k_z}A_z-k_yA_y\,,\\
-\f{-\Sigma_{yy}k_x}{2k_yk_z}&=k_xA_x-\f{k_x^2}{k_z}A_z\,,\\
-\f{-\Sigma_{xy}}{k_z}&=\ps{\f{k_y^2-k_z^2}{k_z}}A_z+k_xA_x-k_yA_y\,.
+\f{-\Sigma_{xx}k_y}{2\mu k_xk_z}&=\f{k_y^2}{k_z}A_z-k_yA_y\,,\\
+\f{-\Sigma_{yy}k_x}{2\mu k_yk_z}&=k_xA_x-\f{k_x^2}{k_z}A_z\,,\\
+\f{-\Sigma_{xy}}{\mu k_z}&=\ps{\f{k_y^2-k_z^2}{k_z}}A_z+k_xA_x-k_yA_y\,.
 \end{align}
@@
 \begin{align}
--\Sigma_{yy}&=2k_y(k_z A_x-k_x A_z)\,,\\
--\Sigma_{zz}&=2k_z(k_x A_y-k_y A_x)\,,
+-\Sigma_{yy}&=2\mu k_y(k_z A_x-k_x A_z)\,,\\
+-\Sigma_{zz}&=2\mu k_z(k_x A_y-k_y A_x)\,,
 \end{align}
@@
 \begin{align}
--\Sigma_{yy}&=2k_y\ps{-\f{k_z}{k_x} \p{k_yA_y+k_zA_z}-k_x A_z}\,,\\
--\Sigma_{zz}&=2k_z\ps{k_x A_y+\f{k_y}{k_x} \p{k_yA_y+k_zA_z}}\,,
+-\Sigma_{yy}&=2\mu k_y\ps{-\f{k_z}{k_x} \p{k_yA_y+k_zA_z}-k_x A_z}\,,\\
+-\Sigma_{zz}&=2\mu k_z\ps{k_x A_y+\f{k_y}{k_x} \p{k_yA_y+k_zA_z}}\,,
 \end{align}
@@
 \begin{align}
--\Sigma_{yy}&=-\f{2k_y}{k_x}\ps{k_y k_z A_y+\p{k_z^2+k_x^2} A_z}\,,\\
--\Sigma_{zz}&=\f{2k_z}{k_x}\ps{\p{k_x^2 + k_y^2}A_y+k_yk_zA_z}\,,
+-\Sigma_{yy}&=-\f{2\mu k_y}{k_x}\ps{k_y k_z A_y+\p{k_z^2+k_x^2} A_z}\,,\\
+-\Sigma_{zz}&=\f{2\mu k_z}{k_x}\ps{\p{k_x^2 + k_y^2}A_y+k_yk_zA_z}\,,
 \end{align}
@@
 \begin{align}
-A_x&=\f{(k_y^2-k_z^2)(\Sigma_{yy}-\Sigma_{zz})+k_x^2(\Sigma_{yy}+\Sigma_{zz})}{2k_x^2k^2}\,,\\
-&=\f{(k_y^2-k_z^2)(\Sigma_{yy}-\Sigma_{zz})-k_x^2\Sigma_{xx}}{2k_x^2k^2}\,,\\
-&=\f{(k_y^2-k_z^2)}{k_x^2}\f{(\Sigma_{yy}-\Sigma_{zz})}{2k^2}-\f{\Sigma_{xx}}{2k^2}\,,\\
+A_x&=\mu\f{(k_y^2-k_z^2)(\Sigma_{yy}-\Sigma_{zz})+k_x^2(\Sigma_{yy}+\Sigma_{zz})}{2k_x^2k^2}\,,\\
+&=\mu\f{(k_y^2-k_z^2)(\Sigma_{yy}-\Sigma_{zz})-k_x^2\Sigma_{xx}}{2k_x^2k^2}\,,\\
+&=\mu\f{(k_y^2-k_z^2)}{k_x^2}\f{(\Sigma_{yy}-\Sigma_{zz})}{2k^2}-\mu\f{\Sigma_{xx}}{2k^2}\,,\\
 \end{align}
@@
 \begin{align}
-A_x&=\f{(k_y^2-k_z^2)}{k_x^2}\f{(\Sigma_{yy}-\Sigma_{zz})}{2k^2}-\f{\Sigma_{xx}}{2k^2}\,,\\
-A_y&=\f{(k_z^2-k_x^2)}{k_y^2}\f{(\Sigma_{zz}-\Sigma_{xx})}{2k^2}-\f{\Sigma_{yy}}{2k^2}\,,\\
-A_z&=\f{(k_x^2-k_y^2)}{k_z^2}\f{(\Sigma_{xx}-\Sigma_{yy})}{2k^2}-\f{\Sigma_{zz}}{2k^2}\,.
+A_x&=\mu\f{(k_y^2-k_z^2)}{k_x^2}\f{(\Sigma_{yy}-\Sigma_{zz})}{2k^2}-\mu\f{\Sigma_{xx}}{2k^2}\,,\\
+A_y&=\mu\f{(k_z^2-k_x^2)}{k_y^2}\f{(\Sigma_{zz}-\Sigma_{xx})}{2k^2}-\mu\f{\Sigma_{yy}}{2k^2}\,,\\
+A_z&=\mu\f{(k_x^2-k_y^2)}{k_z^2}\f{(\Sigma_{xx}-\Sigma_{yy})}{2k^2}-\mu\f{\Sigma_{zz}}{2k^2}\,.
 \end{align}
@@
 \begin{align}
-U_x&=ky A_z-kz A_y\,,\\
-&=\f{1}{2k^2k_y^2k_z^2}\ps{-k_z^3\p{-k_y^2\Sigma_{yy}+(k_x^2-k_z^2)(\Sigma_{xx}-\Sigma_{zz})}+k_y^3\p{(k_x^2-k_y^2)(\Sigma_{xx}-\Sigma_{yy})-k_z^2\Sigma_{zz}}}
+U_x&=k_y A_z-k_z A_y\,,\\
+&=\f{\mu}{2k^2k_y^2k_z^2}\ps{-k_z^3\p{-k_y^2\Sigma_{yy}+(k_x^2-k_z^2)(\Sigma_{xx}-\Sigma_{zz})}+k_y^3\p{(k_x^2-k_y^2)(\Sigma_{xx}-\Sigma_{yy})-k_z^2\Sigma_{zz}}}\,,\\
+&=\f{\mu}{2k^2k_y^2k_z^2}\ps{k_z^2k_y^2(k_z\Sigma_{yy}-k_y\Sigma_{zz})-k_z^3(k_x^2-k_z^2)(\Sigma_{xx}-\Sigma_{zz})+k_y^3(k_x^2-k_y^2)(\Sigma_{xx}-\Sigma_{yy})}\,,\\
+&=\mu\ps{\f{1}{2k^2}(k_z\Sigma_{yy}-k_y\Sigma_{zz})-\f{k_z(k_x^2-k_z^2)}{2k^2k_y^2}(\Sigma_{xx}-\Sigma_{zz})+\f{k_y(k_x^2-k_y^2)}{2k^2k_z^2}(\Sigma_{xx}-\Sigma_{yy})}\,,\\
 \end{align}
 Just cyclically permute the indices to obtain the expressions for $U_y$ and $U_z$.
+\begin{align}
+\f{U_x}{\mu}&=\f{1}{2k^2}(k_z\Sigma_{yy}-k_y\Sigma_{zz})-\f{k_z(k_x^2-k_z^2)}{2k^2k_y^2}(\Sigma_{xx}-\Sigma_{zz})+\f{k_y(k_x^2-k_y^2)}{2k^2k_z^2}(\Sigma_{xx}-\Sigma_{yy})\,,\\
+\f{U_y}{\mu}&=\f{1}{2k^2}(k_x\Sigma_{zz}-k_z\Sigma_{xx})-\f{k_x(k_y^2-k_x^2)}{2k^2k_z^2}(\Sigma_{yy}-\Sigma_{xx})+\f{k_z(k_y^2-k_z^2)}{2k^2k_x^2}(\Sigma_{yy}-\Sigma_{zz})\,,\\
+\f{U_z}{\mu}&=\f{1}{2k^2}(k_y\Sigma_{xx}-k_x\Sigma_{yy})-\f{k_y(k_z^2-k_y^2)}{2k^2k_x^2}(\Sigma_{zz}-\Sigma_{yy})+\f{k_x(k_z^2-k_x^2)}{2k^2k_y^2}(\Sigma_{zz}-\Sigma_{xx})\,,\\
+\end{align}
+Assuming cylindrical symmetry, we have $\Sigma=\Sigma_{zz}=-2\Sigma_{xx}=-2\Sigma_{yy}$.
+\begin{align}
+U_x&=\ps{-(k_z+2k_y)k_x^2k_y^2+3k_zk_x^2(k_x^2-k_z^2)}\f{\mu}{4k^2k_x^2k_y^2}\Sigma\,,\\
+U_y&=\ps{(2k_x+k_z)k_x^2k_y^2-3k_zk_y^2(k_y^2-k_z^2)}\f{\mu}{4k^2k_x^2k_y^2}\Sigma\,,\\
+U_z&=\ps{(k_x-k_y)k_x^2k_y^2+3(k_x^3-k_y^3)k_z^2+3k_y^5-3k_x^5}\f{\mu}{4k^2k_x^2k_y^2}\Sigma\,.
+\end{align}
+The energy of these shear waves is given
+\begin{align}
+E&=\f12\int_V\p{\rho\abs{u_t}^2+\mu\abs{\nabla\cdot u}^2}\,,\\
+&=\rho\int_V\abs{u_t}^2\,,\\
+&=\mu\int_V\int\f{\diff^3 k}{(2\pi)^3}\int\f{\diff^3 k'}{(2\pi)^3}\p{k k'U(\vec k)\bar U(\vec k')}e^{-\I(\vec k\cdot\vec x-i\beta k t)}e^{\I(\vec k'\cdot\vec x-i\beta k' t)}\,,\\
+&=\mu\int\f{\diff^3 k}{(2\pi)^3}\p{k^2\abs{U(\vec k)}^2}\,,\\
+\end{align}
 \\\\
@@
 The first is its passage through the atmosphere.
-The second is its crossing the boundary from air to earth, which we suspect will be relatively uneventful, since the air is 1000$\times$ lower density than earth, and thus would displace relatively little of it.
+The second is its crossing the boundary from air to earth, which we suspect will be relatively uneventful, since the air is 1000$\times$ lower density than earth, and thus the air pressure would displace relatively little of earth.
 The third is the transit of the macro through the earth.
@@
 Given that the macro is dense enough, its loss of momentum will be approximately linear, and we can approximate its energy loss as being approximately constant.
-Estimates have already been made of the stopping power, so the total energy deposition will just be the
+Estimates have already been made of the stopping power, so the total energy deposition will just be
 \begin{align}
@@
 Geometric considerations show that the overpressure will go as $r^{-1}$.
-Thus, suppose that the average pressure in the shock is $\bar p$.
-Then the average pressure at radius $r$ is given
-\begin{align}
-\bar p(r)=p_0\f{r_0+l}{r}\,.
-\end{align}
+Thus, suppose that the peak pressure in the shock is $\bar p$.
 The overpressure is then given by
 \begin{align}
-p=\bar p_{\te{linear}}\f{r-r_0}{\ell}\ps{\theta(r_0+\ell-r)-\theta(r+\ell)}\ps{\theta(z+h/2)-\theta(z-h/2)}
+p=\bar p\f{r-r_0}{\Delta r}\ps{\theta(r_0+\ell-r)-\theta(r+\ell)}\ps{\theta(z+h/2)-\theta(z-h/2)}
 \end{align}
-where $\ell$ is the radial length of the shock and $r_0$ is its base. We now calculate the total energy contained in this shock. Fourier transforming reveals
+where $\Delta r$ is the radial length of the shock and $r_0$ is its base.
+In the limit where $h$ is much larger than all other fixed lengths, we have (after a large but easy mathematica calculation (triangle pressure.nb))
 \begin{align}
-\notag P&=\f{\bar p_{\te{linear}}}{k_r^2k_z\ell}\pi\sin\p{\f{h}{2}k_z}\ps{(\ell+r_0)(2\sqrt{2} k_r\ell-\pi H_0(\sqrt{2} k_r(\ell+r_0))J_1(\sqrt{2}k_r(\ell+r_0))\right.\\&\left.+\pi(\ell+r_0)H_1(\sqrt{2}k_r(\ell+r_0))J_0(\sqrt{2}k_r(\ell+r_0))+\pi r_0 H_0(\sqrt{2}k_r r_0)J_1(\sqrt{2}k_r r_0)-\pi r_0 H_1(\sqrt{2} k_r r_0)J_0(\sqrt{2}k_r r_0)}
+E_{\te{propagated}}&\approx \f{\lambda+2\mu}{K^2}\f{h \bar p^2\pi^2r_0^6}{8\Delta r^2\lambda_0^2}\,.
 \end{align}
-This reduces to, for the limit that $r_0\ll\lambda_{\te{attenuation}}$ 
+Setting this equal to the earlier $E_{\te{propagated}}$ yields
+\begin{align}
+\f{h \bar p^2\pi^2r_0^6}{8\Delta r^2\lambda_0^2}&=(\sigma_Xp_0)^2\f{\pi h}{\lambda_0^2}\,,\\
+\bar p&=\p{2\sqrt{2\pi}\f{r_X^2\Delta r}{r_0^3}}p_0\,.
+\end{align}
+We know that shock waves are rapidly attenuated in the earth.
+Therefore, the estimate of the energy propagated by the initial overpressure serves as an upper bound to the energy propagated during the non-linear phase.
+
 \pagebreak

### 2016-07-03 Macro Impacts.tex
Update: some stuff incomplete and wrong

@@
 \begin{align}
-A_x&=\mu\f{(k_y^2-k_z^2)(\Sigma_{yy}-\Sigma_{zz})+k_x^2(\Sigma_{yy}+\Sigma_{zz})}{2k_x^2k^2}\,,\\
-&=\mu\f{(k_y^2-k_z^2)(\Sigma_{yy}-\Sigma_{zz})-k_x^2\Sigma_{xx}}{2k_x^2k^2}\,,\\
-&=\mu\f{(k_y^2-k_z^2)}{k_x^2}\f{(\Sigma_{yy}-\Sigma_{zz})}{2k^2}-\mu\f{\Sigma_{xx}}{2k^2}\,,\\
+A_x&=\f1\mu\f{(k_y^2-k_z^2)(\Sigma_{yy}-\Sigma_{zz})+k_x^2(\Sigma_{yy}+\Sigma_{zz})}{2k_x^2k^2}\,,\\
+&=\f1\mu\f{(k_y^2-k_z^2)(\Sigma_{yy}-\Sigma_{zz})-k_x^2\Sigma_{xx}}{2k_x^2k^2}\,,\\
+&=\f1\mu\f{(k_y^2-k_z^2)}{k_x^2}\f{(\Sigma_{yy}-\Sigma_{zz})}{2k^2}-\f1\mu\f{\Sigma_{xx}}{2k^2}\,,\\
 \end{align}
@@
 \begin{align}
-A_x&=\mu\f{(k_y^2-k_z^2)}{k_x^2}\f{(\Sigma_{yy}-\Sigma_{zz})}{2k^2}-\mu\f{\Sigma_{xx}}{2k^2}\,,\\
-A_y&=\mu\f{(k_z^2-k_x^2)}{k_y^2}\f{(\Sigma_{zz}-\Sigma_{xx})}{2k^2}-\mu\f{\Sigma_{yy}}{2k^2}\,,\\
-A_z&=\mu\f{(k_x^2-k_y^2)}{k_z^2}\f{(\Sigma_{xx}-\Sigma_{yy})}{2k^2}-\mu\f{\Sigma_{zz}}{2k^2}\,.
+A_x&=\f1\mu\f{(k_y^2-k_z^2)}{k_x^2}\f{(\Sigma_{yy}-\Sigma_{zz})}{2k^2}-\f1\mu\f{\Sigma_{xx}}{2k^2}\,,\\
+A_y&=\f1\mu\f{(k_z^2-k_x^2)}{k_y^2}\f{(\Sigma_{zz}-\Sigma_{xx})}{2k^2}-\f1\mu\f{\Sigma_{yy}}{2k^2}\,,\\
+A_z&=\f1\mu\f{(k_x^2-k_y^2)}{k_z^2}\f{(\Sigma_{xx}-\Sigma_{yy})}{2k^2}-\f1\mu\f{\Sigma_{zz}}{2k^2}\,.
 \end{align}
@@
 U_x&=k_y A_z-k_z A_y\,,\\
-&=\f{\mu}{2k^2k_y^2k_z^2}\ps{-k_z^3\p{-k_y^2\Sigma_{yy}+(k_x^2-k_z^2)(\Sigma_{xx}-\Sigma_{zz})}+k_y^3\p{(k_x^2-k_y^2)(\Sigma_{xx}-\Sigma_{yy})-k_z^2\Sigma_{zz}}}\,,\\
-&=\f{\mu}{2k^2k_y^2k_z^2}\ps{k_z^2k_y^2(k_z\Sigma_{yy}-k_y\Sigma_{zz})-k_z^3(k_x^2-k_z^2)(\Sigma_{xx}-\Sigma_{zz})+k_y^3(k_x^2-k_y^2)(\Sigma_{xx}-\Sigma_{yy})}\,,\\
-&=\mu\ps{\f{1}{2k^2}(k_z\Sigma_{yy}-k_y\Sigma_{zz})-\f{k_z(k_x^2-k_z^2)}{2k^2k_y^2}(\Sigma_{xx}-\Sigma_{zz})+\f{k_y(k_x^2-k_y^2)}{2k^2k_z^2}(\Sigma_{xx}-\Sigma_{yy})}\,,\\
+&=\f1\mu\f{1}{2k^2k_y^2k_z^2}\ps{-k_z^3\p{-k_y^2\Sigma_{yy}+(k_x^2-k_z^2)(\Sigma_{xx}-\Sigma_{zz})}+k_y^3\p{(k_x^2-k_y^2)(\Sigma_{xx}-\Sigma_{yy})-k_z^2\Sigma_{zz}}}\,,\\
+&=\f1\mu\f{1}{2k^2k_y^2k_z^2}\ps{k_z^2k_y^2(k_z\Sigma_{yy}-k_y\Sigma_{zz})-k_z^3(k_x^2-k_z^2)(\Sigma_{xx}-\Sigma_{zz})+k_y^3(k_x^2-k_y^2)(\Sigma_{xx}-\Sigma_{yy})}\,,\\
+&=\f1\mu\ps{\f{1}{2k^2}(k_z\Sigma_{yy}-k_y\Sigma_{zz})-\f{k_z(k_x^2-k_z^2)}{2k^2k_y^2}(\Sigma_{xx}-\Sigma_{zz})+\f{k_y(k_x^2-k_y^2)}{2k^2k_z^2}(\Sigma_{xx}-\Sigma_{yy})}\,,\\
 \end{align}
@@
 \begin{align}
-\f{U_x}{\mu}&=\f{1}{2k^2}(k_z\Sigma_{yy}-k_y\Sigma_{zz})-\f{k_z(k_x^2-k_z^2)}{2k^2k_y^2}(\Sigma_{xx}-\Sigma_{zz})+\f{k_y(k_x^2-k_y^2)}{2k^2k_z^2}(\Sigma_{xx}-\Sigma_{yy})\,,\\
-\f{U_y}{\mu}&=\f{1}{2k^2}(k_x\Sigma_{zz}-k_z\Sigma_{xx})-\f{k_x(k_y^2-k_x^2)}{2k^2k_z^2}(\Sigma_{yy}-\Sigma_{xx})+\f{k_z(k_y^2-k_z^2)}{2k^2k_x^2}(\Sigma_{yy}-\Sigma_{zz})\,,\\
-\f{U_z}{\mu}&=\f{1}{2k^2}(k_y\Sigma_{xx}-k_x\Sigma_{yy})-\f{k_y(k_z^2-k_y^2)}{2k^2k_x^2}(\Sigma_{zz}-\Sigma_{yy})+\f{k_x(k_z^2-k_x^2)}{2k^2k_y^2}(\Sigma_{zz}-\Sigma_{xx})\,,\\
+\mu U_x&=\f{1}{2k^2}(k_z\Sigma_{yy}-k_y\Sigma_{zz})-\f{k_z(k_x^2-k_z^2)}{2k^2k_y^2}(\Sigma_{xx}-\Sigma_{zz})+\f{k_y(k_x^2-k_y^2)}{2k^2k_z^2}(\Sigma_{xx}-\Sigma_{yy})\,,\\
+\mu U_y&=\f{1}{2k^2}(k_x\Sigma_{zz}-k_z\Sigma_{xx})-\f{k_x(k_y^2-k_x^2)}{2k^2k_z^2}(\Sigma_{yy}-\Sigma_{xx})+\f{k_z(k_y^2-k_z^2)}{2k^2k_x^2}(\Sigma_{yy}-\Sigma_{zz})\,,\\
+\mu U_z&=\f{1}{2k^2}(k_y\Sigma_{xx}-k_x\Sigma_{yy})-\f{k_y(k_z^2-k_y^2)}{2k^2k_x^2}(\Sigma_{zz}-\Sigma_{yy})+\f{k_x(k_z^2-k_x^2)}{2k^2k_y^2}(\Sigma_{zz}-\Sigma_{xx})\,.
 \end{align}
-Assuming cylindrical symmetry, we have $\Sigma=\Sigma_{zz}=-2\Sigma_{xx}=-2\Sigma_{yy}$.
+Assuming radial symmetry, we have $\Sigma=\Sigma_{zz}=-2\Sigma_{xx}=-2\Sigma_{yy}$.
 \begin{align}
-U_x&=\ps{-(k_z+2k_y)k_x^2k_y^2+3k_zk_x^2(k_x^2-k_z^2)}\f{\mu}{4k^2k_x^2k_y^2}\Sigma\,,\\
-U_y&=\ps{(2k_x+k_z)k_x^2k_y^2-3k_zk_y^2(k_y^2-k_z^2)}\f{\mu}{4k^2k_x^2k_y^2}\Sigma\,,\\
-U_z&=\ps{(k_x-k_y)k_x^2k_y^2+3(k_x^3-k_y^3)k_z^2+3k_y^5-3k_x^5}\f{\mu}{4k^2k_x^2k_y^2}\Sigma\,.
+U_x&=\ps{-(k_z+2k_y)k_x^2k_y^2+3k_zk_x^2(k_x^2-k_z^2)}\f{1}{4\mu k^2k_x^2k_y^2}\Sigma\,,\\
+U_y&=\ps{(2k_x+k_z)k_x^2k_y^2-3k_zk_y^2(k_y^2-k_z^2)}\f{1}{4\mu k^2k_x^2k_y^2}\Sigma\,,\\
+U_z&=\ps{(k_x-k_y)k_x^2k_y^2+3(k_x^3-k_y^3)k_z^2+3k_y^5-3k_x^5}\f{1}{4\mu k^2k_x^2k_y^2}\Sigma\,.
 \end{align}
@@
 \end{align}
+The integral is horribly divergent about the azimuth - there must have been a mistake...
 \\\\
@@
 \end{align}
-Setting this equal to the earlier $E_{\te{propagated}}$ yields
+Setting this (less than or) equal to the earlier $E_{\te{propagated}}$ yields
 \begin{align}
-\f{h \bar p^2\pi^2r_0^6}{8\Delta r^2\lambda_0^2}&=(\sigma_Xp_0)^2\f{\pi h}{\lambda_0^2}\,,\\
-\bar p&=\p{2\sqrt{2\pi}\f{r_X^2\Delta r}{r_0^3}}p_0\,.
+\f{h \bar p^2\pi^2r_0^6}{8\Delta r^2\lambda_0^2}&\leq (\sigma_Xp_0)^2\f{\pi h}{\lambda_0^2}\,,\\
+\bar p&\leq\p{2\sqrt{2\pi}\f{r_X^2\Delta r}{r_0^3}}p_0\,.
 \end{align}
@@
 Therefore, the estimate of the energy propagated by the initial overpressure serves as an upper bound to the energy propagated during the non-linear phase.
-
+Thus, this value for $\bar p$ as a function of $p_0$ serves as an upper bound to the maximum pressure in the shock.
+By fixing an acceptable value for $\bar p$ to begin the linear propagation, we can find suitable values of $r_0$ and $\Delta r$.
+Note, $\Delta r$ is quite small, and should be on the order of $r_X$, since the width of the shock will not change much from the original (half) width of the overpressure.
+Hence, a reasonable estimate is
+\begin{align}
+\bar p&\leq\p{2\sqrt{2\pi}\f{r_X^3}{r_0^3}}p_0\,.
+\end{align}
+Using this, we can find an upper bound for $r_0$
+\begin{align}
+r_0&\leq r_X\sqrt[3]{\p{2\sqrt{2\pi}}\f{p_0}{\bar p}}\,.
+\end{align}
+It is therefore sufficient to take the linear radius to be equality in the above expression.
+But all this is really saying is that it is sufficient to estimate the fraction of energy propagated by our original calculation using the cylindrical overpressure.
 \pagebreak

### 2016-07-03 Macro Impacts.tex
Correction to Shear
Corrections - integral still divergent...

@@
 \end{align}
-From earlier, we have
+From earlier
 \begin{align}
--\Sigma_{yy}&=2\mu k_y(k_z A_x-k_x A_z)\,,\\
--\Sigma_{zz}&=2\mu k_z(k_x A_y-k_y A_x)\,,
+-\Sigma_{yz}&=\mu\ps{(k_z^2-k_y^2) A_x+k_x(k_y A_y-k_z A_z)}\,,\\
+-\Sigma_{zx}&=\mu\ps{(k_x^2-k_z^2) A_y+k_y(k_z A_z-k_x A_x)}\,.
 \end{align}
-which becomes
+Imposing the Gauge condition,
 \begin{align}
--\Sigma_{yy}&=2\mu k_y\ps{-\f{k_z}{k_x} \p{k_yA_y+k_zA_z}-k_x A_z}\,,\\
--\Sigma_{zz}&=2\mu k_z\ps{k_x A_y+\f{k_y}{k_x} \p{k_yA_y+k_zA_z}}\,,
+-\Sigma_{yz}&=\mu\ps{(k_x^2-k_y^2+k_z^2) A_x+2k_xk_y A_y}\,,\\
+-\Sigma_{zx}&=\mu\ps{(k_x^2-k_y^2-k_z^2) A_y-2k_x k_y A_x}\,.
 \end{align}
-which simplifies to
+Inverting:
 \begin{align}
--\Sigma_{yy}&=-\f{2\mu k_y}{k_x}\ps{k_y k_z A_y+\p{k_z^2+k_x^2} A_z}\,,\\
--\Sigma_{zz}&=\f{2\mu k_z}{k_x}\ps{\p{k_x^2 + k_y^2}A_y+k_yk_zA_z}\,,
+A_z=\f{k_x\Sigma_{yz}-k_y\Sigma_{zx}}{\mu k_z k^2}
 \end{align}
-Hence
+Hence, by symmetry
 \begin{align}
-A_x&=\f1\mu\f{(k_y^2-k_z^2)(\Sigma_{yy}-\Sigma_{zz})+k_x^2(\Sigma_{yy}+\Sigma_{zz})}{2k_x^2k^2}\,,\\
-&=\f1\mu\f{(k_y^2-k_z^2)(\Sigma_{yy}-\Sigma_{zz})-k_x^2\Sigma_{xx}}{2k_x^2k^2}\,,\\
-&=\f1\mu\f{(k_y^2-k_z^2)}{k_x^2}\f{(\Sigma_{yy}-\Sigma_{zz})}{2k^2}-\f1\mu\f{\Sigma_{xx}}{2k^2}\,,\\
+A_x&=\f{k_y\Sigma_{zx}-k_z\Sigma_{xy}}{\mu k_x k^2}\,,\\
+A_y&=\f{k_z\Sigma_{xy}-k_x\Sigma_{yz}}{\mu k_y k^2}\,,\\
+A_z&=\f{k_x\Sigma_{yz}-k_y\Sigma_{zx}}{\mu k_z k^2}\,.
 \end{align}
-By symmetry, we have
-\begin{align}
-A_x&=\f1\mu\f{(k_y^2-k_z^2)}{k_x^2}\f{(\Sigma_{yy}-\Sigma_{zz})}{2k^2}-\f1\mu\f{\Sigma_{xx}}{2k^2}\,,\\
-A_y&=\f1\mu\f{(k_z^2-k_x^2)}{k_y^2}\f{(\Sigma_{zz}-\Sigma_{xx})}{2k^2}-\f1\mu\f{\Sigma_{yy}}{2k^2}\,,\\
-A_z&=\f1\mu\f{(k_x^2-k_y^2)}{k_z^2}\f{(\Sigma_{xx}-\Sigma_{yy})}{2k^2}-\f1\mu\f{\Sigma_{zz}}{2k^2}\,.
-\end{align}
-Observe, in the case that all stresses are equal, we obtain that $A_x=A_y=A_z=0$, as we should.
-We now solve for $A_i$ in terms of $\Sigma_{i}$.
 \\\\
@@
 \begin{align}
-U_x&=k_y A_z-k_z A_y\,,\\
-&=\f1\mu\f{1}{2k^2k_y^2k_z^2}\ps{-k_z^3\p{-k_y^2\Sigma_{yy}+(k_x^2-k_z^2)(\Sigma_{xx}-\Sigma_{zz})}+k_y^3\p{(k_x^2-k_y^2)(\Sigma_{xx}-\Sigma_{yy})-k_z^2\Sigma_{zz}}}\,,\\
-&=\f1\mu\f{1}{2k^2k_y^2k_z^2}\ps{k_z^2k_y^2(k_z\Sigma_{yy}-k_y\Sigma_{zz})-k_z^3(k_x^2-k_z^2)(\Sigma_{xx}-\Sigma_{zz})+k_y^3(k_x^2-k_y^2)(\Sigma_{xx}-\Sigma_{yy})}\,,\\
-&=\f1\mu\ps{\f{1}{2k^2}(k_z\Sigma_{yy}-k_y\Sigma_{zz})-\f{k_z(k_x^2-k_z^2)}{2k^2k_y^2}(\Sigma_{xx}-\Sigma_{zz})+\f{k_y(k_x^2-k_y^2)}{2k^2k_z^2}(\Sigma_{xx}-\Sigma_{yy})}\,,\\
-\end{align}
-Just cyclically permute the indices to obtain the expressions for $U_y$ and $U_z$.
-\begin{align}
-\mu U_x&=\f{1}{2k^2}(k_z\Sigma_{yy}-k_y\Sigma_{zz})-\f{k_z(k_x^2-k_z^2)}{2k^2k_y^2}(\Sigma_{xx}-\Sigma_{zz})+\f{k_y(k_x^2-k_y^2)}{2k^2k_z^2}(\Sigma_{xx}-\Sigma_{yy})\,,\\
-\mu U_y&=\f{1}{2k^2}(k_x\Sigma_{zz}-k_z\Sigma_{xx})-\f{k_x(k_y^2-k_x^2)}{2k^2k_z^2}(\Sigma_{yy}-\Sigma_{xx})+\f{k_z(k_y^2-k_z^2)}{2k^2k_x^2}(\Sigma_{yy}-\Sigma_{zz})\,,\\
-\mu U_z&=\f{1}{2k^2}(k_y\Sigma_{xx}-k_x\Sigma_{yy})-\f{k_y(k_z^2-k_y^2)}{2k^2k_x^2}(\Sigma_{zz}-\Sigma_{yy})+\f{k_x(k_z^2-k_x^2)}{2k^2k_y^2}(\Sigma_{zz}-\Sigma_{xx})\,.
+U_x&=\f{k_z^2(k_x\Sigma_{yz}-k_z\Sigma_{xy})+k_y^2(k_x\Sigma_{yz}-k_y\Sigma_{zx})}{\mu k_y k_z k^2}\,,\\
+U_y&=\f{k_x^2(k_y\Sigma_{zx}-k_x\Sigma_{yz})+k_z^2(k_y\Sigma_{zx}-k_z\Sigma_{xy})}{\mu k_z k_x k^2}\,,\\
+U_z&=\f{k_y^2(k_z\Sigma_{xy}-k_y\Sigma_{zx})+k_x^2(k_z\Sigma_{xy}-k_x\Sigma_{yz})}{\mu k_x k_y k^2}\,,
 \end{align}
 Assuming radial symmetry, we have $\Sigma=\Sigma_{zz}=-2\Sigma_{xx}=-2\Sigma_{yy}$.
-\begin{align}
-U_x&=\ps{-(k_z+2k_y)k_x^2k_y^2+3k_zk_x^2(k_x^2-k_z^2)}\f{1}{4\mu k^2k_x^2k_y^2}\Sigma\,,\\
-U_y&=\ps{(2k_x+k_z)k_x^2k_y^2-3k_zk_y^2(k_y^2-k_z^2)}\f{1}{4\mu k^2k_x^2k_y^2}\Sigma\,,\\
-U_z&=\ps{(k_x-k_y)k_x^2k_y^2+3(k_x^3-k_y^3)k_z^2+3k_y^5-3k_x^5}\f{1}{4\mu k^2k_x^2k_y^2}\Sigma\,.
-\end{align}
+
 The energy of these shear waves is given

### 2016-07-04 Macro Impacts.tex
Small Correction
Estimate Made

@@
 \begin{align}
-p=\bar p\f{r-r_0}{\Delta r}\ps{\theta(r_0+\ell-r)-\theta(r+\ell)}\ps{\theta(z+h/2)-\theta(z-h/2)}
+p=\bar p\f{r-r_0}{\Delta r}\ps{\theta(r_0+\Delta r-r)-\theta(r+\Delta r)}\ps{\theta(z+h/2)-\theta(z-h/2)}
 \end{align}
@@
 \end{align}
-Setting this (less than or) equal to the earlier $E_{\te{propagated}}$ yields
+Generously, we assume that the energy of the wave stayed constant through its non-linear evolution, and calculate the fraction energy deposited into the low frequency modes
 \begin{align}
-\f{h \bar p^2\pi^2r_0^6}{8\Delta r^2\lambda_0^2}&\leq (\sigma_Xp_0)^2\f{\pi h}{\lambda_0^2}\,,\\
-\bar p&\leq\p{2\sqrt{2\pi}\f{r_X^2\Delta r}{r_0^3}}p_0\,.
+\Xi&=\f{h \bar p^2\pi^2r_0^6}{8\Delta r^2\lambda_0^2}\f{1}{4\pi^2p_0^2\sigma_Xh}\,,\\
+&=\f{1}{32}\f{\bar p^2}{p_0^2}\f{r_0^6}{\Delta r^2\sigma_X\lambda_0^2}\,,\\
+&=\f{\pi^2(\lambda+2\mu)}{8K^2}\f{\bar p^2}{\abs{\td{E}{x}{}}}\f{r_0^6}{\Delta r^2\lambda_0^2}\,.
 \end{align}
-We know that shock waves are rapidly attenuated in the earth.
+$\bar p$ can be taken to be the maximum stress such that the elastic limit holds i.e.
+the elastic limit.
+Some reading suggests that this is about 13 GPa.
+$K$ and $\lambda+2\mu$ can be taken to be on the order of $10^{10}$ GPa (obviously we should look into this).
+$\Delta r$ should be very small, on the order of the radius of the macro.
+$\lambda_0$ is about $6$ to $10$ kilometers, and is the wavelength at which modes propagate without significant attenuation.
+$r_0$ can be determined by geometric means.
+A first guess yields
+\begin{align}
+\Xi&\approx\f{K^4}{(\lambda+2\mu)^2}\abs{\td{E}{x}{}}^2\f{1}{512\bar p^4\lambda_0^2\sigma_X}\,,\\
+&\approx10^{-18}
+\end{align}
+This is within one order of magnitude of the answer gotten from (24).
+
+%Setting this (less than or) equal to the earlier $E_{\te{propagated}}$ yields
+%\begin{align}
+%\f{h \bar p^2\pi^2r_0^6}{8\Delta r^2\lambda_0^2}&\leq (\sigma_Xp_0)^2\f{\pi h}{\lambda_0^2}\,,\\
+%\bar p&\leq\p{2\sqrt{2\pi}\f{r_X^2\Delta r}{r_0^3}}p_0\,.
+%\end{align}
+%We know that shock waves are rapidly attenuated in the earth.
 Therefore, the estimate of the energy propagated by the initial overpressure serves as an upper bound to the energy propagated during the non-linear phase.
@@
 Hence, a reasonable estimate is
-\begin{align}
-\bar p&\leq\p{2\sqrt{2\pi}\f{r_X^3}{r_0^3}}p_0\,.
-\end{align}
-Using this, we can find an upper bound for $r_0$
-\begin{align}
-r_0&\leq r_X\sqrt[3]{\p{2\sqrt{2\pi}}\f{p_0}{\bar p}}\,.
-\end{align}
-It is therefore sufficient to take the linear radius to be equality in the above expression.
+%\begin{align}
+%\bar p&\leq\p{2\sqrt{2\pi}\f{r_X^3}{r_0^3}}p_0\,.
+%\end{align}
+%Using this, we can find an upper bound for $r_0$
+%\begin{align}
+%r_0&\leq r_X\sqrt[3]{\p{2\sqrt{2\pi}}\f{p_0}{\bar p}}\,.
+%\end{align}
+%It is therefore sufficient to take the linear radius to be equality in the above expression.
 But all this is really saying is that it is sufficient to estimate the fraction of energy propagated by our original calculation using the cylindrical overpressure.

### 2016-07-04 Macro Impacts.tex
Additional short discussion

@@
 \end{align}
-This is within one order of magnitude of the answer gotten from (24).
+This is within one order of magnitude of the answer gotten from (24). Note, my estimate for $r_0$ turned out to be about 1 kilometer. I'm still not entirely sure of the correct way to calculate $r_0$.
 

### 2016-07-04 Macro Impacts.tex
Last notes before I sleep.
Small correction to units.

@@
 Some reading suggests that this is about 13 GPa.
-$K$ and $\lambda+2\mu$ can be taken to be on the order of $10^{10}$ GPa (obviously we should look into this).
+$K$ and $\lambda+2\mu$ can be taken to be on the order of $10^{10}$ Pa (obviously we should look into this).
 $\Delta r$ should be very small, on the order of the radius of the macro.
@@
 \end{align}
-This is within one order of magnitude of the answer gotten from (24). Note, my estimate for $r_0$ turned out to be about 1 kilometer. I'm still not entirely sure of the correct way to calculate $r_0$.
+This is within one order of magnitude of the answer gotten from (24).
+Note, my estimate for $r_0$ turned out to be about 1 kilometer.
+I'm still not entirely sure of the correct way to calculate $r_0$.
+If we take $\bar p\approx 10^{8}$ Pa, then $\Xi\approx 10^{-10}$.
+That said, it's 2:00 am and I'm doing these estimates in my head, so don't take any of this too seriously.
+The only really important thing is the idea that we can ignore the non-linear evolution since we can reasonably guess its end state and assume no energy loss in between.
 

### 2016-07-04 Macro Impacts Revised.tex
Good Stuff

--- 2016-07-04 Macro Impacts.tex
@@
 \usepackage{fullpage}
-\usepackage{amsmath, amsthm, amsfonts, amssymb, mathtools, calrsfs, tensor, physics,tikz-cd}
+\usepackage{amsmath, amsthm, amsfonts, amssymb, mathtools, calrsfs, tensor, physics, MnSymbol,tikz-cd}
 \usepackage[mathscr]{euscript}
@@
 \begin{align}
--p=K\nabla^2\phi\,,
+-p=K\nabla^2\phi=K\nabla\cdot u\,,
 \end{align}
@@
 \end{align}
+\\\\
+Observe, the total energy can be calculated directly from $p$ as it is always true that half the energy is spring potential and half is kinetic.
+\begin{align}
+E&=\f{\lambda+2\mu}{K^2}\int_V\diff^3 x (p^2)
+\end{align}
 Now consider the case of a step function type pressure source - a cylinder of height $h$ and radius $r_X$
@@
 \end{align}
-Directly integrating in Mathematica (over $\theta$ first) yields
+The total energy is clearly
 \begin{align}
-E_{\te{total}}&=\f{\lambda+2\mu}{K^2}4\pi^2p_0^2\sigma_Xh
+E_{\te{total}}&=\f{\lambda+2\mu}{K^2}p_0^2\sigma_Xh
 \end{align}
@@
 &=\ps{\f{1}{2h}(r_X^2p_0)^2\f{\lambda+2\mu}{K^2}}\ps{hk_0\cos(hk_0)+\sin(hk_0)+hk_0\p{-2+hk_0\te{Si}(hk_0)}}\,,\\
-&=\ps{(r_X^2p_0)^2\f{\lambda+2\mu}{K^2}}\ps{\f{\pi}{\lambda_0}\cos\p{\f{2\pi h}{\lambda_0}}+\sin\p{\f{2\pi h}{\lambda_0}}+\p{\f{\pi}{\lambda_0}}\p{-2+\p{\f{2\pi h}{\lambda_0}}\te{Si}\p{\f{2\pi h}{\lambda_0}}}}\,,\\
 &\approx_{h\gg\lambda_0\gg1}\ps{(r_X^2p_0)^2\f{\lambda+2\mu}{K^2}}\ps{\f{\pi^3 h}{\lambda_0^2}}\,,\\
@@
 \begin{align}
-\Xi&=\f{\sigma_X}{4\pi\lambda_0^2}\,.
+\Xi&=\f{\sigma_X}{\lambda_0^2}\,.
 \end{align}
@@
 \pagebreak
-\section{Vector Modes}
-The following is the equation of motion for the vector potential $a$ without body force:
+\\
+It is wrong, however, to assume that the wave evolves linearly close to the source.
+Modes will be coupled to one another, and our expression (25) will only hold in a small neighborhood of the event.
+Effects such as heating and rock fracturing will cause the high frequency modes in the shock to rapidly attenuate.
+They are, however, difficult to quantify.
+It is not controversial to say that the energy of the shock after its non-linear evolution (when the overpressure exceeds the elastic limit of the Earth) will be less than its initial energy.
+It is also well known that the behavior of shockwaves for long time tends towards a sharp wave-front with a linearly decreasing tail.
+To produce an over-estimate of the detectible energy, we hypothesize an approximate pressure waveform and endow it with energy equivalent to that of the initial blast.
+Then, we calculate the energy per mode, and sum over only those modes whose frequency is in the regime that will not rapidly attenuate.
+\\\\
+We describe the long-time waveform of the shock by
 \begin{align}
-\mu\nabla^2a-\rho\ddot a=\mu\nabla(\nabla\cdot a)-\mu\nabla\times(\nabla\times a)-\rho\ddot a=0\,,
+p=\bar p\f{r-r_0}{\Delta r}\ps{\theta(r_0+\Delta r-r)-\theta(r+\Delta r)}\ps{\theta(z+h/2)-\theta(z-h/2)}\,.
 \end{align}
-where the leftmost term is the vector laplacian. This gives us three wave equations for the three components of $a$. The constraint equation takes the form
+$\Delta r$ is the length of the tail, and $r_0$ is its base.
+$\bar p$ is the peak pressure of the shock, and we can take it to be the stress corresponding to the elastic limit of rock.
+It is reasonable to say that $\Delta r$ should be within an order of magnitude of $r_X$.
+The total energy of this pressure wave is
 \begin{align}
-\sigma_{ij}&=\lambda\delta_{ij}\nabla\cdot \nabla\times a+\mu(\partial_j (\nabla\times a)_i+\partial_i (\nabla\times a)_j)\,,\\
-&=\mu(\partial_j (\nabla\times a)_i+\partial_i (\nabla\times a)_j)\,,\\
-&=\mu\mat{ccc}{2\partial_x(\partial_ya_z-\partial_za_y)&(\partial_y^2-\partial_x^2)a_z+\partial_z(\partial_x a_x-\partial_y a_y)&(\partial_x^2-\partial_z^2)a_y+\partial_y(\partial_z a_z-\partial_x a_x)\\
-&2\partial_y(\partial_z a_x-\partial_x a_z)&(\partial_z^2-\partial_y^2)a_x+\partial_x(\partial_ya_y-\partial_za_z)\\
-&&2\partial_z(\partial_xa_y-\partial_ya_x)}\,.
+E_{\te{total}}=\f{\lambda+2\mu}{K^2}\f16 \bar p^2 \pi\Delta r h(4 r_0+3\Delta r)\,.
 \end{align}
-We now write $a_i$ in terms of its Fourier components
+We require that this be equal to the initial total energy. From this, we can obtain an expression for $r_0$ in terms of $\Delta r$.
 \begin{align}
-a_i(\vec x,t)&=\int\f{\diff^3k}{(2\pi)^3}A_i(\vec k,\omega)e^{\I(\vec k\cdot\vec x-\omega t)}\,.
+r_0&=\f{3(2p_0^2r_X^2-\bar p^2\Delta r^2)}{4\bar p^2\Delta r}\,.
 \end{align}
-Observe the dispersion relation $\beta k=\omega$, which holds for each component $a_i$, and that $\beta=\f\mu\rho$. Thus, the solutions to the wave equation are
+The energy in the longest modes is, for $h\gg\lambda_0$
 \begin{align}
-a_i(\vec x,t)&=\int\f{\diff^3k}{(2\pi)^3}A_i(\vec k,\omega)e^{\I(\vec k\cdot\vec x-\beta k t)}\,.
+E_{\te{propagated}}&\approx\f{\lambda+2\mu}{K^2}\f{\bar p^2 \pi^3 h \Delta r^2(3r_0+2\Delta r)^2}{9\lambda_0^2}\,.
 \end{align}
-We now use the constraint equation to write down the initial vector potential in terms of the initial stress.
-Note, we will obtain three equations constraining the possible initial stresses (i.e., we will be able to eliminate three components of $\sigma$ from the equations), and three equations writing $A_i$ in terms of $\Sigma_{ij}$.
-\\\\
-In Fourier space we have
+Then we have that the fraction of energy that will reach seismometers is
 \begin{align}
--\Sigma_{xx}&=\mu2k_x(k_y A_z-k_z A_y)\,,\\
--\Sigma_{yy}&=\mu2k_y(k_z A_x-k_x A_z)\,,\\
--\Sigma_{zz}&=\mu2k_z(k_x A_y-k_y A_x)\,,\\
--\Sigma_{xy}&=\mu\ps{(k_y^2-k_x^2) A_z+k_z(k_x A_x-k_y A_y)}\,,\\
--\Sigma_{yz}&=\mu\ps{(k_z^2-k_y^2) A_x+k_x(k_y A_y-k_z A_z)}\,,\\
--\Sigma_{zx}&=\mu\ps{(k_x^2-k_z^2) A_y+k_y(k_z A_z-k_x A_x)}\,.
+\Xi&=\f{2\pi^2\Delta r(3r_0+2\Delta r)^2}{3(4 r_0+3\Delta r)\lambda_0^2}\,,\\
+&=\pi^2\p{\f{18 p_0^2 r_X^2-\bar p^2\Delta r^2}{12 p_0\bar p r_X\lambda_0}}^2
 \end{align}
-First observe that any three of these equations together forms a singular linear system in $A_i$. Thus we cannot invert to solve for $A_i$. However, we can get some information about the $\Sigma$'s.
-\\\\
-Taking the sum of 31-33 yields
+Since we know that the total energy is, assuming that the velocity of the macro remains approximately constant throughout its journey through Earth
 \begin{align}
-0&=\Sigma_{xx}+\Sigma_{yy}+\Sigma_{zz}\,.
+\f{\lambda+2\mu}{K^2}p_0^2\sigma_Xh=E_{\te{total}}=h\abs{\td{E}{x}{}}=h\rho_{\oplus}\sigma_Xv_X^2\,.
 \end{align}
-Observe that
+Thus we obtain the following expression for $p_0$
 \begin{align}
-\f{-\Sigma_{xx}k_y}{2\mu k_xk_z}&=\f{k_y^2}{k_z}A_z-k_yA_y\,,\\
-\f{-\Sigma_{yy}k_x}{2\mu k_yk_z}&=k_xA_x-\f{k_x^2}{k_z}A_z\,,\\
-\f{-\Sigma_{xy}}{\mu k_z}&=\ps{\f{k_y^2-k_z^2}{k_z}}A_z+k_xA_x-k_yA_y\,.
+p_0&=\sqrt{\f{\rho}{\lambda+2\mu}}Kv_X\,.
 \end{align}
-Taking the sum of the first two reveals that`
+Thus, the suppression factor is
 \begin{align}
-2k_xk_y\Sigma_{xy}&=k_y^2\Sigma_{xx}+k_x^2\Sigma_{yy}\,.
+\Xi&=\pi \f{(\bar p^2\pi \Delta r^2(\lambda+2\mu)-18K^2\sigma_Xv_X^2\rho_{\oplus})^2}{144K^2(\lambda+2\mu)\rho_{\oplus}\bar p^2 \sigma_X v_X^2\lambda_0^2}\,.
 \end{align}
-If you want to be silly, we find
-\begin{align}
-0&=(\Sigma_{x}k_y-\Sigma_{y}k_x)^2\,.
-\end{align}
-Anyway, we then have the system of three equations
-\begin{align}
-2k_xk_y\Sigma_{xy}&=k_y^2\Sigma_{xx}+k_x^2\Sigma_{yy}\,,\\
-2k_yk_z\Sigma_{yz}&=k_z^2\Sigma_{yy}+k_y^2\Sigma_{zz}\,,\\
-2k_zk_x\Sigma_{zx}&=k_x^2\Sigma_{zz}+k_z^2\Sigma_{xx}\,.
-\end{align}
-which is non-singular. They yield
-\begin{align}
-\Sigma_{xx}&=\f{k_x}{k_yk_z}\p{k_z\Sigma_{xy}-k_x\Sigma_{yz}+k_y\Sigma_{zx}}\,,\\
-\Sigma_{yy}&=\f{k_y}{k_zk_x}\p{k_z\Sigma_{xy}+k_x\Sigma_{yz}-k_y\Sigma_{zx}}\,,\\
-\Sigma_{zz}&=\f{k_z}{k_xk_y}\p{-k_z\Sigma_{xy}+k_x\Sigma_{yz}+k_y\Sigma_{zx}}\,.
-\end{align}
-This, along with being traceless, shows that the shear only has two independent degrees of freedom: the polarizations.
-\\\\
-It is impossible to solve for $A_i$ in terms of the stress as is, hence we must fix a gauge. To do this, we fix $\nabla\cdot a=0$, whence
-\begin{align}
-0=k_xA_x+k_yA_y+k_zA_z\,.
-\end{align}
-From earlier
-\begin{align}
--\Sigma_{yz}&=\mu\ps{(k_z^2-k_y^2) A_x+k_x(k_y A_y-k_z A_z)}\,,\\
--\Sigma_{zx}&=\mu\ps{(k_x^2-k_z^2) A_y+k_y(k_z A_z-k_x A_x)}\,.
-\end{align}
-Imposing the Gauge condition,
-\begin{align}
--\Sigma_{yz}&=\mu\ps{(k_x^2-k_y^2+k_z^2) A_x+2k_xk_y A_y}\,,\\
--\Sigma_{zx}&=\mu\ps{(k_x^2-k_y^2-k_z^2) A_y-2k_x k_y A_x}\,.
-\end{align}
-Inverting:
-\begin{align}
-A_z=\f{k_x\Sigma_{yz}-k_y\Sigma_{zx}}{\mu k_z k^2}
-\end{align}
-Hence, by symmetry
-\begin{align}
-A_x&=\f{k_y\Sigma_{zx}-k_z\Sigma_{xy}}{\mu k_x k^2}\,,\\
-A_y&=\f{k_z\Sigma_{xy}-k_x\Sigma_{yz}}{\mu k_y k^2}\,,\\
-A_z&=\f{k_x\Sigma_{yz}-k_y\Sigma_{zx}}{\mu k_z k^2}\,.
-\end{align}
-\\\\
-Now we take the curl of $A$ to find the shear mode displacement
-\begin{align}
-U_x&=\f{k_z^2(k_x\Sigma_{yz}-k_z\Sigma_{xy})+k_y^2(k_x\Sigma_{yz}-k_y\Sigma_{zx})}{\mu k_y k_z k^2}\,,\\
-U_y&=\f{k_x^2(k_y\Sigma_{zx}-k_x\Sigma_{yz})+k_z^2(k_y\Sigma_{zx}-k_z\Sigma_{xy})}{\mu k_z k_x k^2}\,,\\
-U_z&=\f{k_y^2(k_z\Sigma_{xy}-k_y\Sigma_{zx})+k_x^2(k_z\Sigma_{xy}-k_x\Sigma_{yz})}{\mu k_x k_y k^2}\,,
-\end{align}
-Assuming radial symmetry, we have $\Sigma=\Sigma_{zz}=-2\Sigma_{xx}=-2\Sigma_{yy}$.
-
-The energy of these shear waves is given
-\begin{align}
-E&=\f12\int_V\p{\rho\abs{u_t}^2+\mu\abs{\nabla\cdot u}^2}\,,\\
-&=\rho\int_V\abs{u_t}^2\,,\\
-&=\mu\int_V\int\f{\diff^3 k}{(2\pi)^3}\int\f{\diff^3 k'}{(2\pi)^3}\p{k k'U(\vec k)\bar U(\vec k')}e^{-\I(\vec k\cdot\vec x-i\beta k t)}e^{\I(\vec k'\cdot\vec x-i\beta k' t)}\,,\\
-&=\mu\int\f{\diff^3 k}{(2\pi)^3}\p{k^2\abs{U(\vec k)}^2}\,,\\
-\end{align}
-The integral is horribly divergent about the azimuth - there must have been a mistake...
-\\\\
-For shocks, check the laser physics book.
-
-\pagebreak
-\section{Comparison to ``Passage of Small BH...''}
-Their considerations in the acoustic limit account for a body force generated by the gravitational pull of the miniature black hole.
-They discover that only supersonic blackholes would generate this type of radiation.
-Our calculations, on the other hand, seem independent of these considerations.
-In our case, the gravitational pull of something as dense as a Macro is not negligible, but should not generate as significant an effect this way.
-The principal mechanism for energy deposition is the scattering of matter off the macro.
-However, their methods do bring into question whether the free wave equation is appropriate.
-They also consider the transfer of energy due to pressure from the black hole to matter along its path.
-This is a different calculation from ours since black hole radiation is very weak, as opposed to collisions between baryonic matter.
-\\\\
-However, one key point is that they do neglect shear by using a scalar displacement potential $\psi$ below their equation (3).
-Moreover, they neglect the subtlety of the behavior of the collision near the boundary of the Earth.
-
-\pagebreak
-\section{Our Argument}
-As a Macro passes through the earth, there are several phases to its journey.
-The first is its passage through the atmosphere.
-The second is its crossing the boundary from air to earth, which we suspect will be relatively uneventful, since the air is 1000$\times$ lower density than earth, and thus the air pressure would displace relatively little of earth.
-The third is the transit of the macro through the earth.
-The shockwave it produces should be generated primarily by elastic and inelastic scattering of baryonic matter off the Macro.
-If we estimate that the macro produces an initial overpressure in a tube of its own radius, we can calculate the initial overpressure from the total energy deposition and its cross section.
-Given that the macro is dense enough, its loss of momentum will be approximately linear, and we can approximate its energy loss as being approximately constant.
-Estimates have already been made of the stopping power, so the total energy deposition will just be
-\begin{align}
-\abs{\td{E}{x}{}}h=E_{\te{total}}=\f{\lambda+2\mu}{K^2}4\pi^2p_0^2\sigma_Xh
-\end{align}
-whence the initial overpressure is
-\begin{align}
-p_0=\f{K}{2\pi}\sqrt{\abs{\td{E}{x}{}}\f{1}{\sigma_X(\lambda+2\mu)}}
-\end{align}
-It is not appropriate to use the linear regime until the overpressure is close to 0 compared to some pressure, which we suspect may be $p_{\te{non-linear}}\approx60\te{GPa}$.
-It is reasonable to assume that the elastic limit holds when the pressures are an order of magnitude smaller than $p_{\te{non-linear}}$, denoted $p_{\te{linear}}\approx6\te{GPa}$.
-(This stuff needs to be checked).
-Note that energy losses due to heating, i.e.
-anelastic frequency attenuation, will dilute the energy density of the shock.
-However, for a conservative  estimate, we only consider the geometric attenuation, which will dilute the energy density as $r^{-1}$, where $r$ is the radial distance from the Macro's trajectory to the shock front.
-The shape of the shockwave will rapidly achieve a right-triangular profile.
-Geometric considerations show that the overpressure will go as $r^{-1}$.
-Thus, suppose that the peak pressure in the shock is $\bar p$.
-The overpressure is then given by
-\begin{align}
-p=\bar p\f{r-r_0}{\Delta r}\ps{\theta(r_0+\Delta r-r)-\theta(r+\Delta r)}\ps{\theta(z+h/2)-\theta(z-h/2)}
-\end{align}
-where $\Delta r$ is the radial length of the shock and $r_0$ is its base.
-In the limit where $h$ is much larger than all other fixed lengths, we have (after a large but easy mathematica calculation (triangle pressure.nb))
-\begin{align}
-E_{\te{propagated}}&\approx \f{\lambda+2\mu}{K^2}\f{h \bar p^2\pi^2r_0^6}{8\Delta r^2\lambda_0^2}\,.
-\end{align}
-Generously, we assume that the energy of the wave stayed constant through its non-linear evolution, and calculate the fraction energy deposited into the low frequency modes
-\begin{align}
-\Xi&=\f{h \bar p^2\pi^2r_0^6}{8\Delta r^2\lambda_0^2}\f{1}{4\pi^2p_0^2\sigma_Xh}\,,\\
-&=\f{1}{32}\f{\bar p^2}{p_0^2}\f{r_0^6}{\Delta r^2\sigma_X\lambda_0^2}\,,\\
-&=\f{\pi^2(\lambda+2\mu)}{8K^2}\f{\bar p^2}{\abs{\td{E}{x}{}}}\f{r_0^6}{\Delta r^2\lambda_0^2}\,.
-\end{align}
-$\bar p$ can be taken to be the maximum stress such that the elastic limit holds i.e.
-the elastic limit.
-Some reading suggests that this is about 13 GPa.
-$K$ and $\lambda+2\mu$ can be taken to be on the order of $10^{10}$ GPa (obviously we should look into this).
-$\Delta r$ should be very small, on the order of the radius of the macro.
-$\lambda_0$ is about $6$ to $10$ kilometers, and is the wavelength at which modes propagate without significant attenuation.
-$r_0$ can be determined by geometric means.
-A first guess yields
-\begin{align}
-\Xi&\approx\f{K^4}{(\lambda+2\mu)^2}\abs{\td{E}{x}{}}^2\f{1}{512\bar p^4\lambda_0^2\sigma_X}\,,\\
-&\approx10^{-18}
-\end{align}
-This is within one order of magnitude of the answer gotten from (24).
-
-%Setting this (less than or) equal to the earlier $E_{\te{propagated}}$ yields
-%\begin{align}
-%\f{h \bar p^2\pi^2r_0^6}{8\Delta r^2\lambda_0^2}&\leq (\sigma_Xp_0)^2\f{\pi h}{\lambda_0^2}\,,\\
-%\bar p&\leq\p{2\sqrt{2\pi}\f{r_X^2\Delta r}{r_0^3}}p_0\,.
-%\end{align}
-%We know that shock waves are rapidly attenuated in the earth.
-Therefore, the estimate of the energy propagated by the initial overpressure serves as an upper bound to the energy propagated during the non-linear phase.
-Thus, this value for $\bar p$ as a function of $p_0$ serves as an upper bound to the maximum pressure in the shock.
-By fixing an acceptable value for $\bar p$ to begin the linear propagation, we can find suitable values of $r_0$ and $\Delta r$.
-Note, $\Delta r$ is quite small, and should be on the order of $r_X$, since the width of the shock will not change much from the original (half) width of the overpressure.
-Hence, a reasonable estimate is
-%\begin{align}
-%\bar p&\leq\p{2\sqrt{2\pi}\f{r_X^3}{r_0^3}}p_0\,.
-%\end{align}
-%Using this, we can find an upper bound for $r_0$
-%\begin{align}
-%r_0&\leq r_X\sqrt[3]{\p{2\sqrt{2\pi}}\f{p_0}{\bar p}}\,.
-%\end{align}
-%It is therefore sufficient to take the linear radius to be equality in the above expression.
-But all this is really saying is that it is sufficient to estimate the fraction of energy propagated by our original calculation using the cylindrical overpressure.
-\pagebreak
-\section{What we still need to do}
-What we've calculated is the the pressure from the total energy deposition.
-We need to figure out the total energy, pressure, and shape of the shock after it becomes sufficiently acoustic.
-It would also be good to know the velocity of the shock.
-From this, we can calculate the energy deposited in the measurable range.
-\\\\
-It appears as though *nobody* considers the shear waves... Should we?
-\\\\
-The gravitational effects can be taken into account as in the Black Hole paper.
 \end{document}

### 2016-07-04 Macro Impacts.tex
Good Stuff

@@
 The only really important thing is the idea that we can ignore the non-linear evolution since we can reasonably guess its end state and assume no energy loss in between.
-
+\\\\
+If we want to calculate the total energy, it may be better to work in real space. Observe
+\begin{align}
+U(\vec k)=\I\f{P(\vec k)}{K}\f{\vec k}{k^2}\,.
+\end{align}
+Hence,
+\begin{align}
+\nabla\cdot u&=-\int\f{P(\vec k)}{K}e^{-\I(\vec k\cdot\vec x-\alpha k t)}\,,\\
+&=-\f{p}{K}
+\end{align}
+Thus, the total energy is
+\begin{align}
+E_{\te{total}}&=\f{\lambda+2\mu}{K^2}\int\diff^3 x (p^2)\,,
+\end{align}
+Hence, for the asymptotic shock wave
+\begin{align}
+E_{\te{total}}&=\f{\lambda+2\mu}{K^2}\bar p^2\pi\Delta r h\f16(4 r_0+3\Delta r)\,.
+\end{align}
+Setting this equal to the original energy of the impact yields (note, i think the original total energy calculation is off by a factor of $4\pi^2$ so I correct that here):
+\begin{align}
+\bar p^2\Delta r\f16(4 r_0+3\Delta r)&=p_0^2 r_X^2
+\end{align}
+Assuming that $r_X\approx \Delta r$, we have
+\begin{align}
+r_0&=\f34r_X\f{2p_0^2-\bar p^2}{\bar p^2}
+\end{align}
 %Setting this (less than or) equal to the earlier $E_{\te{propagated}}$ yields

### 2016-07-04 Macro Impacts Revised.tex
update

@@
 \end{align}
-Since we know that the total energy is, assuming that the velocity of the macro remains approximately constant throughout its journey through Earth
+Since we know that the total energy is (assuming that the velocity of the macro remains approximately constant throughout its journey through Earth) we can calculate the initial overpressure.
 \begin{align}

### 2016-07-05 Macro Impacts Revised.tex
Mistakes were made: they need fixing.
I calculated the propagated energy and it was larger than the total
initial energy. Clearly mistakes were made that cannot be accounted for
by the neglect of the nonlinear regime. These mistakes must be fixed!

@@
 \end{align}
-The energy in the longest modes is, for $h\gg\lambda_0$
+The energy in the longest modes is, for $h\gg\lambda_0\gg r_0$
 \begin{align}
@@
 \end{align}
+One source suggests that Earth reacts elastically when the acceleration $\ddot u$ is bounded by $4\te{ms}^{-2}$. Observe,
+\begin{align}
+U(\vec k)=\I\f{P(\vec k)}{K}\f{\vec k}{k^2}\,,
+\end{align}
+hence
+\begin{align}
+\ddot U(\vec k)=-\I\alpha^2\f{P(\vec k)}{K}\vec k\,.
+\end{align}
+The inverse transform yields
+\begin{align}
+\ddot u&=-\f{\alpha^2}{K}\nabla p\,.
+\end{align}
+For our case, within the shock front
+\begin{align}
+\ddot u&=-\f{\alpha^2}{K}\bar p\f{2r-r_0}{r\Delta r}\,.
+\end{align}
+This function is monotonic increasing, and thus has maximum absolute value
+\begin{align}
+\ddot u_{\te{max}}&=\f{\alpha^2}{K}\bar p\f{2\Delta r+r_0}{(\Delta r+r_0)\Delta r}\,.
+\end{align}
+We have $r_0$ in terms of $\Delta r$, and hence we can solve the system for both.
+Unfortunately, the numerical results for $r_0$ and $\Delta r$ are huge...
+roughly $r_0=10^{17}\te{m}$ and $\Delta r=10^5\te{m}$.
+Moreover, plugging these results in for the energy $E_{\te{prop}}$ yields an enormous number, on the order of $10^{57}\te{J}$.
+Given that the total energy deposition is $10^{12}$, it is clear that we made a mistake somewhere...
 \end{document}

### 2016-07-06 Macro Impacts Revised.tex
Answers that make sense!!!
I think we’ve got good stuff here.

--- 2016-07-04 Macro Impacts Revised.tex
@@
 $\bar p$ is the peak pressure of the shock, and we can take it to be the stress corresponding to the elastic limit of rock.
-It is reasonable to say that $\Delta r$ should be within an order of magnitude of $r_X$.
 The total energy of this pressure wave is
@@
 \end{align}
+Reviewing a USGS document (Rock Failure and Earthquakes) suggests that $\bar p$ be set at $10^8$.
+To calculate $\Delta r$, notice that the Earth is initially displaced by $r_X$.
+The Earth will then collapse back into the hole due to ambient pressure at the speed of sound $\alpha$, yielding a time of collapse $r_X/\alpha$.
+The speed of the shockwave initially produced by the object is approximately the speed of the object itself.
+Hence $\Delta r/v_X=r_X/\alpha$.
+Thus $\Delta r\approx\f{v_X}{\alpha}r_X$.
+\\\\
+The following are the approximate quantities used
+\begin{align}
+h&=1.2\times 10^7\te{m}\,,\\
+v_X&=2.5\times 10^6\te{m s}^{-1}\,,\\
+\rho_{\oplus}&=6\times 10^3\te{kg m}^{-3}\,,\\
+\sigma_X&=10^{-11}\te{m}^2\,,\\
+\abs{\td{E}{x}{}}&=\rho_{\oplus}\sigma_X v_X^2=3.75\times 10^5\te{J m}^{-1}\,,\\
+E_{\te{total}}&=4.5\times 10^{12}\te{J}\,,\\
+r_X&=1.8\times 10^{-6}\te{m}\,,\\
+\alpha&=6\times 10^3\te{m s}^{-1}\,,\\
+\beta&=3.5\times 10^{3}\te{m s}^{-1}\,,\\
+\mu&=7.2\times 10^{10}\te{Pa}\,,\\
+\lambda&=7.2\times 10^{10}\te{Pa}\,,\\
+K&=1.2\times 10^{11}\te{Pa}\,.
+\end{align}
+These lead to the results
+\begin{align}
+\Delta r&=7.4\times 10^{-4}\te{m}\,,\\
+r_0&=1.6\times 10^3\te{m}\,,\\
+E_{\te{propagated}}&=\f{8\times 10^{13}\te{J m}^2}{\lambda_0^2}\,,\\
+\Xi&=\f{17.6\te{m}^2}{\lambda_0^2}\,.
+\end{align}
+Conservatively we set $\lambda_0$ at about $6$ kilometers.
+This yields a total suppression factor of $\Xi=4.9\times 10^{-7}$.
+Keep in mind that this estimate is incredibly conservative, and does not take into account any non-conservative processes in the nonlinear regime $r<r_0$.
+Note, even though both $\lambda_0$ and $r_0$ are on the same order of magnitude, the approximations used are still good since they are overestimates of the Bessel $J$ and Struve $H$ functions.
 \end{document}

### 2016-07-06 Macro Impacts Revised.tex
Update

@@
 Thus $\Delta r\approx\f{v_X}{\alpha}r_X$.
-\\\\
+Thus
+\begin{align}
+\Xi&=\pi \f{(\bar p^2\pi \f{v_X^2}{\alpha^2}r_X^2(\lambda+2\mu)-18K^2\sigma_Xv_X^2\rho_{\oplus})^2}{144K^2(\lambda+2\mu)\rho_{\oplus}\bar p^2 \sigma_X v_X^2\lambda_0^2}\,,\\
+&=\p{\pi r_X v_X\f{\bar p^2 -18K^2}{12K\alpha\bar p \lambda_0}}^2\,.
+\end{align}
+Given the relative magnitudes of $\bar p$ and $K^2$,
+\begin{align}
+\Xi&=\p{\f{3\pi r_X v_XK}{2\alpha\bar p \lambda_0}}^2\,,\\
+&=\p{\f{K^2}{\lambda+2\mu}}\p{\f{3\pi}{2\bar p\lambda_0}}^2\abs{\td{E}{x}{}}\,.
+\end{align}
 The following are the approximate quantities used
@@
 \lambda&=7.2\times 10^{10}\te{Pa}\,,\\
-K&=1.2\times 10^{11}\te{Pa}\,.
+K&=1.2\times 10^{11}\te{Pa}\,,\\
+\bar p&=10^8\te{Pa}\,.
 \end{align}
@@
 Note, even though both $\lambda_0$ and $r_0$ are on the same order of magnitude, the approximations used are still good since they are overestimates of the Bessel $J$ and Struve $H$ functions.
+\\\\
+Our result shows that the suppression factor only depends on the stopping factor, which in turn only depends on the velocity and cross-section of the macro.
+This is sensible since the velocity and cross-section of the macro are the defining characteristics of the impact.
+The only factor missing is the density of the macro.
+However, we are assuming that the density is large enough that the average velocity of the macro on its journey through the earth is close to its initial velocity.
+\\\\
+It is significant that $\Xi$ is proportional to $\sigma_X$. For the very largest macros, our very conservative suppression factor is near unity. However, it may still be enough to rule out detection.
+\\\\
+Note, it is incorrect to consider the expression for $\Xi$ in the small and large parameter limits: we required (in some approximations) that $r_0\ll \lambda_0$, which places a lower bound on $\bar p$.
+Moreover $\bar p$ is supposed to be less than $p_0$.
+\pagebreak
+\section{Vector Modes}
+The following is the equation of motion for the vector potential $a$ without body force:
+\begin{align}
+\mu\nabla^2a-\rho\ddot a=\mu\nabla(\nabla\cdot a)-\mu\nabla\times(\nabla\times a)-\rho\ddot a=0\,,
+\end{align}
+where the leftmost term is the vector laplacian. This gives us three wave equations for the three components of $a$. The constraint equation takes the form
+\begin{align}
+\sigma_{ij}&=\lambda\delta_{ij}\nabla\cdot \nabla\times a+\mu(\partial_j (\nabla\times a)_i+\partial_i (\nabla\times a)_j)\,,\\
+&=\mu(\partial_j (\nabla\times a)_i+\partial_i (\nabla\times a)_j)\,,\\
+&=\mu\mat{ccc}{2\partial_x(\partial_ya_z-\partial_za_y)&(\partial_y^2-\partial_x^2)a_z+\partial_z(\partial_x a_x-\partial_y a_y)&(\partial_x^2-\partial_z^2)a_y+\partial_y(\partial_z a_z-\partial_x a_x)\\
+&2\partial_y(\partial_z a_x-\partial_x a_z)&(\partial_z^2-\partial_y^2)a_x+\partial_x(\partial_ya_y-\partial_za_z)\\
+&&2\partial_z(\partial_xa_y-\partial_ya_x)}\,.
+\end{align}
+We now write $a_i$ in terms of its Fourier components
+\begin{align}
+a_i(\vec x,t)&=\int\f{\diff^3k}{(2\pi)^3}A_i(\vec k,\omega)e^{\I(\vec k\cdot\vec x-\omega t)}\,.
+\end{align}
+Observe the dispersion relation $\beta k=\omega$, which holds for each component $a_i$, and that $\beta=\f\mu\rho$. Thus, the solutions to the wave equation are
+\begin{align}
+a_i(\vec x,t)&=\int\f{\diff^3k}{(2\pi)^3}A_i(\vec k,\omega)e^{\I(\vec k\cdot\vec x-\beta k t)}\,.
+\end{align}
+We now use the constraint equation to write down the initial vector potential in terms of the initial stress.
+Note, we will obtain three equations constraining the possible initial stresses (i.e., we will be able to eliminate three components of $\sigma$ from the equations), and three equations writing $A_i$ in terms of $\Sigma_{ij}$.
+\\\\
+In Fourier space we have
+\begin{align}
+-\Sigma_{xx}&=\mu2k_x(k_y A_z-k_z A_y)\,,\\
+-\Sigma_{yy}&=\mu2k_y(k_z A_x-k_x A_z)\,,\\
+-\Sigma_{zz}&=\mu2k_z(k_x A_y-k_y A_x)\,,\\
+-\Sigma_{xy}&=\mu\ps{(k_y^2-k_x^2) A_z+k_z(k_x A_x-k_y A_y)}\,,\\
+-\Sigma_{yz}&=\mu\ps{(k_z^2-k_y^2) A_x+k_x(k_y A_y-k_z A_z)}\,,\\
+-\Sigma_{zx}&=\mu\ps{(k_x^2-k_z^2) A_y+k_y(k_z A_z-k_x A_x)}\,.
+\end{align}
+First observe that any three of these equations together forms a singular linear system in $A_i$. Thus we cannot invert to solve for $A_i$. However, we can get some information about the $\Sigma$'s.
+\\\\
+Taking the sum of 31-33 yields
+\begin{align}
+0&=\Sigma_{xx}+\Sigma_{yy}+\Sigma_{zz}\,.
+\end{align}
+Observe that
+\begin{align}
+\f{-\Sigma_{xx}k_y}{2\mu k_xk_z}&=\f{k_y^2}{k_z}A_z-k_yA_y\,,\\
+\f{-\Sigma_{yy}k_x}{2\mu k_yk_z}&=k_xA_x-\f{k_x^2}{k_z}A_z\,,\\
+\f{-\Sigma_{xy}}{\mu k_z}&=\ps{\f{k_y^2-k_z^2}{k_z}}A_z+k_xA_x-k_yA_y\,.
+\end{align}
+Taking the sum of the first two reveals that`
+\begin{align}
+2k_xk_y\Sigma_{xy}&=k_y^2\Sigma_{xx}+k_x^2\Sigma_{yy}\,.
+\end{align}
+If you want to be silly, we find
+\begin{align}
+0&=(\Sigma_{x}k_y-\Sigma_{y}k_x)^2\,.
+\end{align}
+Anyway, we then have the system of three equations
+\begin{align}
+2k_xk_y\Sigma_{xy}&=k_y^2\Sigma_{xx}+k_x^2\Sigma_{yy}\,,\\
+2k_yk_z\Sigma_{yz}&=k_z^2\Sigma_{yy}+k_y^2\Sigma_{zz}\,,\\
+2k_zk_x\Sigma_{zx}&=k_x^2\Sigma_{zz}+k_z^2\Sigma_{xx}\,.
+\end{align}
+which is non-singular. They yield
+\begin{align}
+\Sigma_{xx}&=\f{k_x}{k_yk_z}\p{k_z\Sigma_{xy}-k_x\Sigma_{yz}+k_y\Sigma_{zx}}\,,\\
+\Sigma_{yy}&=\f{k_y}{k_zk_x}\p{k_z\Sigma_{xy}+k_x\Sigma_{yz}-k_y\Sigma_{zx}}\,,\\
+\Sigma_{zz}&=\f{k_z}{k_xk_y}\p{-k_z\Sigma_{xy}+k_x\Sigma_{yz}+k_y\Sigma_{zx}}\,.
+\end{align}
+This, along with being traceless, shows that the shear only has two independent degrees of freedom: the polarizations.
+\\\\
+It is impossible to solve for $A_i$ in terms of the stress as is, hence we must fix a gauge. To do this, we fix $\nabla\cdot a=0$, whence
+\begin{align}
+0=k_xA_x+k_yA_y+k_zA_z\,.
+\end{align}
+From earlier
+\begin{align}
+-\Sigma_{yz}&=\mu\ps{(k_z^2-k_y^2) A_x+k_x(k_y A_y-k_z A_z)}\,,\\
+-\Sigma_{zx}&=\mu\ps{(k_x^2-k_z^2) A_y+k_y(k_z A_z-k_x A_x)}\,.
+\end{align}
+Imposing the Gauge condition,
+\begin{align}
+-\Sigma_{yz}&=\mu\ps{(k_x^2-k_y^2+k_z^2) A_x+2k_xk_y A_y}\,,\\
+-\Sigma_{zx}&=\mu\ps{(k_x^2-k_y^2-k_z^2) A_y-2k_x k_y A_x}\,.
+\end{align}
+Inverting:
+\begin{align}
+A_z=\f{k_x\Sigma_{yz}-k_y\Sigma_{zx}}{\mu k_z k^2}
+\end{align}
+Hence, by symmetry
+\begin{align}
+A_x&=\f{k_y\Sigma_{zx}-k_z\Sigma_{xy}}{\mu k_x k^2}\,,\\
+A_y&=\f{k_z\Sigma_{xy}-k_x\Sigma_{yz}}{\mu k_y k^2}\,,\\
+A_z&=\f{k_x\Sigma_{yz}-k_y\Sigma_{zx}}{\mu k_z k^2}\,.
+\end{align}
+\\\\
+Now we take the curl of $A$ to find the shear mode displacement
+\begin{align}
+U_x&=\f{k_z^2(k_x\Sigma_{yz}-k_z\Sigma_{xy})+k_y^2(k_x\Sigma_{yz}-k_y\Sigma_{zx})}{\mu k_y k_z k^2}\,,\\
+U_y&=\f{k_x^2(k_y\Sigma_{zx}-k_x\Sigma_{yz})+k_z^2(k_y\Sigma_{zx}-k_z\Sigma_{xy})}{\mu k_z k_x k^2}\,,\\
+U_z&=\f{k_y^2(k_z\Sigma_{xy}-k_y\Sigma_{zx})+k_x^2(k_z\Sigma_{xy}-k_x\Sigma_{yz})}{\mu k_x k_y k^2}\,,
+\end{align}
+Assuming radial symmetry, we have $\Sigma=\Sigma_{zz}=-2\Sigma_{xx}=-2\Sigma_{yy}$.
+
+The energy of these shear waves is given
+\begin{align}
+E&=\f12\int_V\p{\rho\abs{u_t}^2+\mu\abs{\nabla\cdot u}^2}\,,\\
+&=\rho\int_V\abs{u_t}^2\,,\\
+&=\mu\int_V\int\f{\diff^3 k}{(2\pi)^3}\int\f{\diff^3 k'}{(2\pi)^3}\p{k k'U(\vec k)\bar U(\vec k')}e^{-\I(\vec k\cdot\vec x-i\beta k t)}e^{\I(\vec k'\cdot\vec x-i\beta k' t)}\,,\\
+&=\mu\int\f{\diff^3 k}{(2\pi)^3}\p{k^2\abs{U(\vec k)}^2}\,,\\
+\end{align}
+The integral is horribly divergent about the azimuth - there must have been a mistake...
+
 \end{document}

### 2016-07-07 Macro Impacts Revised.tex
Shear

@@
 \end{align}
-Observe the dispersion relation $\beta k=\omega$, which holds for each component $a_i$, and that $\beta=\f\mu\rho$. Thus, the solutions to the wave equation are
+Observe the dispersion relation $\beta k=\omega$, which holds for each component $a_i$, and that $\beta^2=\f\mu\rho$. Thus, the solutions to the wave equation are
 \begin{align}
@@
 \\\\
-Now we take the curl of $A$ to find the shear mode displacement
+Now we take the curl of $A$ to find the shear mode displacement and use the relations (73) through (75) to obtain
 \begin{align}
-U_x&=\f{k_z^2(k_x\Sigma_{yz}-k_z\Sigma_{xy})+k_y^2(k_x\Sigma_{yz}-k_y\Sigma_{zx})}{\mu k_y k_z k^2}\,,\\
-U_y&=\f{k_x^2(k_y\Sigma_{zx}-k_x\Sigma_{yz})+k_z^2(k_y\Sigma_{zx}-k_z\Sigma_{xy})}{\mu k_z k_x k^2}\,,\\
-U_z&=\f{k_y^2(k_z\Sigma_{xy}-k_y\Sigma_{zx})+k_x^2(k_z\Sigma_{xy}-k_x\Sigma_{yz})}{\mu k_x k_y k^2}\,,
+U_x&=-\I\f{\Sigma_{xx}}{2k_x\mu}\,,\\
+U_y&=-\I\f{\Sigma_{yy}}{2k_y\mu}\,,\\
+U_z&=-\I\f{\Sigma_{zz}}{2k_z\mu}\,,
 \end{align}
-Assuming radial symmetry, we have $\Sigma=\Sigma_{zz}=-2\Sigma_{xx}=-2\Sigma_{yy}$.
-
 The energy of these shear waves is given
@@
 &=\rho\int_V\abs{u_t}^2\,,\\
-&=\mu\int_V\int\f{\diff^3 k}{(2\pi)^3}\int\f{\diff^3 k'}{(2\pi)^3}\p{k k'U(\vec k)\bar U(\vec k')}e^{-\I(\vec k\cdot\vec x-i\beta k t)}e^{\I(\vec k'\cdot\vec x-i\beta k' t)}\,,\\
+&=\rho\beta^2\int_V\int\f{\diff^3 k}{(2\pi)^3}\int\f{\diff^3 k'}{(2\pi)^3}\p{k k'U(\vec k)\bar U(\vec k')}e^{-\I(\vec k\cdot\vec x-i\beta k t)}e^{\I(\vec k'\cdot\vec x-i\beta k' t)}\,,\\
 &=\mu\int\f{\diff^3 k}{(2\pi)^3}\p{k^2\abs{U(\vec k)}^2}\,,\\
+&=\mu\int\f{\diff^3 k}{(2\pi)^3}\p{\f{\Sigma_{zz}^2\sec^2\theta+\csc^2\theta(\Sigma_{yy}^2\csc^2\phi+\Sigma_{xx}^2\sec^2\phi)}{4\mu^2}}\,,\\
 \end{align}
-The integral is horribly divergent about the azimuth - there must have been a mistake...
+Assuming axial symmetry, we have $\Sigma_{xx}=\Sigma\cos^2\theta$, $\Sigma_{yy}=\Sigma\sin^2\theta$, and $\Sigma_{zz}=-\Sigma$. Hence, 
+\begin{align}
+E&=\mu\int\f{\diff^3 k}{(2\pi)^3}\Sigma^2\p{\f{\sec^2\theta+\csc^2\theta}{4\mu^2}}\,,\\
+&=\f{1}{\mu}\int\f{\diff^3 k}{(2\pi)^3}\Sigma^2\csc^2(2\theta)\,,\\
+&=\f{1}{\mu}\int\f{\diff k\diff\theta}{(2\pi)^2}\Sigma^2k^2\csc^2(2\theta)\,.
+\end{align}
 

### 2016-07-07 Macro Impacts Revised.tex
Small Correction
Added a convincing argument
The choice of Sigmaxx=Sigma Cos^2theta etc is justified by performing a
rotation and showing that the stress tensor is mapped to itself.
Correction
Upper bound on Delta r

@@
 % Title
-\title{Homework}
-\author{David Cyncynates \\ dcc57@case.edu}
+\title{Macro Impacts}
 \date{\today}
@@
 It is wrong, however, to assume that the wave evolves linearly close to the source.
-Modes will be coupled to one another, and our expression (25) will only hold in a small neighborhood of the event.
+Modes will be coupled to one another, and our expression (24) will only hold in a small neighborhood of the event.
 Effects such as heating and rock fracturing will cause the high frequency modes in the shock to rapidly attenuate.
@@
 \end{align}
-The energy in the longest modes is, for $h\gg\lambda_0\gg r_0$
+A lower bound for $r_0$ is clearly 0, which sets an upper bound for $\Delta r$, i.e.
+\begin{align}
+\Delta r&\leq \f{\sqrt{2}p_0r_X}{\bar p}\,,\\
+&=\f{1}{\bar p}\sqrt{\f{2}{\pi}\f{K^2}{\lambda+2\mu}\abs{\td{E}{x}{}}}\,.
+\end{align}
+Plugging in some numbers (from below) yields
+\begin{align}
+\Delta r\leq 1.2\te{m}\,.
+\end{align}
+The energy in the longest modes is, for $h\gg\lambda_0\gg r_0+\Delta r$
 \begin{align}
@@
 &=\mu\int\f{\diff^3 k}{(2\pi)^3}\p{k^2\abs{U(\vec k)}^2}\,,\\
-&=\mu\int\f{\diff^3 k}{(2\pi)^3}\p{\f{\Sigma_{zz}^2\sec^2\theta+\csc^2\theta(\Sigma_{yy}^2\csc^2\phi+\Sigma_{xx}^2\sec^2\phi)}{4\mu^2}}\,,\\
+&=\mu\int\f{\diff^3 k}{(2\pi)^3}\p{\f{\Sigma_{zz}^2\sec^2\theta+\csc^2\theta(\Sigma_{yy}^2\csc^2\phi+\Sigma_{xx}^2\sec^2\phi)}{4\mu^2}}\,.
 \end{align}
-Assuming axial symmetry, we have $\Sigma_{xx}=\Sigma\cos^2\theta$, $\Sigma_{yy}=\Sigma\sin^2\theta$, and $\Sigma_{zz}=-\Sigma$. Hence, 
+Assuming axial symmetry, we have $\Sigma_{xx}=\Sigma\cos^2\phi$, $\Sigma_{yy}=\Sigma\sin^2\phi$, and $\Sigma_{zz}=-\Sigma$.
+Note that this choice is justified since the full stress tensor is invariant under rotations about the $z$-axis.
+Hence,
 \begin{align}
@@
 &=\f{1}{\mu}\int\f{\diff^3 k}{(2\pi)^3}\Sigma^2\csc^2(2\theta)\,,\\
-&=\f{1}{\mu}\int\f{\diff k\diff\theta}{(2\pi)^2}\Sigma^2k^2\csc^2(2\theta)\,.
+&=\f{1}{\mu}\int\f{\diff k\diff\theta}{(2\pi)^2}\Sigma^2k^2\csc^2(2\theta)\sin\theta\,,\\
+&=\f{1}{4\mu}\int\f{\diff k\diff\theta}{(2\pi)^2}\Sigma^2k^2\csc(\theta)\sec^2(\theta)\,.
 \end{align}
-
+In cartesian coordinates:
+\begin{align}
+E&=\f{1}{4\mu}\int\f{\diff^3 k}{(2\pi)^3}\Sigma^2\f{k^4}{(k_x^2+k_y^2)k_z^2}\,.
+\end{align}
+Something makes me think that $\csc^2(2\theta)$ should be absorbed into the definition of $\Sigma$, but I don't know how to show this.
+\section{}
+For a given macro of given cross-section and velocity, how much energy gets deposited into seismic waves that propagated unattenuated?
+A better question: as a function of the sensitivity of a seismometer, will the seismometers have measured the macro?
+Look at the lunar limits.
 \end{document}

### 2016-07-07 Macro Impacts Revised.tex
Good shit
Check out 37 and 38

@@
 \end{align}
-Reviewing a USGS document (Rock Failure and Earthquakes) suggests that $\bar p$ be set at $10^8$.
+Using the upper bound for $\Delta r$ from earlier
+\begin{align}
+\Xi&\geq\p{\f{K^2}{\lambda+2\mu}}\p{\f{4\pi}{3\bar p\lambda_0}}^2\abs{\td{E}{x}{}}\,.
+\end{align}
+Taking $\Delta r$ to be 0, we find
+\begin{align}
+\Xi&\leq\p{\f{K^2}{\lambda+2\mu}}\p{\f{3\pi}{2\bar p\lambda_0}}^2\abs{\td{E}{x}{}}\,.
+\end{align}
+\\\\
+%Reviewing a USGS document (Rock Failure and Earthquakes) suggests that $\bar p$ be set at $10^8$.
 To calculate $\Delta r$, notice that the Earth is initially displaced by $r_X$.
@@
 Thus
-\begin{align}
-\Xi&=\pi \f{(\bar p^2\pi \f{v_X^2}{\alpha^2}r_X^2(\lambda+2\mu)-18K^2\sigma_Xv_X^2\rho_{\oplus})^2}{144K^2(\lambda+2\mu)\rho_{\oplus}\bar p^2 \sigma_X v_X^2\lambda_0^2}\,,\\
-&=\p{\pi r_X v_X\f{\bar p^2 -18K^2}{12K\alpha\bar p \lambda_0}}^2\,.
-\end{align}
-Given the relative magnitudes of $\bar p$ and $K^2$,
-\begin{align}
-\Xi&=\p{\f{3\pi r_X v_XK}{2\alpha\bar p \lambda_0}}^2\,,\\
-&=\p{\f{K^2}{\lambda+2\mu}}\p{\f{3\pi}{2\bar p\lambda_0}}^2\abs{\td{E}{x}{}}\,.
-\end{align}
+%\begin{align}
+%\Xi&=\pi \f{(\bar p^2\pi \f{v_X^2}{\alpha^2}r_X^2(\lambda+2\mu)-18K^2\sigma_Xv_X^2\rho_{\oplus})^2}{144K^2(\lambda+2\mu)\rho_{\oplus}\bar p^2 \sigma_X v_X^2\lambda_0^2}\,,\\
+%&=\p{\pi r_X v_X\f{\bar p^2 -18K^2}{12K\alpha\bar p \lambda_0}}^2\,.
+%\end{align}
+%Given the relative magnitudes of $\bar p$ and $K^2$,
+%\begin{align}
+%\Xi&=\p{\f{3\pi r_X v_XK}{2\alpha\bar p \lambda_0}}^2\,,\\
+%&=\p{\f{K^2}{\lambda+2\mu}}\p{\f{3\pi}{2\bar p\lambda_0}}^2\abs{\td{E}{x}{}}\,.
+%\end{align}
 The following are the approximate quantities used
@@
 \end{align}
-These lead to the results
+These lead to the results, (using my estimation scheme $\Delta r=\f{v_X}{\alpha}r_X$ from earlier, which may be incorrect)
 \begin{align}

### 2016-07-09 Macro Impacts Revised.tex
Oh man, I hope this is correct

@@
 \begin{align}
-\Xi&\leq\p{\f{K^2}{\lambda+2\mu}}\p{\f{3\pi}{2\bar p\lambda_0}}^2\abs{\td{E}{x}{}}\,.
+\Xi&<\p{\f{K^2}{\lambda+2\mu}}\p{\f{3\pi}{2\bar p\lambda_0}}^2\abs{\td{E}{x}{}}\,.
 \end{align}
+Note the strict inequality: $\Delta r=0$ corresponds to $r_0=\infty$.
 \\\\
@@
 Look at the lunar limits.
+\pagebreak
+\section{P-Wave Vector Propagation}
+Observe, by Snell's law, we have that
+\begin{align}
+p=\f{r\sin\theta}{v}\,,
+\end{align}
+is constant along any fixed ray, and is given by the above form in a spherically symmetric velocity field.
+$\theta$ is the angle of incidence, $r$ is the distance from the origin, and $v$ is the velocity at radius $r$.
+Let $\sigma(s)$ be the parametrized curve followed by a p-wave.
+Then
+\begin{align}
+\cos\theta=\f{\hat r\cdot\dot\sigma(s)}{\|\sigma(s)\|}=\f{\sigma(s)\cdot\dot\sigma(s)}{\|\sigma(s)\|\|\dot\sigma(s)\|}\,.
+\end{align}
+From this we obtain
+\begin{align}
+\p{\f{pv}{r}}^2=1-\f{(\sigma\cdot\dot\sigma)^2}{(\|\sigma(s)\|\|\dot\sigma(s)\|)^2}\,,
+\end{align}
+If we denote the radial component as $r(s)$ and the angular component $\theta(s)$ we obtain the differential equation
+\begin{align}
+\p{\f{pv}{r}}^2=\f{r^2\dot \theta^2}{(\dot r^2+\dot\theta^2 r^2)}\,.
+\end{align}
+But observe, the velocity of the curve $\sigma$ is just the velocity in the medium, hence
+\begin{align}
+\p{\f{pv}{r}}^2=r^2\f{\dot \theta^2}{v^2}\,,
+\end{align}
+from which we obtain the equation for $\theta$,
+\begin{align}
+\dot \theta&=\f{p v^2}{r^2}
+\end{align}
+We now use the velocity definition to obtain an implicit equation for $r$. Observe
+\begin{align}
+v^2&=\dot r^2+\dot\theta^2r^2\,,\\
+&=\dot r^2+\f{p^2 v^4}{r^2}\,,
+\end{align}
+hence
+\begin{align}
+1&=\f{r\dot r}{\sqrt{v^2r^2-p^2v^4}}
+\end{align}
+This can be integrated directly, yielding
+\begin{align}
+s+C&=\int\f{r\diff r}{\sqrt{v^2r^2-p^2v^4}}\,.
+\end{align}
+In the case that $v$ is a power law, i.e.
+\begin{align}
+v(r)&=v_0\p{\f{r_0}{r}}^\alpha
+\end{align}
+we can directly integrate for integer $\alpha$, yielding
+\begin{align}
+s+C&=\f{r^{2\alpha}r_0^{-2\alpha}\sqrt{r^{-4\alpha}r_0^{2\alpha}v_0^2(r^{2+2\alpha}-p^2r_0^{2\alpha}v_0^2)}}{v_0^2(1+\alpha)}\,.
+\end{align}
+It is possible to invert this equation for any particular $\alpha$. One solution which holds for all $\alpha$ is
+\begin{align}
+r(s)&=r_0^{\f{\alpha}{1+\alpha}}v_0^{\f{1}{1+\alpha}}(p^2+(C+s)^2(1+\alpha)^2)^{\f{1}{2(1+\alpha)}}\,.
+\end{align}
+We thus obtain the following expression for $\theta$:
+\begin{align}
+\theta(s)&=\f{1}{1+\alpha}\arctan\ps{\f{1+\alpha}{p}(C+s)}+\theta_0
+\end{align}
+WOAH!
 \end{document}

### 2016-07-11 Macro Impacts Revised.tex
Woah dude cool stuff man

@@
 \begin{align}
-\Xi&\geq\p{\f{K^2}{\lambda+2\mu}}\p{\f{4\pi}{3\bar p\lambda_0}}^2\abs{\td{E}{x}{}}\,.
+\Xi&\geq\f{16}{9}\p{\f{K^2}{\lambda+2\mu}}\p{\f{\pi}{\bar p\lambda_0}}^2\abs{\td{E}{x}{}}\,.
 \end{align}
@@
 \begin{align}
-\Xi&<\p{\f{K^2}{\lambda+2\mu}}\p{\f{3\pi}{2\bar p\lambda_0}}^2\abs{\td{E}{x}{}}\,.
+\Xi&<\f{9}{4}\p{\f{K^2}{\lambda+2\mu}}\p{\f{\pi}{\bar p\lambda_0}}^2\abs{\td{E}{x}{}}\,.
 \end{align}
@@
 \begin{align}
-\dot \theta&=\f{p v^2}{r^2}
+\dot \theta&=\pm\f{p v^2}{r^2}
 \end{align}
@@
 \begin{align}
-1&=\f{r\dot r}{\sqrt{v^2r^2-p^2v^4}}
+1&=\pm\f{r\dot r}{\sqrt{v^2r^2-p^2v^4}}
 \end{align}
@@
 \begin{align}
-s+C&=\int\f{r\diff r}{\sqrt{v^2r^2-p^2v^4}}\,.
+s+C&=\pm\int\f{r\diff r}{\sqrt{v^2r^2-p^2v^4}}\,.
 \end{align}
@@
 \begin{align}
-r(s)&=r_0^{\f{\alpha}{1+\alpha}}v_0^{\f{1}{1+\alpha}}(p^2+(C+s)^2(1+\alpha)^2)^{\f{1}{2(1+\alpha)}}\,.
+r(s,\alpha)&=r_0^{\f{\alpha}{1+\alpha}}v_0^{\f{1}{1+\alpha}}(p^2+(C+s)^2(1+\alpha)^2)^{\f{1}{2(1+\alpha)}}\,.
 \end{align}
@@
 \begin{align}
-\theta(s)&=\f{1}{1+\alpha}\arctan\ps{\f{1+\alpha}{p}(C+s)}+\theta_0
+\theta(s,\alpha)&=\f{1}{1+\alpha}\arctan\ps{\f{1+\alpha}{p}(C+s)}+\theta_0
 \end{align}
-WOAH!
+WOAH! We expect straight lines when $\alpha=0$. Let's check:
+\begin{align}
+r(s,0)&=v_0\sqrt{p^2+(C+s)^2}\,,\\
+\theta(s,0)&=\arctan\ps{\f{C+s}{p}}+\theta_0
+\end{align}
+Setting $\theta_0$ to zero reveals the equation for a vertical line. Thus, adding $\theta_0$ rotates the line, and $p$ sets the initial distance from the origin.
+\\\\
+Now we consider the realistic velocity distribution $v(r)=a^2-b^2r^2$. Proper application of mathematica to the above formulas reveals
+\begin{align}
+r(s)&=\f{a\sqrt{b^2-2be^{2ab(s+C)}+e^{4ab(s+C)}+4a^2b^4p^2}}{b\sqrt{b^2+2be^{2ab(s+C)}+e^{4ab(s+C)}+4a^2b^4p^2}}\,,\\
+\theta(s)&=\arctan\ps{\f{-b^2+e^{4ab(s+C)}+4a^2b^4p^2}{4ab^3p}}+\theta_0
+\end{align}
+Qualitatively, these appear to be arcs of circles which touch the boundary $r=\f ab$ at right angles.
+It would be nice to double check this.
+If that is the case, then this is an instance of rays tracing out geodesics in the Poincare disk.
+\pagebreak
+
+We now want to calculate the distribution of rays about the perimeter of a circle.
+In essence, we want to know $\diff\theta(R_{\te{earth}})$ as a function of $p$ and $\theta_0$.
+First we pick a point $p$ and direction $\psi$.
+we now parametrize all ray trajectories passing through this point by $\psi$.
+We now fix a $\psi$ and add to it $\delta\psi$, chosen small enough so that the two corresponding trajectories are close together.
+We then calculate $\delta\theta(R_{\te{earth}})$, the angular distance between the two rays as measured from the origin when they are at the radius of the earth.
+\\\\
+TO DO: Parametrize the rays through a point.
+Get the final parameter $s(R_{\te{earth}})$ as a function of the angle through the point.
+Then figure out how a small change in the initial angle changes the final angle.
+Get an approximate model for the velocity field through the earth.
+
+%\pagebreak
+%Meeting Agenda: Found bounds for $\Xi$. We need to map intensity to the surface - how? Do we make a generous over estimate again? If so, how should we approach it?
 \end{document}

### 2016-07-12 Macro Impacts Revised.tex
Melt Zone stuff
Added the preliminaries of computing the partition of the energy of a
projectile impact into kinetic, elastic, and plastic energy terms of
the target.

@@
 
+\section{Melt Zone}
+As derived in "A time dependent model for long-rod penetration" the plastic zone (i.e. the melt zone) around an impacting projectile is given by $\alpha*R$, where $\alpha$ is given by 
+\begin{align}
+(1+\frac{\rho_t u^2}{Y_t})\sqrt{K_t - \rho_t \alpha^2 u^2} = (1+\frac{\rho_t \alpha^2 u^2}{2G_t})\sqrt{K_t - \rho_t u^2}.
+\end{align}
+where $u$ is the velocity of the projectile (i.e.
+the macro), $\rho_t$, $K_t$, $G_t$ and $Y_t$ are the density, bulk modulus, sheer modulus, and flow stress of the target (i.e.
+earth or the moon) respectively.
+
+The connection between the energy of the projectile and the value $\alpha*R$ is given in the paper posted "Hypervelocity penetration modeling- momentum vs.
+energy and energy transfer mechanisms".
+A derivation is given for the decomposition of the energy of a projectile into kinetic, elastic and plastic terms in, for example, equations 32, 33, and 38.
+
+Note that the results in the section "Penetration" in this paper "Hypervelocity penetration..." are for eroding rods -- but macro doesn't erode.
+If we decided to use equation 39 and the resulting equations which partition the energy of the impact into kinetic, elastic and plastic energy terms of the target (i.e.
+earth or moon), we'd set u = v, and s = 0 to eliminate the "eroding" effect.
+
 %\pagebreak

### 2016-07-12 Macro Impacts Revised.tex
Poincare

@@
 \end{align}
-Qualitatively, these appear to be arcs of circles which touch the boundary $r=\f ab$ at right angles.
-It would be nice to double check this.
-If that is the case, then this is an instance of rays tracing out geodesics in the Poincare disk.
+These are arcs of circles which touch the boundary $r=\f ab$ at right angles.
+That is, the trajectory of rays is given by geodesics in the Poincare disk.
+This can be seen easily by inspection of the metric a modified Poincare Disk:
+\begin{align}
+\diff s^2&=\f{\sum_i\diff x_i^2}{\p{a^2-b^2\sum_i x_i^2}^2}\,,\\
+&=\f{\sum_i\diff x_i^2}{\p{a^2-b^2\sum_i x_i^2}^2}\,,\\
+&=\f1{v^2}\sum_i\diff x_i^2
+\end{align}
 \pagebreak
@@
 \section{Melt Zone}
-As derived in "A time dependent model for long-rod penetration" the plastic zone (i.e. the melt zone) around an impacting projectile is given by $\alpha*R$, where $\alpha$ is given by 
+As derived in ''A time dependent model for long-rod penetration" the plastic zone (i.e. the melt zone) around an impacting projectile is given by $\alpha*R$, where $\alpha$ is given by 
 \begin{align}
@@
 If we decided to use equation 39 and the resulting equations which partition the energy of the impact into kinetic, elastic and plastic energy terms of the target (i.e.
-earth or moon), we'd set u = v, and s = 0 to eliminate the "eroding" effect.
+earth or moon), we'd set $u = v$, and $s = 0$ to eliminate the "eroding" effect.
 

### 2016-07-13 Macro Impacts Revised.tex
Update

@@
 That is, the trajectory of rays is given by geodesics in the Poincare disk.
-This can be seen easily by inspection of the metric a modified Poincare Disk:
+This can be seen easily by inspection of the metric a modified Poincare Sphere:
 \begin{align}
@@
 \end{align}
+It is then obvious that $b=0$ corresponds to straight lines.
+The importance of this observation is that $b\approx 10^{-7}\te{s}^{-1}$ and $a\approx 10\te{km s}^{-1}$, so the radius of the Poincare sphere corresponding to the trajectories of $p$-waves in earth is approximately $10^8\te{km}$, while the earth is of radius $10^3\te{km}$.
+Hence, the smallest radius of curvature of an arc will be roughly $10^{-5}\te{km}$.
+Thus, it is a reasonable first approximation to take the seismic waves to propagate in straight lines.
 \pagebreak

### 2016-07-14 Macro Impacts Revised.tex
It seems that we can't neglect the bending anywhere but the core.

--- 2016-07-12 Macro Impacts Revised.tex
@@
 \end{align}
+It is then obvious that $b=0$ corresponds to straight lines.
+The importance of this observation is that $b^2\approx 10^{-7}\te{s}^{-1}$ and $a^2\approx 10\te{km s}^{-1}$, so the radius of the Poincare sphere corresponding to the trajectories of $p$-waves in earth is approximately $7\times10^3-1\times 10^4\te{km}$, while the earth is of radius $10^3\te{km}$.
+In particular, for the different layers of the earth, the radius of the layer's outer boundary and its corresponding Poincare sphere is 7.0 for the inner core, 2.0 for the outer core, and 1.8 for the mantle.
+Thus, it is reasonable to approximate the trajectories of $P$-waves in the inner core as straight lines, but necessary to treat those in the other layers as bending.
+\\\\
+It is clear that numerical methods will be necessary to get an answer. We will now consider a sequence of increasingly realistic models. I will begin typing up the first few tomorrow.
+
 \pagebreak
-
-We now want to calculate the distribution of rays about the perimeter of a circle.
-In essence, we want to know $\diff\theta(R_{\te{earth}})$ as a function of $p$ and $\theta_0$.
-First we pick a point $p$ and direction $\psi$.
-we now parametrize all ray trajectories passing through this point by $\psi$.
-We now fix a $\psi$ and add to it $\delta\psi$, chosen small enough so that the two corresponding trajectories are close together.
-We then calculate $\delta\theta(R_{\te{earth}})$, the angular distance between the two rays as measured from the origin when they are at the radius of the earth.
-\\\\
-TO DO: Parametrize the rays through a point.
-Get the final parameter $s(R_{\te{earth}})$ as a function of the angle through the point.
-Then figure out how a small change in the initial angle changes the final angle.
-Get an approximate model for the velocity field through the earth.
-
 \section{Melt Zone}

### 2016-07-14 Macro Impacts Revised.tex
Small clarification.

@@
 The importance of this observation is that $b^2\approx 10^{-7}\te{s}^{-1}$ and $a^2\approx 10\te{km s}^{-1}$, so the radius of the Poincare sphere corresponding to the trajectories of $p$-waves in earth is approximately $7\times10^3-1\times 10^4\te{km}$, while the earth is of radius $10^3\te{km}$.
-In particular, for the different layers of the earth, the radius of the layer's outer boundary and its corresponding Poincare sphere is 7.0 for the inner core, 2.0 for the outer core, and 1.8 for the mantle.
+In particular, for the different layers of the earth, the ratio radius of the layer's outer boundary and the radius of its corresponding Poincare sphere is 7.0 for the inner core, 2.0 for the outer core, and 1.8 for the mantle.
 Thus, it is reasonable to approximate the trajectories of $P$-waves in the inner core as straight lines, but necessary to treat those in the other layers as bending.

### 2016-07-16 Macro Impacts Revised.tex
Realistic Stuff Beginning

@@
 
-%\pagebreak
-%Meeting Agenda: Found bounds for $\Xi$. We need to map intensity to the surface - how? Do we make a generous over estimate again? If so, how should we approach it?
+\pagebreak
+\section{Realistic Model}
+Since I have realized that the curving of rays is non-negligible, Professor Tolley has suggested doing a realistic treatment of the problem.
+The displacement potential satisfies the inhomogeneous wave equation
+\begin{align}
+-\f{f}{\rho}&=v(r)^2\nabla^2\phi-\partial_t^2\phi\,,
+\end{align}
+where $v(r)=a^2-b^2r^2$.
+Note, $b$ is about 8 orders of magnitude smaller than a, so that the background varies slowly with respect to the frequency of the waves so the WKB approximation is appropriate.
+Denote
+\begin{align}
+\hat L=v(r)^2\f{1}{r^2}\partial_r(r^2\partial_r)-\f{1}{r^2}(l(l+1))+\omega^2\,,
+\end{align}
+It is easy to see that $\hat L$ is Hermitian since it can be put in Sturm--Liouville form when stated as an eigenvalue problem
+\begin{align}
+-\f{v(r)^2}{r^2}\ps{\partial_r(r^2\partial_r)+\f{r^2\omega^2-l(l+1)}{v(r)^2}}\phi=\lambda\phi\,.
+\end{align}
+Call the expression in the bracket on the left hand side $\hat L'$.
+We now impose finite boundary conditions, i.e.
+that the 0th and 1st derivatives of a solution vanish at $R_E$.
+Denote the eigenfunction corresponding to $\lambda$ as $\phi_\lambda$.
+Define the $L^2$ inner product
+\begin{align}
+\gen{f,g}=\int_0^{R_E}\diff r \f{v(r)^2}{r^2}\bar f(r)g(r)\,,
+\end{align}
+with respect to which $\hat L'$ is self-adjoint. We now employ the WKB ansatz (where $\delta\ll \f{a^2}{b^2R_E^2}$ *this is a guess - think about it!)
+\begin{align}
+\phi_\lambda(r)=\exp\p{\f1\delta\sum_{n=0}^{\infty}\delta^nS_{\lambda n}(r)}\,,
+\end{align}
+and hence (note that $\delta$ is just an auxiliary variable that we will absorb into $S$ at the end of the calculation)
+\begin{align}
+\partial_r \phi_\lambda(r)&=\p{\f1\delta\sum_{n=0}^{\infty}\delta^nS_{\lambda n}'(r)}\phi_\lambda(r)\,,\\
+&\sim\f1\delta S_{\lambda0}'(r)\phi_\lambda(r)\,,\\
+\partial_r^2\phi_\lambda(r)&=\p{\f1\delta\sum_{n=0}^{\infty}\delta^nS_{\lambda n}''(r)}\phi_\lambda(r)+\p{\f1\delta\sum_{n=0}^{\infty}\delta^nS_{\lambda n}'(r)}^2\phi_\lambda(r)\,,\\
+&\sim\f1\delta S_{\lambda0}''(r)\phi_\lambda(r)+\f1{\delta^2}S_{\lambda0}'^2(r)\phi_\lambda(r)+\f{2}{\delta}S_{\lambda0}'(r)S_{\lambda1}'(r)\phi_\lambda(r)\,.
+\end{align}
+Thus
+\begin{align}
+r^2\p{\f1\delta S_{\lambda0}''(r)+\f1{\delta^2}S_{\lambda0}'^2(r)+\f{2}{\delta}S_{\lambda0}'(r)S_{\lambda1}'(r)}+2r\f1\delta S_{\lambda0}'(r)=-\f{r^2(\lambda-\omega^2)+l(l+1)}{v(r)^2}\,.
+\end{align}
+As we take $\delta$ to zero, the dominant balance is
+\begin{align}
+r^2 S'^2_{\lambda 0}(r)=-\f{r^2(\lambda-\omega^2)+l(l+1)}{v(r)^2}\,,
+\end{align}
+from which we obtain
+\begin{align}
+S_{\lambda 0}(r)=C_0\pm\I\f{\sqrt{(b^2l(l+1)+a^2(\lambda-\omega^2))v(r)}}{a^2b}\te{AppellF1}\ps{\f12,-\f12,1,\f32,\f{(\lambda-\omega^2)v(r)}{b^2l(l+1)+a^2(\lambda-\omega^2)},\f{v(r)}{a^2}}\,,
+\end{align}
+The first order contribution is then determined by
+\begin{align}
+S_{\lambda1}'(r)=-\f{1}{r}-\f{S_{\lambda0}''(r)}{2S_{\lambda0}'(r)}\,.
+\end{align}
+The solution is quite simple
+\begin{align}
+S_{\lambda1}(r)=C_1-\f14\ln\ps{\f{r^2\ps{l(l+1)+r^2(\lambda-\omega^2)}}{v(r)}}\,.
+\end{align}
+Hence, the eigenfunctions are, semiclassically
+\begin{align}
+\notag\phi_\lambda&=K_1\ps{\f{r^2\ps{l(l+1)+r^2(\lambda-\omega^2)}}{v(r)}}^{-1/4}e^{+\I\f{\sqrt{(b^2l(l+1)+a^2(\lambda-\omega^2))v(r)}}{a^2b}\te{AppellF1}\ps{\f12,-\f12,1,\f32,\f{(\lambda-\omega^2)v(r)}{b^2l(l+1)+a^2(\lambda-\omega^2)},\f{v(r)}{a^2}}}\\
+&+K_2\ps{\f{r^2\ps{l(l+1)+r^2(\lambda-\omega^2)}}{v(r)}}^{-1/4}e^{-\I\f{\sqrt{(b^2l(l+1)+a^2(\lambda-\omega^2))v(r)}}{a^2b}\te{AppellF1}\ps{\f12,-\f12,1,\f32,\f{(\lambda-\omega^2)v(r)}{b^2l(l+1)+a^2(\lambda-\omega^2)},\f{v(r)}{a^2}}}\,.
+\end{align}
+Now we demand that $\phi$
 \end{document}

### 2016-07-17 Macro Impacts Revised.tex
Updating Stuff

--- 2016-07-14 Macro Impacts Revised.tex
@@
 
-%\pagebreak
-%Meeting Agenda: Found bounds for $\Xi$. We need to map intensity to the surface - how? Do we make a generous over estimate again? If so, how should we approach it?
+\pagebreak
+\section{Realistic Model}
+Since I have realized that the curving of rays is non-negligible, Professor Tolley has suggested doing a realistic treatment of the problem.
+The displacement potential satisfies the inhomogeneous wave equation
+\begin{align}
+-\f{f}{\rho}&=v(r)^2\nabla^2\phi-\partial_t^2\phi\,,
+\end{align}
+where $v(r)=a^2-b^2r^2$.
+Note, $b^2$ is several orders of magnitude smaller than $a^2$, so that the background varies slowly with respect to the frequency of the waves so the WKB approximation is appropriate.
+Denote
+\begin{align}
+\hat L=\f{v(r)^2}{r^2}\ps{\partial_r(r^2\partial_r)-(l(l+1))}+\omega^2\,,
+\end{align}
+It is easy to see that $\hat L$ is Hermitian since it can be put in Sturm--Liouville form when stated as an eigenvalue problem
+\begin{align}
+-\f{v(r)^2}{r^2}\ps{\partial_r(r^2\partial_r)+\p{\f{r^2}{v(r)^2}\omega^2-l(l+1)}}\phi=\lambda\phi\,.
+\end{align}
+Or, in another rearrangement:
+\begin{align}
+&\ps{\partial_r(r^2\partial_r)+\p{\lambda\f{r^2}{v(r)^2}+\ps{\f{r^2}{v(r)^2}\omega^2-l(l+1)}}}\phi=0\,,\\
+&(s(r)\phi'(r))'+\p{\lambda\rho(r)-q(r)}\phi(r)=0\,.
+\end{align}
+where
+\begin{align}
+s(r)&=r^2\,,\\
+\rho(r)&=\f{r^2}{v(r)^2}\,,\\
+q(r)&=\f{r^2}{v(r)^2}\omega^2-l(l+1)\,.
+\end{align}
+$\rho$ is known as the weight function.
+To satisfy the Sturm--Liouville theorem, $s,\rho,q$ must be continuous on the interval $[0,\f ab]$, and $s,\rho$ positive-valued on $(0,\f ab)$.
+Clearly this is indeed the case.
+Two solutions $\phi_1$ and $\phi_2$ are orthogonal with respect to the Sturm--Liouville equation if
+\begin{align}
+\int_0^{\f ab}\diff r\rho(r)\phi_1(r)\phi_2(r)=0\,.
+\end{align}
+Two eigenfunctions $\phi_1$ and $\phi_2$ are orthogonal if the boundary conditions satisfy
+\begin{align}
+s(r)(\phi_1(r)\phi_2'(r)-\phi_1'(r)\phi_2(r))\vert_0^{\f ab}=0\,.
+\end{align}
+Since $s(0)=0$, we must only be concerned with the behavior of $\phi$ at $\f ab$.
+A brief check will verify that the eigenvectors go to 0 at $\f ab$ hence the our solutions are orthogonal with respect to $\rho$.
+Note that $s(0)\rho(0)=0$ hence the equation is singular, and our eigenvalues may be complex.
+\\\\
+Observe that
+\begin{align}
+\delta(\lambda-\lambda')=\int_0^{\f ab}\diff r\rho(r)\phi_{\lambda}(r)\phi_{\lambda'}(r)\,,
+\end{align}
+hence, since any function can be decomposed in terms of these eigenfunctions
+\begin{align}
+\delta(r-r')&=\int\diff\lambda f_{\lambda}\phi_{\lambda}(r)\,,\\
+\int\diff r\rho(r) \phi_{\lambda'}(r)\delta(r-r')&=\int\diff r \rho(r)\phi_{\lambda'}(r)\int\diff\lambda f_{\lambda}\phi_{\lambda}(r)\,,\\
+\rho(r')\phi_{\lambda'}(r')&=\int\diff\lambda f_\lambda\int\diff r\rho(r)\phi_{\lambda}(r)\phi_{\lambda'}(r)\,,\\
+\rho(r')\phi_{\lambda'}(r')&=\int\diff\lambda f_\lambda\delta(\lambda-\lambda')\,,\\
+\rho(r')\phi_{\lambda'}(r')&=f_{\lambda'}\,,\\
+\end{align}
+Hence
+\begin{align}
+\delta(r-r')=\int\diff\lambda\rho(r')\phi_\lambda(r')\phi_\lambda(r)\,.
+\end{align}
+\\\\
+Call
+\begin{align}
+u=\f{\sqrt{a^2b^2-\lambda-\omega^2}}{2ab}\,.
+\end{align}
+The exact solution to the eigenvalue problem is
+\begin{align}
+\f{v(r)^{\f{1+u}{2}}}{ab^2 r^{l+1}}\p{a C_1 2\te{F}1\ps{\f12u-1,\f12(1+u),\f12-l,\p{\f{b}{a}r}^2}+\I br\p{-\f{b}{a}r}^{2l} C_22\te{F}1\ps{1+l+\f12 u,\f12(1+u),\f32+l,\p{\f ba r}^2}}\,.
+\end{align}
+Regularity at the origin fixes $C_1=0$. The solution is then
+\begin{align}
+\phi_\lambda(r)=\I C\f{b^{2l-1}}{a^{2l+1}}r^lv(r)^{\f{1+u}{2}}\p{\,2\te{F}1\ps{1+l+\f12 u,\f12(1+u),\f32+l,\p{\f ba r}^2}}\,.
+\end{align}
+We now employ the WKB ansatz (where $\delta\ll \f{a^2}{b^2R_E^2}$ *this is a guess - think about it!)
+\begin{align}
+\phi_\lambda(r)=\exp\p{\f1\delta\sum_{n=0}^{\infty}\delta^nS_{\lambda n}(r)}\,,
+\end{align}
+and hence (note that $\delta$ is just an auxiliary variable that we will absorb into $S$ at the end of the calculation)
+\begin{align}
+\partial_r \phi_\lambda(r)&=\p{\f1\delta\sum_{n=0}^{\infty}\delta^nS_{\lambda n}'(r)}\phi_\lambda(r)\,,\\
+&\sim\f1\delta S_{\lambda0}'(r)\phi_\lambda(r)\,,\\
+\partial_r^2\phi_\lambda(r)&=\p{\f1\delta\sum_{n=0}^{\infty}\delta^nS_{\lambda n}''(r)}\phi_\lambda(r)+\p{\f1\delta\sum_{n=0}^{\infty}\delta^nS_{\lambda n}'(r)}^2\phi_\lambda(r)\,,\\
+&\sim\f1\delta S_{\lambda0}''(r)\phi_\lambda(r)+\f1{\delta^2}S_{\lambda0}'^2(r)\phi_\lambda(r)+\f{2}{\delta}S_{\lambda0}'(r)S_{\lambda1}'(r)\phi_\lambda(r)\,.
+\end{align}
+Thus
+\begin{align}
+r^2\p{\f1\delta S_{\lambda0}''(r)+\f1{\delta^2}S_{\lambda0}'^2(r)+\f{2}{\delta}S_{\lambda0}'(r)S_{\lambda1}'(r)}+2r\f1\delta S_{\lambda0}'(r)=-\p{\f{r^2}{v(r)^2}(\lambda+\omega^2)-l(l+1)}\,.
+\end{align}
+As we take $\delta$ to zero, the dominant balance is
+\begin{align}
+S'_{\lambda 0}(r)=\I\delta\sqrt{\p{\f{(\lambda+\omega^2)}{v(r)^2}-\f{l(l+1)}{r^2}}}\,,
+\end{align}
+The first order contribution is then determined by
+\begin{align}
+S_{\lambda1}'(r)=-\f{1}{r}-\f{S_{\lambda0}''(r)}{2S_{\lambda0}'(r)}\,.
+\end{align}
+The WKB Approximation may not be necessary given that we have a relatively easy-to-write exact solution in terms of the hypergeometric 2F1 function.
+Moreover, we are not interested in the particle-like behavior of the waves - we are only interested in the energy density on a surface.
+Now, supposing we've properly normalized $\phi_\lambda$, we have the Green's function
+\begin{align}
+G(r,r')=\int_{-\infty}^{\infty}\diff\omega\sum_{l=1}^{\infty}\sum_{m=-l}^l\int\diff\lambda\rho(r')\f{\bar \phi_{\lambda}(r)\phi_{\lambda}(r')}{\lambda+\I\epsilon}Y_{lm}(\theta,\phi)e^{\I m\phi}e^{\I\omega t}\,.
+\end{align}
+In order to find $\mu$, 
+Now, we wish to consider the source proportional to $\delta(z-v_X t)=\delta(\theta)\delta(\phi)\delta(r-v_X t)$. The solution is then
+\begin{align}
+\int_V\diff V'\int_{-\infty}^{\infty}\diff t' G(r,r')\delta(r'-v_X t')
+\end{align}
 \end{document}

### 2016-07-18 Realistic Macro Impacts.tex
Some more good stuff.
The Green’s function is contained in the Realistic file.

\documentclass{article}

% Packages

\usepackage{fullpage}
\usepackage{amsmath, amsthm, amsfonts, amssymb, mathtools, calrsfs, tensor, physics, MnSymbol,tikz-cd}
\usepackage[mathscr]{euscript}
\usepackage{graphicx}
\graphicspath{ {images/} }
\usepackage{enumitem}
\setlist[description]{font=\normalfont}

% Custom Commands

\newcommand*\diff{\mathop{}\!\mathrm{d}}
\newcommand*\Diff[1]{\mathop{}\!\mathrm{d^#1}}
\newcommand*\nrml{\vartriangleleft}
\newcommand*\scr[1]{\mathscr{#1}}
\newcommand*\bb[1]{\mathbb{#1}}
\newcommand*\la{\langle}
\newcommand*\ra{\rangle}
\newcommand*\gen[1]{\langle #1 \rangle}
\newcommand*\x{\times}
\newcommand*\st{\text{ s.t. }}
\newcommand*\ord[1]{\left\vert#1\right\vert}
\newcommand*\aut{\text{Aut}}
\newcommand*\lcm{\text{lcm}}
\newcommand*\mcal{\mathcal}
\newcommand*\es{\emptyset}
\newcommand*\im{\text{ Im }}
\newcommand*\N{\mathbb N}
\newcommand*\Z{\mathbb Z}
\newcommand*\R{\mathbb R}
\newcommand*\Q{\mathbb Q}
\newcommand*\C{\mathbb C}
\newcommand*\te[1]{\text{#1}}
\newcommand*\en[1]{\begin{enumerate}#1\end{enumerate}}
\newcommand*\e{\varepsilon}
\newcommand*\p[1]{\left(#1\right)}
\newcommand*\ps[1]{\left[#1\right]}
\newcommand*\pc[1]{\left\{#1\right\}}
\newcommand*\f[2]{\frac{#1}{#2}}
\newcommand*\mat[2]{\left(\begin{array}{#1}#2\end{array}\right)}
\newcommand*\ocross{\otimes}
\newcommand*\I{\te{i}}
\newcommand*\pd[3]{\frac{\partial^{#3} #1}{\partial {#2}^{#3}}}
\newcommand*\td[3]{\frac{d^{#3}#1}{d #2^{#3}}}
\newcommand*\m{\te{Mat}}
\newcommand*\End{\te{End}}
\newcommand*\irr{\te{Irr}}
\newcommand*\sgn{\te{sgn}}
\newcommand*\pn[2]{\left\|#1\right\|_{#2}}
\newcommand*\esssup{\te{ess sup}}
\newcommand*\essinf{\te{ess inf}}

% Miscellaneous

\newtheorem{theorem}{Theorem}
\usetikzlibrary{matrix,arrows,decorations.pathmorphing}

% Title
\title{Realistic Macro Impacts}
\author{David Cyncynates \\ dcc57@case.edu}
\date{\today}

\begin{document}
\maketitle
The velocity field in the Earth has the form $v(r)=a^2-b^2r^2$. The change in velocity occurs over several wavelengths of the oscillations we are concerned with, so a WKB approximation is appropriate if necessary. Since we are not concerned with the behavior of individual waves, it is not of analytic interest to pursue a semiclassical solution. We are most concerned with determining the Green's function of the wave equation so that we can consider a realistic source.

Our wave equation is of the form
\begin{align}
-\f f\rho=v(r)^2\nabla^2\phi-\partial_t^2\phi=D\phi\,.
\end{align}
Our differential operator is the sum of two Hermitian operators, and is therefore Hermitian itself. Its eigenvalues are the sum of the eigenvalues of its components. The eigenvalue problem we are interested in
\begin{align}
0=D u+\lambda u
\end{align}
can be reduced to a problem in a single variable since any function can be written in terms of a radial part and a sum over spherical harmonics. Moreover, we may Fourier transform in time, yielding
\begin{align}
u(\vec x,t)&=\sum_{l=0}^{\infty}\sum_{m=-l}^l\int\f{\diff\omega}{2\pi}\tilde u_{lm}(r,\omega)Y_{lm}(\theta,\phi)e^{\I\omega t}\,.
\end{align}
Converting (2) into spherical harmonics, we have
\begin{align}
\tilde D&=v(r)^2\ps{\nabla^2_r-\f{l(l+1)}{r^2}}+\omega^2\,,\\
&=\f{v(r)^2}{r^2}\ps{\partial_r(r^2\partial_r)-l(l+1)}+\omega^2\,,
\end{align}
and hence
\begin{align}
0&=\f{v(r)^2}{r^2}\ps{\partial_r(r^2\partial_r)-l(l+1)}\tilde u+\omega^2\tilde u+\lambda\tilde u.
\end{align}
An equation of the Sturm--Liouville type has the form
\begin{align}
0&=(s(r)\phi'(r))'+\p{\lambda\rho(r)-q(r)}\phi(r)
\end{align}
where $\rho$ is known as the weight function, $s,\rho,q$ must be continuous on the interval $[0,\f ab]$, and $s,\rho$ positive-valued on $(0,\f ab)$. Rewriting $\tilde D$ in clearer form
\begin{align}
0&=(r^2\tilde u')'+\pc{\lambda\f{r^2}{v(r)^2}-\ps{l(l+1)-\f{r^2}{v(r)^2}\omega^2}}\tilde u\,,
\end{align}
where we see that $s(r)=r^2$, $\rho(r)=\f{r^2}{v(r)^2}$, and $q(r)=l(l+1)-\rho(r)\omega^2$. Hence $\tilde D$ is a Sturm-Liouville operator. For the eigenfunctions of $D$ to be orthogonal, we must satisfy the homogeneous boundary conditions
\begin{align}
s(r)(\phi_1(r)\phi_2'(r)-\phi_1'(r)\phi_2(r))\vert_0^{\f ab}=0\,.
\end{align}
Assuming we have chosen suitable eigenfunctions,
\begin{align}
\delta(\lambda-\lambda')=\int\diff r\rho(r)\tilde u(r,\lambda)\tilde u(r,\lambda')\,.
\end{align}
Note, the spectrum of $\tilde D$ is continuous since the boundary conditions above are automatically satisfied when chosen properly.
\\\\
Now, assuming completeness, we may write
\begin{align}
\delta(r-r')&=\int\diff \lambda f(\lambda)\tilde u(r,\lambda)\,,\\
\rho(r')\bar{\tilde u}(r',\lambda')&=\int\diff r\rho(r) \bar{\tilde u}(r',\lambda')\int\diff \lambda f(\lambda)\tilde u(r,\lambda)\,,\\
&=f(\lambda')\,.
\end{align}
Hence
\begin{align}
\delta(r-r')&=\int\diff \lambda \rho(r')\bar {\tilde u}(r',\lambda)\tilde u(r,\lambda)\,.
\end{align}
Now that we know how to write $\delta$ in terms of eigenfunctions of $\tilde D$, we write the full $\delta$-function
\begin{align}
\delta(r-r')\delta(\Omega-\Omega')\delta(t-t')&=\sum_{\abs{m}\leq l\in\Z}\int\f{\diff\omega}{2\pi}\diff \lambda \rho(r')\tilde {\bar u}_{lm}(r',\lambda)\tilde u_{lm}(r,\lambda)\bar Y_{lm}(\Omega')Y_{lm}(\Omega)e^{-\I\omega (t'-t')}\,,\\
&=\sum\Delta
\end{align}
Applying $D$ to the right hand side yields
\begin{align}
D\sum\Delta=-\sum(\lambda+l(l+1)+\omega^2)\Delta
\end{align}
Hence the Green's function of the problem is
\begin{align}
G(x,x')=-\sum_{\abs{m}\leq l\in\Z}\int\f{\diff\omega}{2\pi}\diff \lambda \f{\rho(r')\tilde {\bar u}_{lm}(r',\lambda)\tilde u_{lm}(r,\lambda)\bar Y_{lm}(\Omega')Y_{lm}(\Omega)e^{-\I\omega (t'-t')}}{(\lambda+l(l+1)+\omega^2)}\,.
\end{align}
We now employ the WKB ansatz (where $\delta\ll \f{a^2}{b^2R_E^2}$ *this is a guess - think about it!)
\begin{align}
\phi_\lambda(r)=\exp\p{\f1\delta\sum_{n=0}^{\infty}\delta^nS_{\lambda n}(r)}\,,
\end{align}
\end{document}

### 2016-07-18 Realistic Macro Impacts.tex
Corrections to Green's Function
The old stuff is past the end of the document in the tex file.

@@
 \maketitle
+\section{The Green's Function}
+This should be correct. We have the differential equation
+\begin{align}
+v(r)^2\nabla^2\phi-\partial_t^2\phi=-\f{f}{\rho}
+\end{align}
+We want to write $\phi$ as eigenfunctions of the linear differential operator on the LHS. Fourier transforming in time $\phi\to\tilde\phi$, we may write an eigenvalue problem
+\begin{align}
+v(r)^2\nabla^2\tilde\phi+\lambda\tilde\phi=0\,.
+\end{align}
+Multiplying by $\f{r^2}{v(r)^2\tilde\phi}$ and supposing $\tilde\phi=R(r)Y(\Omega)$, we have
+\begin{align}
+\f{\partial_r(r^2\partial_r R)}{R}+\lambda\f{r^2}{v(r)^2}+\f{r^2\nabla_\Omega Y}{Y}=0
+\end{align}
+It is clear that $\f{r^2\nabla_\Omega Y}{Y}$ depends only on $\Omega$ and that the remaining terms only depend on $r$, hence the equation is separable, and our ansatz is justified.
+The solutions $Y$ are just the spherical harmonics with eigenvalues $r^2\nabla_{\Omega}Y=-l(l+1)Y$, $l\in\N\cup\{0\}$.
+$R$ obeys a more complicated equation
+\begin{align}
+\partial_r(r^2\partial_r R)+\lambda\f{r^2}{v(r)^2}R-l(l+1)R=0
+\end{align}
+which is just a Sturm--Liouville problem for the appropriate boundary conditions at $r=0$ and $r=\f ab$.
+The weight function is $\rho=\f{r^2}{v(r)^2}$.
+Since this equation is in terms of a Sturm--Liouville operator, its eigenfunctions form an orthogonal set with respect to $\rho$, i.e.
+\begin{align}
+\delta(\lambda-\lambda')=\int\diff r\rho(r) \bar R_\lambda(r)R_{\lambda'}(r)\,.
+\end{align}
+Assuming completeness of the eigenfunctions, we may write
+\begin{align}
+\delta(r-r')=\int\diff\lambda\rho(r)\bar R_\lambda(r)R_\lambda(r')\,.
+\end{align}
+We may decompose any function in terms of $R$, $Y$, and $e^{\I\omega t}$ as
+\begin{align}
+f(r,\Omega,t)=\sum_{l=0}^\infty\sum_{m=-l}^l\int\diff\lambda\diff\omega F_{lm}(\lambda,\omega)R_{\lambda l}(r)Y_{lm}(\Omega)e^{\I\omega t}\,.
+\end{align}
+Notice
+\begin{align}
+\ps{v(r)^2\nabla^2-\partial_t^2}\ps{R_\lambda(r)Y_{lm}(\Omega)e^{\I\omega t}}&=R_\lambda(r)Y_{lm}(\Omega)e^{\I\omega t}\ps{\f{v(r)^2\nabla_r^2R}{R}+\f{v(r)^2\nabla_\Omega^2Y}{Y}+\omega^2}\,,\\
+&=R_\lambda(r)Y_{lm}(\Omega)e^{\I\omega t}\ps{-\lambda+\f{v(r)^2}{r^2}l(l+1)-\f{v(r)^2}{r^2}l(l+1)+\omega^2}\,,\\
+&=R_\lambda(r)Y_{lm}(\Omega)e^{\I\omega t}\ps{-\lambda+\omega^2}\,,\\
+\end{align}
+Thus, we see that
+\begin{align}
+G(\vec r,t;\vec r',t')=\rho(r)\sum_{l=0}^\infty\sum_{m=-l}^l\int\diff\lambda\diff\omega\f{\bar R_{\lambda l}(r)R_{\lambda l}(r')\bar Y_{lm}(\Omega)Y_{lm}(\Omega') e^{\I\omega(t-t')}}{\omega^2-\lambda-\I\epsilon}\,.
+\end{align}
+
+\section{The Source}
+We must find an appropriate body force potential $f$.
+As a practice problem, let's consider $f=\nabla g=-4\pi G\ps{M\delta(\vec r-\vec vt)+\delta\rho}$ as in the detection of a small black hole problem, where $\delta\rho=-\rho\nabla u$, where $u$ is the displacement field.
+Then the source term of the wave equation is
+\begin{align}
+-\f f\rho=\f{4\pi M G}{\rho}\delta(\vec r-\vec vt)-4\pi G\phi
+\end{align}
+Since $f$ has a dependent variable in it, we need to slightly modify our Green's function. The eigenvectors $\tilde u$ of $\tilde D$ will now satisfy
+\end{document}
 The velocity field in the Earth has the form $v(r)=a^2-b^2r^2$.
@@
 \end{align}
-Note, the spectrum of $\tilde D$ is continuous since the boundary conditions above are automatically satisfied when chosen properly.
+Note, the spectrum of $\tilde D$ is continuous since the boundary conditions above are automatically satisfied when chosen at the endpoints $0$ and $\f ab$.
 \\\\
@@
 \delta(r-r')\delta(\Omega-\Omega')\delta(t-t')&=\sum_{\abs{m}\leq l\in\Z}\int\f{\diff\omega}{2\pi}\diff \lambda \rho(r')\tilde {\bar u}_{lm}(r',\lambda)\tilde u_{lm}(r,\lambda)\bar Y_{lm}(\Omega')Y_{lm}(\Omega)e^{-\I\omega (t'-t')}\,,\\
-&=\sum\Delta
+&=\sum\Delta\,.
 \end{align}
@@
 \begin{align}
-D\sum\Delta=-\sum(\lambda+l(l+1)+\omega^2)\Delta
+D\sum\Delta=-\sum(\lambda+l(l+1)+\omega^2)\Delta\,.
 \end{align}
@@
 \begin{align}
-G(x,x')=-\sum_{\abs{m}\leq l\in\Z}\int\f{\diff\omega}{2\pi}\diff \lambda \f{\rho(r')\tilde {\bar u}_{lm}(r',\lambda)\tilde u_{lm}(r,\lambda)\bar Y_{lm}(\Omega')Y_{lm}(\Omega)e^{-\I\omega (t'-t')}}{(\lambda+l(l+1)+\omega^2)}\,.
+G(x,x')=-\sum_{\abs{m}\leq l\in\Z}\int\f{\diff\omega}{2\pi}\diff \lambda \f{\rho(r')\tilde {\bar u}_{lm}(r',\lambda)\tilde u_{lm}(r,\lambda)\bar Y_{lm}(\Omega')Y_{lm}(\Omega)e^{-\I\omega (t-t')}}{\lambda-\I\epsilon}\,.
 \end{align}
@@
 \end{align}
-\end{document}
+\section{Corrections!}
+\begin{align}
+0&=(r^2\tilde u')'+\pc{\lambda\f{r^2}{v(r)^2}-\ps{l(l+1)-\f{r^2}{v(r)^2}(\omega^2+4\pi G)}}\tilde u\,.
+\end{align}
+The solution is
+\begin{align}
+\phi&=4\pi M G\int\diff^4 x G(x,x')\f{\delta(\vec r-\vec vt)}{\rho}\,,\\
+&=4\pi M G\int\diff t G(\vec v t,t;\vec r',t')\f1{\rho}\,.
+\end{align}
+$\rho$ is a function of radius, but for the purposes of checking my work, I'll treat it as constant.
+We now calculate $G$ in the case of $b=0$.
+I will do this two ways: first to calculate it with $b\neq 0$, perhaps in WKB, and then take the limit $b\to 0$, and to calculate $G$ with $b=0$ from the outset.

### 2016-07-20 Macro Impacts Revised.tex
Some more good stuff.
The Green’s function is contained in the Realistic file.
Test Again

--- 2016-07-14 Macro Impacts Revised.tex
@@
 \pagebreak
+\section{Numerical Methods}
+From symmetry, it is clear that it is enough to understand the behavior of rays from a point source to understand the propagation of rays in the whole sphere.
+Let $\vec p=(r,\theta)$ denote the position vector of our ray, whose initial coordinates are $\vec p(0)=(z,0)$.
+
+\pagebreak
 \section{Melt Zone}
@@
 earth or moon), we'd set $u = v$, and $s = 0$ to eliminate the "eroding" effect.
+\end{document}
 
-%\pagebreak
-%Meeting Agenda: Found bounds for $\Xi$. We need to map intensity to the surface - how? Do we make a generous over estimate again? If so, how should we approach it?
-\end{document}
+What is the area per year covered by these non-linear zones as a function of macro mass, volume etc (contour plot).

### 2016-07-21 Macro Impacts Revised.tex
Test for the final time
General Source
Something that Prof. Starkman anticipated from the beginning.

@@
 This approximation holds for $\lambda_0^2\gg\sigma_X$, which is appropriate for the case that $\lambda_0$ is on the order of kilometers and $\sigma_X$ is on the order of centimeters squared.
+\pagebreak
+\section{A General Pressure Wave}
+We now do the same calculation assuming that the pressure wave is of finite height, cylindrically symmetric, and of finite radial support.
+Moreover, we assume that the radial pressure distribution can be written as a taylor series.
+Write
+\begin{align}
+p=p_0f(r)\ps{\theta\p{z+\f h2}-\theta\p{z-\f h2}}
+\end{align}
+We may expand $f$ as
+\begin{align}
+f(r)&=\sum_{n=0}^\infty\f{f^{(n)}(r_0)}{n!}(r-r_0)^n\,,\\
+&=\sum_{n=0}^\infty\sum_{m=0}^n(-1)^{n-m}\binom{n}{m}\f{f^{(n)}(r_0)}{n!}r^{m}r_0^{n-m}\,.
+\end{align}
+We now Fourier transform
+\begin{align}
+P(\vec k)=\f{4\pi p_0}{k_z}\sin\p{\f{h k_z}{2}}\sum_{n=0}^\infty\sum_{m=0}^n\f{f^{(n)}(r_0)}{n!}\f{(-r_0)^{n-m}}{2+m}\ps{x^{2+m}\,_q\te{F}_p\p{\pc{1+\f m2},\pc{1,2+\f m2},-\f14 x^2 k_r^2}}_{x=a}^b\,,
+\end{align}
+where $_q\te{F}_p$ is the generalized hypergeometric function. We now convert to spherical coordinates in $k$-space, and write
+\begin{align}
+P(\vec k)=\f{4\pi p_0}{k\cos\theta}\sin\p{\f{h k\cos\theta}{2}}\sum_{n=0}^\infty\sum_{m=0}^n\f{f^{(n)}(r_0)}{n!}\f{(-r_0)^{n-m}}{2+m}\ps{x^{2+m}\,_q\te{F}_p\p{\pc{1+\f m2},\pc{1,2+\f m2},-\f14 x^2 k^2\sin^2\theta}}_{x=a}^b\,,
+\end{align}
+We now expand the hypergeometric function to first order (the first order term is zero, so all that remains is the zeroth order term)
+\begin{align}
+P(\vec k)&=\f{4\pi p_0}{k\cos\theta}\sin\p{\f{h k\cos\theta}{2}}\sum_{n=0}^\infty\sum_{m=0}^n\f{f^{(n)}(r_0)}{n!}\f{(-r_0)^{n-m}}{2+m}\ps{x^{2+m}}_{x=a}^b+\scr O(k^2)\,,\\
+&=\ps{\f{4\pi p_0}{k\cos\theta}\sin\p{\f{h k\cos\theta}{2}}x^2\underbrace{\sum_{n=0}^\infty\sum_{m=0}^n\f{f^{(n)}(r_0)}{n!}\f{(-r_0)^{n-m}}{2+m}x^{m}}_{f_1(x)}}_{x=a}^b+\scr O(k^2)\,,\\
+&=\f{4\pi p_0}{k\cos\theta}\sin\p{\f{h k\cos\theta}{2}}(b^2f_1(b)-a^2f_1(a))+\scr O(k^2)\,.
+\end{align}
+From this, we find that the energy in the lowest modes is
+\begin{align}
+E_{\te{propagated}}&=\f{\lambda+2\mu}{K^2}2p_0^2(b^2f_1(a)-a^2f_1(b))^2\p{-2k_0+k_0\cos(h k_0)+\f{\sin(h k_0)}{h}+h k_0^2\te{Si}(h k_0)}+\scr O(k_0^4)\,,\\
+&\approx_{h\gg k_0}\f{\lambda+2\mu}{K^2} \f{4 p_0^2h\pi^3(b^2 f_1(b)-a^2f_1(a))^2}{\lambda_0^2}\,.
+\end{align}
+Let's do some checks. First consider the basic cylinder pressure where $f=1$ on $[0,r_X]$. Then $f_1=\f12$, and we see that
+\begin{align}
+E&\approx\f{\lambda+2\mu}{K^2}\f{p_0^2h\pi^3r_X^4}{\lambda_0^2}\,,\\
+&=\f{\lambda+2\mu}{K^2}(p_0\sigma_X)^2\f{\pi h}{\lambda_0^2}\,,
+\end{align}
+which is exactly the result from before.
+Now consider $f(r)=\f{r-r_0}{\Delta r}$ on $[r_0,r_0+\Delta r]$.
+Then, taking the endpoint $r_0$ as the base of the Taylor series, $f_1(x)=\f{-r_0}{2\Delta r}+\f{x}{3\Delta r}$.
+Hence
+\begin{align}
+E&\approx\f{\lambda+2\mu}{K^2}\f{h p_0^2\pi^3\Delta r^2(3r_0+2\Delta r)^2}{9\lambda_0^2}
+\end{align}
+This is what we find out later! I'm legitimately surprised that I didn't make a mistake! Woo!
 \pagebreak
@@
 Let $\vec p=(r,\theta)$ denote the position vector of our ray, whose initial coordinates are $\vec p(0)=(z,0)$.
-
+We also insist that the tangent vector of $\vec p$ be at an angle $\alpha$ from the z axis.
 \pagebreak

### 2016-07-21 Macro Impacts Revised.tex
Rays Parametrized in Terms of Initial Condition

@@
 \end{align}
-We now expand the hypergeometric function to first order (the first order term is zero, so all that remains is the zeroth order term)
+We now expand the hypergeometric function to second order (the first order term is zero, so all that remains is the zeroth order term)
 \begin{align}
-P(\vec k)&=\f{4\pi p_0}{k\cos\theta}\sin\p{\f{h k\cos\theta}{2}}\sum_{n=0}^\infty\sum_{m=0}^n\f{f^{(n)}(r_0)}{n!}\f{(-r_0)^{n-m}}{2+m}\ps{x^{2+m}}_{x=a}^b+\scr O(k^2)\,,\\
-&=\ps{\f{4\pi p_0}{k\cos\theta}\sin\p{\f{h k\cos\theta}{2}}x^2\underbrace{\sum_{n=0}^\infty\sum_{m=0}^n\f{f^{(n)}(r_0)}{n!}\f{(-r_0)^{n-m}}{2+m}x^{m}}_{f_1(x)}}_{x=a}^b+\scr O(k^2)\,,\\
-&=\f{4\pi p_0}{k\cos\theta}\sin\p{\f{h k\cos\theta}{2}}(b^2f_1(b)-a^2f_1(a))+\scr O(k^2)\,.
+P(\vec k)&=\f{4\pi p_0}{k\cos\theta}\sin\p{\f{h k\cos\theta}{2}}\sum_{n=0}^\infty\sum_{m=0}^n\f{f^{(n)}(r_0)}{n!}\f{(-r_0)^{n-m}}{2+m}\ps{x^{2+m}}_{x=a}^b+\scr O(k)\,,\\
+&=\ps{\f{4\pi p_0}{k\cos\theta}\sin\p{\f{h k\cos\theta}{2}}x^2\underbrace{\sum_{n=0}^\infty\sum_{m=0}^n\f{f^{(n)}(r_0)}{n!}\f{(-r_0)^{n-m}}{2+m}x^{m}}_{f_1(x)}}_{x=a}^b+\scr O(k)\,,\\
+&=\f{4\pi p_0}{k\cos\theta}\sin\p{\f{h k\cos\theta}{2}}(b^2f_1(b)-a^2f_1(a))+\scr O(k)\,.
 \end{align}
@@
 From symmetry, it is clear that it is enough to understand the behavior of rays from a point source to understand the propagation of rays in the whole sphere.
-Let $\vec p=(r,\theta)$ denote the position vector of our ray, whose initial coordinates are $\vec p(0)=(z,0)$.
-We also insist that the tangent vector of $\vec p$ be at an angle $\alpha$ from the z axis.
+Let $\vec p=(r,\theta)$ denote the position vector of our ray, whose initial coordinates are $\vec p(0)=(x_0,0)$.
+We also insist that the tangent vector of $\vec p$ be at an angle $\alpha$ from the x axis.
+The parametrization in terms of these initial conditions is
+\begin{align}
+r(s)&=\f{a}{b}\sqrt{\f{a^2\p{e^{2abs}-1}^2+b^2\p{e^{2abs}+1}^2x_0^2+2(-1)^{s_1}ab\p{e^{4abs}-1}x_0\abs{\cos\alpha}}{a^2\p{e^{2abs}+1}^2+b^2\p{e^{2abs}-1}^2x_0^2+2(-1)^{s_1}ab\p{e^{4abs}-1}x_0\abs{\cos\alpha}}}\,,\\
+\notag\theta(s)&=\arccot\ps{\f{4(-1)^{s_2}abx_0(a^2-b^2x_0^2)\sin\alpha}{4a^2b^2(1+e^{4abs})x_0^2+4(-1)^{s_2}abe^{4abs}x_0(a^2+b^2x_0^2)\cos\alpha+(e^{4abs}-1)(a^4+b^4x_0^4+2a^2b^2x_0^2\cos(2\alpha))}}-\\
+&\hspace{1cm}-\arctan\ps{\f{(-1)^{s_2}(2abx_0+(-1)^{s_1}(a^2+b^2x_0^2)\cos\alpha)\csc\alpha}{a^2-b^2x_0^2}}
+\end{align}
+We now need to solve for
 \pagebreak

### 2016-07-22 Macro Impacts Revised.tex
Update

@@
 P(\vec k)&=\f{4\pi p_0}{k\cos\theta}\sin\p{\f{h k\cos\theta}{2}}\sum_{n=0}^\infty\sum_{m=0}^n\f{f^{(n)}(r_0)}{n!}\f{(-r_0)^{n-m}}{2+m}\ps{x^{2+m}}_{x=a}^b+\scr O(k)\,,\\
-&=\ps{\f{4\pi p_0}{k\cos\theta}\sin\p{\f{h k\cos\theta}{2}}x^2\underbrace{\sum_{n=0}^\infty\sum_{m=0}^n\f{f^{(n)}(r_0)}{n!}\f{(-r_0)^{n-m}}{2+m}x^{m}}_{f_1(x)}}_{x=a}^b+\scr O(k)\,,\\
+&=\f{4\pi p_0}{k\cos\theta}\sin\p{\f{h k\cos\theta}{2}}\ps{x^2\underbrace{\sum_{n=0}^\infty\sum_{m=0}^n\f{f^{(n)}(r_0)}{n!}\f{(-r_0)^{n-m}}{2+m}x^{m}}_{f_1(x)}}_{x=a}^b+\scr O(k)\,,\\
 &=\f{4\pi p_0}{k\cos\theta}\sin\p{\f{h k\cos\theta}{2}}(b^2f_1(b)-a^2f_1(a))+\scr O(k)\,.
@@
 r(s)&=\f{a}{b}\sqrt{\f{a^2\p{e^{2abs}-1}^2+b^2\p{e^{2abs}+1}^2x_0^2+2(-1)^{s_1}ab\p{e^{4abs}-1}x_0\abs{\cos\alpha}}{a^2\p{e^{2abs}+1}^2+b^2\p{e^{2abs}-1}^2x_0^2+2(-1)^{s_1}ab\p{e^{4abs}-1}x_0\abs{\cos\alpha}}}\,,\\
-\notag\theta(s)&=\arccot\ps{\f{4(-1)^{s_2}abx_0(a^2-b^2x_0^2)\sin\alpha}{4a^2b^2(1+e^{4abs})x_0^2+4(-1)^{s_2}abe^{4abs}x_0(a^2+b^2x_0^2)\cos\alpha+(e^{4abs}-1)(a^4+b^4x_0^4+2a^2b^2x_0^2\cos(2\alpha))}}-\\
+\notag\theta(s)&=\arccot\ps{\f{4(-1)^{s_2}abx_0(a^2-b^2x_0^2)\sin\alpha}{4a^2b^2(1+e^{4abs})x_0^2+4(-1)^{s_1}abe^{4abs}x_0(a^2+b^2x_0^2)\cos\alpha+(e^{4abs}-1)(a^4+b^4x_0^4+2a^2b^2x_0^2\cos(2\alpha))}}-\\
 &\hspace{1cm}-\arctan\ps{\f{(-1)^{s_2}(2abx_0+(-1)^{s_1}(a^2+b^2x_0^2)\cos\alpha)\csc\alpha}{a^2-b^2x_0^2}}
 \end{align}
-We now need to solve for
+Note that $s_1$ and $s_2$ change the quadrant of the ray propagation with respect to the starting position.
+We now need to solve for $s$ such that $r$ is some desired value at that point, call it $r_m$ (where we have chosen $m$ to stand for mantle).
+\\\\
+The time $s_m$ it takes to get to the radius $r_m$ is
+\begin{align}
+s_m=\f{1}{2ab}\ln\ps{\f{a^4-b^4 r_m^2 x_0^2+a^2b^2(r_m^2-x_0^2)+(-1)^{s_3} 2ab\sqrt{(r_m^2-x_0^2)(a^4-b^4 r_m^2x_0^2)+(a^2-b^2r_m^2)^2x_0^2\cos^2\alpha}}{(a^2-b^2r_m^2)(a^2+b^2x_0^2+2(-1)^{s_1}abx_0\cos\alpha)}}
+\end{align}
+We now want to compute the sine of the angle between the tangent vector to the curve and the surface normal at $s_m$. Observe
+\begin{align}
+T\cdot n&=\f{\dot r}{\sqrt{\dot r^2+r^2\dot\theta^2}}\,.
+\end{align}
+Hence
+\begin{align}
+\sin\phi&=\f{r\dot\theta}{\sqrt{\dot r^2+r^2\dot\theta^2}}\,.
+\end{align}
+We now write a theoretical program for computing the energy density on the surface of the earth.
+First, define a list of $M$ points from which we want to propagate rays.
+In our specific case, these will be evenly spaced points along a chord through the earth.
+Store the coordinates of these points.
+From each of these points, we will want to propagate some number $N$ of rays.
+These rays must have uniform angular separation.
+This is the question of tiling the sphere by arbitrarily small polygons.
+This is, of course, only possible for finitely many polygons on a given sphere.
+Thus, we need some other way of uniformly distributing points on a sphere.
+{http://neilsloane.com/packings/dim3/pack.3.130.txt} contains the coordinates of 130 points placed on a sphere such that their angular separation is minimized (18.5 degrees).
+If this isn't enough, there is a tiling on the same website with over 1000 points, but that would be absurd.
+The vectors given by the 130 points determine the plane of propagation (given by the span of the direction vector and the vector pointing from the origin) and the initial propagation angle $\alpha$ with respect to the vector pointing from the origin.
+
 \pagebreak

### 2016-07-23 Macro Impacts Revised.tex
Concept of Program

@@
 The vectors given by the 130 points determine the plane of propagation (given by the span of the direction vector and the vector pointing from the origin) and the initial propagation angle $\alpha$ with respect to the vector pointing from the origin.
+Once we have the set of points and rays to consider, our problem turns into many simpler problems, i.e.
+rays propagating in two dimensions.
+There are four cases to consider.
+\begin{enumerate}
+\item $r(0)>r_m$
+\begin{enumerate}
+\item $s_m\in\C\setminus\R$.
+For these, it is enough to know $\theta(s_E)$, where $s_E$ is the time at which the rays reach the surface.
+In the case that we want to consider surface reflection, we should store the angle of incidence, but that is likely unnecessary for our purposes.
+\item $s_m\in\R$.
+These rays will reflect off the core.
+The angle of reflection with respect to the surface normal is simply minus the angle of incidence.
+Store these data and re-propagate ray after all first-iteration propagation is done.
+\end{enumerate}
+\item $r(0)<r_m$
+\begin{enumerate}
+\item If the angle of incidence is less than the critical angle, then the ray refracts. Store these data and re-propagate after all first iteration propagation is done.
+\item If the angle of incidence is greater than the critical angle, the rays will internally reflect forever, so we can throw these out.
+\end{enumerate}
+\end{enumerate}
+The first round of propagation will produce some rays that hit the surface and some which need to be propagated a second time.
+All those rays propagating in the second round of propagation will originate on the core-mantle boundary, and thus computation will be greatly simplified.
+Once we have stored the final polar coordinate, we must place these final coordinates properly on the sphere.
+This is done by two rotations.
+The first is the inverse of the rotation which took the initial propagation direction vector into the $xy$-plane.
+The second is the inverse of the rotation which took the position vector of the point source to the $x$-axis.
+I believe rotations of points is commutative, but I'm too lazy to check, so it's safest to just do these in the proper order.
 

### 2016-07-23 Macro Impacts Revised.tex
Program mostly figured out.

@@
 I believe rotations of points is commutative, but I'm too lazy to check, so it's safest to just do these in the proper order.
-
+\pagebreak
+\section{The Procedure Made More Explicit}
+\begin{enumerate}
+\item We wish to consider a line source. First, determine the number $N$ of point sources with which we want to approximate the line.
+\item Next we determine the coordinates of these points.
+If the Earth has radius $R_E$, and the line is a distance $D$ from the center, then the length of the line intersecting the earth is $L=2\sqrt{R_E^2-D^2}$.
+we must space the points evenly, so each point will be $\f{L}{N}$ apart from one another.
+To maintain symmetry, we insist that $N$ be odd, and that one point exist in the plane of symmetry.
+The coordinate of the center point is $(x,y,z)=(0,D,0)$.
+The set of points is described as $P=\{(x,D,0):x=\f{L}{N}(n-\f{N-1}{2}),n=\{0,\dots,N\}\}$\,.
+\item Now that we have a set of points, we must describe the set of rays originating at those points.
+The website listed above has a nice set of optimally spaced points on spheres, so we will use that.
+We will import the coordinates of the points from a text document.
+In order to apply our methods, we need to rotate the ray into the $xy$-plane.
+Suppose we want to propagate the ray whose coordinates w.r.t the starting point are
+\begin{align}
+(x,y,z)=\p{\f{L}{N}\p{n_0-\f{N-1}{2}},D,0}\,.
+\end{align}
+in the direction $(a,b,c)$ (given by the text document). We need to take this to a point of the form $(x,0)$. It is clear that
+\begin{align}
+x_0=\sqrt{\f{L^2}{N^2}\p{n_0-\f{N-1}{2}}^2+D^2}
+\end{align}
+where the rotation is by the angle
+\begin{align}
+\alpha=\arctan\p{\f{L}{ND}\p{n_0-\f{N-1}{2}}}
+\end{align}
+and whose matrix is
+\begin{align}
+\mat{ccc}{\cos\alpha&0&\sin\alpha\\0&1&0\\-\sin\alpha&0&\cos\alpha}\,.
+\end{align}
+In this new frame, the initial coordinate of the ray is in the $xy$-plane. The direction of propagation, however, may not be. In this new frame, the ray propagates as
+\begin{align}
+\mat{c}{a'\\b'\\c'}=\mat{ccc}{\cos\alpha&0&\sin\alpha\\0&1&0\\-\sin\alpha&0&\cos\alpha}\mat{c}{a\\b\\c}
+\end{align}
+We now rotate so that the $z$ coordinate is zero, and we extract the angle $\alpha$. The angle we want to rotate by is
+\begin{align}
+\beta=\arctan\p{\f{c'}{b'}}\,,
+\end{align}
+and the rotation matrix is
+\begin{align}
+\mat{ccc}{1&0&0\\0&\cos\beta&-\sin\beta\\0&\sin\beta&\cos\beta}\,.
+\end{align}
+We now have a propagation direction in the $xy$-plane:
+\begin{align}
+\mat{c}{a''\\b''\\c''}=\mat{ccc}{1&0&0\\0&\cos\beta&-\sin\beta\\0&\sin\beta&\cos\beta}\mat{c}{a'\\b'\\c'}\,.
+\end{align}
+\end{enumerate}
 \pagebreak

### 2016-07-23 Macro Impacts Revised.tex
Program almost completely thought out

@@
 \begin{align}
-\mat{c}{a''\\b''\\c''}=\mat{ccc}{1&0&0\\0&\cos\beta&-\sin\beta\\0&\sin\beta&\cos\beta}\mat{c}{a'\\b'\\c'}\,.
+\mat{c}{a''\\b''\\0}=\mat{ccc}{1&0&0\\0&\cos\beta&-\sin\beta\\0&\sin\beta&\cos\beta}\mat{c}{a'\\b'\\c'}\,.
 \end{align}
+From this we can write down the propagation angle
+\begin{align}
+\alpha=\arctan\p{\f{b''}{a''}}\,.
+\end{align}
+We can now use the work from above. 
+\item CHECK: Is $x_0>R_{\te{mantle}}$?
+\begin{enumerate}
+\item If yes, then CHECK: is $s_{\te{mantle}}$ real?
+\begin{enumerate}
+\item If yes, then compute $\theta(s_{\te{mantle}})$ and $\sin\phi(s_{\te{mantle}})$ from the formulas in the Numerical Methods section.
+We now have a new starting angle $\alpha=-\arcsin\phi(s_{\te{mantle}})$.
+This information is then saved along side the angles $\alpha$ and $\beta$ to be used in the next round of computation.
+\item If no, then compute $\theta(s_{\te{Earth}})$, the angle after the ray has propagated to the surface of the earth. This is the final data for this ray.
+\end{enumerate}
+\item If no, then CHECK: is $\phi(s_{\te{mantle}})$ less than $\phi_{\te{critical}}=\arcsin\p{\f{v_{\te{core}}}{v_{\te{mantle}}}}$?
+\begin{enumerate}
+\item If yes, then compute $\theta(s_{\te{mantle}})$ and the new starting angle $\alpha=\arcsin\p{\f{v_{\te{mantle}}}{v_{\te{core}}}\sin\phi(s_{\te{mantle}})}$, which will be used in the next round of computation.
+\item If no, then throw the point away, as it will be internally reflected forever.
+\end{enumerate}
+\end{enumerate}
+\item Now, all the remaining points have trajectories originating on the surface $r_{\te{mantle}}$ and will intersect the surface of the earth.
+Thus, all that is left to compute is $\theta(s_{\te{Earth}})$ for each of these points, making sure to keep track of all relevant angles from the previous round of computation (i.e.
+$\theta(s_{\te{mantle}})$).
+\item At this point, we have computed final angles for all rays in their respective frames of reference.
+What is left is to rotate these points back into the original frame.
+Since all of these coordinates have the same radius, it is only important to keep track of the angle.
 \end{enumerate}

### 2016-07-24 Macro Impacts Revised.tex
More Detail

@@
 The coordinate of the center point is $(x,y,z)=(0,D,0)$.
-The set of points is described as $P=\{(x,D,0):x=\f{L}{N}(n-\f{N-1}{2}),n=\{0,\dots,N\}\}$\,.
+The set of points is described as $P=\{(x,D,0):x=\f{L}{N}(n-\f{N-1}{2}),n=\{1,\dots,N\}\}$\,.
 \item Now that we have a set of points, we must describe the set of rays originating at those points.
@@
 In order to apply our methods, we need to rotate the ray into the $xy$-plane.
+Denote
+\begin{align}
+\ell(n)=\f{L}{N}\p{n-\f{N}{2}}
+\end{align}
 Suppose we want to propagate the ray whose coordinates w.r.t the starting point are
 \begin{align}
-(x,y,z)=\p{\f{L}{N}\p{n_0-\f{N-1}{2}},D,0}\,.
+(x,y,z)=\p{\ell(n),D,0}\,.
 \end{align}
@@
 \begin{align}
-x_0=\sqrt{\f{L^2}{N^2}\p{n_0-\f{N-1}{2}}^2+D^2}
+x_0=\sqrt{\ell(n)^2+D^2}
 \end{align}
@@
 \begin{align}
-\alpha=\arctan\p{\f{L}{ND}\p{n_0-\f{N-1}{2}}}
+\alpha=\arctan2\p{D,\ell(n)}
 \end{align}
@@
 \begin{align}
-\mat{ccc}{\cos\alpha&0&\sin\alpha\\0&1&0\\-\sin\alpha&0&\cos\alpha}\,.
+\mat{ccc}{\cos\alpha&\sin\alpha&0\\-\sin\alpha&\cos\alpha&0\\0&0&1}\,.
 \end{align}
@@
 \begin{align}
-\mat{c}{a'\\b'\\c'}=\mat{ccc}{\cos\alpha&0&\sin\alpha\\0&1&0\\-\sin\alpha&0&\cos\alpha}\mat{c}{a\\b\\c}
+\mat{c}{a'\\b\\c'}=\mat{ccc}{\cos\alpha&\sin\alpha&0\\-\sin\alpha&\cos\alpha&0\\0&0&1}\mat{c}{a+\ell(n)\\b+D\\c}
 \end{align}
@@
 \begin{align}
-\beta=\arctan\p{\f{c'}{b'}}\,,
+\beta=\arctan2\p{c',b'}\,,
 \end{align}
@@
 \begin{align}
-\mat{ccc}{1&0&0\\0&\cos\beta&-\sin\beta\\0&\sin\beta&\cos\beta}\,.
+\mat{ccc}{1&0&0\\0&\cos\beta&\sin\beta\\0&-\sin\beta&\cos\beta}\,.
 \end{align}
@@
 \begin{align}
-\mat{c}{a''\\b''\\0}=\mat{ccc}{1&0&0\\0&\cos\beta&-\sin\beta\\0&\sin\beta&\cos\beta}\mat{c}{a'\\b'\\c'}\,.
+\mat{c}{a''\\b''\\0}=\mat{ccc}{1&0&0\\0&\cos\beta&\sin\beta\\0&-\sin\beta&\cos\beta}\mat{c}{a'\\b'\\c'}\,.
 \end{align}
@@
 \begin{align}
-\alpha=\arctan\p{\f{b''}{a''}}\,.
+\alpha_{\te{ray}}=\arctan\p{\f{b''}{a''-x_0}}\,.
 \end{align}
@@
 \begin{enumerate}
-\item If yes, then CHECK: is $s_{\te{mantle}}$ real?
+\item If yes, then CHECK: is $s_{\te{mantle}}$ real and $s_{\te{mantle}}>s_{x_0}$?
+In these cases, we take $s_2=2$.
+The choice of $s_1=0$ or $1$ is determined by the value of $\alpha$.
+We assume that the propagation begins by heading towards positive $y$ (so we'll need to account for this for points whose $\alpha$ is in the other direction by taking $\alpha\to2\pi-\alpha$).
+If this is the case, where $\alpha=0$ corresponds to propagation towards positive $x$, for $\alpha\in[0,\f\pi2]$, we take $s_1=0$.
+For $\alpha\in[\f\pi2,\pi]$, we take $s_1=1$, and $\alpha\to\pi-\alpha$.
+In the case that $\alpha>\f\pi2$, there is the possibility that the ray hits the mantle.
+The point of intersection corresponds to $s_{\te{mantle}}$ with $s_3=1$.
 \begin{enumerate}
-\item If yes, then compute $\theta(s_{\te{mantle}})$ and $\sin\phi(s_{\te{mantle}})$ from the formulas in the Numerical Methods section.
+\item If yes compute $\theta(s_{\te{mantle}})$ and $\sin\phi(s_{\te{mantle}})$ from the formulas in the Numerical Methods section.
 We now have a new starting angle $\alpha=-\arcsin\phi(s_{\te{mantle}})$.
@@
 What is left is to rotate these points back into the original frame.
-Since all of these coordinates have the same radius, it is only important to keep track of the angle.
+Since all of these coordinates have the same radius, it is only important to keep track of the angles.
 \end{enumerate}
+\pagebreak
+\section{Code}
 \pagebreak

### 2016-07-24 Ray-Tracing/Ray_Tracing.m

@@ -1,0 +1,79 @@
+clc
+clear
+format long
+PointMatrix=[];
+PointMatrix=load('20_PointsOnASphere.txt');
+counter=1;
+macrocounter=1;
+a=length(PointMatrix);
+RayDirectionVectors=[];
+SecondPhase=[];
+AlphaList=[];
+BetaList=[];
+for i=1:a %This loop unpacks the direction vectors from a text file 'M_PointsOnASphere.txt'
+    RayDirectionVectors(macrocounter,counter)=PointMatrix(i);
+    if counter==3
+        counter=1;
+        macrocounter=macrocounter+1;
+    else
+        counter=counter+1;
+    end
+end
+RE=input('What is the radius of the earth? (meters) ')
+D=input('What is the distance of closest approach of the macro to the center? (meters) ')
+N=input('How many points along this line should we consider? ');
+Rmantle=input('What is the radius of the mantle? (meters) ');
+a=Sqrt(input('Assuming that the velocity field has the form a^2-b^2*r^2, what is a^2? '))
+b=Sqrt(input('Assuming that the velcoity field has the form a^2-b^2*r^2, what is b^2? '))
+M=a/3;
+%VARIABLE DECLARATION SECTION
+%IT'S THE FINAAAAAAAL COUNTDOWN
+L=2*((((RE)^2)-((D)^2))^0.5); %The length of the path through the earth.
+for n=1:N-1
+    x0 = X0(L,N,n,D); %X0 is the function which tells you how far from the origin the point source is, while x0 is the value for a given n
+    l = ((L/N)*(n-(N/2))); %l is the distance along the trajectory from the y-axis to the point source before rotation
+    Alpha = atan2(D,l); %Alpha is the angle we rotate by so that the point souce is on the x-axis
+    AlphaList = cat(1,AlphaList,Alpha); %AlphaList keeps track of the Alpha's in a column vector whose length is N
+    RotAlpha = [cos(Alpha),sin(Alpha),0;-sin(Alpha),cos(Alpha),0;0,0,1]; %This is the rotation matrix corresponding to a rotation about the z-axis by Alpha radians CLOCKWISE
+        for m = 1 : M
+        AlphaRayDirectionVectors=RotAlpha*[(RayDirectionVectors(m,1)+l);(RayDirectionVectors(m,2)+D);RayDirectionVectors(m,3)]; %We now rotate the ray direction vector by Alpha so that its tail lies on the x axis
[…]

### 2016-07-24 Ray-Tracing/SR.m

@@ -1,0 +1,5 @@
+function output = SR(R,a,b,x0,AlphaRay,s1,s2,s3)
+    output = (1/(2*a*b))log((a^4-(b^4)*(R^2)*(x0^2)+(a^2)*(b^2)*(R^2-x0^2)+((-1)^(s3))2*a*b*sqrt((R^2-x0^2)*(a^4-(b^4)*(R^2)*(x0^2))+(a^2-(b^2)*(R^2))*(x0^2)*((cos(AlphaRay))^2)))
+    /((a^2-(b^2)*(R^2))((a^2+(b^2)*(R^2)+2((-1)^(s1))*a*b*x0*cos(AlphaRay)))))
+end
+

### 2016-07-24 Ray-Tracing/X0.m

@@ -1,0 +1,3 @@
+function output=X0(L,N,n,D)
+    output=(((L/N)*(n-(N/2)))^2+D^2)^(0.5);
+end

### 2016-07-24 Ray_Tracing.py

@@ -1,0 +1,2 @@
+f = open('130_Points_on_a_Sphere.txt', 'r')
+x = f.readlines()

### 2016-07-25 Ray-Tracing/Ray_Tracing.m
Progress

@@ -5,12 +5,16 @@ PointMatrix=[];
 PointMatrix=load('20_PointsOnASphere.txt');
 counter=1;
 macrocounter=1;
-a=length(PointMatrix);
+LengthofPointmatrix=length(PointMatrix);
 RayDirectionVectors=[];
 SecondPhase=[];
 AlphaList=[];
 BetaList=[];
-for i=1:a %This loop unpacks the direction vectors from a text file 'M_PointsOnASphere.txt'
+Flip=[]; %1 means AlphaRay->2 Pi-AlphaRay 0 means no flip
+TheHolyHandArray=[]; %Angles of Incidence
+Bees=[]; %Do again?
+ThePlebeianThinksTheyreDone=[]; %Angle (as measured from the origin) at which the ray hits the surface of the Earth
+for i=1:LengthofPointmatrix %This loop unpacks the direction vectors from a text file 'M_PointsOnASphere.txt'
     RayDirectionVectors(macrocounter,counter)=PointMatrix(i);
     if counter==3
         counter=1;
@@ -19,13 +23,17 @@ for i=1:a %This loop unpacks the direction vectors from a text file 'M_PointsOnA
         counter=counter+1;
     end
 end
-RE=input('What is the radius of the earth? (meters) ')
-D=input('What is the distance of closest approach of the macro to the center? (meters) ')
+RE=input('What is the radius of the earth? (meters) ');
+D=input('What is the distance of closest approach of the macro to the center? (meters) ');
 N=input('How many points along this line should we consider? ');
 Rmantle=input('What is the radius of the mantle? (meters) ');
-a=Sqrt(input('Assuming that the velocity field has the form a^2-b^2*r^2, what is a^2? '))
-b=Sqrt(input('Assuming that the velcoity field has the form a^2-b^2*r^2, what is b^2? '))
-M=a/3;
+ac=sqrt(input('Inside the core, assuming that the velocity field has the form a^2-b^2*r^2, what is a^2? '));
+bc=sqrt(input('Inside the core, assuming that the velcoity field has the form a^2-b^2*r^2, what is b^2? '));
+am=sqrt(input('Outside the core, assuming that the velocity field has the form a^2-b^2*r^2, what is a^2? '));
+bm=sqrt(input('Outside the core, assuming that the velocity field has the form a^2-b^2*r^2, what is b^2? '));
[…]

### 2016-07-25 Ray-Tracing/SR.m

@@ -1,5 +1,5 @@
-function output = SR(R,a,b,x0,AlphaRay,s1,s2,s3)
-    output = (1/(2*a*b))log((a^4-(b^4)*(R^2)*(x0^2)+(a^2)*(b^2)*(R^2-x0^2)+((-1)^(s3))2*a*b*sqrt((R^2-x0^2)*(a^4-(b^4)*(R^2)*(x0^2))+(a^2-(b^2)*(R^2))*(x0^2)*((cos(AlphaRay))^2)))
-    /((a^2-(b^2)*(R^2))((a^2+(b^2)*(R^2)+2((-1)^(s1))*a*b*x0*cos(AlphaRay)))))
+function output = SR(R,a,b,x0,AlphaRay,s1,~,s3)
+%This function tells us what value of the parameter corresponds to the ray
+%intersecting a surface of radius R. May be incorrectly copied!
+    output = (1/(2*a*b))*log((a^4-(b^4)*(R^2)*(x0^2)+(a^2)*(b^2)*(R^2-x0^2)+((-1)^(s3))*2*a*b*sqrt((R^2-x0^2)*(a^4-(b^4)*(R^2)*(x0^2))+(a^2-(b^2)*(R^2))*(x0^2)*((cos(AlphaRay))^2)))/((a^2-(b^2)*(R^2))*((a^2+(b^2)*(R^2)+2*((-1)^(s1))*a*b*x0*cos(AlphaRay)))));
 end
-

### 2016-07-25 Ray-Tracing/SX.m

@@ -1,0 +1,5 @@
+function output = SX(a,b,x0,AlphaRay,s1,~,~)
+% Tells us for what parameter does the ray intersect the x-axis i.e. the initial parameter value
+    output = log(1 - (8*((-1)^(s1))*a*b*x0*(a^2 + (b^2)*(x0^2))*cos(AlphaRay))/(a^4 + 4*(a^2)*(b^2)*(x0^2) + (b^4)*(x0^4) + 2*a*b*x0*(2*((-1)^(s1))*(a^2 +(b^2)*(x0^2))*cos(AlphaRay) + a*b*x0*cos(2*AlphaRay))))/(4*a*b);
+end
+

### 2016-07-25 Ray-Tracing/X0.m

@@ -1,3 +1,4 @@
+%This function tells us the distance from the origin of the point source
 function output=X0(L,N,n,D)
-    output=(((L/N)*(n-(N/2)))^2+D^2)^(0.5);
+    output = (((L/N)*(n-(N/2)))^2+D^2)^(0.5);
 end

### 2016-07-25 Ray-Tracing/r.m

@@ -1,0 +1,4 @@
+function output = r(s,a,b,AlphaRay,x0,s1,~,~)
+%This is the radial coordinate of the ray as a function of the parameter s
+ output = (1/(b*sqrt((a^2)*((exp(2*a*b*s) + 1)^2) + (b^2)*((exp(2*a*b*s) - 1)^2)*(x0^2) + 2*((-1)^(s1))*a*b*(exp(4*a*b*s) - 1)*x0*abs(cos(AlphaRay)))))*a*sqrt((a^2)*((exp(2*a*b*s) - 1)^2) + (b^2)*((exp(2*a*b*s) + 1)^2)*(x0^2) + 2*((-1)^(s1))*a*b*(exp(4*a*b*s) - 1)*x0*abs(cos(AlphaRay)));
+end

### 2016-07-25 Ray-Tracing/theta.m

@@ -1,0 +1,4 @@
+function output = theta(s,a,b,AlphaRay,x0,s1,s2,~)
+%This is the angular component of the ray as a function of s
+    output = acot((4 *((-1)^(s2))*a*b*x0*(a^2 - (b^2)*(x0^2))*sin(AlphaRay))/(4*(a^2)*(b^2)*(1 + exp(4*a*b*s))*(x0^2) + 4*((-1)^(s1))*a*b*exp(4*a*b*s)*x0*(a^2 + (b^2)*(x0^2))*cos(AlphaRay) + (exp(4*a*b*s) - 1)*(a^4 + (b^4)*(x0^4) + 2*(a^2)*(b^2)*(x0^2)*cos(2*AlphaRay))))- atan((1/(a^2 - (b^2)*(x0^2)))*((-1)^(s2))*(2*a*b*x0 - ((-1)^(s1))*(a^2 + (b^2)*(x0^2))*cos(AlphaRay))*csc(AlphaRay));
+end

### 2016-07-26 Ray-Tracing/Ray_Tracing.m
Color

@@ -17,15 +17,15 @@ SecondPhase=[];
 %        counter = counter + 1;
 %    end
 %end
-RE = 6; %input('What is the radius of the earth? (meters) ');
-D = 2; %input('What is the distance of closest approach of the macro to the center? (meters) ');
-N = 400; %input('How many points along this line should we consider? ') + 1;
-M = 100; %input('How many rays will each point emit? ');
-Rmantle = 2.5; %input('What is the radius of the mantle? (meters) ');
-ac = 1; %sqrt(input('Inside the core, assuming that the velocity field has the form a^2-b^2*r^2, what is a^2? '));
-bc = .1; %sqrt(input('Inside the core, assuming that the velcoity field has the form a^2-b^2*r^2, what is b^2? '));
-am = 1; %sqrt(input('Outside the core, assuming that the velocity field has the form a^2-b^2*r^2, what is a^2? '));
-bm = .01; %sqrt(input('Outside the core, assuming that the velocity field has the form a^2-b^2*r^2, what is b^2? '));
+RE = 6371; %input('What is the radius of the earth? (meters) ');
+D = 3000; %input('What is the distance of closest approach of the macro to the center? (meters) ');
+N = 40; %input('How many points along this line should we consider? ') + 1;
+M = 40; %input('How many rays will each point emit? ');
+Rmantle = 3480; %input('What is the radius of the mantle? (meters) ');
+ac = 11.1502; %sqrt(input('Inside the core, assuming that the velocity field has the form a^2-b^2*r^2, what is a^2? '));
+bc = 2.69692*(10^(-7)); %sqrt(input('Inside the core, assuming that the velcoity field has the form a^2-b^2*r^2, what is b^2? '));
+am = 15.4938; %sqrt(input('Outside the core, assuming that the velocity field has the form a^2-b^2*r^2, what is a^2? '));
+bm = 1.40336*(10^(-7)); %sqrt(input('Outside the core, assuming that the velocity field has the form a^2-b^2*r^2, what is b^2? '));
 RayDirectionVectors = zeros(M,N,3);
 for n = 1 : N
     for m = 1 : M
[…]

### 2016-07-26 Ray-Tracing/T.m

@@ -1,0 +1,13 @@
+function output = T(x,y,z,theta)
+%Rotation about the vector (ux,uy,uz) by the angle theta.
+%   Detailed explanation goes here
+    mag = sqrt(x^2+y^2+z^2);
+    ux = x/mag;
+    uy = y/mag;
+    uz = z/mag;
+    t = 1 - cos(theta);
+    C = cos(theta);
+    S = sin(theta);
+    output = [t*(ux^2)+C,t*ux*uy-S*uz,t*ux*uz+S*uy;t*ux*uy+S*uz,t*(uy^2)+C,t*uy*uz-S*ux;t*ux*uz-S*uy,t*uy*uz+S*ux,t*(uz^2)+C];
+end
+

### 2016-07-26 Ray-Tracing/Test.m

@@ -1,0 +1,5 @@
+figure
+v1=[0.2,0.3 4 ],
+v2=[-0.3,0.3,0.1],
+v=[v2;v1];
+plot3(v(:,1),v(:,2),v(:,3),'r')

### 2016-07-26 Ray-Tracing/Ray_Tracing.m
Update

@@ -19,8 +19,8 @@ SecondPhase=[];
 %end
 RE = 6371; %input('What is the radius of the earth? (meters) ');
 D = 3000; %input('What is the distance of closest approach of the macro to the center? (meters) ');
-N = 40; %input('How many points along this line should we consider? ') + 1;
-M = 40; %input('How many rays will each point emit? ');
+N = 100; %input('How many points along this line should we consider? ') + 1;
+M = 100; %input('How many rays will each point emit? ');
 Rmantle = 3480; %input('What is the radius of the mantle? (meters) ');
 ac = 11.1502; %sqrt(input('Inside the core, assuming that the velocity field has the form a^2-b^2*r^2, what is a^2? '));
 bc = 2.69692*(10^(-7)); %sqrt(input('Inside the core, assuming that the velcoity field has the form a^2-b^2*r^2, what is b^2? '));
@@ -133,9 +133,9 @@ end
 %Now we need to convert this into a pretty picture. This section is slow,
 %and could use some work...
 figure
-scatter3(ImpactPositionList(:,1),ImpactPositionList(:,2),ImpactPositionList(:,3))
-PolarDensity = 50;
-AzimuthalDensity = 50;
+scatter3(ImpactPositionList(:,1),ImpactPositionList(:,2),ImpactPositionList(:,3),'.')
+PolarDensity = 60;
+AzimuthalDensity = 60;
 NumberOfSamplePoints = (PolarDensity) * (AzimuthalDensity - 1);
 SampleAngle = pi/30;
 PointsToBeColored = zeros(AzimuthalDensity * PolarDensity,3);
@@ -166,4 +166,3 @@ for i = 1 : NumberOfSamplePoints
 end
 figure
 scatter3(CartPointsToBeColored(:,1),CartPointsToBeColored(:,2),CartPointsToBeColored(:,3),200,log(NumberOfRaysIncidentInDisk(:)),'filled')
-mesh(CartPointsToBeColored(:,1),CartPointsToBeColored(:,2),log(NumberOfRaysIncidentInDisk(:)))

### 2016-07-31 Ray-Tracing/Ray_Tracing_Generalized.m
Ray Tracing Code (NEARLY DONE)
Everything but the quality factor is in place, but the machinery is
there to deal with it. I should have that done within the hour. It
doesn’t yet output a text file, but that is easy.

@@ -6,9 +6,9 @@ a = [11.2633,10.6835,15.4938].^(1/2); %first entry corresponds to the core
 b = [1.55946*10^(-7),2.11853*10^(-7),1.40336*10^(-7)].^(1/2); %first entry corresponds to the core
 WeaknessOfNeglectedRays = 10^(-1); %input('What fraction of the initial ray energy must a ray contain to not be thrown out? ');
 
-D = 3000;
+D = 0;
 Radii = [0,1221,3480,6371];
-AbsoluteCutoff = 5;
+AbsoluteCutoff = 4;
 
 Layers = length(Radii);
 
@@ -27,8 +27,8 @@ rhoBoundaries = [];
 
 %GENERATING THE RANDOM POINTS ON A SPHERE
 
-M = 1200;
-N = 100;
+M = 1;
+N = 10000;
 Th = rand(M,N).*(2*pi);
 Ph = asin((rand(M,N).*2.-1));
 I = 1:M;
@@ -147,12 +147,13 @@ for Iter = 1 : AbsoluteCutoff
                 RayArrayx0(LIdInwardMissPrime) = Radii(LayerId + 1);
                 RayArrayAngDisp(LIdInwardMissPrime) = RayArrayAngDisp(LIdInwardMiss) + Thetaprime;
                 RayArrayAmp(LIdInwardMissPrime) = 1; %ReflectionCoefficient(sinAngleOfIncidence);
-                
+        
         %RAYS THAT HIT THE INNER LAYER
         
                 %REFRACTED INWARD BOUND RAYS
                 
                 if LayerId > 1
+                    
                     sinAngleOfIncidence = GOD(SInwardHit(LIdInwardHit),a(LayerId),b(LayerId),pi - RayArrayAlpha(LIdInwardHit),RayArrayx0(LIdInwardHit),0,0,1);
                     Thetaprimeprime = theta(SInwardHit(LIdInwardHit),a(LayerId),b(LayerId), pi - RayArrayAlpha(LIdInwardHit),RayArrayx0(LIdInwardHit),0,0,1);
                     RayArrayAlpha(LIdInwardHit) = asin(((vBoundaries(LayerId,1)/(vBoundaries(LayerId,2))).*sinAngleOfIncidence));

### 2016-07-31 Ray-Tracing/Ray_Tracing_Revised.m

@@ -2,13 +2,34 @@ clear
 
 format long
 
-a = [11.2633,10.6835,15.4938].^(1/2); %first entry corresponds to the core
-b = [1.55946*10^(-7),2.11853*10^(-7),1.40336*10^(-7)].^(1/2); %first entry corresponds to the core
-WeaknessOfNeglectedRays = 10^(-1); %input('What fraction of the initial ray energy must a ray contain to not be thrown out? ');
 
-D = 2000;
-Radii = [0,1221,3480,6371];
-ACO = 2;
+
+%INPUTS
+
+M = 1; %NUMBER OF POINTS ON THE LINE
+N = 10000; %NUMBER OF RAYS FROM EACH POINT
+
+a = [11.2633,10.6835,15.4938].^(1/2); %THESE ARE THE CONSTANT TERMS IN THE PARABOLIC VELOCITY FIELD STRUCTURE, THE FIRST ENTRY CORRESPONDING TO THE CORE
+b = [1.55946*10^(-7),2.11853*10^(-7),1.40336*10^(-7)].^(1/2); %THESE ARE THE COEFFICIENTS OF THE QUADRATIC TERM IN THE VELOCITY FIELD
+
+D = 6370; %THE DISTANCE OF CLOSEST APPROACH TO THE CENTER
+Radii = [0,1221,3480,6371]; %NOTE THAT WE MUST TAKE 0 AS A LAYER FOR TECHNICAL PURPOSES
+ACO = 5; %IT TAKES 5 ITERATIONS FOR A RAY TO PASS ENTIRELY THROUGH THE EARTH
+
+Q = ; %THE QUALITY FACTOR AS A FUNCTION OF FREQUENCY
+A = ; %THE AMPLITUDE OF THE WAVE AS A FUNCTION OF FREQUENCY
+
+rhoBoundaries = [ 12.76, 12.17; 9.90, 5.57; 1.02, 1.25*(10^(-3))].*(10^12); %THE DENSITY OF THE MEDIA AT THEIR DISCONTINUOUS BOUNDARIES - THE LEFT ENTRY IN EACH ROW CORRESPONDS TO THE INNER DENSITY AND THE RIGHT CORRESPONDS TO THE OUTER DENSITY
+
+%END INPUTS
+
+
+
+
+
+
+
+
 
[…]

### 2016-07-31 Ray-Tracing/ReflectionCoefficient.m

@@ -1,10 +1,7 @@
-function R = ReflectionCoefficient(LayerId,sinTheta,v1,v2,rho1,rho2)
+function R = ReflectionCoefficient(LayerId,sinTheta,AlphaRay,v1,v2,rho1,rho2)
 %The fluid in which the wave arrives is labeled 1
 %   Detailed explanation goes here
-    m = rho2./rho1;
-    n = v1./v2;
-    Theta = asin(sinTheta);
-    R = abs((m.*cos(Theta)-n.*(1-(n.^(-2)).*(sin(Theta)).^(2)).^(1/2)./(m.*cos(Theta)+n.*(1-(n.^(-2)).*(sin(Theta)).^(2)).^(1/2))));
+    R = 1 - TransmissionCoefficient(LayerId,sinTheta,AlphaRay,v1,v2,rho1,rho2);
     
 end
 

### 2016-07-31 Ray-Tracing/SR.m

@@ -1,10 +1,8 @@
-function output = SR(R,a,b,x0,AlphaRay,s1,~,s3)
+function output = SR(rm,a,b,x0,AlphaRay,s1,~,s3)
 %This function tells us what value of the parameter corresponds to the ray
 %intersecting a surface of radius R. May be incorrectly copied!
-    output = (1/2).*a.^(-1).*b.^(-1).*log((a+(-1).*b.*R).^(-1).*(a+b.*R).^( ...
- -1).*(a.^2+b.^2.*x0.^2+2.*(-1).^s1.*a.*b.*x0.*cos(AlphaRay)).^(-1) ...
-  .*(a.^4+(-1).*b.^4.*R.^2.*x0.^2+a.^2.*b.^2.*(R+(-1).*x0).*(R+ ...
-  x0)+2.*(-1).^s3.*a.*b.*((R+(-1).*x0).*(R+x0).*(a.^4+(-1).*b.^4.* ...
-  R.^2.*x0.^2)+(a.^2+(-1).*b.^2.*R.^2).^2.*x0.^2.*cos(AlphaRay) ...
-  .^2).^(1/2)));
+output = (1/2).*a.^(-1).*b.^(-1).*log((a+(-1).*b.*rm).^(-1).*(a+b.*rm).^( ...
+ -1).*(a.^2+b.^2.*x0.^2+2.*(-1).^s1.*a.*b.*x0.*cos(AlphaRay)).^(-1).*(a.^4+(-1).*b.^4.*rm.^2.*x0.^2+a.^2.*b.^2.*(rm+(-1).*x0).*(rm+x0)+ ...
+2.*(-1).^s3.*a.*b.*((rm+(-1).*x0).*(rm+x0).*(a.^4+(-1).*b.^4.* ...
+rm.^2.*x0.^2)+(a.^2+(-1).*b.^2.*rm.^2).^2.*x0.^2.*cos(AlphaRay).^2).^(1/2)));
 end

### 2016-07-31 Ray-Tracing/TransmissionCoefficient.m

@@ -1,10 +1,18 @@
-function T = TransmissionCoefficient(LayerId,sinTheta,v1,v2,rho1,rho2)
+function T = TransmissionCoefficient(LayerId,sinTheta,AlphaRay,v1,v2,rho1,rho2)
 %The fluid in which the wave arrives is labeled 1
 %   Detailed explanation goes here
-    m = rho2./rho1;
-    n = v1./v2;
-    Theta = asin(sinTheta);
-    T = abs((2.*m.*cos(Theta))./(m.*cos(Theta)+n.*(1-(n.^(-2)).*(sin(Theta)).^(2)).^(1/2)));
-
+    
+    Theta1 = AlphaRay;
+    Theta2 = asin(sinTheta);
+    Z1 = rho1.* v1;
+    Z2 = rho2.* v2;
+    Tpre = (2.* Z2.*sec(Theta2))./(Z1.*sec(Theta1)+Z2.*sec(Theta2));
+    Thigh = Tpre > 1;
+    Tlow = Tpre < 0;
+    Tmid = (true(size(Tpre)) & (~ Thigh)) & (~ Tlow);
+    T(Thigh) = 1;
+    T(Tlow) = 0;
+    T(Tmid) = Tpre(Tmid);
+    
 end
 

### 2016-08-01 Macro Impacts Revised.tex
slight correction
Quality Factor Thoughts

@@
 \begin{align}
-P(\vec k)=\f{4\pi p_0}{k_z}\sin\p{\f{h k_z}{2}}\sum_{n=0}^\infty\sum_{m=0}^n\f{f^{(n)}(r_0)}{n!}\f{(-r_0)^{n-m}}{2+m}\ps{x^{2+m}\,_q\te{F}_p\p{\pc{1+\f m2},\pc{1,2+\f m2},-\f14 x^2 k_r^2}}_{x=a}^b\,,
+P(\vec k)=\f{4\pi p_0}{k_z}\sin\p{\f{h k_z}{2}}\sum_{n=0}^\infty\sum_{m=0}^n\binom{n}{m}\f{f^{(n)}(r_0)}{n!}\f{(-r_0)^{n-m}}{2+m}\ps{x^{2+m}\,_q\te{F}_p\p{\pc{1+\f m2},\pc{1,2+\f m2},-\f14 x^2 k_r^2}}_{x=a}^b\,,
 \end{align}
@@
 \begin{align}
-P(\vec k)=\f{4\pi p_0}{k\cos\theta}\sin\p{\f{h k\cos\theta}{2}}\sum_{n=0}^\infty\sum_{m=0}^n\f{f^{(n)}(r_0)}{n!}\f{(-r_0)^{n-m}}{2+m}\ps{x^{2+m}\,_q\te{F}_p\p{\pc{1+\f m2},\pc{1,2+\f m2},-\f14 x^2 k^2\sin^2\theta}}_{x=a}^b\,,
+P(\vec k)=\f{4\pi p_0}{k\cos\theta}\sin\p{\f{h k\cos\theta}{2}}\sum_{n=0}^\infty\sum_{m=0}^n\binom{n}{m}\f{f^{(n)}(r_0)}{n!}\f{(-r_0)^{n-m}}{2+m}\ps{x^{2+m}\,_q\te{F}_p\p{\pc{1+\f m2},\pc{1,2+\f m2},-\f14 x^2 k^2\sin^2\theta}}_{x=a}^b\,,
 \end{align}
@@
 \begin{align}
-P(\vec k)&=\f{4\pi p_0}{k\cos\theta}\sin\p{\f{h k\cos\theta}{2}}\sum_{n=0}^\infty\sum_{m=0}^n\f{f^{(n)}(r_0)}{n!}\f{(-r_0)^{n-m}}{2+m}\ps{x^{2+m}}_{x=a}^b+\scr O(k)\,,\\
-&=\f{4\pi p_0}{k\cos\theta}\sin\p{\f{h k\cos\theta}{2}}\ps{x^2\underbrace{\sum_{n=0}^\infty\sum_{m=0}^n\f{f^{(n)}(r_0)}{n!}\f{(-r_0)^{n-m}}{2+m}x^{m}}_{f_1(x)}}_{x=a}^b+\scr O(k)\,,\\
+P(\vec k)&=\f{4\pi p_0}{k\cos\theta}\sin\p{\f{h k\cos\theta}{2}}\sum_{n=0}^\infty\sum_{m=0}^n\binom{n}{m}\f{f^{(n)}(r_0)}{n!}\f{(-r_0)^{n-m}}{2+m}\ps{x^{2+m}}_{x=a}^b+\scr O(k)\,,\\
+&=\f{4\pi p_0}{k\cos\theta}\sin\p{\f{h k\cos\theta}{2}}\ps{x^2\underbrace{\sum_{n=0}^\infty\sum_{m=0}^n\binom{n}{m}\f{f^{(n)}(r_0)}{n!}\f{(-r_0)^{n-m}}{2+m}x^{m}}_{f_1(x)}}_{x=a}^b+\scr O(k)\,,\\
 &=\f{4\pi p_0}{k\cos\theta}\sin\p{\f{h k\cos\theta}{2}}(b^2f_1(b)-a^2f_1(a))+\scr O(k)\,.
@@
 \section{Code}
+The actual code that I've implemented is quite a bit more general than that described above.
+The general procedure uses the same ideas, but considers both reflection and transmission, as well as an arbitrary amount of layers.
+The code works by an iterative process, which propagates each ray to the layer next in its trajectory, using the groundwork I've laid out in mathematica.
+I will elaborate further if necessary.
+\pagebreak
+\section{Quality Factor}
+Since we've determined that it is desirable to model anelastic attenuation, I've determined a method by which we can calculate it without reference to the specific trajectory of the ray.
+Observe, if $A(t)$ is the amplitude of a ray at a given time, we can relate it its future amplitude for small time by the following relation
+\begin{align}
+A(t+\delta t) = A(t)e^{K\f{t}{Q(r(t))}}\,.
+\end{align}
+It makes sense to write $Q(r(t))$, since I've already derived the expression $r(t)$ for a given set of initial parameters.
+Hence, as part of the above algorithm, it will not require additional code to implement the quality factor.
+Now, we form a derivative
+\begin{align}
+\f{A(t+\delta t)- A(t)}{\delta t} &= A(t)\f{e^{K\f{\delta t}{Q(r(t))}}-1}{\delta t}\,,\\
+\td{A}{t}{}&= A(t)\lim_{\delta t\to 0}\f{e^{K\f{\delta t}{Q(r(t))}}-1}{\delta t}\,,\\
+\f{1}{A}\td{A}{t}{}&= \f{K}{Q(r(t))}\,,\\
+A &= A(t_0)e^{\int_{t_0}^t\diff t'\f{K}{Q(r(t'))}}\,.
+\end{align}
+We can do the above integral numerically, and perhaps analytically (in the case that we can reasonably write $Q$ as a simple smooth function of $r$).
 \pagebreak

### 2016-08-01 Ray-Tracing/Ray_Tracing_Revised.m

@@ -16,7 +16,7 @@ D = 6370; %THE DISTANCE OF CLOSEST APPROACH TO THE CENTER
 Radii = [0,1221,3480,6371]; %NOTE THAT WE MUST TAKE 0 AS A LAYER FOR TECHNICAL PURPOSES
 ACO = 5; %IT TAKES 5 ITERATIONS FOR A RAY TO PASS ENTIRELY THROUGH THE EARTH
 
-Q = ; %THE QUALITY FACTOR AS A FUNCTION OF FREQUENCY
+Q = ; %THE QUALITY FACTOR AS A FUNCTION OF FREQUENCY, TIME, AND SO ON... TBD
 A = ; %THE AMPLITUDE OF THE WAVE AS A FUNCTION OF FREQUENCY
 
 rhoBoundaries = [ 12.76, 12.17; 9.90, 5.57; 1.02, 1.25*(10^(-3))].*(10^12); %THE DENSITY OF THE MEDIA AT THEIR DISCONTINUOUS BOUNDARIES - THE LEFT ENTRY IN EACH ROW CORRESPONDS TO THE INNER DENSITY AND THE RIGHT CORRESPONDS TO THE OUTER DENSITY

### 2016-08-01 Macro Impacts Revised.tex
update
Thoughts about averaging

@@
 \begin{align}
-A(t+\delta t) = A(t)e^{K\f{t}{Q(r(t))}}\,.
+A(t+\delta t) = A(t)e^{K\f{\delta t}{Q(r(t)}}\,.
 \end{align}
@@
 We can do the above integral numerically, and perhaps analytically (in the case that we can reasonably write $Q$ as a simple smooth function of $r$).
+Next we must determine roughly what $Q$ looks like.
+In the literature, $Q$ is written $Q_p$ when in reference to $p$-waves.
+*Relevant paper on my phone*
+\pagebreak
+\section{Maximum Detectible Surface Area}
+\indent
+
+The model above produces a set of positions on a sphere along with their associated times of impact and relative amplitudes at particular frequencies.
+The detectable energy from any given ray is the energy that is deposited in the frequencies detectable to a seismometer.
+According to Wikipedia, some seismometers can measure frequencies from 500 Hz to 0.00118 Hz.
+The lunar seismometers are considerably less sensitive, and have useful range 0.004 Hz to 2 Hz according to Wikipedia.
+There seems to be a total of 12 lunar seismometers.
+
+Along with the use of the HEALPy package, we will be able to create a map on the sphere of maximum intensity for every distance $D$ of closest approach of a macro.
+The average detectable surface area of a macro impact is then a weighted average of these detectable surface areas for specific $D$.
+How do we weight the different $D$'s?
+
+Suppose now that the macros impact the earth from all directions with equal likelihood.
+Consider any one of these macros.
+It sees a line, and it has equal likelihood of being any distance away from the origin.
+Now, since each point on the line exists as part of a circular cross-section, the associated distance has weight $2\pi R_{\te{Earth}}$.
+That's it!
+Hence, if $A_D$ is a finite set of detectible area measurements over $D = \{D_i:D_i\in[0,R_\te{Earth}],i\in\{1,\dots,N\}\}$.
+Assuming $D_i - D_{i+1}$ is fixed for all $i$, and that $D_N\approx R_{\te{Earth}}$ and $D_1 \approx 0$, then $A=\f{\sum_i A_{D_i}D_i}{\sum_i D_i}$ is the average detectable surface area.
+In the continuous case, this turns into the obvious integral.
+
+Observe that this means that the events closest to the boundary of the earth are weighted the heaviest. These are also the events which deposit the least energy.
+
 \pagebreak

### 2016-08-01 Macro Impacts Revised.tex
Whoops! Transmission+Reflection fixed

@@
 \begin{align}
-A(t+\delta t) = A(t)e^{K\f{\delta t}{Q(r(t)}}\,.
+A(t+\delta t) = A(t)e^{K\f{\delta t}{Q(r(t))}}\,.
 \end{align}
@@
 \td{A}{t}{}&= A(t)\lim_{\delta t\to 0}\f{e^{K\f{\delta t}{Q(r(t))}}-1}{\delta t}\,,\\
+\td{A}{t}{}&= A(t)e^{-K\f{t}{Q(r(t))}}\lim_{\delta t\to 0}\f{e^{K\f{t +\delta t}{Q(r(t))}}-{e^{K\f{t}{Q(r(t))}}}}{\delta t}\,,\\
 \f{1}{A}\td{A}{t}{}&= \f{K}{Q(r(t))}\,,\\
@@
 *Relevant paper on my phone*
+\\\\
+We begin with an amplitude $A(k,t)$, a function of amplitude and wave number, gotten from the Fourier decomposition of the source.
+Since the source depends on the wave vector, it is important to use spherical coordinates in phase space.
+It may be reasonable to just use the first order terms in $k$ since the lunar seismometers measure from  0.004 Hz to 2 Hz.
+However, second and third order terms may be desirable, given that signifiant portions of the measurable range lie at order unity.
+These are gotten by selectively truncating the hypergeometric series in section 2.
 \pagebreak
@@
 Hence, if $A_D$ is a finite set of detectible area measurements over $D = \{D_i:D_i\in[0,R_\te{Earth}],i\in\{1,\dots,N\}\}$.
-Assuming $D_i - D_{i+1}$ is fixed for all $i$, and that $D_N\approx R_{\te{Earth}}$ and $D_1 \approx 0$, then $A=\f{\sum_i A_{D_i}D_i}{\sum_i D_i}$ is the average detectable surface area.
-In the continuous case, this turns into the obvious integral.
+Assuming $D_i - D_{i+1}$ is fixed for all $i$, and that $D_N\approx R_{\te{Earth}}$ and $D_1 \approx 0$, then
+\begin{align}
+A=\f{\sum_i A_{D_i}D_i}{\sum_i D_i}\,,
+\end{align}
+is the average detectable surface area. In the continuous case, this turns into the obvious integral.
 

### 2016-08-01 Ray-Tracing/Ray_Tracing_Revised.m

@@ -7,17 +7,17 @@ format long
 %INPUTS
 
 M = 1; %NUMBER OF POINTS ON THE LINE
-N = 10000; %NUMBER OF RAYS FROM EACH POINT
+N = 5000; %NUMBER OF RAYS FROM EACH POINT
 
 a = [11.2633,10.6835,15.4938].^(1/2); %THESE ARE THE CONSTANT TERMS IN THE PARABOLIC VELOCITY FIELD STRUCTURE, THE FIRST ENTRY CORRESPONDING TO THE CORE
 b = [1.55946*10^(-7),2.11853*10^(-7),1.40336*10^(-7)].^(1/2); %THESE ARE THE COEFFICIENTS OF THE QUADRATIC TERM IN THE VELOCITY FIELD
 
 D = 6370; %THE DISTANCE OF CLOSEST APPROACH TO THE CENTER
 Radii = [0,1221,3480,6371]; %NOTE THAT WE MUST TAKE 0 AS A LAYER FOR TECHNICAL PURPOSES
-ACO = 5; %IT TAKES 5 ITERATIONS FOR A RAY TO PASS ENTIRELY THROUGH THE EARTH
+ACO = 8; %IT TAKES 5 ITERATIONS FOR A RAY TO PASS ENTIRELY THROUGH THE EARTH
 
-Q = ; %THE QUALITY FACTOR AS A FUNCTION OF FREQUENCY, TIME, AND SO ON... TBD
-A = ; %THE AMPLITUDE OF THE WAVE AS A FUNCTION OF FREQUENCY
+%Q = ; %THE QUALITY FACTOR AS A FUNCTION OF FREQUENCY, TIME, AND SO ON... TBD
+%A = ; %THE AMPLITUDE OF THE WAVE AS A FUNCTION OF FREQUENCY
 
 rhoBoundaries = [ 12.76, 12.17; 9.90, 5.57; 1.02, 1.25*(10^(-3))].*(10^12); %THE DENSITY OF THE MEDIA AT THEIR DISCONTINUOUS BOUNDARIES - THE LEFT ENTRY IN EACH ROW CORRESPONDS TO THE INNER DENSITY AND THE RIGHT CORRESPONDS TO THE OUTER DENSITY
 
@@ -182,6 +182,7 @@ for i = 1 : ACO
         
             TempDisp = RayArrayAngDisp(TempId);
             TempTime = RayArrayTime(TempId);
+            TempAmp = RayArrayAmp(TempId);
         
[…]

### 2016-08-01 Ray-Tracing/ReflectionCoefficient.m

@@ -1,7 +1,7 @@
-function R = ReflectionCoefficient(LayerId,sinTheta,AlphaRay,v1,v2,rho1,rho2)
+function R = ReflectionCoefficient(LayerId,TempAmp,sinTheta,AlphaRay,v1,v2,rho1,rho2)
 %The fluid in which the wave arrives is labeled 1
 %   Detailed explanation goes here
-    R = 1 - TransmissionCoefficient(LayerId,sinTheta,AlphaRay,v1,v2,rho1,rho2);
+    R = 1 - TransmissionCoefficient(LayerId,TempAmp,sinTheta,AlphaRay,v1,v2,rho1,rho2);
     
 end
 

### 2016-08-01 Ray-Tracing/TransmissionCoefficient.m

@@ -1,4 +1,4 @@
-function T = TransmissionCoefficient(LayerId,sinTheta,AlphaRay,v1,v2,rho1,rho2)
+function T = TransmissionCoefficient(LayerId,TempAmp,sinTheta,AlphaRay,v1,v2,rho1,rho2)
 %The fluid in which the wave arrives is labeled 1
 %   Detailed explanation goes here
     
@@ -10,9 +10,9 @@ function T = TransmissionCoefficient(LayerId,sinTheta,AlphaRay,v1,v2,rho1,rho2)
     Thigh = Tpre > 1;
     Tlow = Tpre < 0;
     Tmid = (true(size(Tpre)) & (~ Thigh)) & (~ Tlow);
-    T(Thigh) = 1;
+    T(Thigh) = TempAmp(Thigh);
     T(Tlow) = 0;
-    T(Tmid) = Tpre(Tmid);
+    T(Tmid) = Tpre(Tmid).*TempAmp(Tmid);
     
 end
 

### 2016-08-03 Macro Impacts Revised.tex
Energy after attenuation

@@
 \end{align}
-From this, we find that the energy in the lowest modes is
+From this, we find that the energy to leading order is
 \begin{align}
@@
 Something makes me think that $\csc^2(2\theta)$ should be absorbed into the definition of $\Sigma$, but I don't know how to show this.
-\section{}
-For a given macro of given cross-section and velocity, how much energy gets deposited into seismic waves that propagated unattenuated?
-A better question: as a function of the sensitivity of a seismometer, will the seismometers have measured the macro?
-Look at the lunar limits.
 \pagebreak
@@
 These are gotten by selectively truncating the hypergeometric series in section 2.
+\\\\
+According to ``Seismic viscoelastic attenuation,''
+\begin{align}
+Q_p = \f94 Q_s\,,
+\end{align}
+for a Poisson solid ($v_p =\sqrt3v_s$) which is close enough for our purposes.
+\\\\
+On the moon, the very preliminary model has $Q_p$ as a piecewise constant function.
+Therefore, we can do away with the complication of path dependence, and simply break the moon into layers corresponding to these regions.
+\pagebreak
+\section{Specifics of the Moon Model}
+For the region $r \in [380\te{km},1709.1\te{km}]$ the velocity is given by $a^2 - b^2 r^2$ where $a^2 = 8.26955$ and $b^2 = 2.47697\times 10^{-7}$.
+The velocity in the core is not well known, but because it is small, our calculation will be minimally affected by it, so we extrapolate from the mantle.
+In the last 28km, the VPREMOON indicates that for $r\in [1709.1,1725.1]$ the velocity is $5.50\te{km\,s}^{-1}$, for $r\in[1725.1,1736.1]$ the velocity is $3.20\te{km\,s}^{-1}$, and for $r\in[1736.1,1737.1]$ the velocity is $1.00\te{km\,s}^{-1}$.
+\\\\
+Unfortunately for my computer, this means that we must break down the moon into four separate layers simply because of the discontinuity of the velocity field.
+The other component of the model that requires additional iteration is the quality factor $Q_p$ whose value is piecewise constant as a function of $r$.
+There are 5 regions.
+Unfortunately, none of these regions share their boundaries with those of the velocity field.
+Therefore we have a total of 8 regions.
+Therefore, the algorithm must be run 16 times if we are to get propagation from one side of the moon to the other.
+That's quite a bit...
+\\\\
+To keep track of the quality factor, we need to be able to pointwise multiply $e^{-\f{k}{2Q}t}$ by $A(k)$.
+The problem is that Matlab doesn't really do functions...
+Well...
+Suppose we start with an amplitude $A(0,k)$, and that the ray propagates through a region of quality factor $Q_1$ for time $\Delta t_1$.
+Then the amplitude after the propagation is $A(\Delta t_1, k)=A(0,k)F_1 e^{-\f{k}{2Q_1}\Delta t_1}$, where $F_1$ is a transmission or reflection coefficient, which is not a function of $k$.
+Now, suppose it propagates through another region with quality factor $Q_2$ for $\Delta t_2$.
+Then we have $A(\Delta t_1 + \Delta t_2, k)=A(0,k)F_1F_2 e^{-\f{k}{2}\p{\f{\Delta t_1}{Q_1}+\f{\Delta t_2}{Q_2}}}$.
+That's straight forward enough.
+Therefore, to understand what happens to a general ray's amplitude, we only need to know two things:
+\begin{align}
+F &= \prod_i F_i\,,\\
+\f{T}{Q} &= \sum_i\f{\Delta t_i}{Q_i}\,.
+\end{align}
+Now, after the algorithm has been run, and we want to know how much energy is left in a particular ray with initial amplitude distribution $A(k)$, we calculate the energy associated to $\tilde A(k) = A(k)Fe^{-\f{k}{2}\f{T}{Q}}$.
+That's not hard.
+Moreover, we only want to obtain the total detectible energy i.e.
+the energy of those modes in the the frequency range $[0.004,2]\te{Hz}$.
+This translates to the wave number range $[0.025,12.6]$ (since we use the velocity near the surface for measurement, which is $1\te{km\,s}^{-1}$).
+\\\\
+The notion of ray tracing is based in the Eikonal approximation, where a wave evolves in a coherent fashion.
+Each ray can be thought of as containing $1/N$ the total amount of energy, where $N$ is the total number of rays (in the program this is just $N\times M$).
+Thus, the energy of an individual ray will be multiplied by $N^{-1}$.
+
+Now, assuming we've got a pressure wave of the form (that I describe in section 2)
+\begin{align}
+P(\vec k)=\f{4\pi p_0}{\sqrt{N}k\cos\theta}\sin\p{\f{h k\cos\theta}{2}}(b^2f_1(b)-a^2f_1(a))
+\end{align}
+After attenuation, the form of the wave is
+\begin{align}
+\tilde P(\vec k) = P(\vec k)Fe^{-\f{k}{2}\f{T}{Q}}\,.
+\end{align}
+Observe that truncating the hypergeometric function at leading order is an overestimate for all $k$ and $\theta$ (since $F:[0,\infty)\to[0,1]$), so using my approximation is fine.
+The energy of a ray is not really a well defined quantity since a ray itself is somewhat of an infinitesimal wave packet, and is somewhat analogous to a test particle etc.
+One way, however, to extract a usable quantity is to think of a ray as representing one $N$th of the whole wave, and to simply calculate its energy as though it exists throughout the whole space.
+A complication arises from the $r$ dependence of $\rho$ and $\lambda + 2\mu$.
+Because we are only really interested in orders of magnitude, it's fairly reasonable to take $\rho$ and $\lambda + 2\mu$ as their weighted averages, i.e.
+\begin{align}
+\bar\rho = \f{3}{R_{\te{Moon}}^3}\int r^2\diff r\rho(r)
+\end{align}
+and
+\begin{align}
+\overline{\lambda + 2\mu} =  \f{3}{R_{\te{Moon}}^3}\int r^2\diff r\p{\lambda(r) + 2\mu(r)}\,.
+\end{align}
+\pagebreak
+\section{Inhomogeneous}
+Given that we are only looking for numerical results, let's consider the inhomogeneous Moon. The energy deposition is
+\begin{align}
+\td{E}{x}{} = \rho(r)\sigma_X v_X^2\,.
+\end{align}
+Now, the total energy deposition of a macro is
+\begin{align}
+E =2\sigma_X v_X^2 \int_0^{R_{\te{Moon}}}\diff r\rho(r)\,.
+\end{align}
+$\rho = a-b(x-c)^2$ where $a=3.446$, $b = 5\times 10^{-8}$ and $c = 70$, ($\rho$ is given in $\te{kg\,cm}^{-1}$), except for $r<380\te{km}$ where $\rho =5.171\te{kg\,cm}^{-1}$.
+\\\\
+Now, if we're interested in the energy allocated to each ray, let $M$ be the number of points on the source line from which rays will propagate, and let $N$ be the number of rays from each point.
+The energy in the slice (of length $l$) corresponding to some point $m$ is then
+\begin{align}
+E_m = 2\sigma_X v_X^2\int_{x_0(m)- l/2}^{x_0(m) + l/2}\diff r\rho(r)\,.
+\end{align}
+Since $\rho$ is approximately constant over the interval $x_0(m)$, it is reasonable to write
+\begin{align}
+E_m = 2\sigma_Xv_X^2 l\rho(x_0(m))\,.
+\end{align}
+This above expression will be used in the program.
+\\\\
+Now, in the neighborhood of the point, the moon is approximately homogeneous, and so the machinery from earlier works. We consider a pressure source of the form
+\begin{align}
+p=p_0f(r)\ps{\theta\p{z+\f l2}-\theta\p{z-\f l2}}
+\end{align}
+where we've aligned our axes with the trajectory of the macro.
+Since $l$ is not necessarily large with respect to $\lambda_0$, we have to use the full expression from section 2.
+The energy of this pressure source is
+\begin{align}
+E_m = \f{\lambda_m + 2\mu_m}{K_m^2} l p_0(m)^2\int r\diff r f(r)^2
+\end{align}
+We can now fix $p_0(m)$,
+\begin{align}
+p_0(m)^2 = \f{ K_m^2\rho_m}{\lambda_m + 2\mu_m}\f{2l^2\sigma_Xv_X^2}{\int r\diff r f(r)^2}\,.
+\end{align}
+In order to evaluate the effect of the anelastic attenuation we need the spectrum of a ray, and how that relates to the energy of the ray.
+Note, if each of the $M$ segments has $E_m$ energy, and each segment spawns $N$ rays, then each ray has $E_m/N$ energy.
+\\\\
+The energy of a ray is
+\begin{align}
+\f{E_m}{N}=\f{1}{N}\f{\lambda_m+2\mu_m}{K_m^2}\int\f{\diff^3 k}{(2\pi)^3}\abs{P_m(\vec k)}^2
+\end{align}
+where $P(\vec k)$ is given in section 2.
+The quantities out front are that of the neighborhood of the segment since the pressure wave is initially localized in space.
+Since we are only concerned with the measurable energy the integral is only taken over $[0.025,12.6]$.
+Then, after anelastic attenuation and refraction/reflection
+\begin{align}
+\f{E_m'}{N}=\f{1}{N}\f{\lambda_m+2\mu_m}{K_m^2}F_{m,n}^2\int\f{\diff^3 k}{(2\pi)^3}\abs{P_m(\vec k)}^2e^{-k\f{T_{m,n}}{Q_{m,n}}}
+\end{align}
+The approximation (32) holds when $bk_0\ll 1$, and is always an overestimate. Since we know $b$ is on the order of meters, this is, in fact, a good approximation. Thus
+\begin{align}
+\f{E_m'}{N} &= \f{p_0^2}{N}\f{\lambda_m+2\mu_m}{K_m^2}F_{m,n}^2\int\f{\diff^3 k}{(2\pi)^3}\abs{\f{4\pi p_0}{k\cos\theta}\sin\p{\f{h k\cos\theta}{2}}(b^2f_1(b)-a^2f_1(a))}^2e^{-k\f{T_{m,n}}{Q_{m,n}}}\,,\\
+\notag &=\f{Q}{NT^2}F_{m,n}^2e^{-\f{k_0^2T}{Q}}\ps{4T(1-\cos(l k_0)) + \I e^{\f{k_0 T}{Q}} l Q\p{2\te{Ei}\ps{-\I l \notag k_0-\f{k_0 T}{Q}} - 2\te{Ei}\ps{\I l k_0 - \f{k_0 T}{Q}} + \right.\right.\\&\left.\left.+\ln\ps{-\f{Q}{\I l Q+T}}+\ln\notag \ps{-\f{\I l Q + T}{Q}} + 2\ln\ps{\I l - \f{T}{Q}}} - 4 l(Q + k_0 T)\te{Si}\ps{l k_0}}\times\\
+&\times \underbrace{\f{(b^2f_1(b)-a^2f_1(a))^2}{\int r\diff r f(r)^2}}_{A}\rho_m2l^2\sigma_Xv_X^2\,.
+\end{align}
+$A$ is a constant which characterizes the explosion for small $k$. In the case that $f$ is constant, $A = 1$.
 \pagebreak
@@
 \pagebreak
+\section{Thermal Source}
+A simple model for seismic wave generation via macro impact is that a cylinder is heated uniformly.
+Since we are interested in an upper bound to seismic energy generation, it is reasonable to find the optimal volume (i.e.
+radius) and temperature for maximal thermal expansion and minimal energy lost to heating.
+Since the energy lost to heating corresponds to the energy lost in melting, the second requirement is equivalent to minimizing volume...
+
+\end{document}
+
 \section{Melt Zone}
@@
 earth or moon), we'd set $u = v$, and $s = 0$ to eliminate the "eroding" effect.
-\end{document}
 

### 2016-08-03 Ray-Tracing/QualityFactor.m

@@ -1,0 +1,6 @@
+function output = QualityFactor(LayerId,DeltaTime,Q,Suppression)
+%UNTITLED5 Summary of this function goes here
+%   Detailed explanation goes here
+output = Suppression + (DeltaTime./Q(LayerId));
+end
+

### 2016-08-03 Ray-Tracing/RayTracingMoon.m

@@ -205,9 +205,6 @@ for i = 1 : ACO
             end
             RayArrayAmp(TempIdPrime) = ReflectionCoefficient(j,TempAmp,sinAngleOfIncidenceOutward100(TempId),RayArrayAlpha(TempId),vBoundaries(j,1),vBoundaries(j,2),rhoBoundaries(j,1),rhoBoundaries(j,2));
             RayArrayTime(TempIdPrime) = TempTime + SOutward100(TempId) - SXOutward(TempId);
-            
-        %[nnz(SOutward100(TempId) - SXOutward(TempId) < -0.000000000000002),i,j]
-        %[nnz(RayArrayTime(TempId) < -0.000000000000002)]
         
         %TOTALLY REFLECTED OUTWARD BOUND RAYS
         
@@ -215,9 +212,6 @@ for i = 1 : ACO
             RayArrayAlpha(TempIdTIR) = pi - asin(sinAngleOfIncidenceOutward100(TempIdTIR));
             RayArrayx0(TempIdTIR) = Radii(j + 1);
             RayArrayTime(TempIdTIR) = RayArrayTime(TempIdTIR) + SOutward100(TempIdTIR) - SXOutward(TempIdTIR);
-            
-        %[nnz(SOutward100(TempIdTIR) - SXOutward(TempIdTIR) < -0.000000000000002),i,j]
-        %[nnz(RayArrayTime(TempIdTIR) < -0.000000000000002)]
         
         end
         

### 2016-08-03 Ray-Tracing/Ray_Tracing_Moon.m

@@ -9,17 +9,22 @@ format long
 M = 1; %NUMBER OF POINTS ON THE LINE
 N = 5000; %NUMBER OF RAYS FROM EACH POINT
 
-a = [11.2633,10.6835,15.4938].^(1/2); %THESE ARE THE CONSTANT TERMS IN THE PARABOLIC VELOCITY FIELD STRUCTURE, THE FIRST ENTRY CORRESPONDING TO THE CORE
-b = [1.55946*10^(-7),2.11853*10^(-7),1.40336*10^(-7)].^(1/2); %THESE ARE THE COEFFICIENTS OF THE QUADRATIC TERM IN THE VELOCITY FIELD
+a = [8.26955,8.26955,8.26955,8.26955,8.26955,5.5,3.2,1.0].^(1/2); %THESE ARE THE CONSTANT TERMS IN THE PARABOLIC VELOCITY FIELD STRUCTURE, THE FIRST ENTRY CORRESPONDING TO THE CORE
+b = [2.47697*10^(-7),2.47697*10^(-7),2.47697*10^(-7),2.47697*10^(-7),2.47697*10^(-7),10^(-11),10^(-11),10^(-11)].^(1/2); %THESE ARE THE COEFFICIENTS OF THE QUADRATIC TERM IN THE VELOCITY FIELD
 
 D = 6370; %THE DISTANCE OF CLOSEST APPROACH TO THE CENTER
-Radii = [0,1221,3480,6371]; %NOTE THAT WE MUST TAKE 0 AS A LAYER FOR TECHNICAL PURPOSES
+Radii = [0,961.7,1231.7,1461.7,1671.7,1709.1,1725.1,1736.1,1737.1]; %NOTE THAT WE MUST TAKE 0 AS A LAYER FOR TECHNICAL PURPOSES
 ACO = 8; %IT TAKES 5 ITERATIONS FOR A RAY TO PASS ENTIRELY THROUGH THE EARTH
 
-%Q = ; %THE QUALITY FACTOR AS A FUNCTION OF FREQUENCY, TIME, AND SO ON... TBD
-%A = ; %THE AMPLITUDE OF THE WAVE AS A FUNCTION OF FREQUENCY
+Q = [675,1125,3375,9000,6750,6750,6750,6750]; %THE QUALITY FACTOR AS A FUNCTION OF FREQUENCY, TIME, AND SO ON... TBD
 
[…]

### 2016-08-03 Ray-Tracing/Ray_Tracing_Revised.m

@@ -75,6 +75,7 @@ RandZ = -sin(Beta).*RandYrote + cos(Beta).*RandZrote;
 
 RayArrayx0 = zeros(M,N,2^(ACO));
 RayArrayAmp = zeros(M,N,2^(ACO));
+RayArraySup = zeros(M,N,2^(ACO));
 RayArrayAngDisp = zeros(M,N,2^(ACO));
 RayArrayAlpha = zeros(M,N,2^(ACO));
 RayArrayTime = zeros(M,N,2^(ACO));
@@ -205,9 +206,6 @@ for i = 1 : ACO
             end
             RayArrayAmp(TempIdPrime) = ReflectionCoefficient(j,TempAmp,sinAngleOfIncidenceOutward100(TempId),RayArrayAlpha(TempId),vBoundaries(j,1),vBoundaries(j,2),rhoBoundaries(j,1),rhoBoundaries(j,2));
             RayArrayTime(TempIdPrime) = TempTime + SOutward100(TempId) - SXOutward(TempId);
-            
-        %[nnz(SOutward100(TempId) - SXOutward(TempId) < -0.000000000000002),i,j]
-        %[nnz(RayArrayTime(TempId) < -0.000000000000002)]
         
         %TOTALLY REFLECTED OUTWARD BOUND RAYS
         
@@ -215,9 +213,6 @@ for i = 1 : ACO
             RayArrayAlpha(TempIdTIR) = pi - asin(sinAngleOfIncidenceOutward100(TempIdTIR));
             RayArrayx0(TempIdTIR) = Radii(j + 1);
             RayArrayTime(TempIdTIR) = RayArrayTime(TempIdTIR) + SOutward100(TempIdTIR) - SXOutward(TempIdTIR);
-            
-        %[nnz(SOutward100(TempIdTIR) - SXOutward(TempIdTIR) < -0.000000000000002),i,j]
-        %[nnz(RayArrayTime(TempIdTIR) < -0.000000000000002)]
         
         end
         
@@ -262,18 +257,12 @@ for i = 1 : ACO
         RayArrayAmp(TempIdPrime) = ReflectionCoefficient(j,TempAmp,sinAngleOfIncidenceInward000(TempId),RayArrayAlpha(TempId),vBoundaries(j,1),vBoundaries(j,2),rhoBoundaries(j,1),rhoBoundaries(j,2));
         RayArrayTime(TempIdPrime) = TempTime + SInward000(TempId) - SXInward(TempId);
         
[…]

### 2016-08-03 Ray-Tracing/Ray_Tracing_Sparse.m

@@ -73,17 +73,16 @@ RandX = RandXrote;
 RandY = cos(Beta).*RandYrote + sin(Beta).*RandZrote;
 RandZ = -sin(Beta).*RandYrote + cos(Beta).*RandZrote;
 
-RayArrayx0 = zeros(M,N,2^(ACO));
-RayArrayAmp = zeros(M,N,2^(ACO));
-RayArrayAngDisp = zeros(M,N,2^(ACO));
-RayArrayAlpha = zeros(M,N,2^(ACO));
-RayArrayTime = zeros(M,N,2^(ACO));
+RayArrayx0 = sparse(M,N,2^(ACO));
+RayArrayAmp = sparse(M,N,2^(ACO));
+RayArrayAngDisp = sparse(M,N,2^(ACO));
+RayArrayAlpha = sparse(M,N,2^(ACO));
+RayArrayTime = sparse(M,N,2^(ACO));
 
 %ASSIGNMENT OF INITIAL CONDITIONS
 %%{
-RayArrayAlpha(:,:,1) = atan2(RandY,RandX - x0);
-RayArrayx0(:,:,1) = x0(:,:);
-RayArrayx0(:,:,2:2^(ACO)) = NaN;
+RayArrayAlpha(:,:,1) = sparse(atan2(RandY,RandX - x0));
+RayArrayx0(:,:,1) = sparse(x0(:,:));
 RayArrayAmp(:,:,1) = 1;
 RayArrayPlaneAngle = repmat(Alpha,[1,1,2^(ACO + 1)]);
 RayArrayRayAngle = repmat(Beta,[1,1,2^(ACO + 1)]);
@@ -99,34 +98,32 @@ RayArrayRayAngle = repmat(Beta,[1,1,2^(ACO + 1)]);
 %}
 %END TESTING
 
-OutArrayAngDisp = zeros(M,N,2^(ACO + 1));
-OutArrayAmp = zeros(M,N,2^(ACO + 1));
-OutArrayTime = zeros(M,N,2^(ACO + 1));
+OutArrayAngDisp = sparse(M,N,2^(ACO + 1));
+OutArrayAmp = sparse(M,N,2^(ACO + 1));
+OutArrayTime = sparse(M,N,2^(ACO + 1));
 
-SOutward100 = zeros(M,N,2^(ACO));
-SInward000 = zeros(M,N,2^(ACO));
-SInward001 = zeros(M,N,2^(ACO));
[…]

### 2016-08-03 Macro Impacts Revised.tex
correction

@@
 \end{align}
-The approximation (32) holds when $bk_0\ll 1$, and is always an overestimate. Since we know $b$ is on the order of meters, this is, in fact, a good approximation. Thus
+The approximation (32) holds when $bk_0\ll 1$, and is always an overestimate. Since we know $b$ is on the order of meters, this is, in fact, a good approximation ($k_0$ is of order millimeters). Thus
 \begin{align}
@@
 \end{align}
-$A$ is a constant which characterizes the explosion for small $k$. In the case that $f$ is constant, $A = 1$.
+$A$ is a constant which characterizes the explosion for small $k$.
+In the case that $f$ is constant, $A = f\times (b^2-a^2)$.
+If $f$ is the triangle from section 2, then $A = \f16\Delta r(3r_0 + 2\Delta r)$.
 \pagebreak

### 2016-08-03 Macro Impacts Revised.tex
nice analysis

@@
 If $f$ is the triangle from section 2, then $A = \f16\Delta r(3r_0 + 2\Delta r)$.
+When $T$ is zero, we get the result from section 2, which goes approximately as $k_0^2$.
+A quick plot of $E_m'$ shows that it goes as $k_0^2$ for small $k_0$ but asymptotes to a constant value.
+This constant value is achieved slower for larger $Q$ (or smaller $T$).
+In essence, this shows how the higher frequency terms stop contributing, and the small $k$ terms dominate.
 \pagebreak

### 2016-08-03 Macro Impacts Revised.tex
update
Update

@@
 \begin{align}
-\f{E_m'}{N} &= \f{p_0^2}{N}\f{\lambda_m+2\mu_m}{K_m^2}F_{m,n}^2\int\f{\diff^3 k}{(2\pi)^3}\abs{\f{4\pi p_0}{k\cos\theta}\sin\p{\f{h k\cos\theta}{2}}(b^2f_1(b)-a^2f_1(a))}^2e^{-k\f{T_{m,n}}{Q_{m,n}}}\,,\\
+\f{E_m'}{N} &= \f{1}{N}\f{\lambda_m+2\mu_m}{K_m^2}F_{m,n}^2\int\f{\diff^3 k}{(2\pi)^3}\abs{\f{4\pi p_0}{k\cos\theta}\sin\p{\f{h k\cos\theta}{2}}(b^2f_1(b)-a^2f_1(a))}^2e^{-k\f{T_{m,n}}{Q_{m,n}}}\,,\\
 \notag &=\f{Q}{NT^2}F_{m,n}^2e^{-\f{k_0^2T}{Q}}\ps{4T(1-\cos(l k_0)) + \I e^{\f{k_0 T}{Q}} l Q\p{2\te{Ei}\ps{-\I l \notag k_0-\f{k_0 T}{Q}} - 2\te{Ei}\ps{\I l k_0 - \f{k_0 T}{Q}} + \right.\right.\\&\left.\left.+\ln\ps{-\f{Q}{\I l Q+T}}+\ln\notag \ps{-\f{\I l Q + T}{Q}} + 2\ln\ps{\I l - \f{T}{Q}}} - 4 l(Q + k_0 T)\te{Si}\ps{l k_0}}\times\\
@@
 When $T$ is zero, we get the result from section 2, which goes approximately as $k_0^2$.
-A quick plot of $E_m'$ shows that it goes as $k_0^2$ for small $k_0$ but asymptotes to a constant value.
+A quick plot of $E_m'$ shows that it goes as $k_0^2$ for small $k_0$ but asymptotes to a constant value (more precisely, it goes as the expression in section 2).
 This constant value is achieved slower for larger $Q$ (or smaller $T$).
 In essence, this shows how the higher frequency terms stop contributing, and the small $k$ terms dominate.
+Note that $Q$ is on the order of $10^2$ or $10^3$, while $T$ is likely on the order of $10^3$ (seconds).
+\\\\
+In the case that $\f{T}{Q}\gg 1$, then $k_0\to\infty$ is close to the actual value. In this case, the limit is just
+\begin{align}
+E_m'\leq F_{m,n}^24 l p_0^2 \f{Q^2}{T^2} \arctan\ps{l\f{Q}{T}} A\rho_m2l^2\sigma_Xv_X^2\,.
+\end{align}
+Unfortunately, this approximation does not hold for rays originating near the surface (which always exist for our line source), since $Q_p$ near the surface is large and $T$ is small.
+In this case, we can use the expression from section 1.
+But when our computers are super fast, why approximate?
+\\\\
+Now, for a ray that immediately hits the surface, its energy must be the same as when it started. This corresponds to $T = \to 0$, and
+\begin{align}
+E_m = 4l E_mAF_{m,n}^2\p{-2k_0+k_0\cos(h k_0)+\f{\sin(h k_0)}{h}+h k_0^2\te{Si}(h k_0)}
+\end{align}
+where we've taken $l\rho_m\sigma_Xv_X^2=E_m$.
+\begin{align}
+ \p{4lF_{m,n}^2\p{-2k_0+k_0\cos(h k_0)+\f{\sin(h k_0)}{h}+h k_0^2\te{Si}(h k_0)}}^{-1}=  A
+\end{align}
+These units are way wrong. Gonna fix tomorrow.
 \pagebreak
@@
 Since the energy lost to heating corresponds to the energy lost in melting, the second requirement is equivalent to minimizing volume...
-
-\end{document}
-
+\pagebreak
 \section{Melt Zone}
@@
 
+\end{document}
+
 What is the area per year covered by these non-linear zones as a function of macro mass, volume etc (contour plot).

### 2016-08-03 Macro Impacts Revised.tex
Attenuation *possibly* figured out

@@
 \\\\
-To keep track of the quality factor, we need to be able to pointwise multiply $e^{-\f{k}{2Q}t}$ by $A(k)$.
+To keep track of the quality factor, we need to be able to pointwise multiply $e^{-\f{vk}{2Q}t}$ by $A(k)$.
 The problem is that Matlab doesn't really do functions...
@@
 Suppose we start with an amplitude $A(0,k)$, and that the ray propagates through a region of quality factor $Q_1$ for time $\Delta t_1$.
-Then the amplitude after the propagation is $A(\Delta t_1, k)=A(0,k)F_1 e^{-\f{k}{2Q_1}\Delta t_1}$, where $F_1$ is a transmission or reflection coefficient, which is not a function of $k$.
+Then the amplitude after the propagation is $A(\Delta t_1, k)=A(0,k)F_1 e^{-\f{kv}{2Q_1}\Delta t_1}$, where $F_1$ is a transmission or reflection coefficient, which is not a function of $k$.
 Now, suppose it propagates through another region with quality factor $Q_2$ for $\Delta t_2$.
-Then we have $A(\Delta t_1 + \Delta t_2, k)=A(0,k)F_1F_2 e^{-\f{k}{2}\p{\f{\Delta t_1}{Q_1}+\f{\Delta t_2}{Q_2}}}$.
+Then we have $A(\Delta t_1 + \Delta t_2, k)=A(0,k)F_1F_2 e^{-\f{k}{2}\p{\f{\Delta t_1v_1}{Q_1}+\f{\Delta t_2v_2}{Q_2}}}$.
+We take $v_i$ to be the average velocity in a given region.
+This is a fine approximation since the velocity doesn't vary much within the moon.
 That's straight forward enough.
@@
 F &= \prod_i F_i\,,\\
-\f{T}{Q} &= \sum_i\f{\Delta t_i}{Q_i}\,.
+\f{T}{Q} &= \sum_i\f{\Delta t_i v_i}{Q_i}\,.
 \end{align}
@@
 \begin{align}
-p_0(m)^2 = \f{ K_m^2\rho_m}{\lambda_m + 2\mu_m}\f{2l^2\sigma_Xv_X^2}{\int r\diff r f(r)^2}\,.
+p_0(m)^2 = \f{ K_m^2}{\lambda_m + 2\mu_m}\f{2\rho_m\sigma_Xv_X^2}{\int r\diff r f(r)^2}\,.
 \end{align}
@@
 \f{E_m'}{N} &= \f{1}{N}\f{\lambda_m+2\mu_m}{K_m^2}F_{m,n}^2\int\f{\diff^3 k}{(2\pi)^3}\abs{\f{4\pi p_0}{k\cos\theta}\sin\p{\f{h k\cos\theta}{2}}(b^2f_1(b)-a^2f_1(a))}^2e^{-k\f{T_{m,n}}{Q_{m,n}}}\,,\\
-\notag &=\f{Q}{NT^2}F_{m,n}^2e^{-\f{k_0^2T}{Q}}\ps{4T(1-\cos(l k_0)) + \I e^{\f{k_0 T}{Q}} l Q\p{2\te{Ei}\ps{-\I l \notag k_0-\f{k_0 T}{Q}} - 2\te{Ei}\ps{\I l k_0 - \f{k_0 T}{Q}} + \right.\right.\\&\left.\left.+\ln\ps{-\f{Q}{\I l Q+T}}+\ln\notag \ps{-\f{\I l Q + T}{Q}} + 2\ln\ps{\I l - \f{T}{Q}}} - 4 l(Q + k_0 T)\te{Si}\ps{l k_0}}\times\\
-&\times \underbrace{\f{(b^2f_1(b)-a^2f_1(a))^2}{\int r\diff r f(r)^2}}_{A}\rho_m2l^2\sigma_Xv_X^2\,.
+\notag &=\f{Q}{NT^2}e^{-\f{k_0^2T}{Q}}\ps{4T(1-\cos(l k_0)) + \I e^{\f{k_0 T}{Q}} l Q\p{2\te{Ei}\ps{-\I l \notag k_0-\f{k_0 T}{Q}} - 2\te{Ei}\ps{\I l k_0 - \f{k_0 T}{Q}} + \right.\right.\\&\left.\left.+\ln\ps{-\f{Q}{\I l Q+T}}+\ln\notag \ps{-\f{\I l Q + T}{Q}} + 2\ln\ps{\I l - \f{T}{Q}}} - 4 l(Q + k_0 T)\te{Si}\ps{l k_0}}\times\\
+&\times (b^2f_1(b)-a^2f_1(a))^2\f{\lambda_m+2\mu_m}{K_m^2}F_{m,n}^2p_0(m)^2\,,\\
+\notag &=\f{Q}{NT^2}e^{-\f{k_0^2T}{Q}}\ps{4T(1-\cos(l k_0)) + \I e^{\f{k_0 T}{Q}} l Q\p{2\te{Ei}\ps{-\I l \notag k_0-\f{k_0 T}{Q}} - 2\te{Ei}\ps{\I l k_0 - \f{k_0 T}{Q}} + \right.\right.\\&\left.\left.+\ln\ps{-\f{Q}{\I l Q+T}}+\ln\notag \ps{-\f{\I l Q + T}{Q}} + 2\ln\ps{\I l - \f{T}{Q}}} - 4 l(Q + k_0 T)\te{Si}\ps{l k_0}}\times\\
+&\times \underbrace{\f{(b^2f_1(b)-a^2f_1(a))^2}{\int r\diff r f(r)^2}}_{A}F_{m,n}^2 2\rho_m\sigma_Xv_X^2\,.
 \end{align}
@@
 \begin{align}
-E_m'\leq F_{m,n}^24 l p_0^2 \f{Q^2}{T^2} \arctan\ps{l\f{Q}{T}} A\rho_m2l^2\sigma_Xv_X^2\,.
+E_m' =  4 l  \f{Q^2}{T^2} \arctan\ps{l\f{Q}{T}} F_{m,n}^2 A2\rho_m\sigma_Xv_X^2\,.
 \end{align}
@@
 \\\\
-Now, for a ray that immediately hits the surface, its energy must be the same as when it started. This corresponds to $T = \to 0$, and
+How do we remove $A$ from this equation?
+\\\\
+Now, for a ray that immediately hits the surface, its energy must be the same as when it started. This corresponds to $T = \to 0$ and $F_{m,n} = 1$
 \begin{align}
-E_m = 4l E_mAF_{m,n}^2\p{-2k_0+k_0\cos(h k_0)+\f{\sin(h k_0)}{h}+h k_0^2\te{Si}(h k_0)}
+E_m = 4\p{-2k_0+k_0\cos(l k_0)+\f{\sin(h k_0)}{l}+l k_0^2\te{Si}(l k_0)} A \td{E}{x}{}(m)\,.
 \end{align}
-where we've taken $l\rho_m\sigma_Xv_X^2=E_m$.
+Hence
 \begin{align}
- \p{4lF_{m,n}^2\p{-2k_0+k_0\cos(h k_0)+\f{\sin(h k_0)}{h}+h k_0^2\te{Si}(h k_0)}}^{-1}=  A
+A = \f{l}{4} \p{-2k_0+k_0\cos(l k_0)+\f{\sin(h k_0)}{l}+l k_0^2\te{Si}(l k_0)}^{-1}\,.
 \end{align}
-These units are way wrong. Gonna fix tomorrow.
+This is, really, an upper bound to what $A$ can be, since $A$ really depends on $m$.
+When we fix $A$, we lose information about how the frequencies are distributed, and we, in some sense, assume that all the energy from the explosion is initially concentrated in the lower frequencies.
+This is good for an upper estimate of the energy felt by seismometers.
+Note, for bigger $k_0$, $E_m$ experiences a faster drop-off as $T$ gets big.
 \pagebreak
@@
 The model above produces a set of positions on a sphere along with their associated times of impact and relative amplitudes at particular frequencies.
-The detectable energy from any given ray is the energy that is deposited in the frequencies detectable to a seismometer.
+The detectable energy from any given ray is the energy that is depositied in the frequencies detectable to a seismometer.
 According to Wikipedia, some seismometers can measure frequencies from 500 Hz to 0.00118 Hz.

### 2016-08-03 Macro Impacts Revised.tex
Figured out why I was confused, and all is well

@@
 \\\\
-Now, for a ray that immediately hits the surface, its energy must be the same as when it started. This corresponds to $T = \to 0$ and $F_{m,n} = 1$
+Now, for a ray that immediately hits the surface, its energy must be the same as when it started. This corresponds to $T \to 0$ and $F_{m,n} = 1$
 \begin{align}
@@
 \end{align}
-This is, really, an upper bound to what $A$ can be, since $A$ really depends on $m$.
-When we fix $A$, we lose information about how the frequencies are distributed, and we, in some sense, assume that all the energy from the explosion is initially concentrated in the lower frequencies.
+Clearly, a seismometer will not detect all the energy from a macro impact, since it only detects a certain range of frequencies.
+Thus, by fixing $A$ as we have, we are insisting that the energy of the impact is concentrated at lower $k$.
+We are assuming that all the energy from the explosion is initially concentrated in the lower frequencies below $k_0$, and that it is distributed according to the leading order expression inside the integral of (172).
 This is good for an upper estimate of the energy felt by seismometers.
-Note, for bigger $k_0$, $E_m$ experiences a faster drop-off as $T$ gets big.
+Note, for bigger $k_0$, $E_m'$ experiences a faster drop-off as $T$ gets big.
+The choice of $k_0$ is then very important, since it fixes the rate of attenuation.
 \pagebreak

### 2016-08-04 Macro Impacts Revised.tex
UPDATE

@@
 \end{align}
-The approximation (32) holds when $bk_0\ll 1$, and is always an overestimate. Since we know $b$ is on the order of meters, this is, in fact, a good approximation ($k_0$ is of order millimeters). Thus
+The approximation (32) holds when $lk_0\ll 1$, and is always an overestimate. Since we know $b$ is on the order of meters, this is, in fact, a good approximation ($k_0$ is of order millimeters). Thus
 \begin{align}
@@
 Clearly, a seismometer will not detect all the energy from a macro impact, since it only detects a certain range of frequencies.
-Thus, by fixing $A$ as we have, we are insisting that the energy of the impact is concentrated at lower $k$.
+Thus, by fixing $A$ as we have, we are insisting that the energy of the impact be concentrated at lower $k$.
 We are assuming that all the energy from the explosion is initially concentrated in the lower frequencies below $k_0$, and that it is distributed according to the leading order expression inside the integral of (172).
@@
 The choice of $k_0$ is then very important, since it fixes the rate of attenuation.
+As long as $k_0 l<1$, this will be an overestimate.
+\\\\
+One potential flaw with this model is that it DOES over-estimate the effect of anelastic attenuation on the shorter of the long modes, due to the nature of the approximation to the hypergeometric function I used.
 \pagebreak

### 2016-08-04 Ray-Tracing/Ray_Tracing_Moon.m

@@ -26,6 +26,8 @@ rhoBoundaries = [   3.406       ,   3.406               ;...
                     2.762       ,   2.762               ;...
                     2.762       ,   2.600               ].*(10^15); %THE DENSITY OF THE MEDIA AT THEIR DISCONTINUOUS BOUNDARIES - THE LEFT ENTRY IN EACH ROW CORRESPONDS TO THE INNER DENSITY AND THE RIGHT CORRESPONDS TO THE OUTER DENSITY
 
+AverageVelocities = []; %THE AVERAGE VELOCITY IN EACH REGION FOR USE IN CALCULATING ANELASTIC ATTENUATION
+                
 %END INPUTS
 
 

### 2016-08-04 Macro Impacts Revised.tex
Figured out how to make it work!
In a discussion with Josh, we bring up some issues with my method, and
I propose a resolution at the end of page 24.

@@
 \begin{align}
-\f{E_m'}{N}=\f{1}{N}\f{\lambda_m+2\mu_m}{K_m^2}F_{m,n}^2\int\f{\diff^3 k}{(2\pi)^3}\abs{P_m(\vec k)}^2e^{-k\f{T_{m,n}}{Q_{m,n}}}
+\f{E_m'}{N}=\f{1}{N}\f{\lambda_m+2\mu_m}{K_m^2}F_{m,n}\int\f{\diff^3 k}{(2\pi)^3}\abs{P_m(\vec k)}^2e^{-k\f{T_{m,n}}{Q_{m,n}}}
 \end{align}
-The approximation (32) holds when $lk_0\ll 1$, and is always an overestimate. Since we know $b$ is on the order of meters, this is, in fact, a good approximation ($k_0$ is of order millimeters). Thus
+Because $Q_{m,n}$ and $T_{m,n}$ take into account the material properties along the path of the ray, the coefficients out front, which are those of the origin of the ray, act as a normalization, so that in the case of no refraction/reflection and anelastic attenuation the energy is that of the ray at the start of its journey.
+\\\\
+The approximation (32) holds when $bk_0\ll 2$, and is always an overestimate. Since we know $b$ is on the order of meters, this is, in fact, a good approximation ($k_0$ is of order millimeters). Thus
 \begin{align}
-\f{E_m'}{N} &= \f{1}{N}\f{\lambda_m+2\mu_m}{K_m^2}F_{m,n}^2\int\f{\diff^3 k}{(2\pi)^3}\abs{\f{4\pi p_0}{k\cos\theta}\sin\p{\f{h k\cos\theta}{2}}(b^2f_1(b)-a^2f_1(a))}^2e^{-k\f{T_{m,n}}{Q_{m,n}}}\,,\\
+\f{E_m'}{N} &= \f{1}{N}\f{\lambda_m+2\mu_m}{K_m^2}F_{m,n}\int\f{\diff^3 k}{(2\pi)^3}\abs{\f{4\pi p_0}{k\cos\theta}\sin\p{\f{h k\cos\theta}{2}}(b^2f_1(b)-a^2f_1(a))}^2e^{-k\f{T_{m,n}}{Q_{m,n}}}\,,\\
 \notag &=\f{Q}{NT^2}e^{-\f{k_0^2T}{Q}}\ps{4T(1-\cos(l k_0)) + \I e^{\f{k_0 T}{Q}} l Q\p{2\te{Ei}\ps{-\I l \notag k_0-\f{k_0 T}{Q}} - 2\te{Ei}\ps{\I l k_0 - \f{k_0 T}{Q}} + \right.\right.\\&\left.\left.+\ln\ps{-\f{Q}{\I l Q+T}}+\ln\notag \ps{-\f{\I l Q + T}{Q}} + 2\ln\ps{\I l - \f{T}{Q}}} - 4 l(Q + k_0 T)\te{Si}\ps{l k_0}}\times\\
-&\times (b^2f_1(b)-a^2f_1(a))^2\f{\lambda_m+2\mu_m}{K_m^2}F_{m,n}^2p_0(m)^2\,,\\
+&\times (b^2f_1(b)-a^2f_1(a))^2\f{\lambda_m+2\mu_m}{K_m^2}F_{m,n}p_0(m)^2\,,\\
 \notag &=\f{Q}{NT^2}e^{-\f{k_0^2T}{Q}}\ps{4T(1-\cos(l k_0)) + \I e^{\f{k_0 T}{Q}} l Q\p{2\te{Ei}\ps{-\I l \notag k_0-\f{k_0 T}{Q}} - 2\te{Ei}\ps{\I l k_0 - \f{k_0 T}{Q}} + \right.\right.\\&\left.\left.+\ln\ps{-\f{Q}{\I l Q+T}}+\ln\notag \ps{-\f{\I l Q + T}{Q}} + 2\ln\ps{\I l - \f{T}{Q}}} - 4 l(Q + k_0 T)\te{Si}\ps{l k_0}}\times\\
-&\times \underbrace{\f{(b^2f_1(b)-a^2f_1(a))^2}{\int r\diff r f(r)^2}}_{A}F_{m,n}^2 2\rho_m\sigma_Xv_X^2\,.
+&\times \underbrace{\f{(b^2f_1(b)-a^2f_1(a))^2}{\int r\diff r f(r)^2}}_{A}F_{m,n} 2\rho_m\sigma_Xv_X^2\,.
 \end{align}
@@
 \begin{align}
-E_m' =  4 l  \f{Q^2}{T^2} \arctan\ps{l\f{Q}{T}} F_{m,n}^2 A2\rho_m\sigma_Xv_X^2\,.
+E_m' =  4 l  \f{Q^2}{T^2} \arctan\ps{l\f{Q}{T}} F_{m,n} A2\rho_m\sigma_Xv_X^2\,.
 \end{align}
@@
 One potential flaw with this model is that it DOES over-estimate the effect of anelastic attenuation on the shorter of the long modes, due to the nature of the approximation to the hypergeometric function I used.
+\\\\
+POSSIBLE REASONING: This computation is justified in itself, since $b$, even after non-linear evolution, is at most on the order of 10s to 100s of meters - and based on the size of the plastic zone potentially millimeters, $k_0 = 12\te{km}^{-1}$ times $b$ is at most $10^{-1}\ll 2$ so the leading order term in the Hypergeometric series dominates.
+\\\\
+AHA! $k_0$ should be the LOWER frequency i.e. $0.012\te{km}^{-1}$, since any lower would mean it is undetectable, but any higher and we could be over-estimating the amount of attenuation!!!! HAHA!
+\pagebreak
+\section{New Calculation}
+Instead of the hypergeometric function, whose form is unnecessarily linked to the profile of the pressure wave, suppose the pressure wave has the Fourier transform
+\begin{align}
+\f{4\pi p_0}{k\cos\theta}\sin\p{\f{h k\cos\theta}{2}}F(b k\sin\theta)
+\end{align}
+and write
+\begin{align}
+F^2 = \sum_{i = 0}^\infty G_i \times (bk\sin\theta)^i\,.
+\end{align}
+The term $e^{-k\f{Q}{T}}$ tells us at what point we can stop the integral.
 \pagebreak

### 2016-08-05 Macro Impacts Revised.tex
Removed unnecessary section
update

@@
 \begin{align}
-E&\approx\f{\lambda+2\mu}{K^2}\f{p_0^2h\pi^3r_X^4}{\lambda_0^2}\,,\\
+E_{\te{propagated}}&\approx\f{\lambda+2\mu}{K^2}\f{p_0^2h\pi^3r_X^4}{\lambda_0^2}\,,\\
 &=\f{\lambda+2\mu}{K^2}(p_0\sigma_X)^2\f{\pi h}{\lambda_0^2}\,,
@@
 \begin{align}
-E&\approx\f{\lambda+2\mu}{K^2}\f{h p_0^2\pi^3\Delta r^2(3r_0+2\Delta r)^2}{9\lambda_0^2}
+E_{\te{propagated}}&\approx\f{\lambda+2\mu}{K^2}\f{h p_0^2\pi^3\Delta r^2(3r_0+2\Delta r)^2}{9\lambda_0^2}
 \end{align}
 This is what we find out later! I'm legitimately surprised that I didn't make a mistake! Woo!
+\\\\
+The total energy of this general pressure wave is
+\begin{align}
+E_{\te{total}} = 2\pi p_0^2h\f{\lambda+2\mu}{K^2}\int_0^\infty r\diff r f(r)^2\,.
+\end{align}
+Hence, in general
+\begin{align}
+\Xi = \f{2\pi^2}{\lambda_0^2}\f{(b^2 f_1(b)-a^2f_1(a))^2}{\int_0^\infty r\diff r f(r)^2}
+\end{align}
 \pagebreak
@@
 \pagebreak
-\section{New Calculation}
-Instead of the hypergeometric function, whose form is unnecessarily linked to the profile of the pressure wave, suppose the pressure wave has the Fourier transform
+\section{A Good Method of Overestimation}
+Forget about the hypergeometric.
+Take the $f$ source to be of the optimal form to produce seismic waves that will reach the detector, i.e.
+take $f= A\delta(k-k_0)$ where $k_0$ is the lowest frequency of response of the moon seismometers.
+In this case, the total energy of the ray just goes as $e^{-k_0\f{T_{m,n}}{Q_{m,n}}}$.
+According to http://nssdc.gsfc.nasa.gov/nmc/experimentDisplay.do?id=1971-008C-04, the lowest useful range of any of the lunar seismometers (some had higher) was $0.004\te{Hz}$.
+The velocity of p-waves near the surface is $1\te{km\,s}^{-1}$, and so this corresponds to $k_0 = 2\pi\times 0.004\te{km}^{-1}$.
+However, another useful quantity may be the peak response, which is $0.45\te{Hz}$.
+I'll run the model with both of these quantities.
+\pagebreak
+\section{What Counts as Detectable?}
+The most sensitive of the moon seismometers could measure $0.008\te{mgal}=8\times 10^{-8}\te{m\,s}^{-2}$.
+Their mass is approximately $10\te{kg}$, and they are sensitive to displacements down to $0.3\times 10^{-9}\te{m}$.
+If in a HEALPix pixel, the energy density is $\epsilon$, the energy on the seismometer is given by the surface area the seismometer occupies.
+It's radius is $11.5\te{cm}$.
+Call the radius $r_s$, the displacement sensitivity $D$, the mass of the seismometer $M$, and the acceleration sensitivity $A$.
+Then the seismometer will sense $\epsilon$ such that
 \begin{align}
-\f{4\pi p_0}{k\cos\theta}\sin\p{\f{h k\cos\theta}{2}}F(b k\sin\theta)
+\epsilon\f{\pi r_s^2}{MD} \geq A
 \end{align}
-and write
+i.e.
 \begin{align}
-F^2 = \sum_{i = 0}^\infty G_i \times (bk\sin\theta)^i\,.
+\epsilon \geq 6\times 10^{-9} \te{J\,km}^{-2}\,.
 \end{align}
-The term $e^{-k\f{Q}{T}}$ tells us at what point we can stop the integral.
 \pagebreak

### 2016-08-05 Ray-Tracing/Ray_Tracing_Moon.m

@@ -5,18 +5,38 @@ format long
 
 
 %INPUTS
+D = 1000; %THE DISTANCE OF CLOSEST APPROACH TO THE CENTER
+ACO = 9; %IT TAKES 16 ITERATIONS FOR A RAY TO PASS ENTIRELY THROUGH THE MOON
 
-M = 1; %NUMBER OF POINTS ON THE LINE
-N = 5000; %NUMBER OF RAYS FROM EACH POINT
+vX = 250000; %m/s
+sigmaX = 10^(-7)*10^(-4);%kg/m^3
+f0 = 0.004;
 
+M = 10; %NUMBER OF POINTS ON THE LINE
+N = 10; %NUMBER OF RAYS FROM EACH POINT
+%{
+%APPROXIMATION TO OUTER LAYERS
+a = [8.26955,8.26955,8.26955,8.26955,145.46].^(1/2);
+b = [2.47697*10^(-7),2.47697*10^(-7),2.47697*10^(-7),2.47697*10^(-7),0.0000478823].^(1/2);
+Radii = [0,961.7,1231.7,1461.7,1671.7,1737.1];
+AverageV = [8.15502,7.96714,7.81709,7.65888,6.19979];
+Q = [675,1125,3375,9000,6750];
+rhoBoundaries = [   3.406       ,   3.406               ;...
+                    3.379       ,   3.379               ;...
+                    3.350       ,   3.350               ;...
+                    3.318       ,   3.318               ;...
+                    2.762       ,   0.000               ].*(10^15);
+%}
+%%{
+%VPREMOON MODEL
 a = [8.26955,8.26955,8.26955,8.26955,8.26955,5.5,3.2,1.0].^(1/2); %THESE ARE THE CONSTANT TERMS IN THE PARABOLIC VELOCITY FIELD STRUCTURE, THE FIRST ENTRY CORRESPONDING TO THE CORE
 b = [2.47697*10^(-7),2.47697*10^(-7),2.47697*10^(-7),2.47697*10^(-7),2.47697*10^(-7),10^(-11),10^(-11),10^(-11)].^(1/2); %THESE ARE THE COEFFICIENTS OF THE QUADRATIC TERM IN THE VELOCITY FIELD
 
-D = 6370; %THE DISTANCE OF CLOSEST APPROACH TO THE CENTER
[…]

### 2016-08-05 Ray-Tracing/Test_With_Earth_Values.m

@@ -5,53 +5,21 @@ format long
 
 
 %INPUTS
-D = 1000; %THE DISTANCE OF CLOSEST APPROACH TO THE CENTER
-ACO = 9; %IT TAKES 16 ITERATIONS FOR A RAY TO PASS ENTIRELY THROUGH THE MOON
 
-vX = 250000; %m/s
-sigmaX = 10^(-7)*10^(-4);%kg/m^3
-f0 = 0.004;
+M = 1; %NUMBER OF POINTS ON THE LINE
+N = 5000; %NUMBER OF RAYS FROM EACH POINT
 
-M = 10; %NUMBER OF POINTS ON THE LINE
-N = 10; %NUMBER OF RAYS FROM EACH POINT
-%{
-%APPROXIMATION TO OUTER LAYERS
-a = [8.26955,8.26955,8.26955,8.26955,145.46].^(1/2);
-b = [2.47697*10^(-7),2.47697*10^(-7),2.47697*10^(-7),2.47697*10^(-7),0.0000478823].^(1/2);
-Radii = [0,961.7,1231.7,1461.7,1671.7,1737.1];
-AverageV = [8.15502,7.96714,7.81709,7.65888,6.19979];
-Q = [675,1125,3375,9000,6750];
-rhoBoundaries = [   3.406       ,   3.406               ;...
-                    3.379       ,   3.379               ;...
-                    3.350       ,   3.350               ;...
-                    3.318       ,   3.318               ;...
-                    2.762       ,   0.000               ].*(10^15);
-%}
-%%{
-%VPREMOON MODEL
-a = [8.26955,8.26955,8.26955,8.26955,8.26955,5.5,3.2,1.0].^(1/2); %THESE ARE THE CONSTANT TERMS IN THE PARABOLIC VELOCITY FIELD STRUCTURE, THE FIRST ENTRY CORRESPONDING TO THE CORE
-b = [2.47697*10^(-7),2.47697*10^(-7),2.47697*10^(-7),2.47697*10^(-7),2.47697*10^(-7),10^(-11),10^(-11),10^(-11)].^(1/2); %THESE ARE THE COEFFICIENTS OF THE QUADRATIC TERM IN THE VELOCITY FIELD
+a = [11.2633,10.6835,15.4938].^(1/2); %THESE ARE THE CONSTANT TERMS IN THE PARABOLIC VELOCITY FIELD STRUCTURE, THE FIRST ENTRY CORRESPONDING TO THE CORE
[…]

### 2016-08-05 Ray-Tracing/TransmissionCoefficient.m

@@ -1,8 +1,11 @@
 function T = TransmissionCoefficient(LayerId,TempAmp,sinTheta,AlphaRay,v1,v2,rho1,rho2)
 %The fluid in which the wave arrives is labeled 1
 %   Detailed explanation goes here
-    
-    Theta1 = AlphaRay;
+    Theta1 = zeros(size(AlphaRay));
+    Id = AlphaRay < pi / 2;
+    Idp = AlphaRay >= pi / 2;
+    Theta1(Id) = AlphaRay(Id);
+    Theta1(Idp) = pi - AlphaRay(Idp);
     Theta2 = asin(sinTheta);
     Z1 = rho1.* v1;
     Z2 = rho2.* v2;

### 2016-08-05 Ray_Tracing.py

@@ -1,2 +1,15 @@
-f = open('130_Points_on_a_Sphere.txt', 'r')
-x = f.readlines()
+import scipy.io as sio
+
+mat_contents = sio.loadmat('Points.mat')
+
+
+
+
+
+
+#import matlab.engine as ml
+#
+#points = []
+#with open('/Users/David/Macro-Impact/Ray-Tracing/Points.txt') as inputfile:
+#    for line in inputfile:
+#        points.append(line.replace("e","E"))

### 2016-08-05 Macro Impacts Revised.tex
Attenuated Energy

@@
 \begin{align}
-E_{\te{propagated}}&=\f{\lambda+2\mu}{K^2}2p_0^2(b^2f_1(a)-a^2f_1(b))^2\p{-2k_0+k_0\cos(h k_0)+\f{\sin(h k_0)}{h}+h k_0^2\te{Si}(h k_0)}+\scr O(k_0^4)\,,\\
+E_{\te{propagated}}&=\f{\lambda+2\mu}{K^2}2p_0^2(b^2f_1(b)-a^2f_1(a))^2\p{-2k_0+k_0\cos(h k_0)+\f{\sin(h k_0)}{h}+h k_0^2\te{Si}(h k_0)}+\scr O(k_0^4)\,,\\
 &\approx_{h\gg k_0}\f{\lambda+2\mu}{K^2} \f{4 p_0^2h\pi^3(b^2 f_1(b)-a^2f_1(a))^2}{\lambda_0^2}\,.
@@
 I'll run the model with both of these quantities.
+\\\\
+Unfortunately, the above overestimate is too much of an overestimate. It is likely the best line of thinking to use the guessed wave-form. In this case, we have
+\begin{align}
+P(\vec k) = \f{4\pi p_0}{k\cos\theta}\sin\p{\f{h}{2}k\cos\theta}
+\end{align}
+We may just want to do numerical integration. The problem is that these integrals oscillate rather quickly... Another idea is to simply drop all terms that are suppressed by some cutoff factor.
+\pagebreak
+\section{Better Estimate}
+The frequency distribution of the rays is to first order $\f{kb}{2}\ll 1$
+\begin{align}
+P(\vec k) = \f{4\pi p_0}{k\cos\theta}\sin\p{\f{h k\cos\theta}{2}}(b^2f_1(b)-a^2f_1(a))
+\end{align}
+Indeed, since $b$ is on the order of $1\te{m}$, and the frequencies measurable to the lunar seismometers are at most $2\te{Hz}$, we have that $\f{bk}{2}\approx 10^{-3}\ll 1$.
+Now, the attenuated energy in this part of the spectrum goes as
+\begin{align}
+\f{\lambda+2\mu}{K^2}\int\f{\diff^3k}{2\pi}P(\vec k)^2e^{-k\f{T}{Q}}
+\end{align}
+The energy in the range $[k_0,k_1]$ where $\f{k_1 b}{2}\ll 1$. is then
+\begin{align}
+\notag E_{\te{attenuated}} =&\f{\lambda + 2\mu}{K^2}2p_0^2(b^2 f_1(b) - a^2 f_1(a))^2 \f{1}{T^2}e^{-\f{(k_0+k_1)(\I h Q+T)}{Q}} Q\p{-\p{e^{\I h k_0+\f{k_0T}{Q}} \notag -2e^{\I h(k_0+k_1)+\f{k_0 T}{Q}} \right.\right.\\&\left.\left.+ e^{\I h(k_0 + 2k_1) + \f{k_0 T}{Q}} - e^{\I h k_1 \notag + \f{k_1 T}{Q}} + 2 e^{\I h(k_0 + k_1) + \f{k_1 T}{Q}} - e^{\I h(2k_0 + k_1)+\f{k_1 T}{Q}}}T \right.\\&\left.- \I \notag e^{\f{(k_0+k_1)(\I h Q + T)}{Q}}h Q\p{\te{Ei}\ps{-\I h k_0 - \f{k_0 T}{Q}} - \te{Ei}\ps{\I h k_0 - \f{k_0 T}{Q}} - \te{Ei}\ps{-\I h k_1 - \f{k_1 T}{Q}} + \te{Ei}\ps{\I h k_1 - \f{k_1 T}{Q}}   } \right.\\&\left.+ 2e^{\I h(k_0+k_1)} h \p{e^{\f{k_1 T}{Q}}(Q + k_0 T)\te{Si}\ps{h k_0} - e^{\f{k_0 T}{Q}}(Q + k_1 T)\te{Si}\ps{h k_1}}}\,.
+\end{align}
+We know that the energy in this range before attenuation is
+\begin{align}
+E_{\te{detectable}} = \f{\lambda+2\mu}{K^2}2p_0^2(b^2f_1(b)-a^2f_1(a))^2\ps{-2k+k\cos(h k)+\f{\sin(h k)}{h}+h k^2\te{Si}(h k)}_{k=k_0}^{k_1}
+\end{align}
+What is the measurable attenuated energy in terms of the total deposited energy?
+\begin{align}
+E_{\te{total}} = 2\pi p_0^2h\f{\lambda+2\mu}{K^2}\int_0^\infty r\diff r f(r)^2\,.
+\end{align}
+We need to pick a function $f$. A shock wave tends to be a right triangle, so let's pick the triangle from before. We then get
+\begin{align}
+E_{\te{total}}=\f{\lambda+2\mu}{K^2}\f16 p_0^2 \pi\Delta r h(4 r_0+3\Delta r)\,,
+\end{align}
+and
+\begin{align}
+f_1(x)=\f{-r_0}{2\Delta r}+\f{x}{3\Delta r}\,.
+\end{align}
+Hence, for $b = r_0+\Delta r$ and $a = r_0$, we have
+\begin{align}
+b^2 f_1(b)-a^2f_1(a) = \f16\Delta r(3r_0+2\Delta r)\,.
+\end{align}
+The initial energy deposition is
+\begin{align}
+E = \rho\sigma_Xv_X^2h\,.
+\end{align}
+Thus
+\begin{align}
+2p_0^2\f{\lambda+2\mu}{K^2} =  \f{12}{\pi}\f{\rho\sigma_Xv_X^2}{\Delta r (4r_0+3\Delta r)}\,.
+\end{align}
+Hence
+\begin{align}
+\notag E_{\te{attenuated}} =&\f{1}{3\pi}\f{\rho\sigma_Xv_X^2}{\Delta r (4r_0+3\Delta r)}\ps{ \Delta r(3r_0+2\Delta r)}^2 \f{1}{T^2}e^{-\f{(k_0+k_1)(\I h Q+T)}{Q}} Q\p{-\p{e^{\I h k_0+\f{k_0T}{Q}} \notag -2e^{\I h(k_0+k_1)+\f{k_0 T}{Q}} \right.\right.\\&\left.\left.+ e^{\I h(k_0 + 2k_1) + \f{k_0 T}{Q}} - e^{\I h k_1 \notag + \f{k_1 T}{Q}} + 2 e^{\I h(k_0 + k_1) + \f{k_1 T}{Q}} - e^{\I h(2k_0 + k_1)+\f{k_1 T}{Q}}}T \right.\\&\left.- \I \notag e^{\f{(k_0+k_1)(\I h Q + T)}{Q}}h Q\p{\te{Ei}\ps{-\I h k_0 - \f{k_0 T}{Q}} - \te{Ei}\ps{\I h k_0 - \f{k_0 T}{Q}} - \te{Ei}\ps{-\I h k_1 - \f{k_1 T}{Q}} + \te{Ei}\ps{\I h k_1 - \f{k_1 T}{Q}}   } \right.\\&\left.+ 2e^{\I h(k_0+k_1)} h \p{e^{\f{k_1 T}{Q}}(Q + k_0 T)\te{Si}\ps{h k_0} - e^{\f{k_0 T}{Q}}(Q + k_1 T)\te{Si}\ps{h k_1}}}\,,\\
+=&\f{1}{3\pi}\f{\rho\sigma_Xv_X^2\Delta r}{(4r_0+3\Delta r)}\ps{(3r_0+2\Delta r)}^2 \f{1}{T^2}e^{-\f{(k_0+k_1)(\I h Q+T)}{Q}} Q\p{-\p{e^{\I h k_0+\f{k_0T}{Q}} \notag -2e^{\I h(k_0+k_1)+\f{k_0 T}{Q}} \right.\right.\\&\left.\left.+ e^{\I h(k_0 + 2k_1) + \f{k_0 T}{Q}} - e^{\I h k_1 \notag + \f{k_1 T}{Q}} + 2 e^{\I h(k_0 + k_1) + \f{k_1 T}{Q}} - e^{\I h(2k_0 + k_1)+\f{k_1 T}{Q}}}T \right.\\&\left.- \I \notag e^{\f{(k_0+k_1)(\I h Q + T)}{Q}}h Q\p{\te{Ei}\ps{-\I h k_0 - \f{k_0 T}{Q}} - \te{Ei}\ps{\I h k_0 - \f{k_0 T}{Q}} - \te{Ei}\ps{-\I h k_1 - \f{k_1 T}{Q}} + \te{Ei}\ps{\I h k_1 - \f{k_1 T}{Q}}   } \right.\\&\left.+ 2e^{\I h(k_0+k_1)} h \p{e^{\f{k_1 T}{Q}}(Q + k_0 T)\te{Si}\ps{h k_0} - e^{\f{k_0 T}{Q}}(Q + k_1 T)\te{Si}\ps{h k_1}}}\,.
+\end{align}
+Note, the bigger $r_0$ and $\Delta r$ are, the bigger $E_{\te{attenuated}}$ will be.
+A very generous over estimate is to say that $\Delta r = r_0 = 1\te{m}$.
+Another way to do this is as we did earlier, by starting the propagation once the wave has reached a certain pressure $\bar p \approx 10^8\te{Pa}$.
 \pagebreak

### 2016-08-06 Ray-Tracing/Ray_Tracing_Moon.m
Finished Matlab - Python works but needs speeding up
Based on some tests, i’d guess that the detectable energy density
threshold should be about 10^6 J/km^2 = 1J/m^2. That sounds reasonable,
but how do we show it?

@@ -5,14 +5,20 @@ format long
 
 
 %INPUTS
-D = 1000; %THE DISTANCE OF CLOSEST APPROACH TO THE CENTER
+D = 1000; %THE DISTANCE OF CLOSEST APPROACH TO THE CENTER km
 ACO = 9; %IT TAKES 16 ITERATIONS FOR A RAY TO PASS ENTIRELY THROUGH THE MOON
 
-vX = 250000; %m/s
-sigmaX = 10^(-7)*10^(-4);%kg/m^3
-f0 = 0.004;
+vX = 250; %km/s
+sigmaX = (10^(-7))*(10^(-4))*(10^(-6));%kg/km^3
+flow = 0.004;%1/s %LOWEST DETECTABLE FREQUENCY
+fhigh = 2;%1/s %HIGHEST DETECTABLE FREQUENCY
+favg = 1.5;%1/s %WEIGHTED AVERAGE FREQUENCY (Where the energy is)
+TotalDensityAverage = 3.3*10^15; %THE AVERAGE DENSITY THROUGHOUT THE WHOLE MOON
+pbar = 10^8*10^3;%HOOKIAN PRESSURE kg/(km*s^2)
+vs = 4.4 * 10^3;%AVERAGE SHEAR WAVE VELOCITY THROUGHOUT THE WHOLE MOON
+vp = 7.6 * 10^3;%AVERAGE PRESSURE WAVE VELOCITY THROUGHOUT THE WHOLE MOON
 
-M = 10; %NUMBER OF POINTS ON THE LINE
+M = 20; %NUMBER OF POINTS ON THE LINE
 N = 10; %NUMBER OF RAYS FROM EACH POINT
 %{
 %APPROXIMATION TO OUTER LAYERS
@@ -29,14 +35,14 @@ rhoBoundaries = [   3.406       ,   3.406               ;...
 %}
 %%{
 %VPREMOON MODEL
-a = [8.26955,8.26955,8.26955,8.26955,8.26955,5.5,3.2,1.0].^(1/2); %THESE ARE THE CONSTANT TERMS IN THE PARABOLIC VELOCITY FIELD STRUCTURE, THE FIRST ENTRY CORRESPONDING TO THE CORE
[…]

### 2016-08-07 Macro Impacts Revised.tex
Python Functional but SLOW
Finished Matlab - Python works but needs speeding up
Based on some tests, i’d guess that the detectable energy density
threshold should be about 10^6 J/km^2 = 1J/m^2. That sounds reasonable,
but how do we show it?
Displacement
Wrong, but the process is there.

@@
 Another way to do this is as we did earlier, by starting the propagation once the wave has reached a certain pressure $\bar p \approx 10^8\te{Pa}$.
+Then
+\begin{align}
+ r_0 = \f{K^2}{\lambda+2\mu} \f{3}{2\pi\Delta r}\f{\rho\sigma_Xv_X^2 }{p_0^2}-\f{3}{4}\Delta r
+\end{align}
+A quick plot shows that the attenuation here is pretty much negligible.
 \pagebreak
@@
 \begin{align}
-\epsilon \geq 6\times 10^{-9} \te{J\,km}^{-2}\,.
+\epsilon \geq 6\times 10^{-15} \te{J\,m}^{-2}\,.
+\end{align}
+This is probably wrong.
+They can measure a displacement of $3\times 10^{-10}\te{m}$.
+We can calculate the displacement due to a seismic $p$-wave.
+Suppose $P$ is the Fourier transform of the pressure wave.
+Then the displacement field's Fourier transform is
+\begin{align}
+U(\vec k) =\I\f{P(\vec k)}{K}\f{\vec k}{k^2}\,. 
+\end{align}
+The displacement is then... I FORGOT AN $\omega t$!!! I'll redo later tonight
+\begin{align}
+u &= \int\f{\diff^3 k}{(2\pi)^3}\I\f{P(\vec k)}{K}\f{\vec k}{k^2}e^{\I \vec k\cdot\vec x - \I\omega t}\,,\\
+&=\f{1}{K}\int\f{\diff^3 k}{(2\pi)^3}\I\f{4\pi p_0}{k\cos\theta}\sin\p{\f{h k\cos\theta}{2}}(b^2f_1(b)-a^2f_1(a))\f{\vec k}{k^2}e^{\I \vec k\cdot\vec x}\,,\\
+&=\I2 p_0\f{(b^2f_1(b)-a^2f_1(a))}{K}\int\f{\diff k\diff\theta\diff\phi}{(2\pi)^2}\f{k^2\sin\theta}{k\cos\theta}\sin\p{\f{h k\cos\theta}{2}}\f{\hat k}{k}e^{\I (kx\cos\varphi)}\,,\\
+&=\I2 p_0\f{(b^2f_1(b)-a^2f_1(a))}{K}\int\f{\diff k\diff\theta\diff\phi}{(2\pi)^2}\tan\theta\sin\p{\f{h k\cos\theta}{2}}\hat k e^{\I (kx\cos\varphi)}\,,\\
+&=\I2 p_0\f{(b^2f_1(b)-a^2f_1(a))}{K}\int\f{\diff\theta\diff\phi}{(2\pi)^2}\ps{\f{2h\cos\theta-2e^{\I k_0 x\cos\varphi}\p{h\cos\theta\cos\p{\f{h}{2}k_0\cos\theta} - 2\I x\cos\varphi\sin\p{\f{h}{2}k_0\cos\theta}}}{h^2\cos^2\theta-4x^2\cos^2\varphi}}\,,\\
+&=\I2 p_0\f{(b^2f_1(b)-a^2f_1(a))}{K}\int\f{\diff\theta}{2\pi}\ps{\f{2h-2e^{\I k_0 x\cos\theta}\p{h\cos\p{\f{h}{2}k_0\cos\theta} - 2\I x\sin\p{\f{h}{2}k_0\cos\theta}}}{(h^2-4x^2)\cos\theta}}\,.
+\end{align}
+By proper choice of coordinates, we can insist that $\varphi = \theta$. Moreover, we know that $u$ is real, and hence we can write
+\begin{align}
+u &=\I2 p_0\f{(b^2f_1(b)-a^2f_1(a))}{K}\int\f{\diff\theta}{2\pi}\ps{\f{-2\I\p{h\sin\p{k_0 x\cos\theta}\cos\p{\f{h}{2}k_0\cos\theta} - 2 x\cos\p{k_0 x\cos\theta}\sin\p{\f{h}{2}k_0\cos\theta}}}{(h^2-4x^2)\cos\theta}}\,,\\
+&=4 p_0\f{(b^2f_1(b)-a^2f_1(a))}{K}\int\f{\diff\theta}{2\pi}\ps{\f{\p{h\sin\p{k_0 x\cos\theta}\cos\p{\f{h}{2}k_0\cos\theta} - 2 x\cos\p{k_0 x\cos\theta}\sin\p{\f{h}{2}k_0\cos\theta}}}{(h^2-4x^2)\cos\theta}}\,,\\
+&=k_0\f{p_0}{2}\f{(b^2f_1(b)-a^2f_1(a))}{K}\p{_p\te{F}_q\ps{\pc{\f12},\pc{1,\f32},-\p{\f{k_0(h+2x)}{4}}^2} -_p\te{F}_q\ps{\pc{\f12},\pc{1,\f32},-\p{\f{k_0(h-2x)}{4}}^2}}
 \end{align}

### 2016-08-08 Macro Impacts Revised.tex
Good stuff

@@
 \end{align}
+
+CORRECTION
+\\\\
+Note that we want to know the amplitude as a function of cylindrical $r$, hence choose $k\cdot x = k r \sin\theta$, since they should be aligned when $\theta$ is $\pi/2$.
+That integral doesn't seem to work, but the displacement as a function of $z$ is
+\begin{align}
+u &= \int\f{\diff^3 k}{(2\pi)^3}\I\f{P(\vec k)}{K}\f{\vec k}{k^2}e^{\I \vec k\cdot\vec x - \I\omega t}\,,\\
+&=\f{1}{K}\int\f{\diff^3 k}{(2\pi)^3}\I\f{4\pi p_0}{k\cos\theta}\sin\p{\f{h k\cos\theta}{2}}(b^2f_1(b)-a^2f_1(a))\f{\vec k}{k^2}e^{\I \vec k\cdot\vec x - \I k v t}\,,\\
+&=\f{\I4\pi p_0}{K}(b^2f_1(b)-a^2f_1(a))\int\f{\diff^3 k}{(2\pi)^3}\f{1}{k\cos\theta}\sin\p{\f{h k\cos\theta}{2}}\f{\vec k}{k^2}e^{\I k(z\cos\theta -  v t)}\,,\\
+&=\f{\I2 p_0}{K}(b^2f_1(b)-a^2f_1(a))\int\f{\diff k\diff\theta\diff\phi}{(2\pi)^2}\tan\theta\sin\p{\f{h k\cos\theta}{2}}e^{\I k(z\cos\theta -  v t)}\hat k\,,\\
+\end{align}
+Note, then that $u\cdot\vec  = \abs{u}z\cos\theta$ and that
+\begin{align}
+\abs{u}&=\f{\I2 p_0}{K}(b^2f_1(b)-a^2f_1(a))\int\f{\diff k\diff\theta\diff\phi}{(2\pi)^2}\tan\theta\sin\p{\f{h k\cos\theta}{2}}e^{\I k(r\cos\theta -  v t)}\,,\\
+\end{align}
+A priori we know that only the complex part of the integral survives, and we are left with
+\begin{align}
+\notag\abs{u} =& \f{ p_0}{K}(b^2f_1(b)-a^2f_1(a))\f{1}{tv}\ps{-2\cos(k_0 tv)\p{\te{Si}\ps{\f12 k_0(h - 2z)} + \te{Si}\ps{\f12 k_0(h + 2z)}}\right.\\&\left.
++ \te{Si} \ps{\f12 k_0(h+2z-2tv)}+ \te{Si}\ps{\f12 k_0(h-2z+2tv)}+\te{Si}\ps{\f12 k_0(h+2z+2tv)}+\te{Si}\ps{\f12 k_0(h-2z-2tv)}}
+\end{align}
+Note that $r$ is the cylindrical coordinate.
+Taking $z = vt$, we get the maximum amplitude of the propagating displacement wave.
+For large $t$, the stuff in the square bracket tends to $2\te{Si}\ps{h k_0/2}$.
+The convergence is quite rapid.
+Note, the cosine term dominates the behavior of the background in response to the source, and the independent sine integral terms dominate the propagation of the wave.
+\pagebreak
+\section{BEST ESTIMATE THIS TIME!}
+\begin{align}
+\epsilon A = \f12M_{\te{seismometer}}v_p^2D_{\te{displacement sensitivity}}
+\end{align}
 \pagebreak
@@
 The model above produces a set of positions on a sphere along with their associated times of impact and relative amplitudes at particular frequencies.
-The detectable energy from any given ray is the energy that is depositied in the frequencies detectable to a seismometer.
+The detectable energy from any given ray is the energy that is deposited in the frequencies detectable to a seismometer.
 According to Wikipedia, some seismometers can measure frequencies from 500 Hz to 0.00118 Hz.

### 2016-08-11 Macro Impacts Revised.tex
Update

@@
 \pagebreak
-\section{BEST ESTIMATE THIS TIME!}
-\begin{align}
-\epsilon A = \f12M_{\te{seismometer}}v_p^2D_{\te{displacement sensitivity}}
-\end{align}
+\section{Prof. Starkman's Estimate}
+\begin{align}
+d_{\te{threshold}} > \frac{1}{f} \sqrt{ \frac{E_{\te{ray}}}{\rho v \Delta T A_{\te{pix}}}}
+\end{align}
+This estimate works in the case that the wave only contains one frequency. 
+\pagebreak
+\section{Another Estimate}
+Suppose that we have the energy in the frequencies less than $f$ is
+\begin{align}
+E = Cf^2\,.
+\end{align}
+This means that each frequency contributes energy proportional to itself, i.e.
+\begin{align}
+E(f) = 2 Cf
+\end{align}
+This frequency is then attenuated
+\begin{align}
+E(f) =  2 C_1 f e^{- C_2 f}
+\end{align}
+and so the energy in the spectrum below $f$ is
+\begin{align}
+E = \f{2 C_1(1-e^{-C_2 f}(1+C_2 f))}{C_2^2}
+\end{align}
+To see this more formally, observe that if the energy below frequency $f$ is
+\begin{align}
+E=C_1f^2\,,
+\end{align}
+then the energy in the interval $[f,f+\delta]$ is
+\begin{align}
+\delta E = E(f+\delta)-E(f)
+\end{align}
+This energy is then approximately attenuated as though all the energy were at frequency $f$, i.e.
+\begin{align}
+\delta E = e^{-C_2f}(E(f+\delta)-E(f))\,.
+\end{align}
+Hence the total attenuated energy is
+\begin{align}
+E = \sum_f\delta Ee^{-C_2f} = \sum_f\delta e^{-C_2f}\f{(E(f+\delta)-E(f))}{\delta}\,.
+\end{align}
+Taking the limit as $\delta\to 0$ then leads to
+\begin{align}
+E = \int_0^f\diff f' \td{E(f')}{f'}{}e^{-C_2f}\,.
+\end{align}
+Now that we have attenuated $E$ as a function of $f$, we try to determine displacement. This is possible because we know how the energy is distributed as a function of $f$.
+\\\\
+Suppose we have a displacement wave at wavenumber $k$ and energy $E$. We can, in particular, write the wave in the form
+\begin{align}
+u_f = A_fe^{-i(\vec k\cdot \vec x - k v t)}\,.
+\end{align}
+Then the energy is
+\begin{align}
+E(f+\delta)-E(f) &= \rho\int\diff^3 x \abs{\partial_t A_fe^{-\I(\vec k\cdot \vec x - k v t)}}^2\,,\\
+&= \rho\int\diff^3 x \abs{\I k v A_fe^{-\I(\vec k\cdot \vec x - k v t)}}^2\,,\\
+&= \rho\int\diff^3 x  k^2 v^2 A_f^2\,,\\
+&= \rho V  k^2 v^2 A_f^2\,,\\
+&= \rho V  (2\pi)^2 f^2 A_f^2\,.
+\end{align}
+\begin{align}
+A^2 = \lim_{\delta\to 0}\sum_f (A_f^2) &= \lim_{\delta\to 0}\sum_f \f{E(f+\delta)-E(f)}{f^2}\p{\rho V  (2\pi)^2}^{-1}\,,\\
+&=\f{1}{\rho V  (2\pi)^2} \int \f{\diff E}{f^2}\,,\\
+&=\f{1}{\rho V  (2\pi)^2} \int \f{\diff f}{f^2}\td{E}{f}{}\,,
+\end{align}
+so,
+\begin{align}
+A = \sqrt{\f{1}{\rho V  (2\pi)^2} \int \f{\diff f}{f^2}\td{E}{f}{}}\,.
+\end{align}
+In our case,
+\begin{align}
+A &= \sqrt{\f{1}{\rho V  (2\pi)^2} \int_0^f \diff f' C_1 e^{-C_2 f'}}\,,\\
+&= \sqrt{\f{1}{\rho V  (2\pi)^2}C_1(1- e^{-C_2 f})}\,,\\
+&= \f{1}{f}\sqrt{\f{E_{ray}}{\rho V  (2\pi)^2}(1- e^{-C_2 f})}\,,\\
+&= \f{1}{2\pi f}\sqrt{\f{E_{ray}}{\rho A_{\te{ray}}\Delta T v_p}(1- e^{-C_2 f})}\,,
+\end{align}
+which coincides with Prof. Starkman's estimate for $C_2 = 0$.
 \pagebreak

### 2016-08-11 Ray-Tracing/Ray_Tracing_Moon.m

@@ -13,7 +13,7 @@ sigmaX = (10^(-7))*(10^(-4))*(10^(-6));%kg/km^3
 flow = 0.004;%1/s %LOWEST DETECTABLE FREQUENCY
 fhigh = 2;%1/s %HIGHEST DETECTABLE FREQUENCY
 favg = 1.5;%1/s %WEIGHTED AVERAGE FREQUENCY (Where the energy is)
-TotalDensityAverage = 3.3*10^15; %THE AVERAGE DENSITY THROUGHOUT THE WHOLE MOON
+TotalDensityAverage = 3.3*10^12; %THE AVERAGE DENSITY THROUGHOUT THE WHOLE MOON
 pbar = 10^8*10^3;%HOOKIAN PRESSURE kg/(km*s^2)
 vs = 4.4 * 10^3;%AVERAGE SHEAR WAVE VELOCITY THROUGHOUT THE WHOLE MOON
 vp = 7.6 * 10^3;%AVERAGE PRESSURE WAVE VELOCITY THROUGHOUT THE WHOLE MOON
@@ -58,8 +58,8 @@ rhoBoundaries = [   3.406       ,   3.406               ;...
                     %OUTER DENSITY kg/km^3
 %}
 
-c = 3.446 * 10^15; %THE CONSTANTS WHICH DESCRIBE THE DENSITY FIELD c - d(r - e)^2 kg/km^3
-d = 5*(10^(-8)) * 10^15; %THESE ARE USED TO GET THE INITIAL ENERGY OF THE RAYS d=kg/km^5
+c = 3.446 * 10^12; %THE CONSTANTS WHICH DESCRIBE THE DENSITY FIELD c - d(r - e)^2 kg/km^3
+d = 5*(10^(-8)) * 10^12; %THESE ARE USED TO GET THE INITIAL ENERGY OF THE RAYS d=kg/km^5
 e = 70; %NOTE THE DIFFERENCE IN UNITS! km
 
 %END INPUTS
@@ -382,8 +382,9 @@ for i = 1 : ACO
     OutArrayTime(IdSurfacePrime) = RayArrayTime(IdSurface);
     
 end
-
[…]

### 2016-08-12 Macro Impacts Revised.tex
update
Slight Correction

@@
 \pagebreak
-\section{Prof. Starkman's Estimate}
-\begin{align}
-d_{\te{threshold}} > \frac{1}{f} \sqrt{ \frac{E_{\te{ray}}}{\rho v \Delta T A_{\te{pix}}}}
-\end{align}
-This estimate works in the case that the wave only contains one frequency. 
-\pagebreak
 \section{Another Estimate}
@@
 \end{align}
+OR?
+\begin{align}
+A = \lim_{\delta\to 0}\sum_f (A_f) &= \lim_{\delta\to 0}\sum_f\sqrt{ \f{E(f+\delta)-E(f)}{f^2}\p{\rho V  (2\pi)^2}^{-1}}\,,\\
+&=\f{1}{\sqrt{\rho V}  2\pi} \int \f{\diff \sqrt{E}}{f}\,,\\
+&=\f{1}{\sqrt{\rho V}  2\pi} \int \f{\diff f}{f}\td{\sqrt{E}}{f}{}\,.
+\end{align}
 so,
@@
 \begin{align}
-A &= \sqrt{\f{1}{\rho V  (2\pi)^2} \int_0^f \diff f' C_1 e^{-C_2 f'}}\,,\\
-&= \sqrt{\f{1}{\rho V  (2\pi)^2}C_1(1- e^{-C_2 f})}\,,\\
-&= \f{1}{f}\sqrt{\f{E_{ray}}{\rho V  (2\pi)^2}(1- e^{-C_2 f})}\,,\\
-&= \f{1}{2\pi f}\sqrt{\f{E_{ray}}{\rho A_{\te{ray}}\Delta T v_p}(1- e^{-C_2 f})}\,,
+A &= \sqrt{\f{1}{\rho V  (2\pi)^2} \int_{f_0}^{f_1} \diff f' \f{C_1 e^{-C_2 f'}}{f}}\,,\\
+&= \sqrt{\f{1}{\rho V  (2\pi)^2}C_1\p{\te{Ei}\ps{-C_2f_1}-\te{Ei}\ps{-C_2f_0}}}\,,\\
+&= \f{1}{f}\sqrt{\f{E_{ray}}{\rho V  (2\pi)^2}\p{\te{Ei}\ps{-C_2f_1}-\te{Ei}\ps{-C_2f_0}}}\,,\\
+&= \f{1}{2\pi f}\sqrt{\f{E_{ray}}{\rho A_{\te{ray}}\Delta T v_p}\p{\te{Ei}\ps{-C_2f_1}-\te{Ei}\ps{-C_2f_0}}}\,,
 \end{align}
 which coincides with Prof. Starkman's estimate for $C_2 = 0$.
+\pagebreak
+\section{Revised Estimate}
+Suppose we have the displacement field
+\begin{align}
+u &= \int\f{\diff^3 k}{(2\pi)^3}U(\vec k)e^{-\I(\vec k\cdot x-k v_p t)}\,.
+\end{align}
+Since we want the maximum displacement, we set $t=0$. In the case that $U$ doesn't depend on $\vec k$, we have
+\begin{align}
+u &=\int\f{\diff^3 k}{(2\pi)^3}U(k)e^{-\I(\vec k\cdot x)}\,,\\
+&=\int\f{\diff k\diff\theta\diff\phi}{(2\pi)^3}k^2\sin\theta U( k)e^{-\I k r \cos\phi}\,,\\
+&=\int\f{\diff k}{(2\pi)^2}k^2U( k) J_0(k r)\,.
+\end{align}
+When$kr\ll 1$, we have
+\begin{align}
+u&\approx \int\f{\diff k}{(2\pi)^2}k^2U(k)\,.
+\end{align}
+Then
+\begin{align}
+\partial_t u =\I v_p\int\f{\diff^3 k}{(2\pi)^3}kU(\vec k)e^{-\I(\vec k\cdot \vec x-k v_p t)}\,,
+\end{align}
+and
+\begin{align}
+\abs{\partial_t u}^2 = v_p^2\int\f{\diff^3 k}{(2\pi)^3}\int\f{\diff^3 k'}{(2\pi)^3}kk'U(\vec k)\bar U(\vec k')e^{-\I(\vec k'\cdot \vec x-k' v_p t)}e^{-\I(\vec k\cdot \vec x-k v_p t)}
+\end{align}
+Thus
+\begin{align}
+E = \rho\int\diff^3 x (\partial_t u)^2 &= v_p^2\rho\int\diff^3 x\int\f{\diff^3 k}{(2\pi)^3}\int\f{\diff^3 k'}{(2\pi)^3}kk'U(\vec k)\bar U(\vec k')e^{\I(\vec k'\cdot \vec x-k' v_p t)}e^{-\I(\vec k\cdot \vec x-k v_p t)}\,,\\
+&=v_p^2\int\f{\diff^3 k}{(2\pi)^3}\int\f{\diff^3 k'}{(2\pi)^3}kk'U(\vec k)\bar U(\vec k')\rho\int\diff^3 xe^{\I(\vec k'\cdot \vec x-k' v_p t)}e^{-\I(\vec k\cdot \vec x-k v_p t)}\,,\\
+&=v_p^2\int\f{\diff^3 k}{(2\pi)^3}\int\f{\diff^3 k'}{(2\pi)^3}kk'U(\vec k)\bar U(\vec k')\rho\int\diff^3 xe^{\I((\vec k'-\vec k)\cdot \vec x-(k'-k) v_p t)}\,,\\
+&=v_p^2\int\f{\diff^3 k}{(2\pi)^3}\int\f{\diff^3 k'}{(2\pi)^3}kk'U(\vec k)\bar U(\vec k')\rho \delta(\vec k-\vec k')e^{\I(k-k') v_p t}\,,\\
+&=v_p^2\int\f{\diff^3 k}{(2\pi)^3}\int\f{\diff^3 k'}{(2\pi)^3}kk'U(\vec k)\bar U(\vec k')\rho \delta(\vec k-\vec k')\,,\\
+&=\rho v_p^2\int\f{\diff^3 k}{(2\pi)^3}k^2\abs{U(\vec k)}^2\,.
+\end{align}
+Assuming $U$ has no $\hat k$ dependence
+\begin{align}
+E&=2\rho v_p^2\int_{0}^{\infty}\f{\diff k}{(2\pi)^2}k^4\abs{U(k)}^2\,.
+\end{align}
+Define
+\begin{align}
+E_k &=2\rho v_p^2\int_{0}^{k}\f{\diff k'}{(2\pi)^2}k'^4\abs{U(k')}^2\,.
+\end{align}
+Then
+\begin{align}
+\td{E_k}{k}{} =\f{2\rho v_p^2}{(2\pi)^2}k^4\abs{U(k)}^2
+\end{align}
+Hence
+\begin{align}
+\abs{U(k)} = \f{2\pi}{\sqrt{2\rho v_p^2}}\f{1}{k^2}\sqrt{\td{E_k}{k}{}}\,.
+\end{align}
+Whence
+\begin{align}
+U = \int_0^\infty \f{\diff k}{(2\pi)^2} k^2\abs{U(k)} = \f{1}{2\pi\sqrt{2\rho v_p^2}}\int_0^\infty\diff k\sqrt{\td{E_k}{k}{}}\,.
+\end{align}
+In our case, when we want to only consider modes up to some $k_0$, we have
+\begin{align}
+U_k =  \f{1}{2\pi\sqrt{2\rho v_p^2}}\int_0^k\diff k'\sqrt{\td{E_k'}{k'}{}}
+\end{align}
+For us, before attenuation we have
+\begin{align}
+E_k = C_1 k^2\,,
+\end{align}
+so before attenuation we have
+\begin{align}
+\td{E_k'}{k'}{} = 2 C_1 k'\,,
+\end{align}
+and after attenuation
+\begin{align}
+\td{E_k'}{k'}{} = 2 C_1 k'e^{-k v_p\f{T}{Q}}\,,
+\end{align}
+whence
+\begin{align}
+U_k &=  \f{\sqrt{C_1}}{2\pi\sqrt{\rho v_p^2}}\int_0^k\diff k' \sqrt{k'}e^{-\f{k v_p}{2}\f{T}{Q}}\,,\\
+&=\f{\sqrt{E_{\te{ray}}}}{2\pi k\sqrt{\rho v_p^2}}\int_0^k\diff k' \sqrt{k'}e^{-\f{k v_p}{2}\f{T}{Q}}\,,\\
+&=\f{1}{2\pi kv_p}\sqrt{\f{E_{\te{ray}}}{\rho}}\f{Q}{v_p T}\p{\sqrt{2\pi}\sqrt{ \f{Q}{v_p T}}\te{Erf}\ps{\sqrt{\f{k v_p T}{2 Q}}} -2\sqrt{k} e^{-\f{k v_p T}{2 Q}}}\,,\\
+\end{align}
 \pagebreak

### 2016-08-12 Macro Impacts Revised.tex
further update
Final??? Code uploaded

@@
 \end{align}
-When$kr\ll 1$, we have
+When $kr\ll 1$, we have
 \begin{align}
@@
 \end{align}
-Then
+The requirement that $kr\ll 1$ may determine the maximum size of the pixels. Then
 \begin{align}
@@
 \begin{align}
-U = \int_0^\infty \f{\diff k}{(2\pi)^2} k^2\abs{U(k)} = \f{1}{2\pi\sqrt{2\rho v_p^2}}\int_0^\infty\diff k\sqrt{\td{E_k}{k}{}}\,.
-\end{align}
-In our case, when we want to only consider modes up to some $k_0$, we have
-\begin{align}
-U_k =  \f{1}{2\pi\sqrt{2\rho v_p^2}}\int_0^k\diff k'\sqrt{\td{E_k'}{k'}{}}
+u \leq \int_0^\infty \f{\diff k}{(2\pi)^2} k^2\abs{U(k)} = \f{1}{2\pi\sqrt{2\rho v_p^2}}\int_0^\infty\diff k\sqrt{\td{E_k}{k}{}}\,.
+\end{align}
+In our case, when we want to only consider modes up to some $k$, we have
+\begin{align}
+u_k \leq \f{1}{2\pi\sqrt{2\rho v_p^2}}\int_0^k\diff k'\sqrt{\td{E_k'}{k'}{}}
 \end{align}
@@
 \begin{align}
-\td{E_k'}{k'}{} = 2 C_1 k'e^{-k v_p\f{T}{Q}}\,,
-\end{align}
-whence
-\begin{align}
-U_k &=  \f{\sqrt{C_1}}{2\pi\sqrt{\rho v_p^2}}\int_0^k\diff k' \sqrt{k'}e^{-\f{k v_p}{2}\f{T}{Q}}\,,\\
+\td{E_k'}{k'}{} = 2 C_1 k'e^{-k' v_p\f{T}{Q}}\,,
+\end{align}
+whence, the maximum amplitude in the vicinity of the ray impact is
+\begin{align}
+u &\leq \f{\sqrt{C_1}}{2\pi\sqrt{\rho v_p^2}}\int_0^k\diff k' \sqrt{k'}e^{-\f{k v_p}{2}\f{T}{Q}}\,,\\
 &=\f{\sqrt{E_{\te{ray}}}}{2\pi k\sqrt{\rho v_p^2}}\int_0^k\diff k' \sqrt{k'}e^{-\f{k v_p}{2}\f{T}{Q}}\,,\\
-&=\f{1}{2\pi kv_p}\sqrt{\f{E_{\te{ray}}}{\rho}}\f{Q}{v_p T}\p{\sqrt{2\pi}\sqrt{ \f{Q}{v_p T}}\te{Erf}\ps{\sqrt{\f{k v_p T}{2 Q}}} -2\sqrt{k} e^{-\f{k v_p T}{2 Q}}}\,,\\
+&=\f{1}{2\pi kv_p}\sqrt{\f{E_{\te{ray}}}{\rho}}\f{Q}{v_p T}\p{\sqrt{2\pi}\sqrt{ \f{Q}{v_p T}}\te{Erf}\ps{\sqrt{\f{k v_p T}{2 Q}}} -2\sqrt{k} e^{-\f{k v_p T}{2 Q}}}\,.
+\end{align}
+This equation tells us the maximum displacement within the healpix pixel.
+Note that this is not a function of the area of the pixel.
+This is reasonable because the energy distribution is not a function of our partition of the sphere.
+\pagebreak
+\section{Double Thought Out}
+Thanks to Josh for a very useful conversation in helping to deduce what follows:
+\\\\
+A key problem we are encountering is what follows.
+Suppose we shoot out a large number of rays that uniformly hit the surface of the sphere.
+If we have $N$ rays in a pixel, and then halve the area of the pixel, we will have $N/2$ rays in the pixel.
+This, in turn, reduces the energy in the pixel, and if not accounted for properly, the measured displacement.
+If, however, when increase the number of pixels, we also multiply the energy in each pixel by the number of pixels, then assuming a uniform distribution of rays, the average displacement across pixels does not change as the number of pixels increases.
+\\\\
+Thus, suppose we have $M$ rays and $N$ pixels. Let $M_j$ be the number of rays incident on pixel $j$. Let $E_k^{ij}$ be the energy of the $i$th ray incident on the $j$th pixel. We then calculate
+\begin{align}
+E_k^j =N\sum_{i=1}^{M_j}E_k^{ij}\,.
+\end{align}
+We now calculate the displacement, where $C_2^{ij} = v_p \f{T^{ij}}{Q^{ij}}$.
+\begin{align}
+\td{E_k^{j}}{k}{} = N\sum_{i = 1}^{M_j}2 C_1^{ij} k'e^{-C_2^{ij} k}\,.
+\end{align}
+The integral would be impossible without an approximation
+\begin{align}
+\sqrt{\td{E_k^{j}}{k}{}} & = \sqrt{N\sum_{i = 1}^{M_j}2 C_1^{ij} k'e^{-C_2^{ij} k}}\,,\\
+& \leq \sqrt{N\p{\sum_{i = 1}^{M_j}\sqrt{2 C_1^{ij} k'e^{-C_2^{ij} k}}}^2}\,,\\
+&=\sqrt{N}\sum_{i = 1}^{M_j}2 C_1^{ij} \sqrt{k'}e^{-C_2^{ij}\f{k}{2}}\,.
+\end{align}
+Whence
+\begin{align}
+u_k^j&\leq\f{\sqrt{N}}{2\pi kv_p\sqrt{\rho}}\sum_{i}^{M_j}\f{\sqrt{E_k^{ij}}}{C_2^{ij}}\p{\sqrt{ \f{2\pi}{C_2^{ij}}}\te{Erf}\ps{\sqrt{\f{k}{2}C_2^{ij}}} -2\sqrt{k} e^{-\f{k }{2}C_2^{ij}}}\,.
 \end{align}

### 2016-08-12 Ray-Tracing/QualityFactor.m

@@ -1,5 +1,5 @@
-function output = QualityFactor(LayerId,DeltaTime,vBoundaries,Q,Suppression)
+function output = QualityFactor(LayerId,DeltaTime,AverageV,Q,Suppression)
 %UNTITLED5 Summary of this function goes here
 %   Detailed explanation goes here
-output = Suppression + ((vBoundaries(LayerId).*DeltaTime)./Q(LayerId));
+output = Suppression + ((AverageV(LayerId).*DeltaTime)./Q(LayerId));
 end

### 2016-08-12 Ray-Tracing/Ray_Tracing_Moon.m

@@ -5,21 +5,21 @@ format long
 
 
 %INPUTS
-D = 1000; %THE DISTANCE OF CLOSEST APPROACH TO THE CENTER km
+D = 1200; %THE DISTANCE OF CLOSEST APPROACH TO THE CENTER km
 ACO = 9; %IT TAKES 16 ITERATIONS FOR A RAY TO PASS ENTIRELY THROUGH THE MOON
 
 vX = 250; %km/s
-sigmaX = (10^(-7))*(10^(-4))*(10^(-6));%kg/km^3
-flow = 0.004;%1/s %LOWEST DETECTABLE FREQUENCY
+sigmaX = (10^(-11))*(10^(-4))*(10^(-6));%kg/km^3
+%flow = 0.004;%1/s %LOWEST DETECTABLE FREQUENCY
 fhigh = 2;%1/s %HIGHEST DETECTABLE FREQUENCY
-favg = 1.5;%1/s %WEIGHTED AVERAGE FREQUENCY (Where the energy is)
+%favg = 1.5;%1/s %WEIGHTED AVERAGE FREQUENCY (Where the energy is)
 TotalDensityAverage = 3.3*10^12; %THE AVERAGE DENSITY THROUGHOUT THE WHOLE MOON
 pbar = 10^8*10^3;%HOOKIAN PRESSURE kg/(km*s^2)
 vs = 4.4 * 10^3;%AVERAGE SHEAR WAVE VELOCITY THROUGHOUT THE WHOLE MOON
 vp = 7.6 * 10^3;%AVERAGE PRESSURE WAVE VELOCITY THROUGHOUT THE WHOLE MOON
 
-M = 20; %NUMBER OF POINTS ON THE LINE
-N = 10; %NUMBER OF RAYS FROM EACH POINT
+M = 100; %NUMBER OF POINTS ON THE LINE
+N = 20; %NUMBER OF RAYS FROM EACH POINT
 %{
 %APPROXIMATION TO OUTER LAYERS
 a = [8.26955,8.26955,8.26955,8.26955,145.46].^(1/2);
@@ -382,9 +382,9 @@ for i = 1 : ACO
     OutArrayTime(IdSurfacePrime) = RayArrayTime(IdSurface);
     
 end
-Eray = Xi.*(RayArrayDensity(OutArrayTime > 0 & OutArrayAmp > 0)).*L.*(vX.^2).*sigmaX./(M*N);
[…]

### 2016-08-12 Ray_Tracing.py

@@ -1,15 +1,119 @@
+
+# coding: utf-8
+
+# In[4]:
+
 import scipy.io as sio
+from scipy.stats import mode
+import healpy as hp
+import numpy as np
+import itertools as it
+import math
 
-mat_contents = sio.loadmat('Points.mat')
+nside = 16;
+R = 1.731E6; #Radius of Moon
+AverageDensity = 3.0E3
+AverageVelocity = 8.0E3
+frequencymax = 2.0E0
+DisplacementThreshold = 3.0E-10; #How much does the detector need to be displaced in order to register the ray?
+
+rho = AverageDensity
+v = AverageVelocity
+D = DisplacementThreshold
+
+A = hp.nside2pixarea(nside) * R**2 #Area of pixel
+T = (A**(1/2))/v; #How close in time do two rays have to be in order to be considered hitting together?
+kmax = frequencymax * 2 * np.pi * (v**(-1));
+N = hp.nside2npix(nside);
+Energy = np.zeros(N);
+
+#Loading Data from Matlab
+mat_contents = sio.loadmat('/Users/David/Macro-Impact/Ray-Tracing/Points.mat');
+points = mat_contents['output']; #Points has the format (x,y,z,time,energy,vTQ)
+length = len(points);
+
+#Assigning each point its HEALPix coordinate
+hppoints = hp.pixelfunc.vec2pix(nside, points[:,0],points[:,1],points[:,2])
+#Mode = mode(hppoints)[1][0]; #Mode is the maximum number of times a pixel is struck by a ray
+
+PixelTimes = np.zeros((N,len(hppoints))); #Each row contains a list of times at which rays struck the nth pixel
+PixelEnergies = np.zeros((N,len(hppoints))); #This is the corresponding list of energies
+PixelvTQ = np.zeros((N,len(hppoints))); #Quality Factor (ish) of each ray
+PixelDisplacements = np.zeros((N,len(hppoints))); #Maximum Displacements measured in a pixel
+
+#Now we assign PixelTimes and PixelEnergies their values
+for i in range(0,N - 1):
+    counter = 0;
+    for j in range(0,length - 1):
+        if hppoints[j] == i:
+            PixelTimes[i][counter] = points[j,3];
+            PixelEnergies[i][counter] = points[j,4];
[…]

### 2016-08-17 Macro Impacts Revised.tex
update

@@
 \begin{align}
-u &= \int\f{\diff^3 k}{(2\pi)^3}U(\vec k)e^{-\I(\vec k\cdot x-k v_p t)}\,.
-\end{align}
-Since we want the maximum displacement, we set $t=0$. In the case that $U$ doesn't depend on $\vec k$, we have
-\begin{align}
-u &=\int\f{\diff^3 k}{(2\pi)^3}U(k)e^{-\I(\vec k\cdot x)}\,,\\
+u &= \int\f{\diff^3 k}{(2\pi)^3}U(\vec k)e^{-\I(\vec k\cdot \vec x-k v_p t)}\,.
+\end{align}
+Since we want the maximum displacement, we set $t=0$. In the case that $U$ doesn't depend on $\hat k$, we have
+\begin{align}
+u &=\int\f{\diff^3 k}{(2\pi)^3}U(k)e^{-\I(\vec k\cdot \vec x)}\,,\\
 &=\int\f{\diff k\diff\theta\diff\phi}{(2\pi)^3}k^2\sin\theta U( k)e^{-\I k r \cos\phi}\,,\\
@@
 This is reasonable because the energy distribution is not a function of our partition of the sphere.
+\pagebreak
+\section{Fourier Series}
+We take the Fourier series in time along the direction of the pulse
+\begin{align}
+u =\f{1}{2\pi L} \sum_{k = 0}^{N} U(k) e^{-2\pi \I \f{L k}{N}(x -v_p t)}
+\end{align}
+Then
+\begin{align}
+\partial_t u = \f{\I v_p}{(2\pi L)^2} \sum_{k = 0}^{N} k U(k) e^{-2\pi \I \f{L k}{N}(x -v_p t)}\,.
+\end{align}
+Thus
+\begin{align}
+E &= A_{\te{ray}}\rho \int_0^L\diff x\abs{\partial_t u}^2\,,\\
+&= A_{\te{ray}}\rho \int_0^L\diff x\f{v_p^2}{(2\pi L)^2} \sum_{k,k' = 0}^{N} k k' U(k)\bar U(k') e^{-2\pi \I \f{L (k-k')}{N}(x -v_p t)}\,,\\
+&= A_{\te{ray}}\rho \f{v_p^2}{(2\pi L)^2} \sum_{k,k' = 0}^{N} k k' U(k)\bar U(k') \int_0^L\diff x e^{-2\pi \I \f{L (k-k')}{N}(x -v_p t)}\,,\\
+&= A_{\te{ray}}\rho \f{v_p^2}{(2\pi L)^2} \sum_{k,k' = 0}^{N} k k' U(k)\bar U(k') 2\pi L\delta_{k k'}e^{2\pi \I \f{L (k-k')}{N}(v_p t)}\,,\\
+&= A_{\te{ray}}\rho \f{v_p^2}{2\pi L} \sum_{k= 0}^{N} k^2 \abs{U(k)}^2\,.
+\end{align}
+Define
+\begin{align}
+E_k =  A_{\te{ray}}\rho \f{v_p^2}{2\pi L} k^2 \abs{U(k)}^2\,.
+\end{align}
+What is $E_k$? Using the general cylindrically symmetric source from before, we know $E_k= C_1 \f{k^2}{(2\pi L)^2}$. Solving for $\abs{U}$, we have
+\begin{align}
+\abs{U(k)} = \sqrt{\f{2\pi L}{v_p^2 A_{\te{ray}}\rho}\f{E_k}{ k^2}}
+\end{align}
+In our case, we have
+\begin{align}
+\abs{U(k)} = \sqrt{\f{C_1}{2\pi L v_p^2 A_{\te{ray}}\rho}}\,.
+\end{align}
+This is just a constant, so $U(k)$ is a pure phase, which comes out of the sum, so
+\begin{align}
+\abs{u} =\f{1}{2\pi L}\sqrt{\f{C_1}{2\pi L v_p^2 A_{\te{ray}}\rho}} \sum_{k = 0}^{N} \cos\p{2\pi\f{L k}{N}(x -v_p t)}
+\end{align}
+\pagebreak
+\\
+Hm, something's fishy... What about this:
+\begin{align}
+u(\vec x,t) =\int\f{\diff k}{2\pi}\, U(k)\chi_{A_{\te{ray}}} e^{-\I k(x -v_p t)}\,.
+\end{align}
+The part of $u$ that detectors will pick up is
+\begin{align}
+u(\vec x,t) =\int_0^k\f{\diff k'}{2\pi}\, U(k')\chi_{A_{\te{ray}}} e^{-\I k'(x -v_p t)}\,.
+\end{align}
+We approximate in the $x$ direction
+\begin{align}
+u(x,t) &\leq \int_0^k\f{\diff k'}{2\pi}\, \abs{U(k')}\,.
+\end{align}
+Now, we make use of the orthogonality of the basis functions to eliminate the spatial integral as above. Denote the width of the pulse as $L$.
+\begin{align}
+E &=\rho\int\diff^3 x\abs{\partial_t u}^2\,,\\
+&=\rho v_p^2\int\diff^3 x\chi_{A_{\te{ray}}}\int\f{\diff k}{2\pi}\int\f{\diff k'}{2\pi}k k'U(k)\bar U(k') e^{-\I (k-k')(x -v_p t)}\,,\\
+&=\rho v_p^2 A_{\te{ray}}\int\diff x\int\f{\diff k}{2\pi}\int\f{\diff k'}{2\pi}k k'U(k)\bar U(k') e^{-\I (k-k')(x -v_p t)}\,,\\
+&=\rho v_p^2 A_{\te{ray}}\int\f{\diff k}{2\pi}\int \diff k'k k'U(k)\bar U(k') \delta(k-k')e^{\I (k-k')v_p t}\,,\\
+&=\rho v_p^2 A_{\te{ray}}\int\f{\diff k}{2\pi}k^2\abs{U(k)}^2\,.
+\end{align}
+We denote, as before,
+\begin{align}
+E_k = \rho v_p^2 A_{\te{ray}}\int_0^k\f{\diff k}{2\pi}k^2\abs{U(k)}^2\,,
+\end{align}
+so
+\begin{align}
+\td{E_k}{k}{} =\f{\rho v_p^2 A_{\te{ray}}k^2}{2\pi}\abs{U(k)}^2\,.
+\end{align}
+Thus
+\begin{align}
+\abs{U(k)} = \sqrt{\f{2\pi}{\rho v_p^2 A_{\te{ray}}}}\f{1}{k}\sqrt{\td{E_k}{k}{}}\,,
+\end{align}
+and so
+\begin{align}
+u(x,t) \leq \sqrt{\f{1}{2\pi \rho v_p^2 A_{\te{ray}}}}\int_0^k\f{\diff k'}{k'}\sqrt{\td{E_k'}{k'}{}}\,.
+\end{align}
+Hence, in our case, where
+\begin{align}
+\td{E_k}{k}{} = 2C_1 k e^{-C_2 k}\,.
+\end{align}
+we have
+\begin{align}
+u(x,t) \leq \sqrt{\f{2}{\rho v_p^2 A_{\te{ray}}}}\sqrt{\f{C_1}{C_2}}\te{Erf}\ps{\sqrt{\f12 C_2 k}}
+\end{align}
+We can write
+\begin{align}
+C_1 = \f{E_\te{ray}}{k^2}\,,
+\end{align}
+hence
+\begin{align}
+u(x,t) \leq \sqrt{\f{2}{\rho v_p^2 A_{\te{ray}}}}\sqrt{\f{E_\te{ray}}{C_2}}\f1k\te{Erf}\ps{\sqrt{\f12 C_2 k}}\,.
+\end{align}
+Now, suppose that the time width of the wave is $\Delta T$. This corresponds to the minimum angular frequency associated to the wave. 
+\begin{align}
+\Delta T \geq \f{2\pi}{\omega} = \f{2\pi}{v_p k}\,.
+\end{align}
+Thus
+\begin{align}
+k \geq\f{2\pi}{v_p\Delta T}\,.
+\end{align}
 \pagebreak
@@
 \section{Thermal Source}
-A simple model for seismic wave generation via macro impact is that a cylinder is heated uniformly.
-Since we are interested in an upper bound to seismic energy generation, it is reasonable to find the optimal volume (i.e.
-radius) and temperature for maximal thermal expansion and minimal energy lost to heating.
-Since the energy lost to heating corresponds to the energy lost in melting, the second requirement is equivalent to minimizing volume...
-\pagebreak
-\section{Melt Zone}
-As derived in ''A time dependent model for long-rod penetration" the plastic zone (i.e. the melt zone) around an impacting projectile is given by $\alpha*R$, where $\alpha$ is given by 
-\begin{align}
-(1+\frac{\rho_t u^2}{Y_t})\sqrt{K_t - \rho_t \alpha^2 u^2} = (1+\frac{\rho_t \alpha^2 u^2}{2G_t})\sqrt{K_t - \rho_t u^2}.
-\end{align}
-where $u$ is the velocity of the projectile (i.e.
-the macro), $\rho_t$, $K_t$, $G_t$ and $Y_t$ are the density, bulk modulus, sheer modulus, and flow stress of the target (i.e.
-earth or the moon) respectively.
-
-The connection between the energy of the projectile and the value $\alpha*R$ is given in the paper posted "Hypervelocity penetration modeling- momentum vs.
-energy and energy transfer mechanisms".
-A derivation is given for the decomposition of the energy of a projectile into kinetic, elastic and plastic terms in, for example, equations 32, 33, and 38.
-
-Note that the results in the section "Penetration" in this paper "Hypervelocity penetration..." are for eroding rods -- but macro doesn't erode.
-If we decided to use equation 39 and the resulting equations which partition the energy of the impact into kinetic, elastic and plastic energy terms of the target (i.e.
-earth or moon), we'd set $u = v$, and $s = 0$ to eliminate the "eroding" effect.
-
+As relayed in an email to Josh, observe that the thermal source is
+\begin{align}
+T = \f{v_0^2}{c_p}\theta(r_X-r)\,,
+\end{align}
+where $c_p$ is the specific heat capacity of the material. The equation governing the evolution of the temperature field in 2 dimensions is, with no driving term,
+\begin{align}
+\partial_t T - \alpha\nabla^2 T = 0
+\end{align}
+where $\alpha$ is known as the thermal diffusivity, and $\alpha=\f{k}{c_p\rho}$. In cylindrical coordinates and for $T = T(r)$, we have
+\begin{align}
+\partial_t T - \alpha\nabla_r T = 0
+\end{align}
+We now Fourier transform in $r$ and $\phi$, yielding
+\begin{align}
+\partial_t\tilde T =-\alpha k_r^2 \tilde T\,,
+\end{align}
+where
+\begin{align}
+\tilde T = 2\pi \int_0^\infty r \diff r  T J_0(k_r r)\,.
+\end{align}
+Now, we integrate
+\begin{align}
+\tilde T = C_1e^{-\alpha k_r^2 t}
+\end{align}
+Now, to determine $C_1$, we set $T = \f{v_0^2}{c_p}\theta(r_X-r)$ at $t = 0$. Observe, this initial condition corresponds to the transformed statement
+\begin{align}
+\tilde T(0) = \f{r_X}{k_r}J_1(k_r r_X)\,.
+\end{align}
+This fixes $C_1$. We now inverse transform and obtain
+\begin{align}
+T &= \int_0^\infty k_r\diff k_r e^{-\alpha k_r^2 t}\f{r_X}{k_r}J_1(k_r r_X) J_0(k_r r)\,,\\
+&=r_X\int_0^\infty \diff k_r e^{-\alpha k_r^2 t} J_1(k_r r_X) J_0(k_r r)\,.
+\end{align}
+We'll have to do this integral numerically.
+However, we are interested in solving for $r(t)$ such that $T(r(t),t) = T_{\te{melt}}$.
+We then want to find $\dot r$.
+Denote this special $r(t)$ as $r_\te{melt}$.
+Then
+\begin{align}
+\f{T_\te{melt}}{r_X} = \int_0^\infty \diff k_r e^{-\alpha k_r^2 t} J_1(k_r r_X) J_0(k_r r_\te{melt})
+\end{align}
+and
+\begin{align}
+0&=\int_0^\infty \diff k_r \ps{e^{-\alpha k_r^2 t} J_1(k_r r_X) \p{-k_r\dot r_\te{melt}}J_1(k_r r_\te{melt}) +  \p{-\alpha k_r^2}e^{-\alpha k_r^2 t} J_1(k_r r_X)J_0(k_r r_\te{melt})}\,,\\
+0&=\int_0^\infty k_r \diff k_r e^{-\alpha k_r^2 t} J_1(k_r r_X) \ps{\p{\dot r_\te{melt}}J_1(k_r r_\te{melt}) +  \p{\alpha k_r}J_0(k_r r_\te{melt})}\,.
+\end{align}
+\pagebreak\\
+Eh... None of this is producing useful results, i.e. those we can use to solve for $r_\te{melt}$. Let's consider a delta source i.e.
+\begin{align}
+T = \f{v_0^2}{c_p}r_X\delta(r)\,.
+\end{align}
+Then
+\begin{align}
+C_1 =2\pi \f{v_0^2}{c_p}r_x
+\end{align}
+Thus,
+\begin{align}
+T &= \int_0^\infty k_r\diff k_r e^{-\alpha k_r^2 t}J_0(k_r r)2\pi \f{v_0^2}{c_p}r_x\,,\\
+&=\f{r_X v_0^2}{2 c_p t \alpha} e^{-\f{r^2}{4t\alpha}}\,.
+\end{align}
+Setting $T = T_\te{melt}$, we have
+\begin{align}
+r_\te{melt} = \sqrt{4t\alpha\ln\ps{\f{r_X v_0^2}{2 c_p t \alpha T_\te{melt}}}}\,.
+\end{align}
+where we've taken the positive branch, since we only care about the melt radius increasing. Then
+\begin{align}
+\dot r_\te{melt} &=\sqrt{\f{\alpha}{t}}\f{\ln\p{\f{r_Xv_0^2}{2 c_p t\alpha T}} - 1}{\sqrt{\ln\p{\f{r_Xv_0^2}{2 c_p t\alpha T}}}}\,.
+\end{align}
+For our parameters, it is a good approximation to take
+\begin{align}
+\dot r_\te{melt} &=\sqrt{\f{\alpha}{t}\ln\p{\f{r_Xv_0^2}{2 c_p\alpha T}}}\,.
+\end{align}
+Thus, the time at which the velocity of the melt front is that of the speed of sound is
+\begin{align}
+t_{\te{fast}} = \f{\alpha}{v_p^2}\ln\p{\f{r_Xv_0^2}{2 c_p\alpha T_\te{melt}}}
+\end{align}
+at a radius, which is a good approximation in our case, of
+\begin{align}
+r_\te{fast melt} =  2\f{\alpha}{v_p}\ln\ps{\f{r_X v_0^2}{2 c_p \alpha T_\te{melt}}}
+\end{align}
+which is on the order of micrometers to tenths of micrometers for our case.
 \end{document}
-
-What is the area per year covered by these non-linear zones as a function of macro mass, volume etc (contour plot).

### 2016-08-17 Ray-Tracing/Ray_Tracing_Moon.m

@@ -10,11 +10,9 @@ ACO = 9; %IT TAKES 16 ITERATIONS FOR A RAY TO PASS ENTIRELY THROUGH THE MOON
 
 vX = 250; %km/s
 sigmaX = (10^(-11))*(10^(-4))*(10^(-6));%kg/km^3
-%flow = 0.004;%1/s %LOWEST DETECTABLE FREQUENCY
 fhigh = 2;%1/s %HIGHEST DETECTABLE FREQUENCY
-%favg = 1.5;%1/s %WEIGHTED AVERAGE FREQUENCY (Where the energy is)
 TotalDensityAverage = 3.3*10^12; %THE AVERAGE DENSITY THROUGHOUT THE WHOLE MOON
-pbar = 10^8*10^3;%HOOKIAN PRESSURE kg/(km*s^2)
+pbar = 10^8;%HOOKIAN PRESSURE kg/(m*s^2)
 vs = 4.4 * 10^3;%AVERAGE SHEAR WAVE VELOCITY THROUGHOUT THE WHOLE MOON
 vp = 7.6 * 10^3;%AVERAGE PRESSURE WAVE VELOCITY THROUGHOUT THE WHOLE MOON
 

### 2016-08-19 Draft.tex
update

\documentclass[prd,reprint,10pt,tightenlines]{revtex4-1}

% Packages

\usepackage{fullpage}
\usepackage{amsmath, amsthm, amsfonts, amssymb, mathtools, calrsfs, tensor, physics,tikz-cd}
\usepackage[mathscr]{euscript}
\usepackage{graphicx}
\graphicspath{ {images/} }
\usepackage{enumitem}
\setlist[description]{font=\normalfont}

% Custom Commands

\newcommand*\diff{\mathop{}\!\mathrm{d}}
\newcommand*\Diff[1]{\mathop{}\!\mathrm{d^#1}}
\newcommand*\nrml{\vartriangleleft}
\newcommand*\scr[1]{\mathscr{#1}}
\newcommand*\bb[1]{\mathbb{#1}}
\newcommand*\la{\langle}
\newcommand*\ra{\rangle}
\newcommand*\gen[1]{\langle #1 \rangle}
\newcommand*\x{\times}
\newcommand*\st{\text{ s.t. }}
\newcommand*\ord[1]{\left\vert#1\right\vert}
\newcommand*\aut{\text{Aut}}
\newcommand*\lcm{\text{lcm}}
\newcommand*\mcal{\mathcal}
\newcommand*\es{\emptyset}
\newcommand*\im{\text{ Im }}
\newcommand*\N{\mathbb N}
\newcommand*\Z{\mathbb Z}
\newcommand*\R{\mathbb R}
\newcommand*\Q{\mathbb Q}
\newcommand*\C{\mathbb C}
\newcommand*\te[1]{\text{#1}}
\newcommand*\en[1]{\begin{enumerate}#1\end{enumerate}}
\newcommand*\e{\varepsilon}
\newcommand*\p[1]{\left(#1\right)}
\newcommand*\ps[1]{\left[#1\right]}
\newcommand*\pc[1]{\left\{#1\right\}}
\newcommand*\f[2]{\frac{#1}{#2}}
\newcommand*\mat[2]{\left(\begin{array}{#1}#2\end{array}\right)}
\newcommand*\ocross{\otimes}
\newcommand*\I{\te{i}}
\newcommand*\pd[3]{\frac{\partial^{#3} #1}{\partial {#2}^{#3}}}
\newcommand*\td[3]{\frac{d^{#3}#1}{d #2^{#3}}}
\newcommand*\m{\te{Mat}}
\newcommand*\End{\te{End}}
\newcommand*\irr{\te{Irr}}
\newcommand*\sgn{\te{sgn}}
\newcommand*\pn[2]{\left\|#1\right\|_{#2}}
\newcommand*\esssup{\te{ess sup}}
\newcommand*\essinf{\te{ess inf}}

% Miscellaneous

\newtheorem{theorem}{Theorem}
\usetikzlibrary{matrix,arrows,decorations.pathmorphing}

% Title

\begin{document}

\title{New seismological constraints on the available parameter space of macroscopic dark matter}
\author{David Cyncynates \\ dcc57@case.edu}
\date{\today}
\begin{abstract}
Recent limits have been proposed constraining the available parameter space of macroscopic dark matter (Macros). Previous limits were based on the energy deposition of Macros being akin to that of a nuclear bomb. Our estimates take into account the effect of seismometer sensitivity and energy distribution across frequencies, anelastic attenuation, geometric effects due to internal anisotropy of the Earth or Moon, as well as energy loss due to melting. We produce new constraints on the Macro parameter space based on the total lunar seismic event rate.
\end{abstract}
\maketitle
\section{Introduction}

\section{The Seismic Source}
\subsection{The Melt Wave}
The section of parameter space we are interested in contains Macros whose cross sectional area is small enough that the act of the macro penetrating the Moon does not significantly contribute to the seismic signal. That is to say, a small enough amount of moon is displaced that the energy lost due to this displacement is negligible compared to the total energy deposition. When this scenario holds, the energy deposited by the Macro can be treated as being used to heat up a column of cross sectional area $\sigma_X$ and length $\ell$.

We immediately see that this corresponds to a temperature distribution
\begin{align}
T(r,0) = \f{v_X^2}{c_p}\theta(r_X-r)\,.
\end{align}
It is reasonable to approximate this by a $\delta$ source of the form
\begin{align}
T(r,0) = \f{v_X^2}{c_p}r_X\delta(r)\,.
\end{align}
The diffusion equation then provides that the radius of the melt front is
\begin{align}
r_\te{melt} = \sqrt{4t\alpha\ln\ps{\f{r_X v_0^2}{2 c_p t \alpha T_\te{melt}}}}\,,
\end{align}
where $\alpha$ is the thermal diffusivity. 
\subsection{Seismic Wave Generation}
The energy from the initial impact generates a column of melted rock. The super-heated rock, held at constant volume, generates a pressure which sources the seismic waves that can be felt at detectors. Assuming the Macro's velocity is insignificantly changed by its encounter with the Moon, we should expect it to source a pressure of the form
\begin{align}
p = p_0 f(r)\chi_{(r,z)\in [a,b]\times [-\f \ell 2,\f \ell 2]}\,,
\end{align}
where $f$ is an analytic function whose range is a subset of $[-1,1]$, and $p_0$ is the maximum pressure of the source. Moreover, after a short time, the pressure should still be of this form, since the anisotropy of the Moon is significant only on very large scales.

The seismometers on the moon have a net useful range (the union of all useful ranges of all seismometers) of $0.004-20\text{\,Hz}$ and are sensitive to displacements as small as $0.3\text{\,nm}$. The energy measured by seismometers is a subset of that in the net useful range.

The Fourier transform of $p$ to leading order in $kb$ is
\begin{align}
P = \f{4\pi p_0}{k\cos\theta}\sin\p{\f{h k\cos\theta}{2}}F+\scr O(k^0)\,,
\end{align}
where $\theta,\phi$ are the momentum space polar angles, $F = b^2f_1(b)-a^2f_1(a)$ and
\begin{align}
f_1(x) = \sum_{n=0}^\infty\sum_{m=0}^n\binom{n}{m}\f{f^{(n)}(x_0)}{n!}\f{(-x_0)^{n-m}}{2+m}x^{m}\,,
\end{align}
for some $x_0\in[a,b]$. The energy of a seismic $p$-wave is
\begin{align}
E = \int\diff^3 x\p{ \rho\abs{\partial_t u}^2+(\lambda+2\mu)\abs{\nabla u}^2}\,,
\end{align}
where $u$ is the displacement field, $\rho,\lambda,\mu$ are the density and Lam\`e coefficients respectively. For $p$-waves, $p = -K\nabla\cdot u$ where $K$ is the bulk modulus. Define $\kappa = (\lambda + 2\mu)/K^2$ Fourier transforming, we find that $U = \I P\vec k/K k^2$ and hence
\begin{align}
E =\kappa\int\f{\diff^3 k}{(2\pi)^3}\abs{P}^2\,.
\end{align}
Since a seismometer can only detect lower frequency modes, the detectible energy is given by 
\begin{align}
E_k = \kappa\int_0^k\f{\diff k'\diff\theta}{(2\pi)^2}k'^2\sin\theta\abs{P}^2\,.
\end{align}
Substituting in our $P$, we find that
\begin{align}
\notag E_k&=\kappa 2p_0^2F^2\ell k^2\\\notag&\times\p{\f{\sin(\ell k)+k\ell(\cos(\ell k)-2)}{\ell^2 k^2}+\te{Si}(\ell k)}+\scr O(k^4)\,.
\end{align}
When $\ell k>1$ it is a good approximation to take
\begin{align}
E_k&=\kappa \pi\ell p_0^2F^2 k^2:=C_1 k^2\,.
\end{align}

Although the pressure initial conditions are fixed by the fast behavior of the melt wave, linear elasticity may not be appropriate for the pressures involved. As the pressure wave propagates, it will be geometrically attenuated until the pressure differential is within the linear regime. Given that the Macro travels at super-sonic speeds, it will generate a shock wave. Often these shock waves have pressure profiles resembling a right triangle i.e. $f = \p{r - r_0}/\Delta r$ where $a = r_0$ and $b = r_0 + \Delta r$. This shape is also chosen for its simplicity. In this case $f_1(x) = \p{2 x-3r_0}/6\Delta r$, and hence
\begin{align}
E_k = \kappa \f{\Delta r^2(3r_0+2\Delta r)^2}{36} \pi\ell p_0^2k^2\,.
\end{align}
The total energy of the pressure wave is
\begin{align}
E \notag&= 2\pi p_0^2\ell\kappa\int_a^b r\diff r f(r)^2\,,\\
&=\kappa\f{p_0^2}{6}\pi\Delta r \ell(4r_0 + 3\Delta r)\,.
\end{align}
The Macro deposits energy
\begin{align}
E_\te{initial} = \abs{\td{E}{x}{}}\ell = \rho\sigma_X v_X^2\ell\,,
\end{align}
and loses some energy due to melting. Thus, the pressure waves have initial energy
\begin{align}
E_\te{propagated} \notag&= E_\te{initial} - E_\te{melt}\,,\\
&= \p{\rho\sigma_X v_X^2 - \epsilon_\te{melt}}\ell:=\epsilon\ell\,.
\end{align}
A very unrealistic assumption is that no energy is lost during the non-linear evolution. Nonetheless, it will produce a generous over-estimate of the energy in the linear regime. We thus set $E = E_\te{propagated}$ and obtain an expression for $r_0$
\begin{align}
r_0 = \f{K^2}{\lambda+2\mu}\f{3\epsilon}{2\pi p_0^2\Delta r}-\f{3\Delta r}{4}\,.
\end{align}
$r_0$ demarcates the end of the non-linear regime. As the length of the pulse tends to zero, the non-linear regime extends without bound. We require $p_0\leq 10^8\te{\,Pa}$, corresponding to an order of magnitude below the elastic limit of granite. A lower bound on $r_0$ is 0, corresponding to entirely linear behavior. This, in turn, imposes an upper bound on the pulse width
\begin{align}
\Delta r\leq\sqrt{\f{2\kappa \p{\rho\sigma_X v_X^2 - \epsilon_\te{melt}}}{\pi p_0^2}}\,.
\end{align}
We now form $\Xi:=E_k/E_\te{propagated}$ representing the fraction of deposited energy detectable to seismometers
\begin{align}
\Xi = k^2\f{\p{\pi p_0^2\Delta r^2-18\kappa \epsilon}^2}{576 \pi p_0^2 \kappa \epsilon}\,.
\end{align}
When $\Delta r$ is restricted to its physical range, $\Xi$ is a monotonic decreasing function in $\Delta r$. Thus
\begin{align}
\f{4}{9}\f{\kappa}{\pi p_0^2} \epsilon k^2\leq \Xi <\f{9}{16}\f{\kappa}{\pi p_0^2}\epsilon k^2\,.
\end{align}
It is important to remember that these expressions only hold for $k(r_0+\Delta r)\ll 1$, however they will always provide an over-estimate of the fraction of detectable energy.

\section{Seismic Wave Propagation}
The velocity of $p$-waves as a function of radius within the Earth and Moon (and presumably other spherical rocky celestial bodies) is of the form $v = a^2 - b^2 r^2$. Using Snell's law, we obtain the differential equations for the trajectory of $p$-wave rays within such bodies
\begin{align}
v^2 \notag&= \dot r^2 + \f{p_\te{ray}^2 v^4}{r^2}\,,\\
0 &=\dot\theta\pm\f{p_\te{ray} v^2}{r^2}\,.
\end{align}
where $r$ is the radial coordinate of the ray, $\theta$ is the polar angle of the ray measured from the center of the body, and $p_\te{ray}$ is the ray constant, whose value is fixed along a ray trajectory. These equations can be integrated. In the case that $v = a^2 - b^2 r^2$, we obtain for some constants $q$ and $\theta_0$.
\begin{align}
\notag&r(t) = \f{a\sqrt{(qe^{2abt}-b)^2 + 4a^2b^4 p_\te{ray}}}{b\sqrt{(qe^{2abt}+b)^2 + 4a^2b^4 p_\te{ray}}}\,,\\
&\tan(\theta(t) - \theta_0) = \f{(qe^{2abt}-b)(qe^{2abt}+b)}{4ab^3p_\te{ray}}+abp_\te{ray}\,.
\end{align}
\textit{A priori} these are geodesics on the Poincar\'e disc of radius $\f ab$ based on the form of $v$.

The Earth and Moon are stratified. At each boundary, a ray will be reflected and transmitted. We assume that the reflection and transmission coefficients are frequency independent for simplicity.

The last effect to account for is anelastic attenuation, which does depend on frequency. Anelastic attenuation is characterized by the quality factor $Q$, which is, in general, dependent on $r$. For a given mode, the ratio of final to initial amplitude is
\begin{align}
\exp\ps{-k \int_{t_0}^t\diff t'\f{v(r(t))}{2Q(r(t))}}:=\exp\ps{-k \te{Att}}\,.
\end{align}
The VPREMOON model provides piecewise constant data for $Q$, so it is reasonable to subdivide the moon further into strata of different $Q$. For propagation within a given layer $i$, the factor $\te{Att}$ is given by $\Delta t_i v_i/Q_i$, where we take $v_i$ to be the average velocity within a given strata. For the case of the Earth and Moon, this is a good approximation since $v$ doesn't change much within a given layer of constant $Q$. Thus, the amplitude of a ray can be computed by knowing the two numbers
\begin{align}
\te{Ref} \notag&= \prod_i\te{Ref}_i\,,\\
\te{Att} &=\sum_i\f{\Delta t_i v_i}{Q_i}\,,
\end{align}
where $\te{Ref}_i$ are the reflection or transmission coefficients of boundary $i$ on which the ray is incident.

\section{Seismic Wave Detection}
The seismometers on the Moon are sensitive to displacements as small as $0.3\te{\,nm}$. We calculate the displacement due to each ray, and describe how they add. Consider a $p$-wave traveling towards positive $x$ and of compact support $S$ in the plane normal to to its motion. Denote $A =\int_S\diff y\diff z$ The displacement field is
\begin{align}
u(\vec x,t) &= \chi_{\R\times S}\int\f{\diff k}{2\pi}U(k)e^{-\I k(x-v_p t)}\,,\\
\abs{u(\vec x,t)}&\leq\chi_{\R\times S}\int\f{\diff k}{2\pi}\abs{U(k)}\,,
\end{align}
and the energy is
\begin{align}
E = \rho v_p^2 A\int\f{\diff k}{2\pi}k^2\abs{U(k)}^2\,.
\end{align}
As before, we denote
\begin{align}
E_k = \rho v_p^2 A\int_0^k\f{\diff k'}{2\pi}k'^2\abs{U(k')}^2\,.
\end{align}
It follows that
\begin{align}
\abs{U(k)} = \sqrt{\f{2\pi}{\rho v_p^2 A}}\f1k\sqrt{\td{E_k}{k}{}}\,,
\end{align}
and from the estimate above
\begin{align}
\abs{u(\vec x,t)}\leq(2\pi\rho v_p^2 A)^{-1/2}\int_0^k\f{\diff k'}{k'}\sqrt{\td{E_{k'}}{k'}{}}\,.
\end{align}
In our case $\Xi E=E_k = C_1 k^2$ before attenuation. After anelastic attenuation, $E_k' =\te{Ref}\,2C_1 k e^{-\te{Att}}$
\begin{align}
\abs{u(\vec x,t)}\leq\sqrt{\f{2}{\rho v_p^2 A}}\sqrt{\f{\te{Ref}\,\Xi E}{\te{Att}}}\f1k\te{Erf}\ps{\sqrt{\f{\te{Att}\,k}{2}}}\,.
\end{align}
Using the upper bound on $\Xi$ for the triangle wave, we have
\begin{align}
\abs{u(\vec x,t)}\leq \f{3}{4}\sqrt{\f{2\kappa \epsilon^2 \ell}{\rho p_0^2 v_p^2 \pi A  }}\sqrt{\f{\te{Ref}}{\te{Att}}}\te{Erf}\ps{\sqrt{\f{\te{Att}\,k}{2}}}\,.
\end{align}
\section{Simulation}

\section{Results}

\section{Conclusion}
\end{document}

### 2016-08-19 Macro Impacts Revised.tex
update

@@
 \pagebreak
-\section{Fourier Series}
-We take the Fourier series in time along the direction of the pulse
-\begin{align}
-u =\f{1}{2\pi L} \sum_{k = 0}^{N} U(k) e^{-2\pi \I \f{L k}{N}(x -v_p t)}
-\end{align}
-Then
-\begin{align}
-\partial_t u = \f{\I v_p}{(2\pi L)^2} \sum_{k = 0}^{N} k U(k) e^{-2\pi \I \f{L k}{N}(x -v_p t)}\,.
-\end{align}
-Thus
-\begin{align}
-E &= A_{\te{ray}}\rho \int_0^L\diff x\abs{\partial_t u}^2\,,\\
-&= A_{\te{ray}}\rho \int_0^L\diff x\f{v_p^2}{(2\pi L)^2} \sum_{k,k' = 0}^{N} k k' U(k)\bar U(k') e^{-2\pi \I \f{L (k-k')}{N}(x -v_p t)}\,,\\
-&= A_{\te{ray}}\rho \f{v_p^2}{(2\pi L)^2} \sum_{k,k' = 0}^{N} k k' U(k)\bar U(k') \int_0^L\diff x e^{-2\pi \I \f{L (k-k')}{N}(x -v_p t)}\,,\\
-&= A_{\te{ray}}\rho \f{v_p^2}{(2\pi L)^2} \sum_{k,k' = 0}^{N} k k' U(k)\bar U(k') 2\pi L\delta_{k k'}e^{2\pi \I \f{L (k-k')}{N}(v_p t)}\,,\\
-&= A_{\te{ray}}\rho \f{v_p^2}{2\pi L} \sum_{k= 0}^{N} k^2 \abs{U(k)}^2\,.
-\end{align}
-Define
-\begin{align}
-E_k =  A_{\te{ray}}\rho \f{v_p^2}{2\pi L} k^2 \abs{U(k)}^2\,.
-\end{align}
-What is $E_k$? Using the general cylindrically symmetric source from before, we know $E_k= C_1 \f{k^2}{(2\pi L)^2}$. Solving for $\abs{U}$, we have
-\begin{align}
-\abs{U(k)} = \sqrt{\f{2\pi L}{v_p^2 A_{\te{ray}}\rho}\f{E_k}{ k^2}}
-\end{align}
-In our case, we have
-\begin{align}
-\abs{U(k)} = \sqrt{\f{C_1}{2\pi L v_p^2 A_{\te{ray}}\rho}}\,.
-\end{align}
-This is just a constant, so $U(k)$ is a pure phase, which comes out of the sum, so
-\begin{align}
-\abs{u} =\f{1}{2\pi L}\sqrt{\f{C_1}{2\pi L v_p^2 A_{\te{ray}}\rho}} \sum_{k = 0}^{N} \cos\p{2\pi\f{L k}{N}(x -v_p t)}
-\end{align}
-\pagebreak
-\\
-Hm, something's fishy... What about this:
+\section{Directed Ray}
+This time, we assume the oscillation is just in the $x$ direction.
 \begin{align}
@@
 k \geq\f{2\pi}{v_p\Delta T}\,.
-\end{align}
-\pagebreak
-\section{Double Thought Out}
-Thanks to Josh for a very useful conversation in helping to deduce what follows:
-\\\\
-A key problem we are encountering is what follows.
-Suppose we shoot out a large number of rays that uniformly hit the surface of the sphere.
-If we have $N$ rays in a pixel, and then halve the area of the pixel, we will have $N/2$ rays in the pixel.
-This, in turn, reduces the energy in the pixel, and if not accounted for properly, the measured displacement.
-If, however, when increase the number of pixels, we also multiply the energy in each pixel by the number of pixels, then assuming a uniform distribution of rays, the average displacement across pixels does not change as the number of pixels increases.
-\\\\
-Thus, suppose we have $M$ rays and $N$ pixels. Let $M_j$ be the number of rays incident on pixel $j$. Let $E_k^{ij}$ be the energy of the $i$th ray incident on the $j$th pixel. We then calculate
-\begin{align}
-E_k^j =N\sum_{i=1}^{M_j}E_k^{ij}\,.
-\end{align}
-We now calculate the displacement, where $C_2^{ij} = v_p \f{T^{ij}}{Q^{ij}}$.
-\begin{align}
-\td{E_k^{j}}{k}{} = N\sum_{i = 1}^{M_j}2 C_1^{ij} k'e^{-C_2^{ij} k}\,.
-\end{align}
-The integral would be impossible without an approximation
-\begin{align}
-\sqrt{\td{E_k^{j}}{k}{}} & = \sqrt{N\sum_{i = 1}^{M_j}2 C_1^{ij} k'e^{-C_2^{ij} k}}\,,\\
-& \leq \sqrt{N\p{\sum_{i = 1}^{M_j}\sqrt{2 C_1^{ij} k'e^{-C_2^{ij} k}}}^2}\,,\\
-&=\sqrt{N}\sum_{i = 1}^{M_j}2 C_1^{ij} \sqrt{k'}e^{-C_2^{ij}\f{k}{2}}\,.
-\end{align}
-Whence
-\begin{align}
-u_k^j&\leq\f{\sqrt{N}}{2\pi kv_p\sqrt{\rho}}\sum_{i}^{M_j}\f{\sqrt{E_k^{ij}}}{C_2^{ij}}\p{\sqrt{ \f{2\pi}{C_2^{ij}}}\te{Erf}\ps{\sqrt{\f{k}{2}C_2^{ij}}} -2\sqrt{k} e^{-\f{k }{2}C_2^{ij}}}\,.
 \end{align}

### 2016-08-19 Macro Impacts Revised.tex
Thermal source revisions/v2
Added a variation of the approach presented, with a couple of
corrections.  Interestingly, the results of micrometers to tens of
micrometers remains true.

@@
 \pagebreak
+
 \section{Revised Estimate}
@@
 \pagebreak
+
 \section{Directed Ray}
@@
 \end{align}
+(David, what happened to the factor of $2\pi$?)
 Setting $T = T_\te{melt}$, we have
@@
 \begin{align}
-\dot r_\te{melt} &=\sqrt{\f{\alpha}{t}\ln\p{\f{r_Xv_0^2}{2 c_p\alpha T}}}\,.
+\dot r_\te{melt} &=\sqrt{\f{\alpha}{t}\ln\p{\f{r_Xv_0^2}{2 t c_p\alpha T}}}\,.
 \end{align}
@@
 which is on the order of micrometers to tenths of micrometers for our case.
+
+\pagebreak
+Note: The following is based on the above written by David, and modified by Josh (David, feel free to take whatever you'd like and apply to the above):
+
+The equation governing the evolution of the temperature field in 2 dimensions is, with no driving term,
+\begin{align}
+\partial_t T - \alpha\nabla^2 T = 0
+\end{align}
+where $\alpha$ is the thermal diffusivity, and $\alpha=\f{k}{c_p\rho}$. In cylindrical coordinates and for $T = T(r)$, we have
+\begin{align}
+\partial_t T - \alpha\nabla_r T = 0
+\end{align}
+We now Fourier transform in $r$ and $\phi$, yielding
+\begin{align}
+\partial_t\tilde T =-\alpha k_r^2 \tilde T\,,
+\end{align}
+where
+\begin{align}
+\tilde T =  \int_0^\infty r \diff r\int_{0}^{2\pi} T e^{i r(k_x\cos\phi +k_y\sin\phi)}\diff \phi\, = 2\pi \int_0^\infty r \diff r  T J_0(k_r r)\,.
+\end{align}
+where
+\begin{align}
+k_r = k_x\cos\phi +k_y\sin\phi
+\end{align}
+Now, we integrate $\partial_t\tilde T =-\alpha k_r^2 \tilde T\,$ and find that
+\begin{align}
+\tilde T = C_1e^{-\alpha k_r^2 t}.
+\end{align}
+
+Consider the initial condition of a delta source along the z-axis in cylindrical coordinates:
+\begin{align}
+T(r,0) = \f{\abs{\frac{dE}{dx}}}{\rho \sigma_x c_p}\delta(r),
+\end{align}
+Then, taking the Fourier transform of this initial condition over r and $\phi$ fixes $C_1$ as 
+\begin{align}
+C_1 =  2\pi \f{\abs{\frac{dE}{dx}}}{\rho \sigma_x c_p}\int_{0}^{\infty}\delta(r)e^{2\pi i k r} dr = 2\pi\f{\abs{\frac{dE}{dx}}}{\rho \sigma_x c_p}\,,
+\end{align}
+where the factor of $2 \pi$ comes from the $\phi$ integral.
+$T$ in real space is given by inverting the Fourier transform:
+\begin{align}
+T(r,t) &= \int_0^\infty k_r \diff{k_r}\tilde{T} = 4\pi^2\f{\abs{\frac{dE}{dx}}}{\rho \sigma_x c_p}\int_0^\infty k_r\diff k_r e^{-\alpha k_r^2 t}J_0(k_r r)\,,\\
+&=\f{\abs{\frac{dE}{dx}}}{2 \rho \sigma_x c_p \alpha t}\ e^{-\f{r^2}{4t\alpha}}\,.
+\end{align}
+(I'm not sure about the last equality given that I'm still a bit unclear about the factors of $2\pi$ for the inverse transform as noted above after eq.
+(300) It would seem there are factors from $C_1$ and $\tilde{T}$.
+However, the rest of what follows holds, up to some factors of $2\pi$ that hopefully we can clarify).
+Setting $T = T_\te{melt}$, we have
+\begin{align}
+r_\te{melt} = \sqrt{4t\alpha\ln\ps{\f{\abs{\frac{dE}{dx}}}{2 \rho \sigma_x c_p \alpha T_\te{melt} t}}}\,.
+\end{align}
+where we've taken the positive branch of the square root, since we only care about the melt radius increasing. Then taking the derivative w.r.t to time gives
+\begin{align}
+\dot r_\te{melt} &=\sqrt{\f{\alpha}{t}}\f{\ln\p{\f{\abs{\frac{dE}{dx}}}{2 \rho \sigma_x c_p \alpha T_\te{melt} t}} - 1}{\sqrt{\ln\p{\f{\abs{\frac{dE}{dx}}}{2 \rho \sigma_x c_p \alpha T_\te{melt} t}}}}\,.
+\end{align}
+Since, for the parameters at hand, $\ln\p{\f{\abs{\frac{dE}{dx}}}{2 \rho \sigma_x c_p \alpha T_\te{melt} t}}$ is at least of order 10 $>>$ 1, it is a good approximation to take
+\begin{align}
+\dot r_\te{melt} &=\sqrt{\f{\alpha}{t}\ln\p{\f{\abs{\frac{dE}{dx}}}{2 \rho \sigma_x c_p \alpha T_\te{melt} t}}}\,.
+\end{align}
+Thus, the time at which the velocity of the melt front is that of the speed of sound is given by using the Lambert W-function (or "ProductLog" in Mathamatica) as
+\begin{align}
+t_{\te{fast}} = \f{\alpha}{v_p^2}W\p{{\f{\abs{\frac{dE}{dx}v_p^2}}{2 \rho \sigma_x c_p \alpha^2 T_\te{melt}}}}
+\end{align}
+Plugging in $t_{\te{fast}}$ to $r_\te{melt}$, which is a good approximation in our case, gives
+\begin{align}
+r_\te{fast melt} =  \frac{2\alpha}{v_p}\sqrt{W\p{{\f{\abs{\frac{dE}{dx}v_p^2}}{2 \rho \sigma_x c_p \alpha^2 T_\te{melt}}}}\ln\ps{\p{\frac{\abs{\frac{dE}{dx}v_p^2}}{2 \rho \sigma_x c_p \alpha^2 T_\te{melt}}}\frac{1}{W\p{{\f{\abs{\frac{dE}{dx}v_p^2}}{2 \rho \sigma_x c_p \alpha^2 T_\te{melt}}}}
+}}}\,.
+\end{align}
+Notice that this has the form of $\sqrt{W(x)\ln\p{{\frac{x}{W(x)}}}}$, which gives $\sqrt{W(x)^2}$ by the identity $\ln\p{{\frac{x}{W(x)}}} = W(x)$ which holds when $x \geq -1/e$ which is true for the parameters at hand.
+Thus, we have,
+\begin{align}
+r_\te{fast melt} =\frac{2\alpha}{v_p}W\p{{\f{\abs{\frac{dE}{dx}v_p^2}}{2 \rho \sigma_x c_p \alpha^2 T_\te{melt}}}}.
+\end{align}
+which is on the order of micrometers to tenths of micrometers for our case.
+
 \end{document}

### 2016-08-19 Macro Impacts Revised.tex
minor stuff
minor indeed

@@
 \end{align}
-Thus, the time at which the velocity of the melt front is that of the speed of sound is given by using the Lambert W-function (or "ProductLog" in Mathamatica) as
+Thus, the time at which the velocity of the melt front is that of the speed of sound, $v_p$, is given by using the Lambert W-function (or "ProductLog" in Mathamatica) as
 \begin{align}
@@
 \end{align}
-Plugging in $t_{\te{fast}}$ to $r_\te{melt}$, which is a good approximation in our case, gives
+Plugging in $t_{\te{fast}}$ to $r_\te{melt}$, which is a solid approximation in our case, gives
 \begin{align}

### 2016-08-19 Macro Impacts Revised.tex
actually nothing
style points

@@
 \end{align}
-Since, for the parameters at hand, $\ln\p{\f{\abs{\frac{dE}{dx}}}{2 \rho \sigma_x c_p \alpha T_\te{melt} t}}$ is at least of order 10 $>>$ 1, it is a good approximation to take
+Since, for the parameters at hand, $\ln\p{\f{\abs{\frac{dE}{dx}}}{2 \rho \sigma_x c_p \alpha T_\te{melt} t}}$ is at least of order 10 $>>$ 1, it is a reasonable approximation to take
 \begin{align}
@@
 \end{align}
-Plugging in $t_{\te{fast}}$ to $r_\te{melt}$, which is a solid approximation in our case, gives
+Plugging in $t_{\te{fast}}$ to $r_\te{melt}$, which is a solid approximation for the given case, gives
 \begin{align}

### 2016-08-19 Macro Impacts Revised.tex
Question answered
By wiki on Hankel transform -- the inverse transform has a factor of
(2Pi)^-2

@@
 \end{align}
-(David, what happened to the factor of $2\pi$?)
 Setting $T = T_\te{melt}$, we have
@@
 \begin{align}
-T(r,t) &= \int_0^\infty k_r \diff{k_r}\tilde{T} = 4\pi^2\f{\abs{\frac{dE}{dx}}}{\rho \sigma_x c_p}\int_0^\infty k_r\diff k_r e^{-\alpha k_r^2 t}J_0(k_r r)\,,\\
+T(r,t) &=\frac{1}{\p{2\pi}^2} \int_0^\infty k_r \diff{k_r}\tilde{T} = \frac{4\pi^2}{4\pi^2}\f{\abs{\frac{dE}{dx}}}{\rho \sigma_x c_p}\int_0^\infty k_r\diff k_r e^{-\alpha k_r^2 t}J_0(k_r r)\,,\\
 &=\f{\abs{\frac{dE}{dx}}}{2 \rho \sigma_x c_p \alpha t}\ e^{-\f{r^2}{4t\alpha}}\,.
 \end{align}
-(I'm not sure about the last equality given that I'm still a bit unclear about the factors of $2\pi$ for the inverse transform as noted above after eq.
-(300) It would seem there are factors from $C_1$ and $\tilde{T}$.
-However, the rest of what follows holds, up to some factors of $2\pi$ that hopefully we can clarify).
 Setting $T = T_\te{melt}$, we have

### 2016-08-19 Macro Impacts Revised.tex
Not so fast...
Um, maybe those factors should be there afterall.

@@
 \end{align}
-where the factor of $2 \pi$ comes from the $\phi$ integral.
+where the factor of $2 \pi$ comes from the $\phi$ integral (notice this factor in $C_1$ cancels against the factor in $\tilde{T}$ -- David, is this is correc?).
 $T$ in real space is given by inverting the Fourier transform:
 \begin{align}
-T(r,t) &=\frac{1}{\p{2\pi}^2} \int_0^\infty k_r \diff{k_r}\tilde{T} = \frac{4\pi^2}{4\pi^2}\f{\abs{\frac{dE}{dx}}}{\rho \sigma_x c_p}\int_0^\infty k_r\diff k_r e^{-\alpha k_r^2 t}J_0(k_r r)\,,\\
+T(r,t) &=\frac{1}{\p{2\pi}^2} \int_0^\infty k_r \diff{k_r}\tilde{T} = \frac{1}{4\pi^2}\f{\abs{\frac{dE}{dx}}}{\rho \sigma_x c_p}\int_0^\infty k_r\diff k_r e^{-\alpha k_r^2 t}J_0(k_r r)\,,\\
 &=\f{\abs{\frac{dE}{dx}}}{2 \rho \sigma_x c_p \alpha t}\ e^{-\f{r^2}{4t\alpha}}\,.
 \end{align}
+(If the third equation is valid up to some factors of $2\pi$, then the rest is valid  but needs to be fixed to include these factors properly).
 Setting $T = T_\te{melt}$, we have

### 2016-08-19 Macro Impacts Revised.tex
One final note
Conceptual point added at the end

@@
 \end{align}
-Then, taking the Fourier transform of this initial condition over r and $\phi$ fixes $C_1$ as 
+Taking the Fourier transform of this initial condition over r and $\phi$ fixes $C_1$ as 
 \begin{align}
@@
 \end{align}
-(If the third equation is valid up to some factors of $2\pi$, then the rest is valid  but needs to be fixed to include these factors properly).
+(If the third equation is valid up to some factors of $2\pi$ that I'm too tired to figure out right now, then the rest is valid  but needs to be fixed to include these factors properly).
 Setting $T = T_\te{melt}$, we have
@@
 \begin{align}
-t_{\te{fast}} = \f{\alpha}{v_p^2}W\p{{\f{\abs{\frac{dE}{dx}v_p^2}}{2 \rho \sigma_x c_p \alpha^2 T_\te{melt}}}}
+t_{\te{fast}} = \f{\alpha}{v_p^2}W\p{{\f{\abs{\frac{dE}{dx}}v_p^2}{2 \rho \sigma_x c_p \alpha^2 T_\te{melt}}}}
 \end{align}
@@
 \begin{align}
-r_\te{fast melt} =  \frac{2\alpha}{v_p}\sqrt{W\p{{\f{\abs{\frac{dE}{dx}v_p^2}}{2 \rho \sigma_x c_p \alpha^2 T_\te{melt}}}}\ln\ps{\p{\frac{\abs{\frac{dE}{dx}v_p^2}}{2 \rho \sigma_x c_p \alpha^2 T_\te{melt}}}\frac{1}{W\p{{\f{\abs{\frac{dE}{dx}v_p^2}}{2 \rho \sigma_x c_p \alpha^2 T_\te{melt}}}}
+r_\te{fast melt} =  \frac{2\alpha}{v_p}\sqrt{W\p{{\f{\abs{\frac{dE}{dx}}v_p^2}{2 \rho \sigma_x c_p \alpha^2 T_\te{melt}}}}\ln\ps{\p{\frac{\abs{\frac{dE}{dx}}v_p^2}{2 \rho \sigma_x c_p \alpha^2 T_\te{melt}}}\frac{1}{W\p{{\f{\abs{\frac{dE}{dx}}v_p^2}{2 \rho \sigma_x c_p \alpha^2 T_\te{melt}}}}
 }}}\,.
@@
 \begin{align}
-r_\te{fast melt} =\frac{2\alpha}{v_p}W\p{{\f{\abs{\frac{dE}{dx}v_p^2}}{2 \rho \sigma_x c_p \alpha^2 T_\te{melt}}}}.
+r_\te{fast melt} =\frac{2\alpha}{v_p}W\p{{\f{\abs{\frac{dE}{dx}}v_p^2}{2 \rho \sigma_x c_p \alpha^2 T_\te{melt}}}}.
 \end{align}
@@
 
+Conceptually, it would seem that $r_\te{fast melt}$ should be added to $r_\te{Macro}$ to give the full extent of material melted down.
+
 \end{document}

### 2016-08-19 Draft.tex
Update

@@
 Previous limits were based on the energy deposition of Macros being akin to that of a nuclear bomb.
-Our estimates take into account the effect of seismometer sensitivity and energy distribution across frequencies, anelastic attenuation, geometric effects due to internal anisotropy of the Earth or Moon, as well as energy loss due to melting.
+Our estimates take into account the effect of seismometer sensitivity and energy distribution across frequencies, anelastic attenuation, geometric effects, internal anisotropy of the Earth or Moon, as well as energy loss due to melting.
 We produce new constraints on the Macro parameter space based on the total lunar seismic event rate.
@@
 \subsection{The Melt Wave}
-The section of parameter space we are interested in contains Macros whose cross sectional area is small enough that the act of the macro penetrating the Moon does not significantly contribute to the seismic signal.
-That is to say, a small enough amount of moon is displaced that the energy lost due to this displacement is negligible compared to the total energy deposition.
-When this scenario holds, the energy deposited by the Macro can be treated as being used to heat up a column of cross sectional area $\sigma_X$ and length $\ell$.
+The section of parameter space we are interested in contains Macros whose cross sectional area is small enough that the energy lost due to the macro displacing rock is negligible compared to the total energy deposition.
+When this scenario holds, the energy deposited by the Macro can be treated as heating a column of cross sectional area $\sigma_X$ and length $\ell$.
 
@@
 \begin{align}
-r_\te{melt} = \sqrt{4t\alpha\ln\ps{\f{r_X v_0^2}{2 c_p t \alpha T_\te{melt}}}}\,,
+r_\te{melt}= \sqrt{4t\alpha\ln\ps{\f{r_X v_0^2}{2 c_p t \alpha T_\te{melt}}}}\,,
 \end{align}
@@
 For $p$-waves, $p = -K\nabla\cdot u$ where $K$ is the bulk modulus.
-Define $\kappa = (\lambda + 2\mu)/K^2$ Fourier transforming, we find that $U = \I P\vec k/K k^2$ and hence
+Define $\kappa = K^2/(\lambda + 2\mu)$ Fourier transforming, we find that $U = \I P\vec k/K k^2$ and hence
 \begin{align}
-E =\kappa\int\f{\diff^3 k}{(2\pi)^3}\abs{P}^2\,.
+E =\f1\kappa\int\f{\diff^3 k}{(2\pi)^3}\abs{P}^2\,.
 \end{align}
@@
 \begin{align}
-E_k = \kappa\int_0^k\f{\diff k'\diff\theta}{(2\pi)^2}k'^2\sin\theta\abs{P}^2\,.
+E_k = \f1\kappa\int_0^k\f{\diff k'\diff\theta}{(2\pi)^2}k'^2\sin\theta\abs{P}^2\,.
 \end{align}
@@
 \begin{align}
-\notag E_k&=\kappa 2p_0^2F^2\ell k^2\\\notag&\times\p{\f{\sin(\ell k)+k\ell(\cos(\ell k)-2)}{\ell^2 k^2}+\te{Si}(\ell k)}+\scr O(k^4)\,.
+\notag E_k&=\f1\kappa 2p_0^2F^2\ell k^2\\\notag&\times\p{\f{\sin(\ell k)+k\ell(\cos(\ell k)-2)}{\ell^2 k^2}+\te{Si}(\ell k)}+\scr O(k^4)\,.
 \end{align}
@@
 \begin{align}
-E_k&=\kappa \pi\ell p_0^2F^2 k^2:=C_1 k^2\,.
+E_k&=\f1\kappa \pi\ell p_0^2F^2 k^2:=C_1 k^2\,.
 \end{align}
@@
 \begin{align}
-E_k = \kappa \f{\Delta r^2(3r_0+2\Delta r)^2}{36} \pi\ell p_0^2k^2\,.
+E_k = \f{\Delta r^2(3r_0+2\Delta r)^2}{36 \kappa} \pi\ell p_0^2k^2\,.
 \end{align}
@@
 \begin{align}
-E \notag&= 2\pi p_0^2\ell\kappa\int_a^b r\diff r f(r)^2\,,\\
-&=\kappa\f{p_0^2}{6}\pi\Delta r \ell(4r_0 + 3\Delta r)\,.
+E \notag&= \f{2\pi p_0^2\ell}{\kappa}\int_a^b r\diff r f(r)^2\,,\\
+&=\f{p_0^2}{6\kappa}\pi\Delta r \ell(4r_0 + 3\Delta r)\,.
 \end{align}
@@
 \begin{align}
-r_0 = \f{K^2}{\lambda+2\mu}\f{3\epsilon}{2\pi p_0^2\Delta r}-\f{3\Delta r}{4}\,.
+r_0 =  \f{3\kappa\epsilon}{2\pi p_0^2\Delta r}-\f{3\Delta r}{4}\,.
 \end{align}
@@
 \begin{align}
-\Delta r\leq\sqrt{\f{2\kappa \p{\rho\sigma_X v_X^2 - \epsilon_\te{melt}}}{\pi p_0^2}}\,.
+\Delta r\leq\sqrt{\f{2\kappa \epsilon}{\pi p_0^2}}\,.
 \end{align}
@@
 \begin{align}
-\f{4}{9}\f{\kappa}{\pi p_0^2} \epsilon k^2\leq \Xi <\f{9}{16}\f{\kappa}{\pi p_0^2}\epsilon k^2\,.
+\f{4}{9}\f{\kappa\epsilon k^2}{\pi  p_0^2} \leq \Xi <\f{9}{16}\f{\kappa\epsilon k^2}{\pi  p_0^2}\,.
 \end{align}
@@
 \end{align}
-In our case $\Xi E=E_k = C_1 k^2$ before attenuation. After anelastic attenuation, $E_k' =\te{Ref}\,2C_1 k e^{-\te{Att}}$
+In our case $\Xi E= C_1 k^2$ before attenuation. After anelastic attenuation, $E_k =\te{Ref}\,2C_1 k e^{-k\,\te{Att}}$
 \begin{align}
@@
 \begin{align}
-\abs{u(\vec x,t)}\leq \f{3}{4}\sqrt{\f{2\kappa \epsilon^2 \ell}{\rho p_0^2 v_p^2 \pi A  }}\sqrt{\f{\te{Ref}}{\te{Att}}}\te{Erf}\ps{\sqrt{\f{\te{Att}\,k}{2}}}\,.
+\abs{u(\vec x,t)}\leq \f{3}{4}\sqrt{\f2\pi\f{\kappa \epsilon^2 \ell}{\rho p_0^2 v_p^2 A  }}\sqrt{\f{\te{Ref}}{\te{Att}}}\te{Erf}\ps{\sqrt{\f{\te{Att}\,k}{2}}}\,.
 \end{align}

### 2016-08-19 Ray-Tracing/Ray_Tracing_Moon.m

@@ -5,19 +5,19 @@ format long
 
 
 %INPUTS
-D = 1200; %THE DISTANCE OF CLOSEST APPROACH TO THE CENTER km
+D = 0; %THE DISTANCE OF CLOSEST APPROACH TO THE CENTER km
 ACO = 9; %IT TAKES 16 ITERATIONS FOR A RAY TO PASS ENTIRELY THROUGH THE MOON
 
-vX = 250; %km/s
-sigmaX = (10^(-11))*(10^(-4))*(10^(-6));%kg/km^3
-fhigh = 2;%1/s %HIGHEST DETECTABLE FREQUENCY
-TotalDensityAverage = 3.3*10^12; %THE AVERAGE DENSITY THROUGHOUT THE WHOLE MOON
+vX = 2.5 * 10^5; %m/s
+sigmaX = (10^(-7)) * (10^(-4));% m^2
+fhigh = 20;%1/s %HIGHEST DETECTABLE FREQUENCY
+TotalDensityAverage = 3.3*10^3; %THE AVERAGE DENSITY THROUGHOUT THE WHOLE MOON
 pbar = 10^8;%HOOKIAN PRESSURE kg/(m*s^2)
-vs = 4.4 * 10^3;%AVERAGE SHEAR WAVE VELOCITY THROUGHOUT THE WHOLE MOON
-vp = 7.6 * 10^3;%AVERAGE PRESSURE WAVE VELOCITY THROUGHOUT THE WHOLE MOON
+vs = 4.4 * 10^3;%AVERAGE SHEAR WAVE VELOCITY THROUGHOUT THE WHOLE MOON m/s
+vp = 7.6 * 10^3;%AVERAGE PRESSURE WAVE VELOCITY THROUGHOUT THE WHOLE MOON m/s
 
-M = 100; %NUMBER OF POINTS ON THE LINE
-N = 20; %NUMBER OF RAYS FROM EACH POINT
+M = 10; %NUMBER OF POINTS ON THE LINE
+N = 10; %NUMBER OF RAYS FROM EACH POINT
 %{
 %APPROXIMATION TO OUTER LAYERS
 a = [8.26955,8.26955,8.26955,8.26955,145.46].^(1/2);
@@ -33,14 +33,14 @@ rhoBoundaries = [   3.406       ,   3.406               ;...
 %}
 %%{
 %VPREMOON MODEL
[…]

### 2016-08-20 Draft.tex
Lovely result at the end of Draft.pdf

@@
 \begin{align}
-r_\te{melt}= \sqrt{4t\alpha\ln\ps{\f{r_X v_0^2}{2 c_p t \alpha T_\te{melt}}}}\,,
+r_\te{melt}= \sqrt{4t\alpha\ln\ps{\f{r_X v_X^2}{2 c_p t \alpha T_\te{melt}}}}\,,
 \end{align}
@@
 It is important to remember that these expressions only hold for $k(r_0+\Delta r)\ll 1$, however they will always provide an over-estimate of the fraction of detectable energy.
+Moreover, this condition holds for a wide variety of reasonable parameters.
 
@@
 \begin{align}
-\notag&r(t) = \f{a\sqrt{(qe^{2abt}-b)^2 + 4a^2b^4 p_\te{ray}}}{b\sqrt{(qe^{2abt}+b)^2 + 4a^2b^4 p_\te{ray}}}\,,\\
-&\tan(\theta(t) - \theta_0) = \f{(qe^{2abt}-b)(qe^{2abt}+b)}{4ab^3p_\te{ray}}+abp_\te{ray}\,.
+\notag&r(t) = \f{a\sqrt{(q^2e^{2abt}-b)^2 + 4a^2b^4 p_\te{ray}}}{b\sqrt{(qe^{2abt}+b)^2 + 4a^2b^4 p_\te{ray}}}\,,\\
+&\tan(\theta(t) - \theta_0) = \f{qe^{4abt}-b^2}{4ab^3p_\te{ray}}+abp_\te{ray}\,.
 \end{align}
@@
 u(\vec x,t) &= \chi_{\R\times S}\int\f{\diff k}{2\pi}U(k)e^{-\I k(x-v_p t)}\,,\\
-\abs{u(\vec x,t)}&\leq\chi_{\R\times S}\int\f{\diff k}{2\pi}\abs{U(k)}\,,
+\abs{u(\vec x,t)}&\leq\int\f{\diff k}{2\pi}\abs{U(k)}\,,
 \end{align}
@@
 \end{align}
-Using the upper bound on $\Xi$ for the triangle wave, we have
+\section{Simulation}
+The simulation is broken down into two natural parts: data generation and data analysis.
+The data generation consists of propagating a large number of rays to approximate a line source of $p$-waves and tracking the positions and energies at which they contact the surface of the moon.
+The data analysis makes use of HEALPix to approximate the energy density on the sphere and then makes use of section IV to measure displacements.
+\subsection{Data Generation}
+To generate the data, we consider a Macro trajectory which passes a distance $D$ from the center of the moon.
+This trajectory has a length $L$.
+Along this trajectory, we consider a set of $M$ points, from each of which we shoot $N$ rays, each endowed with $E_m = \rho(r_{m})\sigma_Xv_X^2 L/(MN)$ energy, where $m\in\{1,\dots,M\}$ labels the point.
+Because of the spherical symmetry, each ray is confined to a subspace of two dimensions.
+We use the trajectories in section III to propagate the rays.
+Since the moon is stratified, we must halt the propagation at the boundary of each layer and reflect/transmit rays.
+During a ray's propagation through a given stratum $\Delta t_i$ is recorded and added to $\Delta t$, $\te{ATT}_i$ is recorded and added to $\te{ATT}$, and $\te{REF}_i$ is recorded at the boundary and is multiplied by $\te{REF}$.
+Each time a ray makes contact with the surface of the Moon, its position, $\te{ATT}$, $\te{REF}$, $\Delta t$, and $E_m$ are recorded.
+The final data is a table of these values corresponding to each ray intersection with the surface.
+We iterate 16 times since it takes 16 iterations for a ray to pass entirely through the VPREMOON model stratification.
+\subsection{Data Analysis}
+We now convert the position data to HEALPix coordinates for a given $n_\te{side}$.
+Define $A_\te{pix} = 4\pi R_\te{moon}^2/12\times 2^{n_{\te{side}}}$, the area of a HEALPix pixel.
+The time it takes a ray to cross a HEALPix pixel can be estimated $t_\te{crossing}^2 = A_\te{pix}/\pi v_p^2$.
+Rays that contact a pixel within $t_\te{crossing}$ of one another are considered to add constructively.
+Since the integral in section IV is unreasonable to do for more than one ray, we make use of Minkowski's inequality and obtain an upper bound on displacement by simply adding the displacements from each ray.
+We suppose that each ray distributes its energy evenly over the area of the HEALPix pixel, and thus set $A = A_\te{pix}$.
+This is a good approximation when $N$ is the same as the number of HEALPix pixels.
+
+Using (29) we compute an upper bound for the displacement within a given HEALPix pixel, and compare that to the sensitivity of the lunar seismometers.
+If the displacement is less than the sensitivity then the pixel is marked undetectable and is otherwise marked detectable.
+The number of detectable pixels is divided by the total number of pixels to obtain the fraction $\scr F_D$ of the lunar surface which could plausibly register a signal.
+
+This procedure is repeated for 17 values of $D$ spaced evenly by $100\,\te{km}$. The average fraction of detectable surface area is then
 \begin{align}
-\abs{u(\vec x,t)}\leq \f{3}{4}\sqrt{\f2\pi\f{\kappa \epsilon^2 \ell}{\rho p_0^2 v_p^2 A  }}\sqrt{\f{\te{Ref}}{\te{Att}}}\te{Erf}\ps{\sqrt{\f{\te{Att}\,k}{2}}}\,.
+\scr F = \sum_D\f{\scr F_D D}{D}\,.
 \end{align}
-\section{Simulation}
+If there are $n$ lunar seismometers, suppose each occupies its own HEALPix pixel.
+Then $\scr N = n/12\times 2^{n_\te{side}}$ is the fraction of the moon which could potentially measure a signal.
+The likelihood of detection is then
+\begin{align}
+\scr P = 1-(1-\scr F)(1-\scr N)\,.
+\end{align}
+If $\scr M$ Macros impact the moon, the likelihood of any of them being detected is
+\begin{align}
+{\cal P} = 1-(1-\scr P)^\scr{M} = 1-\ps{(1-\scr F)(1-\scr N)}^\scr M\,.
+\end{align}
 
+If the energy of a ray from every point along the line hitting a single pixel (with no reflection, refraction, or attenuation) is less than the displacement threshold, there is no chance of detection and no need to run the simulation.
+(If two rays from the same point on the line source hit the same pixel as $n_\te{side}\to\infty$, then they must be the same ray).
+\begin{align}
+u\leq\sqrt{\f{\Xi E}{\pi^2\rho k v_p^2 R_\te{Moon}^2}}
+\end{align}
+This is independent of the choice of partition. For the triangle wave, we need not test $\sigma_X\leq10^{-9}\te{m}^2$ (I WILL VERIFY THIS).
 \section{Results}

### 2016-08-20 Ray-Tracing/Ray_Tracing_Moon.m

@@ -53,7 +53,7 @@ rhoBoundaries = [   3.406       ,   3.406               ;...
                     %THE DENSITY OF THE MEDIA AT THEIR DISCONTINUOUS
                     %BOUNDARIES - THE LEFT ENTRY IN EACH ROW CORRESPONDS TO
                     %THE INNER DENSITY AND THE RIGHT CORRESPONDS TO THE
-                    %OUTER DENSITY kg/km^3
+                    %OUTER DENSITY kg/m^3
 %}
 
 c = 3.446 * 10^3; %THE CONSTANTS WHICH DESCRIBE THE DENSITY FIELD c - d(r - e)^2 kg/m^3
@@ -396,15 +396,6 @@ Zrote = sin(OutRay).*Y + cos(OutRay).*Z;
 Xfinal = cos(OutPla).*Xrote - sin(OutPla).*Yrote;
 Yfinal = sin(OutPla).*Xrote + cos(OutPla).*Yrote;
 Zfinal = Zrote;
-%{
-figure
-t0 = 5*10^2;
-tf = 6*10^3;
-scatter3(Xfinal(t0 < OutTim & OutTim < tf),Yfinal(t0 < OutTim & OutTim < tf),Zfinal(t0 < OutTim & OutTim < tf),'.')
-%}
-%%{
-%figure
-%scatter3(Xfinal,Yfinal,Zfinal,1,OutEnergy)
-output = cat(2,Xfinal,Yfinal,Zfinal,OutTim,InitialEnergy,REF,ATT); %(the 10^(6)) is to convert to J from kg km^2/s^2
+
+output = cat(2,Xfinal,Yfinal,Zfinal,OutTim,InitialEnergy,REF,ATT);
 save Points.mat output
-%}

### 2016-08-21 Draft.tex
Update

@@
 \end{align}
-where $r$ is the radial coordinate of the ray, $\theta$ is the polar angle of the ray measured from the center of the body, and $p_\te{ray}$ is the ray constant, whose value is fixed along a ray trajectory.
+where $r$ is the radial coordinate of the ray, $\theta$ is the polar angle of the ray measured from the center of the body, and $p_\te{ray}$ is the ray parameter, whose value is fixed along a ray trajectory.
 These equations can be integrated.
@@
 Then $\scr N = n/12\times 2^{n_\te{side}}$ is the fraction of the moon which could potentially measure a signal.
-The likelihood of detection is then
-\begin{align}
-\scr P = 1-(1-\scr F)(1-\scr N)\,.
-\end{align}
 If $\scr M$ Macros impact the moon, the likelihood of any of them being detected is
 \begin{align}
-{\cal P} = 1-(1-\scr P)^\scr{M} = 1-\ps{(1-\scr F)(1-\scr N)}^\scr M\,.
+\scr P = 1-\ps{(1-\scr F)(1-\scr N)}^\scr M\,.
 \end{align}

### 2016-08-21 Ray-Tracing/Ray_Tracing_Moon.m

@@ -381,7 +381,7 @@ for i = 1 : ACO
     
 end
 REF = OutArrayAmp(OutArrayTime > 0 & OutArrayAmp > 0);
-InitialEnergy = (RayArrayDensity(OutArrayTime > 0 & OutArrayAmp > 0)).*sigmaX.*(vX.^2).*L./(M*N);
+Source = (RayArrayDensity(OutArrayTime > 0 & OutArrayAmp > 0)).*L/(M*N);
 ATT= OutArraySup(OutArrayTime > 0 & OutArrayAmp > 0);
 OutTim = OutArrayTime(OutArrayTime > 0 & OutArrayAmp > 0);
 
@@ -397,5 +397,5 @@ Xfinal = cos(OutPla).*Xrote - sin(OutPla).*Yrote;
 Yfinal = sin(OutPla).*Xrote + cos(OutPla).*Yrote;
 Zfinal = Zrote;
 
-output = cat(2,Xfinal,Yfinal,Zfinal,OutTim,InitialEnergy,REF,ATT);
+output = cat(2,Xfinal,Yfinal,Zfinal,OutTim,Source,REF,ATT);
 save Points.mat output

### 2016-08-24 HPC/Ray-Tracing/RayTracingMoon.m
Update

@@ -1,0 +1,335 @@
+clear
+
+format long
+
+
+
+%INPUTS
+
+M = 1; %NUMBER OF POINTS ON THE LINE
+N = 5000; %NUMBER OF RAYS FROM EACH POINT
+
+a = [11.2633,10.6835,15.4938].^(1/2); %THESE ARE THE CONSTANT TERMS IN THE PARABOLIC VELOCITY FIELD STRUCTURE, THE FIRST ENTRY CORRESPONDING TO THE CORE
+b = [1.55946*10^(-7),2.11853*10^(-7),1.40336*10^(-7)].^(1/2); %THESE ARE THE COEFFICIENTS OF THE QUADRATIC TERM IN THE VELOCITY FIELD
+
+D = 6370; %THE DISTANCE OF CLOSEST APPROACH TO THE CENTER
+Radii = [0,1221,3480,6371]; %NOTE THAT WE MUST TAKE 0 AS A LAYER FOR TECHNICAL PURPOSES
+ACO = 8; %IT TAKES 5 ITERATIONS FOR A RAY TO PASS ENTIRELY THROUGH THE EARTH
+
+%Q = ; %THE QUALITY FACTOR AS A FUNCTION OF FREQUENCY, TIME, AND SO ON... TBD
+%A = ; %THE AMPLITUDE OF THE WAVE AS A FUNCTION OF FREQUENCY
+
+rhoBoundaries = [ 12.76, 12.17; 9.90, 5.57; 1.02, 1.25*(10^(-3))].*(10^12); %THE DENSITY OF THE MEDIA AT THEIR DISCONTINUOUS BOUNDARIES - THE LEFT ENTRY IN EACH ROW CORRESPONDS TO THE INNER DENSITY AND THE RIGHT CORRESPONDS TO THE OUTER DENSITY
+
+%END INPUTS
+
+
+
+
+
+
+
+
+
+Layers = length(Radii);
+
+vBoundaries = zeros(Layers-2,2); %v(:,1) corresponds to the inner velocity on the :th layer, and v(:,2) corresponds to the outer velocity on the :th layer
+ReflectionCoefficients = zeros(Layers - 1,2); %these correspond to 4 functions of the angle of incidence
+TransmissionCoefficients = zeros(Layers - 1,2); %these correspond to 4 functions of the angle of incidence
+for i = 1 : Layers - 2
[…]

### 2016-08-24 HPC/Ray-Tracing/Ray_Tracing_Generalized.m

@@ -1,0 +1,197 @@
+clear
+
+format long
+
+a = [11.2633,10.6835,15.4938].^(1/2); %first entry corresponds to the core
+b = [1.55946*10^(-7),2.11853*10^(-7),1.40336*10^(-7)].^(1/2); %first entry corresponds to the core
+WeaknessOfNeglectedRays = 10^(-1); %input('What fraction of the initial ray energy must a ray contain to not be thrown out? ');
+
+D = 0;
+Radii = [0,1221,3480,6371];
+AbsoluteCutoff = 4;
+
+Layers = length(Radii);
+
+vBoundaries = zeros(Layers-2,2); %v(:,1) corresponds to the inner velocity on the :th layer, and v(:,2) corresponds to the outer velocity on the :th layer
+ReflectionCoefficients = zeros(Layers - 1,2); %these correspond to 4 functions of the angle of incidence
+TransmissionCoefficients = zeros(Layers - 1,2); %these correspond to 4 functions of the angle of incidence
+for i = 1 : Layers - 2
+    vBoundaries(i,1) = (a(i)^2)-(b(i)^2)*(Radii(i+1))^2; %inner
+    vBoundaries(i,2) = (a(i+1)^2)-(b(i+1)^2)*(Radii(i+1))^2; %outer
+end
+
+vBoundaries(Layers - 1,1) = (a(Layers - 1)^2)-(b(Layers - 1)^2)*(Radii(Layers))^2;
+vBoundaries(Layers - 1,2) = 0.34042; %Air
+
+rhoBoundaries = [];
+
+%GENERATING THE RANDOM POINTS ON A SPHERE
+
+M = 1;
+N = 10000;
+Th = rand(M,N).*(2*pi);
+Ph = asin((rand(M,N).*2.-1));
+I = 1:M;
+J = 1:N;
+RandSph = zeros(M,N,3);
+RandSph(:,:,1) = Th(:,:);
+RandSph(:,:,2) = Ph(:,:);
+RandSph(I,J,3) = 1;
+[RandX,RandY,RandZ] = sph2cart(RandSph(I,J,1),RandSph(I,J,2),RandSph(I,J,3));
+
+%PREPARING THE INITIAL CONDITIONS FOR THE RAYS
+
+L = 2*((((Radii(Layers))^2)-((D)^2))^0.5);
+l = (I-((M+1)/2)).*(L/(M+1));
+Alpha = atan2(D,transpose(l));
+x0 = transpose(repmat(X0(L,(M+1),I,D), [N,1]));
[…]

### 2016-08-24 HPC/Ray-Tracing/Ray_Tracing_Moon.m

@@ -1,0 +1,404 @@
+clear
+
+format long
+
+
+
+%INPUTS
+D = 1000; %THE DISTANCE OF CLOSEST APPROACH TO THE CENTER km
+ACO = 9; %IT TAKES 16 ITERATIONS FOR A RAY TO PASS ENTIRELY THROUGH THE MOON
+
+vX = 2.5 * 10^5; %m/s
+sigmaX = (10^(-7)) * (10^(-4));% m^2
+fhigh = 20;%1/s %HIGHEST DETECTABLE FREQUENCY
+TotalDensityAverage = 3.3*10^3; %THE AVERAGE DENSITY THROUGHOUT THE WHOLE MOON
+pbar = 10^8;%HOOKIAN PRESSURE kg/(m*s^2)
+vs = 4.4 * 10^3;%AVERAGE SHEAR WAVE VELOCITY THROUGHOUT THE WHOLE MOON m/s
+vp = 7.6 * 10^3;%AVERAGE PRESSURE WAVE VELOCITY THROUGHOUT THE WHOLE MOON m/s
+
+M = 10; %NUMBER OF POINTS ON THE LINE
+N = 192; %NUMBER OF RAYS FROM EACH POINT
+%{
+%APPROXIMATION TO OUTER LAYERS
+a = [8.26955,8.26955,8.26955,8.26955,145.46].^(1/2);
+b = [2.47697*10^(-7),2.47697*10^(-7),2.47697*10^(-7),2.47697*10^(-7),0.0000478823].^(1/2);
+Radii = [0,961.7,1231.7,1461.7,1671.7,1737.1];
+AverageV = [8.15502,7.96714,7.81709,7.65888,6.19979];
+Q = [675,1125,3375,9000,6750];
+rhoBoundaries = [   3.406       ,   3.406               ;...
+                    3.379       ,   3.379               ;...
+                    3.350       ,   3.350               ;...
+                    3.318       ,   3.318               ;...
+                    2.762       ,   0.000               ].*(10^15);
+%}
+%%{
+%VPREMOON MODEL
+a = ([8.26955,8.26955,8.26955,8.26955,8.26955,5.5,3.2,1.0].*10^3).^(1/2); %THESE ARE THE CONSTANT TERMS IN THE PARABOLIC VELOCITY FIELD STRUCTURE, THE FIRST ENTRY CORRESPONDING TO THE CORE km/s
[…]

### 2016-08-24 HPC/Ray-Tracing/Ray_Tracing_Moon_1.m

@@ -1,0 +1,411 @@
+clear
+
+format long
+
+
+
+%INPUTS
+D = 100*10^3; %THE DISTANCE OF CLOSEST APPROACH TO THE CENTER m
+ACO = 9; %IT TAKES 16 ITERATIONS FOR A RAY TO PASS ENTIRELY THROUGH THE MOON
+
+vX = 2.5 * 10^5; %m/s
+sigmaX = (10^(-7)) * (10^(-4));% m^2
+fhigh = 20;%1/s %HIGHEST DETECTABLE FREQUENCY
+TotalDensityAverage = 3.3*10^3; %THE AVERAGE DENSITY THROUGHOUT THE WHOLE MOON
+pbar = 10^8;%HOOKIAN PRESSURE kg/(m*s^2)
+vs = 4.4 * 10^3;%AVERAGE SHEAR WAVE VELOCITY THROUGHOUT THE WHOLE MOON m/s
+vp = 7.6 * 10^3;%AVERAGE PRESSURE WAVE VELOCITY THROUGHOUT THE WHOLE MOON m/s
+
+M = 200; %NUMBER OF POINTS ON THE LINE
+N = 192; %NUMBER OF RAYS FROM EACH POINT
+%{
+%APPROXIMATION TO OUTER LAYERS
+a = [8.26955,8.26955,8.26955,8.26955,145.46].^(1/2);
+b = [2.47697*10^(-7),2.47697*10^(-7),2.47697*10^(-7),2.47697*10^(-7),0.0000478823].^(1/2);
+Radii = [0,961.7,1231.7,1461.7,1671.7,1737.1];
+AverageV = [8.15502,7.96714,7.81709,7.65888,6.19979];
+Q = [675,1125,3375,9000,6750];
+rhoBoundaries = [   3.406       ,   3.406               ;...
+                    3.379       ,   3.379               ;...
+                    3.350       ,   3.350               ;...
+                    3.318       ,   3.318               ;...
+                    2.762       ,   0.000               ].*(10^15);
+%}
+%%{
+%VPREMOON MODEL
[…]

### 2016-08-24 HPC/Ray-Tracing/Ray_Tracing_Moon_10.m

@@ -1,0 +1,411 @@
+clear
+
+format long
+
+
+
+%INPUTS
+D = 1000*10^3; %THE DISTANCE OF CLOSEST APPROACH TO THE CENTER m
+ACO = 9; %IT TAKES 16 ITERATIONS FOR A RAY TO PASS ENTIRELY THROUGH THE MOON
+
+vX = 2.5 * 10^5; %m/s
+sigmaX = (10^(-7)) * (10^(-4));% m^2
+fhigh = 20;%1/s %HIGHEST DETECTABLE FREQUENCY
+TotalDensityAverage = 3.3*10^3; %THE AVERAGE DENSITY THROUGHOUT THE WHOLE MOON
+pbar = 10^8;%HOOKIAN PRESSURE kg/(m*s^2)
+vs = 4.4 * 10^3;%AVERAGE SHEAR WAVE VELOCITY THROUGHOUT THE WHOLE MOON m/s
+vp = 7.6 * 10^3;%AVERAGE PRESSURE WAVE VELOCITY THROUGHOUT THE WHOLE MOON m/s
+
+M = 200; %NUMBER OF POINTS ON THE LINE
+N = 192; %NUMBER OF RAYS FROM EACH POINT
+%{
+%APPROXIMATION TO OUTER LAYERS
+a = [8.26955,8.26955,8.26955,8.26955,145.46].^(1/2);
+b = [2.47697*10^(-7),2.47697*10^(-7),2.47697*10^(-7),2.47697*10^(-7),0.0000478823].^(1/2);
+Radii = [0,961.7,1231.7,1461.7,1671.7,1737.1];
+AverageV = [8.15502,7.96714,7.81709,7.65888,6.19979];
+Q = [675,1125,3375,9000,6750];
+rhoBoundaries = [   3.406       ,   3.406               ;...
+                    3.379       ,   3.379               ;...
+                    3.350       ,   3.350               ;...
+                    3.318       ,   3.318               ;...
+                    2.762       ,   0.000               ].*(10^15);
+%}
+%%{
+%VPREMOON MODEL
[…]

### 2016-08-24 HPC/Ray-Tracing/Ray_Tracing_Moon_12.m

@@ -1,0 +1,411 @@
+clear
+
+format long
+
+
+
+%INPUTS
+D = 1200*10^3; %THE DISTANCE OF CLOSEST APPROACH TO THE CENTER m
+ACO = 9; %IT TAKES 16 ITERATIONS FOR A RAY TO PASS ENTIRELY THROUGH THE MOON
+
+vX = 2.5 * 10^5; %m/s
+sigmaX = (10^(-7)) * (10^(-4));% m^2
+fhigh = 20;%1/s %HIGHEST DETECTABLE FREQUENCY
+TotalDensityAverage = 3.3*10^3; %THE AVERAGE DENSITY THROUGHOUT THE WHOLE MOON
+pbar = 10^8;%HOOKIAN PRESSURE kg/(m*s^2)
+vs = 4.4 * 10^3;%AVERAGE SHEAR WAVE VELOCITY THROUGHOUT THE WHOLE MOON m/s
+vp = 7.6 * 10^3;%AVERAGE PRESSURE WAVE VELOCITY THROUGHOUT THE WHOLE MOON m/s
+
+M = 200; %NUMBER OF POINTS ON THE LINE
+N = 192; %NUMBER OF RAYS FROM EACH POINT
+%{
+%APPROXIMATION TO OUTER LAYERS
+a = [8.26955,8.26955,8.26955,8.26955,145.46].^(1/2);
+b = [2.47697*10^(-7),2.47697*10^(-7),2.47697*10^(-7),2.47697*10^(-7),0.0000478823].^(1/2);
+Radii = [0,961.7,1231.7,1461.7,1671.7,1737.1];
+AverageV = [8.15502,7.96714,7.81709,7.65888,6.19979];
+Q = [675,1125,3375,9000,6750];
+rhoBoundaries = [   3.406       ,   3.406               ;...
+                    3.379       ,   3.379               ;...
+                    3.350       ,   3.350               ;...
+                    3.318       ,   3.318               ;...
+                    2.762       ,   0.000               ].*(10^15);
+%}
+%%{
+%VPREMOON MODEL
[…]

### 2016-08-24 HPC/Ray-Tracing/Ray_Tracing_Moon_13.m

@@ -1,0 +1,411 @@
+clear
+
+format long
+
+
+
+%INPUTS
+D = 1300*10^3; %THE DISTANCE OF CLOSEST APPROACH TO THE CENTER m
+ACO = 9; %IT TAKES 16 ITERATIONS FOR A RAY TO PASS ENTIRELY THROUGH THE MOON
+
+vX = 2.5 * 10^5; %m/s
+sigmaX = (10^(-7)) * (10^(-4));% m^2
+fhigh = 20;%1/s %HIGHEST DETECTABLE FREQUENCY
+TotalDensityAverage = 3.3*10^3; %THE AVERAGE DENSITY THROUGHOUT THE WHOLE MOON
+pbar = 10^8;%HOOKIAN PRESSURE kg/(m*s^2)
+vs = 4.4 * 10^3;%AVERAGE SHEAR WAVE VELOCITY THROUGHOUT THE WHOLE MOON m/s
+vp = 7.6 * 10^3;%AVERAGE PRESSURE WAVE VELOCITY THROUGHOUT THE WHOLE MOON m/s
+
+M = 200; %NUMBER OF POINTS ON THE LINE
+N = 192; %NUMBER OF RAYS FROM EACH POINT
+%{
+%APPROXIMATION TO OUTER LAYERS
+a = [8.26955,8.26955,8.26955,8.26955,145.46].^(1/2);
+b = [2.47697*10^(-7),2.47697*10^(-7),2.47697*10^(-7),2.47697*10^(-7),0.0000478823].^(1/2);
+Radii = [0,961.7,1231.7,1461.7,1671.7,1737.1];
+AverageV = [8.15502,7.96714,7.81709,7.65888,6.19979];
+Q = [675,1125,3375,9000,6750];
+rhoBoundaries = [   3.406       ,   3.406               ;...
+                    3.379       ,   3.379               ;...
+                    3.350       ,   3.350               ;...
+                    3.318       ,   3.318               ;...
+                    2.762       ,   0.000               ].*(10^15);
+%}
+%%{
+%VPREMOON MODEL
[…]

### 2016-08-24 HPC/Ray-Tracing/Ray_Tracing_Moon_15.m

@@ -1,0 +1,411 @@
+clear
+
+format long
+
+
+
+%INPUTS
+D = 1500*10^3; %THE DISTANCE OF CLOSEST APPROACH TO THE CENTER m
+ACO = 9; %IT TAKES 16 ITERATIONS FOR A RAY TO PASS ENTIRELY THROUGH THE MOON
+
+vX = 2.5 * 10^5; %m/s
+sigmaX = (10^(-7)) * (10^(-4));% m^2
+fhigh = 20;%1/s %HIGHEST DETECTABLE FREQUENCY
+TotalDensityAverage = 3.3*10^3; %THE AVERAGE DENSITY THROUGHOUT THE WHOLE MOON
+pbar = 10^8;%HOOKIAN PRESSURE kg/(m*s^2)
+vs = 4.4 * 10^3;%AVERAGE SHEAR WAVE VELOCITY THROUGHOUT THE WHOLE MOON m/s
+vp = 7.6 * 10^3;%AVERAGE PRESSURE WAVE VELOCITY THROUGHOUT THE WHOLE MOON m/s
+
+M = 200; %NUMBER OF POINTS ON THE LINE
+N = 192; %NUMBER OF RAYS FROM EACH POINT
+%{
+%APPROXIMATION TO OUTER LAYERS
+a = [8.26955,8.26955,8.26955,8.26955,145.46].^(1/2);
+b = [2.47697*10^(-7),2.47697*10^(-7),2.47697*10^(-7),2.47697*10^(-7),0.0000478823].^(1/2);
+Radii = [0,961.7,1231.7,1461.7,1671.7,1737.1];
+AverageV = [8.15502,7.96714,7.81709,7.65888,6.19979];
+Q = [675,1125,3375,9000,6750];
+rhoBoundaries = [   3.406       ,   3.406               ;...
+                    3.379       ,   3.379               ;...
+                    3.350       ,   3.350               ;...
+                    3.318       ,   3.318               ;...
+                    2.762       ,   0.000               ].*(10^15);
+%}
+%%{
+%VPREMOON MODEL
[…]

### 2016-08-24 HPC/Ray-Tracing/Ray_Tracing_Moon_17.m

@@ -1,0 +1,411 @@
+clear
+
+format long
+
+
+
+%INPUTS
+D = 1700*10^3; %THE DISTANCE OF CLOSEST APPROACH TO THE CENTER m
+ACO = 9; %IT TAKES 16 ITERATIONS FOR A RAY TO PASS ENTIRELY THROUGH THE MOON
+
+vX = 2.5 * 10^5; %m/s
+sigmaX = (10^(-7)) * (10^(-4));% m^2
+fhigh = 20;%1/s %HIGHEST DETECTABLE FREQUENCY
+TotalDensityAverage = 3.3*10^3; %THE AVERAGE DENSITY THROUGHOUT THE WHOLE MOON
+pbar = 10^8;%HOOKIAN PRESSURE kg/(m*s^2)
+vs = 4.4 * 10^3;%AVERAGE SHEAR WAVE VELOCITY THROUGHOUT THE WHOLE MOON m/s
+vp = 7.6 * 10^3;%AVERAGE PRESSURE WAVE VELOCITY THROUGHOUT THE WHOLE MOON m/s
+
+M = 200; %NUMBER OF POINTS ON THE LINE
+N = 192; %NUMBER OF RAYS FROM EACH POINT
+%{
+%APPROXIMATION TO OUTER LAYERS
+a = [8.26955,8.26955,8.26955,8.26955,145.46].^(1/2);
+b = [2.47697*10^(-7),2.47697*10^(-7),2.47697*10^(-7),2.47697*10^(-7),0.0000478823].^(1/2);
+Radii = [0,961.7,1231.7,1461.7,1671.7,1737.1];
+AverageV = [8.15502,7.96714,7.81709,7.65888,6.19979];
+Q = [675,1125,3375,9000,6750];
+rhoBoundaries = [   3.406       ,   3.406               ;...
+                    3.379       ,   3.379               ;...
+                    3.350       ,   3.350               ;...
+                    3.318       ,   3.318               ;...
+                    2.762       ,   0.000               ].*(10^15);
+%}
+%%{
+%VPREMOON MODEL
[…]

### 2016-08-24 HPC/Ray-Tracing/Ray_Tracing_Moon_3.m

@@ -1,0 +1,411 @@
+clear
+
+format long
+
+
+
+%INPUTS
+D = 300*10^3; %THE DISTANCE OF CLOSEST APPROACH TO THE CENTER m
+ACO = 9; %IT TAKES 16 ITERATIONS FOR A RAY TO PASS ENTIRELY THROUGH THE MOON
+
+vX = 2.5 * 10^5; %m/s
+sigmaX = (10^(-7)) * (10^(-4));% m^2
+fhigh = 20;%1/s %HIGHEST DETECTABLE FREQUENCY
+TotalDensityAverage = 3.3*10^3; %THE AVERAGE DENSITY THROUGHOUT THE WHOLE MOON
+pbar = 10^8;%HOOKIAN PRESSURE kg/(m*s^2)
+vs = 4.4 * 10^3;%AVERAGE SHEAR WAVE VELOCITY THROUGHOUT THE WHOLE MOON m/s
+vp = 7.6 * 10^3;%AVERAGE PRESSURE WAVE VELOCITY THROUGHOUT THE WHOLE MOON m/s
+
+M = 200; %NUMBER OF POINTS ON THE LINE
+N = 192; %NUMBER OF RAYS FROM EACH POINT
+%{
+%APPROXIMATION TO OUTER LAYERS
+a = [8.26955,8.26955,8.26955,8.26955,145.46].^(1/2);
+b = [2.47697*10^(-7),2.47697*10^(-7),2.47697*10^(-7),2.47697*10^(-7),0.0000478823].^(1/2);
+Radii = [0,961.7,1231.7,1461.7,1671.7,1737.1];
+AverageV = [8.15502,7.96714,7.81709,7.65888,6.19979];
+Q = [675,1125,3375,9000,6750];
+rhoBoundaries = [   3.406       ,   3.406               ;...
+                    3.379       ,   3.379               ;...
+                    3.350       ,   3.350               ;...
+                    3.318       ,   3.318               ;...
+                    2.762       ,   0.000               ].*(10^15);
+%}
+%%{
+%VPREMOON MODEL
[…]

### 2016-08-24 HPC/Ray-Tracing/Ray_Tracing_Moon_8.m

@@ -1,0 +1,411 @@
+clear
+
+format long
+
+
+
+%INPUTS
+D = 800*10^3; %THE DISTANCE OF CLOSEST APPROACH TO THE CENTER m
+ACO = 9; %IT TAKES 16 ITERATIONS FOR A RAY TO PASS ENTIRELY THROUGH THE MOON
+
+vX = 2.5 * 10^5; %m/s
+sigmaX = (10^(-7)) * (10^(-4));% m^2
+fhigh = 20;%1/s %HIGHEST DETECTABLE FREQUENCY
+TotalDensityAverage = 3.3*10^3; %THE AVERAGE DENSITY THROUGHOUT THE WHOLE MOON
+pbar = 10^8;%HOOKIAN PRESSURE kg/(m*s^2)
+vs = 4.4 * 10^3;%AVERAGE SHEAR WAVE VELOCITY THROUGHOUT THE WHOLE MOON m/s
+vp = 7.6 * 10^3;%AVERAGE PRESSURE WAVE VELOCITY THROUGHOUT THE WHOLE MOON m/s
+
+M = 200; %NUMBER OF POINTS ON THE LINE
+N = 192; %NUMBER OF RAYS FROM EACH POINT
+%{
+%APPROXIMATION TO OUTER LAYERS
+a = [8.26955,8.26955,8.26955,8.26955,145.46].^(1/2);
+b = [2.47697*10^(-7),2.47697*10^(-7),2.47697*10^(-7),2.47697*10^(-7),0.0000478823].^(1/2);
+Radii = [0,961.7,1231.7,1461.7,1671.7,1737.1];
+AverageV = [8.15502,7.96714,7.81709,7.65888,6.19979];
+Q = [675,1125,3375,9000,6750];
+rhoBoundaries = [   3.406       ,   3.406               ;...
+                    3.379       ,   3.379               ;...
+                    3.350       ,   3.350               ;...
+                    3.318       ,   3.318               ;...
+                    2.762       ,   0.000               ].*(10^15);
+%}
+%%{
+%VPREMOON MODEL
[…]

### 2016-08-24 HPC/Ray-Tracing/Ray_Tracing_Moon_9.m

@@ -1,0 +1,411 @@
+clear
+
+format long
+
+
+
+%INPUTS
+D = 900*10^3; %THE DISTANCE OF CLOSEST APPROACH TO THE CENTER m
+ACO = 9; %IT TAKES 16 ITERATIONS FOR A RAY TO PASS ENTIRELY THROUGH THE MOON
+
+vX = 2.5 * 10^5; %m/s
+sigmaX = (10^(-7)) * (10^(-4));% m^2
+fhigh = 20;%1/s %HIGHEST DETECTABLE FREQUENCY
+TotalDensityAverage = 3.3*10^3; %THE AVERAGE DENSITY THROUGHOUT THE WHOLE MOON
+pbar = 10^8;%HOOKIAN PRESSURE kg/(m*s^2)
+vs = 4.4 * 10^3;%AVERAGE SHEAR WAVE VELOCITY THROUGHOUT THE WHOLE MOON m/s
+vp = 7.6 * 10^3;%AVERAGE PRESSURE WAVE VELOCITY THROUGHOUT THE WHOLE MOON m/s
+
+M = 200; %NUMBER OF POINTS ON THE LINE
+N = 192; %NUMBER OF RAYS FROM EACH POINT
+%{
+%APPROXIMATION TO OUTER LAYERS
+a = [8.26955,8.26955,8.26955,8.26955,145.46].^(1/2);
+b = [2.47697*10^(-7),2.47697*10^(-7),2.47697*10^(-7),2.47697*10^(-7),0.0000478823].^(1/2);
+Radii = [0,961.7,1231.7,1461.7,1671.7,1737.1];
+AverageV = [8.15502,7.96714,7.81709,7.65888,6.19979];
+Q = [675,1125,3375,9000,6750];
+rhoBoundaries = [   3.406       ,   3.406               ;...
+                    3.379       ,   3.379               ;...
+                    3.350       ,   3.350               ;...
+                    3.318       ,   3.318               ;...
+                    2.762       ,   0.000               ].*(10^15);
+%}
+%%{
+%VPREMOON MODEL
[…]

### 2016-08-24 HPC/Ray-Tracing/Ray_Tracing_Really_Generalized.m

@@ -1,0 +1,65 @@
+clear
+
+%GENERATING THE RANDOM POINTS ON A SPHERE
+
+M = 7;
+N = 5;
+Th = rand(M,N).*(2*pi);
+Ph = asin((rand(M,N).*2.-1));
+I = 1:M;
+J = 1:N;
+RandSph = zeros(M,N,3);
+RandSph(:,:,1) = Th(:,:);
+RandSph(:,:,2) = Ph(:,:);
+RandSph(I,J,3) = 1;
+[RandX,RandY,RandZ] = sph2cart(RandSph(I,J,1),RandSph(I,J,2),RandSph(I,J,3));
+
+%PREPARING THE INITIAL CONDITIONS FOR THE RAYS
+
+D = 2000;
+Radii = [0,1221,3480,6371];
+AbsoluteCutoff = 5;
+
+Layers = length(Radii);
+
+L = 2*((((Radii(Layers))^2)-((D)^2))^0.5);
+l = (I-((M+1)/2)).*(L/(M+1));
+RayArray = zeros(M,N,2^(AbsoluteCutoff - 1),3); % = (point M, ray N, daughter P, (x,AlphaRay,Amplitude))
+Alpha = atan2(D,transpose(l));
+for i = 1 : M
+    RotMatrixAlpha = [cos(Alpha(i)),sin(Alpha(i)),0;-sin(Alpha(i)),cos(Alpha(i)),0;0,0,1];
+    for j = 1 : N
+        RotRand = RotMatrixAlpha*[RandX(i,j)+l(i);RandY(i,j)+D;RandZ(i,j)];
+        Beta(i,j) = atan2(RotRand(3),RotRand(2));
+        RotMatrixBeta = [1,0,0;0,cos(Beta(i,j)),sin(Beta(i,j));0,-sin(Beta(i,j)),cos(Beta(i,j))];
+        Vec = RotMatrixBeta*RotRand;
+        AlphaRay(i,j) = atan2(Vec(2),Vec(1));
+    end
+end
+x0 = transpose(repmat(X0(L,(M+1),I,D), [N,1]));
+RayArray(:,:,1,1) = x0(:,:);
+RayArray(:,:,1,2) = AlphaRay(:,:);
+RayArray(:,:,1,3) = 1;
+
+%PROPAGATION
+
+LeftRays = zeros(M,N,2^(AbsoluteCutoff - 1),1);
[…]

### 2016-08-24 HPC/Ray-Tracing/Test_With_Earth_Values.m

@@ -1,0 +1,360 @@
+clear
+
+format long
+
+
+
+%INPUTS
+
+M = 1; %NUMBER OF POINTS ON THE LINE
+N = 5000; %NUMBER OF RAYS FROM EACH POINT
+
+a = [11.2633,10.6835,15.4938].^(1/2); %THESE ARE THE CONSTANT TERMS IN THE PARABOLIC VELOCITY FIELD STRUCTURE, THE FIRST ENTRY CORRESPONDING TO THE CORE
+b = [1.55946*10^(-7),2.11853*10^(-7),1.40336*10^(-7)].^(1/2); %THESE ARE THE COEFFICIENTS OF THE QUADRATIC TERM IN THE VELOCITY FIELD
+
+D = 6370; %THE DISTANCE OF CLOSEST APPROACH TO THE CENTER
+Radii = [0,1221,3480,6371]; %NOTE THAT WE MUST TAKE 0 AS A LAYER FOR TECHNICAL PURPOSES
+ACO = 5; %IT TAKES 5 ITERATIONS FOR A RAY TO PASS ENTIRELY THROUGH THE EARTH
+
+%Q = ; %THE QUALITY FACTOR AS A FUNCTION OF FREQUENCY, TIME, AND SO ON... TBD
+%A = ; %THE AMPLITUDE OF THE WAVE AS A FUNCTION OF FREQUENCY
+
+rhoBoundaries = [ 12.76, 12.17; 9.90, 5.57; 1.02, 1.25*(10^(-3))].*(10^12); %THE DENSITY OF THE MEDIA AT THEIR DISCONTINUOUS BOUNDARIES - THE LEFT ENTRY IN EACH ROW CORRESPONDS TO THE INNER DENSITY AND THE RIGHT CORRESPONDS TO THE OUTER DENSITY
+
+%END INPUTS
+
+
+
+
+
+
+
+
+
+Layers = length(Radii);
+
+vBoundaries = zeros(Layers-2,2); %v(:,1) corresponds to the inner velocity on the :th layer, and v(:,2) corresponds to the outer velocity on the :th layer
+ReflectionCoefficients = zeros(Layers - 1,2); %these correspond to 4 functions of the angle of incidence
+TransmissionCoefficients = zeros(Layers - 1,2); %these correspond to 4 functions of the angle of incidence
+for i = 1 : Layers - 2
[…]

### 2016-08-24 HPC/Ray-Tracing/X0.m

@@ -1,0 +1,4 @@
+%This function tells us the distance from the origin of the point source
+function output=X0(L,N,n,D)
+    output = (((L/N).*(n-(N/2))).^2+D^2).^(0.5);
+end

### 2016-08-24 Ray-Tracing/Amplitude.m

@@ -1,7 +1,0 @@
-function A = Amplitude( k )
-%UNTITLED4 Summary of this function goes here
-%   Detailed explanation goes here
-
-
-end
-

### 2016-08-24 Ray-Tracing/Ray_Tracing.m

@@ -1,168 +1,0 @@
-clc
-clear
-format long
-%EvenlyDistributedPoints=[];
-%EvenlyDistributedPoints=load('130_Points_On_A_Sphere.txt');
-counter=1;
-macrocounter=1;
-%LengthofPointmatrix=length(EvenlyDistributedPoints);
-%RayDirectionVectors=zeros(LengthofPointmatrix/3,3);
-SecondPhase=[];
-%for i = 1 : LengthofPointmatrix %This loop unpacks the direction vectors from a text file 'M_PointsOnASphere.txt'
-%    RayDirectionVectors(macrocounter,counter) = EvenlyDistributedPoints(i);
-%    if counter == 3
-%        counter = 1;
-%        macrocounter = macrocounter + 1;
-%    else
-%        counter = counter + 1;
-%    end
-%end
-RE = 6371; %input('What is the radius of the earth? (meters) ');
-D = 3000; %input('What is the distance of closest approach of the macro to the center? (meters) ');
-N = 100; %input('How many points along this line should we consider? ') + 1;
-M = 100; %input('How many rays will each point emit? ');
-Rmantle = 3480; %input('What is the radius of the mantle? (meters) ');
-ac = 11.1502; %sqrt(input('Inside the core, assuming that the velocity field has the form a^2-b^2*r^2, what is a^2? '));
-bc = 2.69692*(10^(-7)); %sqrt(input('Inside the core, assuming that the velcoity field has the form a^2-b^2*r^2, what is b^2? '));
-am = 15.4938; %sqrt(input('Outside the core, assuming that the velocity field has the form a^2-b^2*r^2, what is a^2? '));
-bm = 1.40336*(10^(-7)); %sqrt(input('Outside the core, assuming that the velocity field has the form a^2-b^2*r^2, what is b^2? '));
-RayDirectionVectors = zeros(M,N,3);
-for n = 1 : N
-    for m = 1 : M
-        Th = 2*pi*rand;
-        Ph = asin(-1+2*rand);
-        [x,y,z] = sph2cart(Th,Ph,1);
-        RayDirectionVectors(m,n,:) = [x,y,z];
-    end
-end
-vm = (am^2)-(bm^2)*(Rmantle)^2;
-vc = (ac^2)-(bc^2)*(Rmantle)^2;
-CriticalAngle = asin(vc/vm);
[…]

### 2016-08-24 Ray-Tracing/Ray_Tracing_Generalized.m

@@ -1,197 +1,0 @@
-clear
-
-format long
-
-a = [11.2633,10.6835,15.4938].^(1/2); %first entry corresponds to the core
-b = [1.55946*10^(-7),2.11853*10^(-7),1.40336*10^(-7)].^(1/2); %first entry corresponds to the core
-WeaknessOfNeglectedRays = 10^(-1); %input('What fraction of the initial ray energy must a ray contain to not be thrown out? ');
-
-D = 0;
-Radii = [0,1221,3480,6371];
-AbsoluteCutoff = 4;
-
-Layers = length(Radii);
-
-vBoundaries = zeros(Layers-2,2); %v(:,1) corresponds to the inner velocity on the :th layer, and v(:,2) corresponds to the outer velocity on the :th layer
-ReflectionCoefficients = zeros(Layers - 1,2); %these correspond to 4 functions of the angle of incidence
-TransmissionCoefficients = zeros(Layers - 1,2); %these correspond to 4 functions of the angle of incidence
-for i = 1 : Layers - 2
-    vBoundaries(i,1) = (a(i)^2)-(b(i)^2)*(Radii(i+1))^2; %inner
-    vBoundaries(i,2) = (a(i+1)^2)-(b(i+1)^2)*(Radii(i+1))^2; %outer
-end
-
-vBoundaries(Layers - 1,1) = (a(Layers - 1)^2)-(b(Layers - 1)^2)*(Radii(Layers))^2;
-vBoundaries(Layers - 1,2) = 0.34042; %Air
-
-rhoBoundaries = [];
-
-%GENERATING THE RANDOM POINTS ON A SPHERE
-
-M = 1;
-N = 10000;
-Th = rand(M,N).*(2*pi);
-Ph = asin((rand(M,N).*2.-1));
-I = 1:M;
-J = 1:N;
-RandSph = zeros(M,N,3);
-RandSph(:,:,1) = Th(:,:);
-RandSph(:,:,2) = Ph(:,:);
-RandSph(I,J,3) = 1;
-[RandX,RandY,RandZ] = sph2cart(RandSph(I,J,1),RandSph(I,J,2),RandSph(I,J,3));
-
-%PREPARING THE INITIAL CONDITIONS FOR THE RAYS
-
-L = 2*((((Radii(Layers))^2)-((D)^2))^0.5);
-l = (I-((M+1)/2)).*(L/(M+1));
-Alpha = atan2(D,transpose(l));
-x0 = transpose(repmat(X0(L,(M+1),I,D), [N,1]));
[…]

### 2016-08-24 Ray-Tracing/Ray_Tracing_Moon.m

@@ -1,401 +1,0 @@
-clear
-
-format long
-
-
-
-%INPUTS
-D = 0; %THE DISTANCE OF CLOSEST APPROACH TO THE CENTER km
-ACO = 9; %IT TAKES 16 ITERATIONS FOR A RAY TO PASS ENTIRELY THROUGH THE MOON
-
-vX = 2.5 * 10^5; %m/s
-sigmaX = (10^(-7)) * (10^(-4));% m^2
-fhigh = 20;%1/s %HIGHEST DETECTABLE FREQUENCY
-TotalDensityAverage = 3.3*10^3; %THE AVERAGE DENSITY THROUGHOUT THE WHOLE MOON
-pbar = 10^8;%HOOKIAN PRESSURE kg/(m*s^2)
-vs = 4.4 * 10^3;%AVERAGE SHEAR WAVE VELOCITY THROUGHOUT THE WHOLE MOON m/s
-vp = 7.6 * 10^3;%AVERAGE PRESSURE WAVE VELOCITY THROUGHOUT THE WHOLE MOON m/s
-
-M = 10; %NUMBER OF POINTS ON THE LINE
-N = 10; %NUMBER OF RAYS FROM EACH POINT
-%{
-%APPROXIMATION TO OUTER LAYERS
-a = [8.26955,8.26955,8.26955,8.26955,145.46].^(1/2);
-b = [2.47697*10^(-7),2.47697*10^(-7),2.47697*10^(-7),2.47697*10^(-7),0.0000478823].^(1/2);
-Radii = [0,961.7,1231.7,1461.7,1671.7,1737.1];
-AverageV = [8.15502,7.96714,7.81709,7.65888,6.19979];
-Q = [675,1125,3375,9000,6750];
-rhoBoundaries = [   3.406       ,   3.406               ;...
-                    3.379       ,   3.379               ;...
-                    3.350       ,   3.350               ;...
-                    3.318       ,   3.318               ;...
-                    2.762       ,   0.000               ].*(10^15);
-%}
-%%{
-%VPREMOON MODEL
-a = ([8.26955,8.26955,8.26955,8.26955,8.26955,5.5,3.2,1.0].*10^3).^(1/2); %THESE ARE THE CONSTANT TERMS IN THE PARABOLIC VELOCITY FIELD STRUCTURE, THE FIRST ENTRY CORRESPONDING TO THE CORE km/s
[…]

### 2016-08-24 Ray-Tracing/Ray_Tracing_Really_Generalized.m

@@ -1,65 +1,0 @@
-clear
-
-%GENERATING THE RANDOM POINTS ON A SPHERE
-
-M = 7;
-N = 5;
-Th = rand(M,N).*(2*pi);
-Ph = asin((rand(M,N).*2.-1));
-I = 1:M;
-J = 1:N;
-RandSph = zeros(M,N,3);
-RandSph(:,:,1) = Th(:,:);
-RandSph(:,:,2) = Ph(:,:);
-RandSph(I,J,3) = 1;
-[RandX,RandY,RandZ] = sph2cart(RandSph(I,J,1),RandSph(I,J,2),RandSph(I,J,3));
-
-%PREPARING THE INITIAL CONDITIONS FOR THE RAYS
-
-D = 2000;
-Radii = [0,1221,3480,6371];
-AbsoluteCutoff = 5;
-
-Layers = length(Radii);
-
-L = 2*((((Radii(Layers))^2)-((D)^2))^0.5);
-l = (I-((M+1)/2)).*(L/(M+1));
-RayArray = zeros(M,N,2^(AbsoluteCutoff - 1),3); % = (point M, ray N, daughter P, (x,AlphaRay,Amplitude))
-Alpha = atan2(D,transpose(l));
-for i = 1 : M
-    RotMatrixAlpha = [cos(Alpha(i)),sin(Alpha(i)),0;-sin(Alpha(i)),cos(Alpha(i)),0;0,0,1];
-    for j = 1 : N
-        RotRand = RotMatrixAlpha*[RandX(i,j)+l(i);RandY(i,j)+D;RandZ(i,j)];
-        Beta(i,j) = atan2(RotRand(3),RotRand(2));
-        RotMatrixBeta = [1,0,0;0,cos(Beta(i,j)),sin(Beta(i,j));0,-sin(Beta(i,j)),cos(Beta(i,j))];
-        Vec = RotMatrixBeta*RotRand;
-        AlphaRay(i,j) = atan2(Vec(2),Vec(1));
-    end
-end
-x0 = transpose(repmat(X0(L,(M+1),I,D), [N,1]));
-RayArray(:,:,1,1) = x0(:,:);
-RayArray(:,:,1,2) = AlphaRay(:,:);
-RayArray(:,:,1,3) = 1;
-
-%PROPAGATION
-
-LeftRays = zeros(M,N,2^(AbsoluteCutoff - 1),1);
[…]

### 2016-08-24 Ray-Tracing/Ray_Tracing_Revised.m

@@ -1,336 +1,0 @@
-clear
-
-format long
-
-
-
-%INPUTS
-
-M = 1; %NUMBER OF POINTS ON THE LINE
-N = 5000; %NUMBER OF RAYS FROM EACH POINT
-
-a = [11.2633,10.6835,15.4938].^(1/2); %THESE ARE THE CONSTANT TERMS IN THE PARABOLIC VELOCITY FIELD STRUCTURE, THE FIRST ENTRY CORRESPONDING TO THE CORE
-b = [1.55946*10^(-7),2.11853*10^(-7),1.40336*10^(-7)].^(1/2); %THESE ARE THE COEFFICIENTS OF THE QUADRATIC TERM IN THE VELOCITY FIELD
-
-D = 6370; %THE DISTANCE OF CLOSEST APPROACH TO THE CENTER
-Radii = [0,1221,3480,6371]; %NOTE THAT WE MUST TAKE 0 AS A LAYER FOR TECHNICAL PURPOSES
-ACO = 8; %IT TAKES 5 ITERATIONS FOR A RAY TO PASS ENTIRELY THROUGH THE EARTH
-
-%Q = ; %THE QUALITY FACTOR AS A FUNCTION OF FREQUENCY, TIME, AND SO ON... TBD
-%A = ; %THE AMPLITUDE OF THE WAVE AS A FUNCTION OF FREQUENCY
-
-rhoBoundaries = [ 12.76, 12.17; 9.90, 5.57; 1.02, 1.25*(10^(-3))].*(10^12); %THE DENSITY OF THE MEDIA AT THEIR DISCONTINUOUS BOUNDARIES - THE LEFT ENTRY IN EACH ROW CORRESPONDS TO THE INNER DENSITY AND THE RIGHT CORRESPONDS TO THE OUTER DENSITY
-
-%END INPUTS
-
-
-
-
-
-
-
-
-
-Layers = length(Radii);
-
-vBoundaries = zeros(Layers-2,2); %v(:,1) corresponds to the inner velocity on the :th layer, and v(:,2) corresponds to the outer velocity on the :th layer
-ReflectionCoefficients = zeros(Layers - 1,2); %these correspond to 4 functions of the angle of incidence
-TransmissionCoefficients = zeros(Layers - 1,2); %these correspond to 4 functions of the angle of incidence
-for i = 1 : Layers - 2
[…]

### 2016-08-24 Ray-Tracing/ReflectionCoefficient.m

@@ -1,7 +1,0 @@
-function R = ReflectionCoefficient(LayerId,TempAmp,sinTheta,AlphaRay,v1,v2,rho1,rho2)
-%The fluid in which the wave arrives is labeled 1
-%   Detailed explanation goes here
-    R = 1 - TransmissionCoefficient(LayerId,TempAmp,sinTheta,AlphaRay,v1,v2,rho1,rho2);
-    
-end
-

### 2016-08-24 Ray-Tracing/T.m

@@ -1,13 +1,0 @@
-function output = T(x,y,z,theta)
-%Rotation about the vector (ux,uy,uz) by the angle theta.
-%   Detailed explanation goes here
-    mag = sqrt(x^2+y^2+z^2);
-    ux = x/mag;
-    uy = y/mag;
-    uz = z/mag;
-    t = 1 - cos(theta);
-    C = cos(theta);
-    S = sin(theta);
-    output = [t*(ux^2)+C,t*ux*uy-S*uz,t*ux*uz+S*uy;t*ux*uy+S*uz,t*(uy^2)+C,t*uy*uz-S*ux;t*ux*uz-S*uy,t*uy*uz+S*ux,t*(uz^2)+C];
-end
-

### 2016-08-24 Ray-Tracing/Test_With_Earth_Values.m

@@ -1,360 +1,0 @@
-clear
-
-format long
-
-
-
-%INPUTS
-
-M = 1; %NUMBER OF POINTS ON THE LINE
-N = 5000; %NUMBER OF RAYS FROM EACH POINT
-
-a = [11.2633,10.6835,15.4938].^(1/2); %THESE ARE THE CONSTANT TERMS IN THE PARABOLIC VELOCITY FIELD STRUCTURE, THE FIRST ENTRY CORRESPONDING TO THE CORE
-b = [1.55946*10^(-7),2.11853*10^(-7),1.40336*10^(-7)].^(1/2); %THESE ARE THE COEFFICIENTS OF THE QUADRATIC TERM IN THE VELOCITY FIELD
-
-D = 6370; %THE DISTANCE OF CLOSEST APPROACH TO THE CENTER
-Radii = [0,1221,3480,6371]; %NOTE THAT WE MUST TAKE 0 AS A LAYER FOR TECHNICAL PURPOSES
-ACO = 5; %IT TAKES 5 ITERATIONS FOR A RAY TO PASS ENTIRELY THROUGH THE EARTH
-
-%Q = ; %THE QUALITY FACTOR AS A FUNCTION OF FREQUENCY, TIME, AND SO ON... TBD
-%A = ; %THE AMPLITUDE OF THE WAVE AS A FUNCTION OF FREQUENCY
-
-rhoBoundaries = [ 12.76, 12.17; 9.90, 5.57; 1.02, 1.25*(10^(-3))].*(10^12); %THE DENSITY OF THE MEDIA AT THEIR DISCONTINUOUS BOUNDARIES - THE LEFT ENTRY IN EACH ROW CORRESPONDS TO THE INNER DENSITY AND THE RIGHT CORRESPONDS TO THE OUTER DENSITY
-
-%END INPUTS
-
-
-
-
-
-
-
-
-
-Layers = length(Radii);
-
-vBoundaries = zeros(Layers-2,2); %v(:,1) corresponds to the inner velocity on the :th layer, and v(:,2) corresponds to the outer velocity on the :th layer
-ReflectionCoefficients = zeros(Layers - 1,2); %these correspond to 4 functions of the angle of incidence
-TransmissionCoefficients = zeros(Layers - 1,2); %these correspond to 4 functions of the angle of incidence
-for i = 1 : Layers - 2
[…]

### 2016-08-24 Ray-Tracing/X0.m

@@ -1,4 +1,0 @@
-%This function tells us the distance from the origin of the point source
-function output=X0(L,N,n,D)
-    output = (((L/N).*(n-(N/2))).^2+D^2).^(0.5);
-end

### 2016-08-24 Ray-Tracing/r.m

@@ -1,8 +1,0 @@
-function output = r(s,a,b,AlphaRay,x0,s1,~,~)
-%This is the radial coordinate of the ray as a function of the parameter s
-output = ((1+exp(1).^(2.*s)).^2+((-1)+exp(1).^(2.*s)).^2.*x0.^2+(-2).*((-1) ...
-  +exp(1).^(4.*s)).*x0.*abs(cos(\[Alpha]))).^(-1/2).*(((-1)+exp(1).^(\
-2.*s)) ...
-.^2+(1+exp(1).^(2.*s)).^2.*x0.^2+(-2).*((-1)+exp(1).^(4.*s)).*x0.* ...
-  abs(cos(\[Alpha]))).^(1/2);
-end

### 2016-08-24 Macro Impacts Revised.tex
small correction
Fixed a few things
:)

@@
 \begin{align}
-k_r = k_x\cos\phi +k_y\sin\phi
+k_r = \sqrt{k_x^2 +k_y^2}
 \end{align}
@@
 \begin{align}
-C_1 =  2\pi \f{\abs{\frac{dE}{dx}}}{\rho \sigma_x c_p}\int_{0}^{\infty}\delta(r)e^{2\pi i k r} dr = 2\pi\f{\abs{\frac{dE}{dx}}}{\rho \sigma_x c_p}\,,
-\end{align}
-where the factor of $2 \pi$ comes from the $\phi$ integral (notice this factor in $C_1$ cancels against the factor in $\tilde{T}$ -- David, is this is correc?).
+C_1 =  2\pi \f{\abs{\frac{dE}{dx}}}{\rho \sigma_x c_p}\int_{0}^{\infty}\delta(r)e^{i k r} dr = 2\pi\f{\abs{\frac{dE}{dx}}}{\rho \sigma_x c_p}\,,
+\end{align}
+where the factor of $2 \pi$ comes from the $\phi$ integral.
 $T$ in real space is given by inverting the Fourier transform:
 \begin{align}
-T(r,t) &=\frac{1}{\p{2\pi}^2} \int_0^\infty k_r \diff{k_r}\tilde{T} = \frac{1}{4\pi^2}\f{\abs{\frac{dE}{dx}}}{\rho \sigma_x c_p}\int_0^\infty k_r\diff k_r e^{-\alpha k_r^2 t}J_0(k_r r)\,,\\
+T(r,t) &=\frac{1}{\p{2\pi}} \int_0^\infty k_r \diff{k_r}\tilde{T} = \frac{2\pi}{2\pi}\f{\abs{\frac{dE}{dx}}}{\rho \sigma_x c_p}\int_0^\infty k_r\diff k_r e^{-\alpha k_r^2 t}J_0(k_r r)\,,\\
 &=\f{\abs{\frac{dE}{dx}}}{2 \rho \sigma_x c_p \alpha t}\ e^{-\f{r^2}{4t\alpha}}\,.
 \end{align}
-(If the third equation is valid up to some factors of $2\pi$ that I'm too tired to figure out right now, then the rest is valid  but needs to be fixed to include these factors properly).
 Setting $T = T_\te{melt}$, we have
@@
 \begin{align}
-r_\te{fast melt} =\frac{2\alpha}{v_p}W\p{{\f{\abs{\frac{dE}{dx}}v_p^2}{2 \rho \sigma_x c_p \alpha^2 T_\te{melt}}}}.
+r_\te{fast melt} =\frac{2\alpha}{v_p}W\p{{\f{\abs{\frac{dE}{dx}}v_p^2}{2 \rho \sigma_x c_p \alpha^2 T_\te{melt}}}} = \frac{2\alpha}{v_p}W\p{\frac{v_{X} v_p^2}{2 c_p \alpha^2 T_\te{melt}}}.
 \end{align}

### 2016-08-24 Macro Impacts Revised.tex
added r_x factor
:)

@@
 \begin{align}
-r_\te{fast melt} =\frac{2\alpha}{v_p}W\p{{\f{\abs{\frac{dE}{dx}}v_p^2}{2 \rho \sigma_x c_p \alpha^2 T_\te{melt}}}} = \frac{2\alpha}{v_p}W\p{\frac{v_{X} v_p^2}{2 c_p \alpha^2 T_\te{melt}}}.
+r_\te{fast melt} =\frac{2\alpha}{v_p}W\p{{\f{\abs{\frac{dE}{dx}}r_{X}v_p^2}{2 \rho \sigma_x c_p \alpha^2 T_\te{melt}}}} = \frac{2\alpha}{v_p}W\p{\frac{r_{X}v_{X} v_p^2}{2 c_p \alpha^2 T_\te{melt}}}.
 \end{align}

### 2016-08-24 Macro Impacts Revised.tex
:)

@@
 \begin{align}
-T(r,0) = \f{\abs{\frac{dE}{dx}}}{\rho \sigma_x c_p}\delta(r),
+T(r,0) = \f{\abs{\frac{dE}{dx}}r_X}{\rho \sigma_x c_p}\delta(r),
 \end{align}
@@
 \begin{align}
-C_1 =  2\pi \f{\abs{\frac{dE}{dx}}}{\rho \sigma_x c_p}\int_{0}^{\infty}\delta(r)e^{i k r} dr = 2\pi\f{\abs{\frac{dE}{dx}}}{\rho \sigma_x c_p}\,,
+C_1 =  2\pi \f{\abs{\frac{dE}{dx}}r_X}{\rho \sigma_x c_p}\int_{0}^{\infty}\delta(r)e^{i k r} dr = 2\pi\f{\abs{\frac{dE}{dx}}r_X}{\rho \sigma_x c_p}\,,
 \end{align}
@@
 \begin{align}
-T(r,t) &=\frac{1}{\p{2\pi}} \int_0^\infty k_r \diff{k_r}\tilde{T} = \frac{2\pi}{2\pi}\f{\abs{\frac{dE}{dx}}}{\rho \sigma_x c_p}\int_0^\infty k_r\diff k_r e^{-\alpha k_r^2 t}J_0(k_r r)\,,\\
-&=\f{\abs{\frac{dE}{dx}}}{2 \rho \sigma_x c_p \alpha t}\ e^{-\f{r^2}{4t\alpha}}\,.
+T(r,t) &=\frac{1}{\p{2\pi}} \int_0^\infty k_r \diff{k_r}\tilde{T} = \frac{2\pi}{2\pi}\f{\abs{\frac{dE}{dx}}r_X}{\rho \sigma_x c_p}\int_0^\infty k_r\diff k_r e^{-\alpha k_r^2 t}J_0(k_r r)\,,\\
+&=\f{\abs{\frac{dE}{dx}r_X}}{2 \rho \sigma_x c_p \alpha t}\ e^{-\f{r^2}{4t\alpha}}\,.
 \end{align}
@@
 \begin{align}
-r_\te{melt} = \sqrt{4t\alpha\ln\ps{\f{\abs{\frac{dE}{dx}}}{2 \rho \sigma_x c_p \alpha T_\te{melt} t}}}\,.
+r_\te{melt} = \sqrt{4t\alpha\ln\ps{\f{\abs{\frac{dE}{dx}}r_X}{2 \rho \sigma_x c_p \alpha T_\te{melt} t}}}\,.
 \end{align}
@@
 \begin{align}
-\dot r_\te{melt} &=\sqrt{\f{\alpha}{t}}\f{\ln\p{\f{\abs{\frac{dE}{dx}}}{2 \rho \sigma_x c_p \alpha T_\te{melt} t}} - 1}{\sqrt{\ln\p{\f{\abs{\frac{dE}{dx}}}{2 \rho \sigma_x c_p \alpha T_\te{melt} t}}}}\,.
-\end{align}
-Since, for the parameters at hand, $\ln\p{\f{\abs{\frac{dE}{dx}}}{2 \rho \sigma_x c_p \alpha T_\te{melt} t}}$ is at least of order 10 $>>$ 1, it is a reasonable approximation to take
-\begin{align}
-\dot r_\te{melt} &=\sqrt{\f{\alpha}{t}\ln\p{\f{\abs{\frac{dE}{dx}}}{2 \rho \sigma_x c_p \alpha T_\te{melt} t}}}\,.
+\dot r_\te{melt} &=\sqrt{\f{\alpha}{t}}\f{\ln\p{\f{\abs{\frac{dE}{dx}}r_X}{2 \rho \sigma_x c_p \alpha T_\te{melt} t}} - 1}{\sqrt{\ln\p{\f{\abs{\frac{dE}{dx}} r_X}{2 \rho \sigma_x c_p \alpha T_\te{melt} t}}}}\,.
+\end{align}
+Since, for the parameters at hand, $\ln\p{\f{\abs{\frac{dE}{dx}}r_X}{2 \rho \sigma_x c_p \alpha T_\te{melt} t}}$ is at least of order 10 $>>$ 1, it is a reasonable approximation to take
+\begin{align}
+\dot r_\te{melt} &=\sqrt{\f{\alpha}{t}\ln\p{\frac{\abs{\frac{dE}{dx}}r_X}{2 \rho \sigma_x c_p \alpha T_\te{melt} t}}}\,.
 \end{align}
@@
 \begin{align}
-t_{\te{fast}} = \f{\alpha}{v_p^2}W\p{{\f{\abs{\frac{dE}{dx}}v_p^2}{2 \rho \sigma_x c_p \alpha^2 T_\te{melt}}}}
+t_{\te{fast}} = \f{\alpha}{v_p^2}W\p{{\f{\abs{\frac{dE}{dx}}r_Xv_p^2}{2 \rho \sigma_x c_p \alpha^2 T_\te{melt}}}}
 \end{align}
@@
 \begin{align}
-r_\te{fast melt} =  \frac{2\alpha}{v_p}\sqrt{W\p{{\f{\abs{\frac{dE}{dx}}v_p^2}{2 \rho \sigma_x c_p \alpha^2 T_\te{melt}}}}\ln\ps{\p{\frac{\abs{\frac{dE}{dx}}v_p^2}{2 \rho \sigma_x c_p \alpha^2 T_\te{melt}}}\frac{1}{W\p{{\f{\abs{\frac{dE}{dx}}v_p^2}{2 \rho \sigma_x c_p \alpha^2 T_\te{melt}}}}
+r_\te{fast melt} =  \frac{2\alpha}{v_p}\sqrt{W\p{{\f{\abs{\frac{dE}{dx}}r_{X}v_p^2}{2 \rho \sigma_x c_p \alpha^2 T_\te{melt}}}}\ln\ps{\p{\frac{\abs{\frac{dE}{dx}}r_{X}v_p^2}{2 \rho \sigma_x c_p \alpha^2 T_\te{melt}}}\frac{1}{W\p{{\f{\abs{\frac{dE}{dx}}r_{X}v_p^2}{2 \rho \sigma_x c_p \alpha^2 T_\te{melt}}}}
 }}}\,.

### 2016-08-24 Macro Impacts Revised.tex
nitpicking
.

--- 2016-08-24 Macro Impacts Revised.tex
@@
 \begin{align}
-T(r,0) = \f{\abs{\frac{dE}{dx}}}{\rho \sigma_x c_p}\delta(r),
+T(r,0) = \f{\abs{\frac{dE}{dx}}r_X}{\rho \sigma_X c_p}\delta(r),
 \end{align}
@@
 \begin{align}
-C_1 =  2\pi \f{\abs{\frac{dE}{dx}}}{\rho \sigma_x c_p}\int_{0}^{\infty}\delta(r)e^{i k r} dr = 2\pi\f{\abs{\frac{dE}{dx}}}{\rho \sigma_x c_p}\,,
+C_1 =  2\pi \f{\abs{\frac{dE}{dx}}r_X}{\rho \sigma_X c_p}\int_{0}^{\infty}\delta(r)e^{i k r} dr = 2\pi\f{\abs{\frac{dE}{dx}}r_X}{\rho \sigma_X c_p}\,,
 \end{align}
@@
 \begin{align}
-T(r,t) &=\frac{1}{\p{2\pi}} \int_0^\infty k_r \diff{k_r}\tilde{T} = \frac{2\pi}{2\pi}\f{\abs{\frac{dE}{dx}}}{\rho \sigma_x c_p}\int_0^\infty k_r\diff k_r e^{-\alpha k_r^2 t}J_0(k_r r)\,,\\
-&=\f{\abs{\frac{dE}{dx}}}{2 \rho \sigma_x c_p \alpha t}\ e^{-\f{r^2}{4t\alpha}}\,.
+T(r,t) &=\frac{1}{\p{2\pi}} \int_0^\infty k_r \diff{k_r}\tilde{T} = \frac{2\pi}{2\pi}\f{\abs{\frac{dE}{dx}}r_X}{\rho \sigma_X c_p}\int_0^\infty k_r\diff k_r e^{-\alpha k_r^2 t}J_0(k_r r)\,,\\
+&=\f{\abs{\frac{dE}{dx}}r_X}{2 \rho \sigma_X c_p \alpha t}\ e^{-\f{r^2}{4t\alpha}}\,.
 \end{align}
@@
 \begin{align}
-r_\te{melt} = \sqrt{4t\alpha\ln\ps{\f{\abs{\frac{dE}{dx}}}{2 \rho \sigma_x c_p \alpha T_\te{melt} t}}}\,.
+r_\te{melt} = \sqrt{4t\alpha\ln\ps{\f{\abs{\frac{dE}{dx}}r_X}{2 \rho \sigma_X c_p \alpha T_\te{melt} t}}}\,.
 \end{align}
@@
 \begin{align}
-\dot r_\te{melt} &=\sqrt{\f{\alpha}{t}}\f{\ln\p{\f{\abs{\frac{dE}{dx}}}{2 \rho \sigma_x c_p \alpha T_\te{melt} t}} - 1}{\sqrt{\ln\p{\f{\abs{\frac{dE}{dx}}}{2 \rho \sigma_x c_p \alpha T_\te{melt} t}}}}\,.
-\end{align}
-Since, for the parameters at hand, $\ln\p{\f{\abs{\frac{dE}{dx}}}{2 \rho \sigma_x c_p \alpha T_\te{melt} t}}$ is at least of order 10 $>>$ 1, it is a reasonable approximation to take
-\begin{align}
-\dot r_\te{melt} &=\sqrt{\f{\alpha}{t}\ln\p{\f{\abs{\frac{dE}{dx}}}{2 \rho \sigma_x c_p \alpha T_\te{melt} t}}}\,.
+\dot r_\te{melt} &=\sqrt{\f{\alpha}{t}}\f{\ln\p{\f{\abs{\frac{dE}{dx}}r_X}{2 \rho \sigma_X c_p \alpha T_\te{melt} t}} - 1}{\sqrt{\ln\p{\f{\abs{\frac{dE}{dx}} r_X}{2 \rho \sigma_X c_p \alpha T_\te{melt} t}}}}\,.
+\end{align}
+Since, for the parameters at hand, $\ln\p{\f{\abs{\frac{dE}{dx}}r_X}{2 \rho \sigma_X c_p \alpha T_\te{melt} t}}$ is at least of order 10 $>>$ 1, it is a reasonable approximation to take
+\begin{align}
+\dot r_\te{melt} &=\sqrt{\f{\alpha}{t}\ln\p{\frac{\abs{\frac{dE}{dx}}r_X}{2 \rho \sigma_X c_p \alpha T_\te{melt} t}}}\,.
 \end{align}
@@
 \begin{align}
-t_{\te{fast}} = \f{\alpha}{v_p^2}W\p{{\f{\abs{\frac{dE}{dx}}v_p^2}{2 \rho \sigma_x c_p \alpha^2 T_\te{melt}}}}
+t_{\te{fast}} = \f{\alpha}{v_p^2}W\p{{\f{\abs{\frac{dE}{dx}}r_Xv_p^2}{2 \rho \sigma_X c_p \alpha^2 T_\te{melt}}}}
 \end{align}
@@
 \begin{align}
-r_\te{fast melt} =  \frac{2\alpha}{v_p}\sqrt{W\p{{\f{\abs{\frac{dE}{dx}}v_p^2}{2 \rho \sigma_x c_p \alpha^2 T_\te{melt}}}}\ln\ps{\p{\frac{\abs{\frac{dE}{dx}}v_p^2}{2 \rho \sigma_x c_p \alpha^2 T_\te{melt}}}\frac{1}{W\p{{\f{\abs{\frac{dE}{dx}}v_p^2}{2 \rho \sigma_x c_p \alpha^2 T_\te{melt}}}}
+r_\te{fast melt} =  \frac{2\alpha}{v_p}\sqrt{W\p{{\f{\abs{\frac{dE}{dx}}r_{X}v_p^2}{2 \rho \sigma_X c_p \alpha^2 T_\te{melt}}}}\ln\ps{\p{\frac{\abs{\frac{dE}{dx}}r_{X}v_p^2}{2 \rho \sigma_X c_p \alpha^2 T_\te{melt}}}\frac{1}{W\p{{\f{\abs{\frac{dE}{dx}}r_{X}v_p^2}{2 \rho \sigma_X c_p \alpha^2 T_\te{melt}}}}
 }}}\,.
@@
 \begin{align}
-r_\te{fast melt} =\frac{2\alpha}{v_p}W\p{{\f{\abs{\frac{dE}{dx}}v_p^2}{2 \rho \sigma_x c_p \alpha^2 T_\te{melt}}}} = \frac{2\alpha}{v_p}W\p{\frac{v_{X} v_p^2}{2 c_p \alpha^2 T_\te{melt}}}.
+r_\te{fast melt} =\frac{2\alpha}{v_p}W\p{{\f{\abs{\frac{dE}{dx}}r_{X}v_p^2}{2 \rho \sigma_X c_p \alpha^2 T_\te{melt}}}} = \frac{2\alpha}{v_p}W\p{\frac{r_{X}v_{X} v_p^2}{2 c_p \alpha^2 T_\te{melt}}}.
 \end{align}

### 2016-08-24 Macro Impacts Revised.tex
conceptual points added

@@
 \end{align}
+Note that this model/initial condition is reasonable given that the delta source becomes a Gaussian with the same energy (assuming energy is conserved) an instant after the initial input of the delta source.
+
 Taking the Fourier transform of this initial condition over r and $\phi$ fixes $C_1$ as 
@@
 \end{align}
-which is on the order of micrometers to tenths of micrometers for our case.
-
-Conceptually, it would seem that $r_\te{fast melt}$ should be added to $r_\te{Macro}$ to give the full extent of material melted down.
+which is on the order of micrometers to tenths of micrometers for most marco radii which, for $r_X > 10^-8$ results in $r_\te{fast melt} < r_X$ which is something of a problem.
+
+This suggests that much of the melting occurs once the temperature field is expanding slower than the speed of sound, and that the expansion speed of the melt zone slows down very quickly.
 

### 2016-08-24 Macro Impacts Revised.tex
further conceptual points added

@@
 
-This suggests that much of the melting occurs once the temperature field is expanding slower than the speed of sound, and that the expansion speed of the melt zone slows down very quickly.
+This either suggests that much of the melting occurs once the temperature field is expanding slower than the speed of sound, and that the expansion speed of the melt zone slows down very quickly or that the material parameters -- especially $\alpha$ -- are far from constant (or may not even be well defined) in our case.
 

### 2016-08-24 Macro Impacts Revised.tex
Vaporization computation added plus other minor fixes

--- 2016-08-24 Macro Impacts Revised.tex
@@
 \end{align}
-Since, for the parameters at hand, $\ln\p{\f{\abs{\frac{dE}{dx}}r_X}{2 \rho \sigma_X c_p \alpha T_\te{melt} t}}$ is at least of order 10 $>>$ 1, it is a reasonable approximation to take
+Since, for the parameters at hand, $\ln\p{\f{\abs{\frac{dE}{dx}}r_X}{2 \rho \sigma_X c_p \alpha T_\te{melt} t}}$ is at least of order $10 \gg 1$ it is a reasonable approximation to take
 \begin{align}
@@
 \end{align}
-Notice that this has the form of $\sqrt{W(x)\ln\p{{\frac{x}{W(x)}}}}$, which gives $\sqrt{W(x)^2}$ by the identity $\ln\p{{\frac{x}{W(x)}}} = W(x)$ which holds when $x \geq -1/e$ which is true for the parameters at hand.
+Notice that this has the form of $\sqrt{W(x)\ln\p{{\frac{x}{W(x)}}}}$, which gives $\sqrt{W(x)^2}$ by the identity $\ln\p{{\frac{x}{W(x)}}} = W(x)$ which holds when $x \geq -1/e$r which is true for the parameters at hand.
 Thus, we have,
@@
 \end{align}
-which is on the order of micrometers to tenths of micrometers for most marco radii which, for $r_X > 10^-8$ results in $r_\te{fast melt} < r_X$ which is something of a problem.
-
-This suggests that much of the melting occurs once the temperature field is expanding slower than the speed of sound, and that the expansion speed of the melt zone slows down very quickly.
+This expression for $r_\te{fast melt}$ is highly sensitive to $\alpha$ and $v_p$ and relatively insensitive to the macro's parameters.
+
+It gives results on the order of micrometers to tenths of micrometers for most marco radii which, for $r_X > 10^-8$ results in $r_\te{fast melt} < r_X$ which is a bit of a problem.
+
+It is likely that either much of the melting occurs once the temperature field's expansion is slower than the speed of sound and this slow-down occurs very quickly, or that the material parameters -- especially $\alpha$ and $c_p$ -- are far from constant (or may not even be well defined) in our case.
+
+As attempt to establish a lower bound for the energy that is unequivocally dissipated that relies on fewer parameters of the impacted material, consider the energy required to vaporize a cylinder of material (with parameters akin to rock) with radius equal to the macro and length h equal to the diameter of the moon, which is given by
+\begin{align}
+Q_\te{sublimate} = (L_\te{melt} + L_\te{vaporization})\rho \pi h(r_X)^2,
+\end{align}
+
+As an example, for $r_X \propto 10^{-6}$, this gives $Q \propto 10^2 J$ which is quite small, and for $r_X < 10^{-9}$ this gives results that are less than 1 J.
 

### 2016-08-24 Macro Impacts Revised.tex
Another fix

@@
 \begin{align}
-r_\te{fast melt} =\frac{2\alpha}{v_p}W\p{{\f{\abs{\frac{dE}{dx}}r_{X}v_p^2}{2 \rho \sigma_X c_p \alpha^2 T_\te{melt}}}} = \frac{2\alpha}{v_p}W\p{\frac{r_{X}v_{X} v_p^2}{2 c_p \alpha^2 T_\te{melt}}}.
+r_\te{fast melt} =\frac{2\alpha}{v_p}W\p{{\f{\abs{\frac{dE}{dx}}r_{X}v_p^2}{2 \rho \sigma_X c_p \alpha^2 T_\te{melt}}}} = \frac{2\alpha}{v_p}W\p{\frac{r_{X}v_{X}^2 v_p^2}{2 c_p \alpha^2 T_\te{melt}}}.
 \end{align}

### 2016-08-24 Draft.tex

@@
 \end{align}
+(28) is impossible to integrate when $E_k$ consists of the energies of two different rays, each with different attenuation factors.
+When this case arrises, we average $\te{Att}$ among the coincident rays.
+For the lowest frequency modes $f<20\te{Hz}$, $\te{Att} k$ order 10 at most, and does not contribute significantly to $u$.
+Taking $\te{Att} = 0$, we have
+\begin{align}
+\abs{u(\vec x,t)}\leq\sqrt{\f{2}{\rho v_p^2 A}}\sqrt{\f{\te{Ref}\,\Xi E}{\te{Att}}}\f1k\te{Erf}\ps{\sqrt{\f{\te{Att}\,k}{2}}}\,.
+\end{align}
 \section{Simulation}
@@
 \end{align}
-This is independent of the choice of partition. For the triangle wave, we need not test $\sigma_X\leq10^{-9}\te{m}^2$ (I WILL VERIFY THIS).
+This is independent of the choice of partition. For the triangle wave, we need not test $\sigma_X\leq 4\times 10^{-11}\te{m}^2$.
 \section{Results}

### 2016-08-24 Macro Impacts Revised.tex

--- 2016-08-24 Macro Impacts Revised.tex
@@
 \begin{align}
-T(r,0) = \f{\abs{\frac{dE}{dx}}r_X}{\rho \sigma_X c_p}\delta(r),
-\end{align}
-Note that this model/initial condition is reasonable given that the delta source becomes a Gaussian with the same energy (assuming energy is conserved) an instant after the initial input of the delta source.
-
+T(r,0) = \f{\abs{\frac{dE}{dx}}}{\rho \sigma_x c_p}\delta(r),
+\end{align}
 Taking the Fourier transform of this initial condition over r and $\phi$ fixes $C_1$ as 
 \begin{align}
-C_1 =  2\pi \f{\abs{\frac{dE}{dx}}r_X}{\rho \sigma_X c_p}\int_{0}^{\infty}\delta(r)e^{i k r} dr = 2\pi\f{\abs{\frac{dE}{dx}}r_X}{\rho \sigma_X c_p}\,,
+C_1 =  2\pi \f{\abs{\frac{dE}{dx}}}{\rho \sigma_x c_p}\int_{0}^{\infty}\delta(r)e^{i k r} dr = 2\pi\f{\abs{\frac{dE}{dx}}}{\rho \sigma_x c_p}\,,
 \end{align}
@@
 \begin{align}
-T(r,t) &=\frac{1}{\p{2\pi}} \int_0^\infty k_r \diff{k_r}\tilde{T} = \frac{2\pi}{2\pi}\f{\abs{\frac{dE}{dx}}r_X}{\rho \sigma_X c_p}\int_0^\infty k_r\diff k_r e^{-\alpha k_r^2 t}J_0(k_r r)\,,\\
-&=\f{\abs{\frac{dE}{dx}}r_X}{2 \rho \sigma_X c_p \alpha t}\ e^{-\f{r^2}{4t\alpha}}\,.
+T(r,t) &=\frac{1}{\p{2\pi}} \int_0^\infty k_r \diff{k_r}\tilde{T} = \frac{2\pi}{2\pi}\f{\abs{\frac{dE}{dx}}}{\rho \sigma_x c_p}\int_0^\infty k_r\diff k_r e^{-\alpha k_r^2 t}J_0(k_r r)\,,\\
+&=\f{\abs{\frac{dE}{dx}}}{2 \rho \sigma_x c_p \alpha t}\ e^{-\f{r^2}{4t\alpha}}\,.
 \end{align}
@@
 \begin{align}
-r_\te{melt} = \sqrt{4t\alpha\ln\ps{\f{\abs{\frac{dE}{dx}}r_X}{2 \rho \sigma_X c_p \alpha T_\te{melt} t}}}\,.
+r_\te{melt} = \sqrt{4t\alpha\ln\ps{\f{\abs{\frac{dE}{dx}}}{2 \rho \sigma_x c_p \alpha T_\te{melt} t}}}\,.
 \end{align}
@@
 \begin{align}
-\dot r_\te{melt} &=\sqrt{\f{\alpha}{t}}\f{\ln\p{\f{\abs{\frac{dE}{dx}}r_X}{2 \rho \sigma_X c_p \alpha T_\te{melt} t}} - 1}{\sqrt{\ln\p{\f{\abs{\frac{dE}{dx}} r_X}{2 \rho \sigma_X c_p \alpha T_\te{melt} t}}}}\,.
-\end{align}
-Since, for the parameters at hand, $\ln\p{\f{\abs{\frac{dE}{dx}}r_X}{2 \rho \sigma_X c_p \alpha T_\te{melt} t}}$ is at least of order 10 $>>$ 1, it is a reasonable approximation to take
-\begin{align}
-\dot r_\te{melt} &=\sqrt{\f{\alpha}{t}\ln\p{\frac{\abs{\frac{dE}{dx}}r_X}{2 \rho \sigma_X c_p \alpha T_\te{melt} t}}}\,.
+\dot r_\te{melt} &=\sqrt{\f{\alpha}{t}}\f{\ln\p{\f{\abs{\frac{dE}{dx}}}{2 \rho \sigma_x c_p \alpha T_\te{melt} t}} - 1}{\sqrt{\ln\p{\f{\abs{\frac{dE}{dx}}}{2 \rho \sigma_x c_p \alpha T_\te{melt} t}}}}\,.
+\end{align}
+Since, for the parameters at hand, $\ln\p{\f{\abs{\frac{dE}{dx}}}{2 \rho \sigma_x c_p \alpha T_\te{melt} t}}$ is at least of order 10 $>>$ 1, it is a reasonable approximation to take
+\begin{align}
+\dot r_\te{melt} &=\sqrt{\f{\alpha}{t}\ln\p{\f{\abs{\frac{dE}{dx}}}{2 \rho \sigma_x c_p \alpha T_\te{melt} t}}}\,.
 \end{align}
@@
 \begin{align}
-t_{\te{fast}} = \f{\alpha}{v_p^2}W\p{{\f{\abs{\frac{dE}{dx}}r_Xv_p^2}{2 \rho \sigma_X c_p \alpha^2 T_\te{melt}}}}
+t_{\te{fast}} = \f{\alpha}{v_p^2}W\p{{\f{\abs{\frac{dE}{dx}}v_p^2}{2 \rho \sigma_x c_p \alpha^2 T_\te{melt}}}}
 \end{align}
@@
 \begin{align}
-r_\te{fast melt} =  \frac{2\alpha}{v_p}\sqrt{W\p{{\f{\abs{\frac{dE}{dx}}r_{X}v_p^2}{2 \rho \sigma_X c_p \alpha^2 T_\te{melt}}}}\ln\ps{\p{\frac{\abs{\frac{dE}{dx}}r_{X}v_p^2}{2 \rho \sigma_X c_p \alpha^2 T_\te{melt}}}\frac{1}{W\p{{\f{\abs{\frac{dE}{dx}}r_{X}v_p^2}{2 \rho \sigma_X c_p \alpha^2 T_\te{melt}}}}
+r_\te{fast melt} =  \frac{2\alpha}{v_p}\sqrt{W\p{{\f{\abs{\frac{dE}{dx}}v_p^2}{2 \rho \sigma_x c_p \alpha^2 T_\te{melt}}}}\ln\ps{\p{\frac{\abs{\frac{dE}{dx}}v_p^2}{2 \rho \sigma_x c_p \alpha^2 T_\te{melt}}}\frac{1}{W\p{{\f{\abs{\frac{dE}{dx}}v_p^2}{2 \rho \sigma_x c_p \alpha^2 T_\te{melt}}}}
 }}}\,.
@@
 \begin{align}
-r_\te{fast melt} =\frac{2\alpha}{v_p}W\p{{\f{\abs{\frac{dE}{dx}}r_{X}v_p^2}{2 \rho \sigma_X c_p \alpha^2 T_\te{melt}}}} = \frac{2\alpha}{v_p}W\p{\frac{r_{X}v_{X} v_p^2}{2 c_p \alpha^2 T_\te{melt}}}.
-\end{align}
-which is on the order of micrometers to tenths of micrometers for most marco radii which, for $r_X > 10^-8$ results in $r_\te{fast melt} < r_X$ which is something of a problem.
-
-This either suggests that much of the melting occurs once the temperature field is expanding slower than the speed of sound, and that the expansion speed of the melt zone slows down very quickly or that the material parameters -- especially $\alpha$ -- are far from constant (or may not even be well defined) in our case.
+r_\te{fast melt} =\frac{2\alpha}{v_p}W\p{{\f{r_X\abs{\frac{dE}{dx}}v_p^2}{2 \rho \sigma_x c_p \alpha^2 T_\te{melt}}}} = \frac{2\alpha}{v_p}W\p{\frac{r_Xv_{X} v_p^2}{2 c_p \alpha^2 T_\te{melt}}}.
+\end{align}
+which is on the order of micrometers to tenths of micrometers for our case.
+
+Conceptually, it would seem that $r_\te{fast melt}$ should be added to $r_\te{Macro}$ to give the full extent of material melted down.
 

### 2016-08-25 Draft.tex

@@
 If there are $n$ lunar seismometers, suppose each occupies its own HEALPix pixel.
-Then $\scr N = n/12\times 2^{n_\te{side}}$ is the fraction of the moon which could potentially measure a signal.
-If $\scr M$ Macros impact the moon, the likelihood of any of them being detected is
+Define $\scr N = 12\times 2^{n_\te{side}}$.
+Define $m = \scr F\scr N$, the average number of pixels with detectable frequency.
+If $n+m\geq \scr N$, then detection is guaranteed.
+Otherwise, if $\scr M$ Macros impact the moon, the likelihood of any of them being detected is
 \begin{align}
-\scr P = 1-\ps{(1-\scr F)(1-\scr N)}^\scr M\,.
+\scr P = 1-\ps{\f{(\scr N-n)!(\scr N-m)!}{\scr{N}!(\scr N-n-m)!}}^{\scr M}\,.
 \end{align}

### 2016-08-25 Macro Impacts Revised.tex
Just to fix the inconsistencies of the various versions
A few aesthetic points

--- 2016-08-24 Macro Impacts Revised.tex
@@
 \pagebreak
-Note: The following is based on the above written by David, and modified by Josh (David, feel free to take whatever you'd like and apply to the above):
+Note: The following is based on some of the above written by David, which has been modified and completed by Josh.
 
@@
 \end{align}
-where we've taken the positive branch of the square root, since we only care about the melt radius increasing. Then taking the derivative w.r.t to time gives
+where the positive branch of the square root has been taken as this is the physical result. Then taking the derivative w.r.t to time gives
 \begin{align}
@@
 \end{align}
-Since, for the parameters at hand, $\ln\p{\f{\abs{\frac{dE}{dx}}r_X}{2 \rho \sigma_X c_p \alpha T_\te{melt} t}}$ is at least of order $10 \gg 1$ it is a reasonable approximation to take
+Since, for the parameters at hand, $\ln\p{\f{\abs{\frac{dE}{dx}}r_X}{2 \rho \sigma_X c_p \alpha T_\te{melt} t}}$ is at least of order $10 \gg 1$, it is a reasonable approximation to take
 \begin{align}
@@
 \end{align}
-Notice that this has the form of $\sqrt{W(x)\ln\p{{\frac{x}{W(x)}}}}$, which gives $\sqrt{W(x)^2}$ by the identity $\ln\p{{\frac{x}{W(x)}}} = W(x)$ which holds when $x \geq -1/e$r which is true for the parameters at hand.
+Notice that this has the form of $\sqrt{W(x)\ln\p{{\frac{x}{W(x)}}}}$, which gives $\sqrt{W(x)^2}$ by the identity $\ln\p{{\frac{x}{W(x)}}} = W(x)$ which holds when $x \geq -1/e$ which is true for the parameters at hand.
 Thus, we have,
@@
 \end{align}
-This expression for $r_\te{fast melt}$ is highly sensitive to $\alpha$ and $v_p$ and relatively insensitive to the macro's parameters.
+(Note the last equality follows from a result David found of $\frac{v_{X}^2}{c_p} =  \frac{\rho \sigma_X v_X^2}{\rho \sigma_X c_p} = \frac{\abs{\frac{dE}{dx}}}{\rho \sigma_X c_p}$).
+\\\
+Notice that this expression for $r_\te{fast melt}$ is highly sensitive to $\alpha$ and $v_p$ and relatively insensitive to the macro's parameters.
 

### 2016-08-25 Macro Impacts Revised.tex
One other typo fixed

@@
 
-It gives results on the order of micrometers to tenths of micrometers for most marco radii which, for $r_X > 10^-8$ results in $r_\te{fast melt} < r_X$ which is a bit of a problem.
+It gives results on the order of micrometers to tenths of micrometers for most marco radii which, for $r_X > 10^{-8}$ results in $r_\te{fast melt} < r_X$ which is a bit of a problem.
 

### 2016-08-29 Draft.tex
Update

@@
-\documentclass[prd,reprint,10pt,tightenlines]{revtex4-1}
+\documentclass[prd,reprint,10pt]{revtex4-1}
 
@@
 \title{New seismological constraints on the available parameter space of macroscopic dark matter}
-\author{David Cyncynates \\ dcc57@case.edu}
-\date{\today}
+\author{David Cyncynates}
+\affiliation{Physics Department\\ Case Western Reserve University\\ Cleveland, Ohio 44106-7079, USA}
+
 \begin{abstract}
 Recent limits have been proposed constraining the available parameter space of macroscopic dark matter (Macros).
-Previous limits were based on the energy deposition of Macros being akin to that of a nuclear bomb.
-Our estimates take into account the effect of seismometer sensitivity and energy distribution across frequencies, anelastic attenuation, geometric effects, internal anisotropy of the Earth or Moon, as well as energy loss due to melting.
-We produce new constraints on the Macro parameter space based on the total lunar seismic event rate.
+These limits were based on the energy deposition of Macros into low frequency seismic modes being akin to that of a nuclear or chemical bomb.
+We show that this assumption does not hold by considering the mechanism by which the Macro impact generates seismic waves.
+Our new estimates take into account the effect of seismometer sensitivity and energy distribution across frequencies, anelastic attenuation, geometric effects, internal anisotropy of the Earth or Moon, as well as energy loss due to melting.
+We produce limits on the parameter space of Macros which can be ruled out by seismic event rate.
 \end{abstract}
@@
 \section{Introduction}
-
+Teplitz \textit{et al.} \cite{banerdt2005seismic} have suggested that the energy deposition into the $1\,\te{Hz}$ range from a nuclearite (Macro) impact should be $0.05$ of the total energy deposition.
+This, as shown in section II A, is a gross overestimate even compared to our own generous overestimation.
+We produce a more accurate model of the seismic effects of Macro impacts, including in our model the effects of geometric lensing, stratification of the Moon, anelastic attenuation, and geometric attenuation.
+The result of this analysis is an upper bound on the event rate that would be measured by the Apollo lunar seismometers.
+We also include a simple argument which demonstrates that a large portion of the available parameter space cannot be ruled out by seismological constraints.
 \section{The Seismic Source}
-\subsection{The Melt Wave}
-The section of parameter space we are interested in contains Macros whose cross sectional area is small enough that the energy lost due to the macro displacing rock is negligible compared to the total energy deposition.
-When this scenario holds, the energy deposited by the Macro can be treated as heating a column of cross sectional area $\sigma_X$ and length $\ell$.
-
-We immediately see that this corresponds to a temperature distribution
-\begin{align}
-T(r,0) = \f{v_X^2}{c_p}\theta(r_X-r)\,.
-\end{align}
-It is reasonable to approximate this by a $\delta$ source of the form
-\begin{align}
-T(r,0) = \f{v_X^2}{c_p}r_X\delta(r)\,.
-\end{align}
-The diffusion equation then provides that the radius of the melt front is
-\begin{align}
-r_\te{melt}= \sqrt{4t\alpha\ln\ps{\f{r_X v_X^2}{2 c_p t \alpha T_\te{melt}}}}\,,
-\end{align}
-where $\alpha$ is the thermal diffusivity. 
 \subsection{Seismic Wave Generation}
 The energy from the initial impact generates a column of melted rock.
-The super-heated rock, held at constant volume, generates a pressure which sources the seismic waves that can be felt at detectors.
-Assuming the Macro's velocity is insignificantly changed by its encounter with the Moon, we should expect it to source a pressure of the form
+The super-heated rock, held at constant volume, generates a pressure which sources the seismic waves that can be measured at detectors.
+Macro's with velocity insignificantly changed by their encounter with the Moon source a pressure of the form
 \begin{align}
@@
 \end{align}
-where $f$ is an analytic function whose range is a subset of $[-1,1]$, and $p_0$ is the maximum pressure of the source.
-Moreover, after a short time, the pressure should still be of this form, since the anisotropy of the Moon is significant only on very large scales.
+where $f$ is an analytic function whose range is a subset of $[-1,1]$, and $p_0$ is the maximum differential pressure in this region.
+After a short time, the pressure is still of this form, since the anisotropy of the Moon is significant only on large scales.
 
-The seismometers on the moon have a net useful range (the union of all useful ranges of all seismometers) of $0.004-20\text{\,Hz}$ and are sensitive to displacements as small as $0.3\text{\,nm}$.
-The energy measured by seismometers is a subset of that in the net useful range.
+The seismometers on the moon have a net useful range of up to $20\,\te{Hz}$ and are sensitive to displacements as small as $0.3\,\text{nm}$ \cite{latham1973lunar}.
+Therefore, we only calculate the energy contained in the modes of frequency less than $20\,\te{Hz}$.
 
@@
 \begin{align}
-P = \f{4\pi p_0}{k\cos\theta}\sin\p{\f{h k\cos\theta}{2}}F+\scr O(k^0)\,,
+P = \f{4\pi p_0}{k\cos\theta}\sin\p{\f{h k\cos\theta}{2}}F+\scr O((kb)^0)\,,
 \end{align}
-where $\theta,\phi$ are the momentum space polar angles, $F = b^2f_1(b)-a^2f_1(a)$ and
+where $\theta,\phi$ are the momentum space polar angles, $k$ is the magnitude of the wave-vector, $F = b^2f_1(b)-a^2f_1(a)$ and
 \begin{align}
@@
 \end{align}
-where $u$ is the displacement field, $\rho,\lambda,\mu$ are the density and Lam\`e coefficients respectively.
+where $u$ is the displacement field, and $\rho,\lambda,\mu$ are the density and Lam\`e coefficients respectively.
 For $p$-waves, $p = -K\nabla\cdot u$ where $K$ is the bulk modulus.
-Define $\kappa = K^2/(\lambda + 2\mu)$ Fourier transforming, we find that $U = \I P\vec k/K k^2$ and hence
+Define $\kappa = K^2/(\lambda + 2\mu)$.
+It follows that
 \begin{align}
@@
 \end{align}
-Since a seismometer can only detect lower frequency modes, the detectible energy is given by 
+Since a seismometer can only detect lower frequency modes, the detectible energy is
 \begin{align}
@@
 \begin{align}
-\notag E_k&=\f1\kappa 2p_0^2F^2\ell k^2\\\notag&\times\p{\f{\sin(\ell k)+k\ell(\cos(\ell k)-2)}{\ell^2 k^2}+\te{Si}(\ell k)}+\scr O(k^4)\,.
+\notag E_k&=\f1\kappa 2p_0^2F^2\ell k^2\\\notag&\times\p{\f{\sin(\ell k)+k\ell(\cos(\ell k)-2)}{\ell^2 k^2}+\te{Si}(\ell k)}+\scr O((kb)^4)\,.
 \end{align}
@@
 
-Although the pressure initial conditions are fixed by the fast behavior of the melt wave, linear elasticity may not be appropriate for the pressures involved.
-As the pressure wave propagates, it will be geometrically attenuated until the pressure differential is within the linear regime.
-Given that the Macro travels at super-sonic speeds, it will generate a shock wave.
-Often these shock waves have pressure profiles resembling a right triangle i.e.
+Although the initial pressure is fixed by the fast behavior of the melt wave, linear elasticity may not be appropriate for the pressures near the source.
+As the pressure wave propagates outward, it is geometrically attenuated until the pressure differential is within the linear regime.
+The Macro travels at super-sonic speeds and will generate a shock wave.
+Shock waves typically evolve to pressure fronts resembling a right triangle \cite{forbes2013shock} i.e.
 $f = \p{r - r_0}/\Delta r$ where $a = r_0$ and $b = r_0 + \Delta r$.
 This shape is also chosen for its simplicity.
-In this case $f_1(x) = \p{2 x-3r_0}/6\Delta r$, and hence
+In this case $f_1(x) = \p{2 x-3r_0}/6\Delta r$ and
 \begin{align}
@@
 \end{align}
-and loses some energy due to melting. Thus, the pressure waves have initial energy
+and loses some energy from phase changes of its surroundings. Thus, the pressure waves have initial energy
 \begin{align}
@@
 $r_0$ demarcates the end of the non-linear regime.
-As the length of the pulse tends to zero, the non-linear regime extends without bound.
-We require $p_0\leq 10^8\te{\,Pa}$, corresponding to an order of magnitude below the elastic limit of granite.
-A lower bound on $r_0$ is 0, corresponding to entirely linear behavior.
-This, in turn, imposes an upper bound on the pulse width
+The non-linear regime is characterized by faulting and fracturing.
+Brittle failure for granite occurs at stress exceeding $3\times 10^8\,\te{Pa}$ \cite{lockner200232}.
+We thus take $p_0 = \min\p{10^8\,\te{Pa},p_\te{source}}$.
+Note that $p_\te{source}\gg 10^8\,\te{Pa}$ for Macros that we will consider.
+By ignoring the effects of the non-linear regime on the seismic waves, we are grossly overestimating the energy that could reach detectors.
+
+A lower bound on $r_0$ is 0, corresponding to entirely linear behavior. This, in turn, imposes an upper bound on the pulse width
 \begin{align}
@@
 \end{align}
-It is important to remember that these expressions only hold for $k(r_0+\Delta r)\ll 1$, however they will always provide an over-estimate of the fraction of detectable energy.
-Moreover, this condition holds for a wide variety of reasonable parameters.
+It is important to note that these expressions only hold for $k(r_0+\Delta r)\ll 1$, however they will always provide an over-estimate of the fraction of detectable energy.
+Moreover, this condition holds for a wide variety of relevant parameters.
+Taking $\epsilon_\te{melt} = 0$, $\rho = 3.3\times 10^3\,\te{kg m}^{-3}$, $v_X = 2.5\times 10^5\,\te{m s}^{-1}$, $\kappa = 5.5\times 10^{10}\,\te{Pa}$, and $k = 1.5\times 10^{-2}\,\te{m}^{-1}$ \cite{garcia2011very}, we obtain $\Xi<4.5\times 10^4 (\sigma_X/\te{m}^2)$.
+To obtain the figure that Teplitz \textit{et al.} have used, one must take $\sigma_X >10^{-6}\te{m}^2$, which is rather large.
+
+It is important to note that $p_0\to 0$ does not imply $\Xi\to\infty$, since $p_0$ is implicitly a function of $\epsilon$ when $p_0<10^8\,\te{Pa}$.
+In this case, the ratio $\epsilon/p_0^2$ is always finite since $\epsilon\propto p_0^2$.
 
 \section{Seismic Wave Propagation}
-The velocity of $p$-waves as a function of radius within the Earth and Moon (and presumably other spherical rocky celestial bodies) is of the form $v = a^2 - b^2 r^2$.
+The velocity of $p$-waves as a function of distance from the center $r$ of the Earth and Moon (and presumably other spherical rocky celestial bodies) is of the form $v = a^2 - b^2 r^2$ \cite{garcia2011very}\cite{dziewonski1981preliminary}.
 Using Snell's law, we obtain the differential equations for the trajectory of $p$-wave rays within such bodies
@@
 \end{align}
-where $r$ is the radial coordinate of the ray, $\theta$ is the polar angle of the ray measured from the center of the body, and $p_\te{ray}$ is the ray parameter, whose value is fixed along a ray trajectory.
+where $r$ is the radial coordinate of the ray, $\theta$ is the polar angle of the ray measured from the center of the body, and $p_\te{ray}$ is the ray parameter, which is fixed along a ray trajectory.
 These equations can be integrated.
@@
 \end{align}
-\textit{A priori} these are geodesics on the Poincar\'e disc of radius $\f ab$ based on the form of $v$.
+\textit{A priori} these are geodesics on the Poincar\'e disc of radius $\f ab$, which is easily seen from the form of $v$.
 
@@
 \end{align}
-The VPREMOON model provides piecewise constant data for $Q$, so it is reasonable to subdivide the moon further into strata of different $Q$.
+The VPREMOON Model \cite{garcia2011very} provides piecewise constant data for $Q$, so it is reasonable to subdivide the moon further into strata of different $Q$.
 For propagation within a given layer $i$, the factor $\te{Att}$ is given by $\Delta t_i v_i/Q_i$, where we take $v_i$ to be the average velocity within a given strata.
-For the case of the Earth and Moon, this is a good approximation since $v$ doesn't change much within a given layer of constant $Q$.
+For the case of the Earth and Moon, this is a good approximation since $v$ doesn't change significantly within a given layer of constant $Q$.
 Thus, the amplitude of a ray can be computed by knowing the two numbers
@@
 \section{Seismic Wave Detection}
-The seismometers on the Moon are sensitive to displacements as small as $0.3\te{\,nm}$.
-We calculate the displacement due to each ray, and describe how they add.
-Consider a $p$-wave traveling towards positive $x$ and of compact support $S$ in the plane normal to to its motion.
-Denote $A =\int_S\diff y\diff z$ The displacement field is
+Consider a $p$-wave traveling towards positive $x$ and of compact support $S$ in the plane normal to to its motion. Denote $A =\int_S\diff y\diff z$ The displacement field is
 \begin{align}
@@
 \end{align}
-As before, we denote
+As before, we denote the energy in the low frequency spectrum
 \begin{align}
@@
 \end{align}
-(28) is impossible to integrate when $E_k$ consists of the energies of two different rays, each with different attenuation factors.
-When this case arrises, we average $\te{Att}$ among the coincident rays.
-For the lowest frequency modes $f<20\te{Hz}$, $\te{Att} k$ order 10 at most, and does not contribute significantly to $u$.
-Taking $\te{Att} = 0$, we have
+(25) is impossible to integrate when $E_k$ consists of the energies of two different rays, each with different attenuation factors.
+If attenuation were important, we may average $\te{Att}$ among the coincident rays and obtain an approximate expression.
+However, since we only wish to consider the lowest frequency modes, $f<20\te{Hz}$, the suppression $\te{Att} k$ is order unity, and does not contribute significantly to $u$.
+Taking $\te{Att} = 0$, the displacement caused by the incident $p$-wave is bounded above by
 \begin{align}
-\abs{u(\vec x,t)}\leq\sqrt{\f{2}{\rho v_p^2 A}}\sqrt{\f{\te{Ref}\,\Xi E}{\te{Att}}}\f1k\te{Erf}\ps{\sqrt{\f{\te{Att}\,k}{2}}}\,.
+\abs{u(\vec x,t)}\leq\sqrt{\f{4\te{Ref}\,\Xi E}{\pi k\rho v_p^2 A}}\,.
 \end{align}
 \section{Simulation}
-The simulation is broken down into two natural parts: data generation and data analysis.
-The data generation consists of propagating a large number of rays to approximate a line source of $p$-waves and tracking the positions and energies at which they contact the surface of the moon.
-The data analysis makes use of HEALPix to approximate the energy density on the sphere and then makes use of section IV to measure displacements.
+In previous works, e.g.
+\cite{banerdt2005seismic}, the homogeneous Earth and Moon models have been used to place constraints of the parameter space of macroscopic dark matter.
+This approach neglects lensing which occurs because of the velocity gradient and the spherical boundaries of strata, and neglects the energy losses from reflection and refraction across these boundaries.
+We use the analysis in section III to propagate rays, each carrying a fraction of the total energy deposited by the Macro, to the boundary of the Moon.
+We then use HEALPix to create an intensity map of the lunar surface for a representative sample of Macro impacts.
+We then convert the intensity maps to displacement maps, and using the sensitivity of the lunar seismometers, we obtain an average event rate that the lunar seismometers would measure.
 \subsection{Data Generation}
-To generate the data, we consider a Macro trajectory which passes a distance $D$ from the center of the moon.
-This trajectory has a length $L$.
-Along this trajectory, we consider a set of $M$ points, from each of which we shoot $N$ rays, each endowed with $E_m = \rho(r_{m})\sigma_Xv_X^2 L/(MN)$ energy, where $m\in\{1,\dots,M\}$ labels the point.
+We consider a Macro trajectory which passes a distance $D$ from the center of the moon.
+The Macro trajectory has length $L$, and along its trajectory we consider a set of $M$ points.
+From each of these points we propagate $N$ randomly oriented rays, each endowed with $E_i = \rho(r_{i})\sigma_Xv_X^2 L/(MN)$ energy, where $i\in\{1,\dots,M\}$ labels the point, and $\rho$ is taken to be a function of the radius.
 Because of the spherical symmetry, each ray is confined to a subspace of two dimensions.
 We use the trajectories in section III to propagate the rays.
-Since the moon is stratified, we must halt the propagation at the boundary of each layer and reflect/transmit rays.
-During a ray's propagation through a given stratum $\Delta t_i$ is recorded and added to $\Delta t$, $\te{ATT}_i$ is recorded and added to $\te{ATT}$, and $\te{REF}_i$ is recorded at the boundary and is multiplied by $\te{REF}$.
-Each time a ray makes contact with the surface of the Moon, its position, $\te{ATT}$, $\te{REF}$, $\Delta t$, and $E_m$ are recorded.
-The final data is a table of these values corresponding to each ray intersection with the surface.
-We iterate 16 times since it takes 16 iterations for a ray to pass entirely through the VPREMOON model stratification.
+Since the moon is stratified, we must halt the propagation at the boundary of each layer to reflect and transmit rays.
+During a ray's propagation through a given stratum, its time spent in that layer $\Delta t_i$ is recorded, the attenuation factor in that layer $\te{Att}_i$ is recorded, and the reflection/refraction coefficient $\te{Ref}_i$ is recorded.
+Each time a ray makes contact with the surface of the Moon, its position, $\te{Att}$, $\te{Ref}$, and $\Delta t$ are recorded.
+The data produced by the propagation routine is a table of these values and the corresponding surface coordinates, as well as density at the source, $\kappa$ at the source, and $p$-wave velocity at the source.
+In this model, it takes 16 iterations to propagate a ray from one side of the moon to the other.
+Rays which propagate from one side of the moon to the other only after 16 iterations will be weak from undergoing 16 refractions.
+Thus in order to save on computation time, it is reasonable to reduce the number of iterations to 9.
 \subsection{Data Analysis}
-We now convert the position data to HEALPix coordinates for a given $n_\te{side}$.
-Define $A_\te{pix} = 4\pi R_\te{moon}^2/12\times 2^{n_{\te{side}}}$, the area of a HEALPix pixel.
-The time it takes a ray to cross a HEALPix pixel can be estimated $t_\te{crossing}^2 = A_\te{pix}/\pi v_p^2$.
+Analysis begins by converting the position data to HEALPix coordinates for a given $n_\te{side}$.
+We pick $n_\te{side} = 4$ since this corresponds to an angular resolution of 7 degrees, which accounts for the effects of diffraction about the strata boundaries.
+Define $A_\te{pix} = 4\pi R_\te{moon}^2/n_\te{pix}$ the area of a HEALPix pixel, where $n_\te{pix} = 12\times 2^{n_{\te{side}}}$.
+The time it takes a ray to cross a HEALPix pixel can be estimated $t_\te{crossing}^2 = A_\te{pix}/\pi v_\te{surface}^2$.
+According to VPREMOON, $v_\te{surface} = 1\,\te{km s}^{-1}$.
 Rays that contact a pixel within $t_\te{crossing}$ of one another are considered to add constructively.
-Since the integral in section IV is unreasonable to do for more than one ray, we make use of Minkowski's inequality and obtain an upper bound on displacement by simply adding the displacements from each ray.
-We suppose that each ray distributes its energy evenly over the area of the HEALPix pixel, and thus set $A = A_\te{pix}$.
-This is a good approximation when $N$ is the same as the number of HEALPix pixels.
+Since the integral in section IV is unreasonable to do for more than one ray, we average $\te{Att}$ over the coincident rays.
+We require that each ray distributes its energy evenly over the area of the HEALPix pixel, and thus set $A = A_\te{pix}$.
+This is a good approximation when $N=n_\te{pix}$, since the average angular separation of the rays at the source corresponds to the average angular separation of the HEALPix pixels.
 
-Using (29) we compute an upper bound for the displacement within a given HEALPix pixel, and compare that to the sensitivity of the lunar seismometers.
-If the displacement is less than the sensitivity then the pixel is marked undetectable and is otherwise marked detectable.
-The number of detectable pixels is divided by the total number of pixels to obtain the fraction $\scr F_D$ of the lunar surface which could plausibly register a signal.
+Using (27) we compute an upper bound for the displacement within a given HEALPix pixel, and compare that to the sensitivity of the lunar seismometers given in \cite{latham1973lunar}.
+If the calculated displacement is less than the seismometer sensitivity then the pixel is marked undetectable and is otherwise marked detectable.
+The number of detectable pixels is divided by the total number of pixels to obtain the fraction $\scr F_D$ of the lunar surface with a detectable signal for a Macro making closest approach $D$ to the lunar center.
 
-This procedure is repeated for 17 values of $D$ spaced evenly by $100\,\te{km}$. The average fraction of detectable surface area is then
+This procedure is repeated for 17 values of $D$ spaced evenly by $100\,\te{km}$. The average fraction of detectable surface area is then approximately
 \begin{align}
@@
 \end{align}
-If there are $n$ lunar seismometers, suppose each occupies its own HEALPix pixel.
-Define $\scr N = 12\times 2^{n_\te{side}}$.
-Define $m = \scr F\scr N$, the average number of pixels with detectable frequency.
-If $n+m\geq \scr N$, then detection is guaranteed.
+If there are $n$ lunar seismometers, we suppose that each occupies its own HEALPix pixel.
+Define $m = \scr Fn_\te{pix}$, the average number of pixels with detectable frequency.
+If $n+m\geq n_\te{pix}$, then detection is guaranteed.
 Otherwise, if $\scr M$ Macros impact the moon, the likelihood of any of them being detected is
 \begin{align}
-\scr P = 1-\ps{\f{(\scr N-n)!(\scr N-m)!}{\scr{N}!(\scr N-n-m)!}}^{\scr M}\,.
+\scr P &= 1-\ps{\f{(n_\te{pix}-n)!(n_\te{pix}-m)!}{n_\te{pix}!(n_\te{pix}-n-m)!}}^{\scr M}\,.
 \end{align}
-
+\subsection{Analytic Upper Bound}
 If the energy of a ray from every point along the line hitting a single pixel (with no reflection, refraction, or attenuation) is less than the displacement threshold, there is no chance of detection and no need to run the simulation.
 (If two rays from the same point on the line source hit the same pixel as $n_\te{side}\to\infty$, then they must be the same ray).
+Thus, we bound the displacement by
 \begin{align}
@@
 \end{align}
-This is independent of the choice of partition. For the triangle wave, we need not test $\sigma_X\leq 4\times 10^{-11}\te{m}^2$.
+This expression is independent of the choice of $n_\te{side}$. For the triangle wave, we need not test $\sigma_X\leq 4\times 10^{-11}\te{m}^2$.
 \section{Results}
+Data has been generated but not run through the analysis routine yet. Preliminary results suggest that the computer analysis will not produce results much stronger than (30).
+\section{Conclusion}
+For Macros with mass to area ratio sufficient to pass nearly unimpeded through the Moon, and in particular nuclear dense objects such as strange quark nuggets, we have demonstrated that seismological constraints are insufficient to rule them out.
+In order to use the Moon as a low noise detector for high density Macros, it would be necessary to increase the usable frequency range of seismometers to several hundred Hertz.
+However, since the Moon (and Earth) preferentially attenuate higher frequency modes, it is unlikely that measuring high frequencies would greatly improve sensitivity to these types of impacts.
 
-\section{Conclusion}
+On the other hand, increasing the lunar seismometer sensitivity to small displacements would increase the volume of Macro parameters one could rule out.
+That said, it is uncertain whether seismic noise at such small displacements would make Macro impacts indistinguishable from the background.
+\section{Acknowledgements}
+The author would like to thank SOURCE for supporting this research.
+\bibliography{Macro-Impact}{}
+\bibliographystyle{apsrev4-1}
 \end{document}

### 2016-08-30 Draft.tex
Update

@@
 \section{Conclusion}
-For Macros with mass to area ratio sufficient to pass nearly unimpeded through the Moon, and in particular nuclear dense objects such as strange quark nuggets, we have demonstrated that seismological constraints are insufficient to rule them out.
-In order to use the Moon as a low noise detector for high density Macros, it would be necessary to increase the usable frequency range of seismometers to several hundred Hertz.
-However, since the Moon (and Earth) preferentially attenuate higher frequency modes, it is unlikely that measuring high frequencies would greatly improve sensitivity to these types of impacts.
-
-On the other hand, increasing the lunar seismometer sensitivity to small displacements would increase the volume of Macro parameters one could rule out.
+For Macros with density sufficient to pass nearly unimpeded through the Moon, and in particular nuclear dense objects such as strange quark nuggets, we have demonstrated that seismological constraints are insufficient to rule them out.
+Since the Moon (and Earth) preferentially attenuate higher frequency modes, it is unlikely that measuring high frequencies would greatly improve sensitivity to these types of impacts.
+On the other hand, increasing the lunar seismometer sensitivity to small displacements would allow one to use seismological evidence to rule out high density Macros.
 That said, it is uncertain whether seismic noise at such small displacements would make Macro impacts indistinguishable from the background.
@@
 The author would like to thank SOURCE for supporting this research.
+\section{Summer Reflection}
+My research this summer will be very important when I make my case to graduate schools that I am capable of doing independent research and problem solving.
+This project will likely be developed into my capstone, and we will try to publish this work.
+For next year's students, drink lots of coffee.
 \bibliography{Macro-Impact}{}

### 2016-08-30 P423 HW1.tex
Update

\documentclass{article}

% Packages

\usepackage{fullpage}
\usepackage{amsmath, amsthm, amsfonts, amssymb, mathtools, calrsfs, tensor, physics, MnSymbol,tikz-cd}
\usepackage[mathscr]{euscript}
\usepackage{graphicx}
\graphicspath{ {images/} }
\usepackage{enumitem}
\setlist[description]{font=\normalfont}

% Custom Commands

\newcommand*\diff{\mathop{}\!\mathrm{d}}
\newcommand*\Diff[1]{\mathop{}\!\mathrm{d^#1}}
\newcommand*\nrml{\vartriangleleft}
\newcommand*\scr[1]{\mathscr{#1}}
\newcommand*\bb[1]{\mathbb{#1}}
\newcommand*\la{\langle}
\newcommand*\ra{\rangle}
\newcommand*\gen[1]{\langle #1 \rangle}
\newcommand*\x{\times}
\newcommand*\st{\text{ s.t. }}
\newcommand*\ord[1]{\left\vert#1\right\vert}
\newcommand*\aut{\text{Aut}}
\newcommand*\lcm{\text{lcm}}
\newcommand*\mcal{\mathcal}
\newcommand*\es{\emptyset}
\newcommand*\im{\text{ Im }}
\newcommand*\N{\mathbb N}
\newcommand*\Z{\mathbb Z}
\newcommand*\R{\mathbb R}
\newcommand*\Q{\mathbb Q}
\newcommand*\C{\mathbb C}
\newcommand*\te[1]{\text{#1}}
\newcommand*\en[1]{\begin{enumerate}#1\end{enumerate}}
\newcommand*\e{\varepsilon}
\newcommand*\p[1]{\left(#1\right)}
\newcommand*\ps[1]{\left[#1\right]}
\newcommand*\pc[1]{\left\{#1\right\}}
\newcommand*\f[2]{\frac{#1}{#2}}
\newcommand*\mat[2]{\left(\begin{array}{#1}#2\end{array}\right)}
\newcommand*\ocross{\otimes}
\newcommand*\I{\te{i}}
\newcommand*\pd[3]{\frac{\partial^{#3} #1}{\partial {#2}^{#3}}}
\newcommand*\td[3]{\frac{d^{#3}#1}{d #2^{#3}}}
\newcommand*\m{\te{Mat}}
\newcommand*\End{\te{End}}
\newcommand*\irr{\te{Irr}}
\newcommand*\sgn{\te{sgn}}
\newcommand*\pn[2]{\left\|#1\right\|_{#2}}
\newcommand*\esssup{\te{ess sup}}
\newcommand*\essinf{\te{ess inf}}

% Miscellaneous

\newtheorem{theorem}{Theorem}
\usetikzlibrary{matrix,arrows,decorations.pathmorphing}

% Title
\title{P423 Homework 1}
\author{David Cyncynates \\ dcc57@case.edu}
\date{\today}

\begin{document}
\maketitle
\paragraph{1.3} The following are identities computed through the Levi-Civita symbol.
\begin{description}
\item{(a)} $(\vec a\times\vec b)\cdot(\vec c\times\vec d) = (\vec a\cdot\vec c)(\vec b\cdot\vec d)-(\vec a\cdot\vec d)(\vec b\cdot\vec c)$.
\begin{align}
(\vec a\times\vec b)\cdot(\vec c\times\vec d)&=(\epsilon_{ijk}a_j b_k)(\epsilon_{ilm}c_l d_m)\,,\\
&=\epsilon_{ijk}\epsilon_{ilm}(a_j b_k c_l d_m)\,,\\
&=\p{\delta_{jl}\delta_{km}-\delta_{jm}\delta_{kl}}(a_j b_k c_l d_m)\,,\\
&=a_j b_k c_j d_k-a_j b_k c_k d_j\,,\\
&=(a_j c_j) (b_k d_k)-(a_j d_j) (b_k c_k)\,,\\
&=(\vec a\cdot\vec c)(\vec b\cdot\vec d)-(\vec a\cdot\vec d)(\vec b\cdot\vec c)\,.
\end{align}
\item{(b)} $\nabla\cdot(\vec f\times\vec g) = \vec g\cdot(\nabla\times\vec f)-\vec f\cdot(\nabla\times\vec g)$. Consider the components of the LHS
\begin{align}
\ps{\nabla\cdot(\vec f\times\vec g)}_i &=\partial_i(\epsilon_{ijk} f_j g_k)\,,\\
&= \epsilon_{ijk}\partial_i(f_j g_k)\,,\\
&= \epsilon_{ijk}(g_k\partial_if_j +f_j \partial_i g_k)\,,\\
&=g_i (\epsilon_{ijk}\partial_j f_k) - f_i (\epsilon_{ijk}\partial_j g_k)\,,\\
&=g_i \ps{\nabla\times \vec f}_i- f_i \ps{\nabla\times\vec g}_i\,,\\
&=\vec g\cdot \p{\nabla\times \vec f}- \vec f\cdot \p{\nabla\times\vec g}\,.
\end{align}
The negative sign on the second term in equation 10 is from exchanging indices by an odd permutation, while the first term is acted on by an even permutation.
\item{(c)} $(\vec a\times\vec b)\times(\vec c\times\vec d) = (\vec a\cdot\vec c\times\vec d)\vec b-(\vec b\cdot\vec c\times\vec d)\vec a$. Consider the components of the LHS
\begin{align}
\ps{(\vec a\times\vec b)\times(\vec c\times\vec d)}_i&=\epsilon_{ijk}\ps{\vec a\times\vec b}_j\ps{\vec c\times\vec d}_k\,,\\
&=\epsilon_{ijk}\epsilon_{jmn}\epsilon_{kpq}a_mb_nc_p d_q\,,\\
&=\p{\delta_{km}\delta_{in}-\delta_{kn}\delta_{im}}\epsilon_{kpq}a_mb_nc_p d_q\,,\\
&=\delta_{km}\delta_{in}\epsilon_{kpq}a_mb_nc_p d_q-\delta_{kn}\delta_{im}\epsilon_{kpq}a_mb_nc_p d_q\,,\\
&=\p{a_k\epsilon_{kpq}c_p d_q}b_i-\p{b_k\epsilon_{kpq}c_p d_q}a_i\,,\\
&=\p{a_k\ps{\vec c\times\vec d}_k}b_i-\p{b_k\ps{\vec c\times\vec d}_k}a_i\,,\\
&=\p{\vec a\cdot \vec c\times\vec d}b_i-\p{\vec b\cdot \vec c\times\vec d}a_i\,,\\
&=\ps{\p{\vec a\cdot \vec c\times\vec d}\vec b-\p{\vec b\cdot \vec c\times\vec d}\vec a}_i\,.
\end{align}
\item{(d)} $(\vec\sigma\cdot\vec a)(\vec \sigma\cdot\vec b) = \vec a\cdot\vec b + \I\vec\sigma\cdot(\vec a\times\vec b)$. This follows immediately since the Pauli matrices are a 2 dimensional representation of the Quaternion group over $\C$. Or rather:
\begin{align}
(\vec\sigma\cdot\vec a)(\vec \sigma\cdot\vec b)&=\sigma_ia_i\sigma_jb_j\,,\\
&=\sigma_i\sigma_ja_ib_j\,,\\
&=\p{\delta_{ij}+\I\epsilon_{ijk}\sigma_k}a_ib_j\,,\\
&=a_ib_i+\I \sigma_i \epsilon_{ijk}a_jb_k\,,\\
&=a_ib_i+\I\vec\sigma\cdot (\vec a\times \vec b)\,.
\end{align}
Note the even permutation from 23 to 24.
\end{description}
\paragraph{1.21} Observe
\begin{align}
\f12\epsilon_{ijk}(\vec a\times\vec b)_k &= \f12\epsilon_{ijk}\epsilon_{klm}a_l b_m\,,\\
&=\f12\epsilon_{kij}\epsilon_{klm}a_l b_m\,,\\
&=\f12\ps{\delta_{il}\delta_{jm}-\delta_{im}\delta_{jl}}a_l b_m\,,\\
&=\f12\ps{a_i b_j-a_j b_i}\,,\\
&=-\f12\ps{a_i b_j+a_j b_i}+a_ib_j\,.
\end{align}
Hence
\begin{align}
a_ib_j=\f12\epsilon_{ijk}(\vec a\times\vec b)_k+\f12\ps{a_i b_j+a_j b_i}\,.
\end{align}
wwtbd.
\paragraph{3.11} A two-dimensional disk of radius $R$ carries a uniform charge per unit area $\sigma>0$.
\begin{description}
\item{(a)} Calculate the potential at any point on the symmetry axis of the disk.
\\\\
The Maxwell equations imply that the electric field on a charge distribution is given by (3.8). Following the example in the text, we have
\begin{align}
\vec E(z) &= \f{\sigma}{4\pi\epsilon_0}\hat z\int_0^Rr\diff r\int_0^{2\pi}\diff\theta\f{z}{(z^2+r^2)^{3/2}}\,,\\
&= \f{\sigma}{4\pi\epsilon_0}\hat z\int_0^R\diff r\f{2\pi r z}{(z^2+r^2)^{3/2}}\,,\\
&= \f{\sigma}{2\epsilon_0}\hat z\ps{1-\f{z}{\sqrt{z^2+R^2}}}\,.
\end{align}
We can check this answer against what we expect for an infinite sheet of charge. Picking a box of size length $z$ centered on the distribution, we have $E = \f{\sigma z^2}{\epsilon_02z^2} = \f\sigma{2\epsilon_0}$, which is the limit in our case as $R\to\infty$.
\item{(b)} Calculate the potential at any point on the rim of the disk. Hint: Use a point on the rim as the origin.
\\\\
Observe that the potential is given by
\begin{align}
\phi(\te{rim}) &= \f{\sigma}{4\pi\epsilon_0}\int_0^{\pi}\diff\theta \int_0^{2R\sin\theta} r\diff r\f{1}{r}\,,\\
&= \f{R\sigma}{2\pi\epsilon_0}\int_0^{\pi}\diff\theta \sin\theta\,,\\
&= \f{R\sigma}{\pi\epsilon_0}\,.
\end{align}
\item{(c)} Sketch the electric field pattern everywhere in the plane of the disk.
\\\\
In the plane of the disk, we have rotational symmetry and reflection symmetry, so the only possible configuration of electric field lines is lines through the origin.
\item{(d)} Calculate the total energy $U_E$ of the disk.
\end{description}
\end{document}

### 2016-08-30 Draft.tex
Update

@@
 where $f$ is an analytic function whose range is a subset of $[-1,1]$, and $p_0$ is the maximum differential pressure in this region.
-After a short time, the pressure is still of this form, since the anisotropy of the Moon is significant only on large scales.
+After a short time, the pressure is still of this form, since the inhomogeneity of the Moon is significant only on large scales.
 
@@
 \end{align}
-\subsection{Analytic Upper Bound}
-If the energy of a ray from every point along the line hitting a single pixel (with no reflection, refraction, or attenuation) is less than the displacement threshold, there is no chance of detection and no need to run the simulation.
-(If two rays from the same point on the line source hit the same pixel as $n_\te{side}\to\infty$, then they must be the same ray).
-Thus, we bound the displacement by
+\subsection{Isotropic Limit Bound}
+In the case of a homogeneous moon, we obtain the following upper bound.
 \begin{align}
@@
 \end{align}
-This expression is independent of the choice of $n_\te{side}$. For the triangle wave, we need not test $\sigma_X\leq 4\times 10^{-11}\te{m}^2$.
+This expression is independent of the choice of $n_\te{side}$. For the triangle wave $\sigma_X\leq 4.4\times 10^{-7}\te{\,cm}^2$ is undetectable in the homogeneous limit.
 \section{Results}
@@
 \section{Conclusion}
-For Macros with density sufficient to pass nearly unimpeded through the Moon, and in particular nuclear dense objects such as strange quark nuggets, we have demonstrated that seismological constraints are insufficient to rule them out.
+For Macros with density sufficient to pass nearly unimpeded through the Moon and sufficiently small cross-section, and in particular nuclear dense objects such as strange quark nuggets with cross-section $\sigma_X\leq 4\times 10^{-7}\te{\, cm}^2$, we have demonstrated that seismological constraints are insufficient to rule them out.
 Since the Moon (and Earth) preferentially attenuate higher frequency modes, it is unlikely that measuring high frequencies would greatly improve sensitivity to these types of impacts.
-On the other hand, increasing the lunar seismometer sensitivity to small displacements would allow one to use seismological evidence to rule out high density Macros.
-That said, it is uncertain whether seismic noise at such small displacements would make Macro impacts indistinguishable from the background.
+On the other hand, increasing the lunar seismometer sensitivity to small displacements may allow one to use seismological evidence to rule out high density Macros, although it is uncertain whether seismic noise at such small displacements would make Macro impacts indistinguishable from the background.
+
+Future work will include new lower bounds on lunar and terrestrial seismic response to high density Macros.
+In the future, a more sensitive lunar array will allow for a better understanding of the lunar structure and for a greater volume of Macro parameter space to be considered through seismic means.
+In the case that the lunar seismic background is too loud for extremely small displacements to be distinguished, it will be necessary to reconstruct the seismic response to high density Macros in order to measure an approximate event rate.
 \section{Acknowledgements}
-The author would like to thank SOURCE for supporting this research.
+TO BE FINISHED: The author would like to thank SOURCE for supporting this research.
 \section{Summer Reflection}

### 2016-09-02 Article_Draft.tex
Update

--- 2016-08-30 Draft.tex
@@
 \title{New seismological constraints on the available parameter space of macroscopic dark matter}
-\author{David Cyncynates}
+\author{}
 \affiliation{Physics Department\\ Case Western Reserve University\\ Cleveland, Ohio 44106-7079, USA}
@@
 \begin{abstract}
-Recent limits have been proposed constraining the available parameter space of macroscopic dark matter (Macros).
+Limits have been proposed constraining the available parameter space of macroscopic dark matter (Macros).
 These limits were based on the energy deposition of Macros into low frequency seismic modes being akin to that of a nuclear or chemical bomb.
-We show that this assumption does not hold by considering the mechanism by which the Macro impact generates seismic waves.
+We show that this assumption does not hold by considering the mechanism through which Macro impacts generates seismic waves.
 Our new estimates take into account the effect of seismometer sensitivity and energy distribution across frequencies, anelastic attenuation, geometric effects, internal anisotropy of the Earth or Moon, as well as energy loss due to melting.
-We produce limits on the parameter space of Macros which can be ruled out by seismic event rate.
+We produce limits describing the Macro parameter space which can be ruled out by current seismological evidence.
 \end{abstract}
@@
 We also include a simple argument which demonstrates that a large portion of the available parameter space cannot be ruled out by seismological constraints.
+
+The moon is an attractive site to carry out a seismological search for Macro impacts.
+Unlike the Earth, the Moon is nearly dormant.
+Most internal seismological activity in the Moon originates from deep Moonquakes, which are very attenuated by the time they reach the surface.
+Most of the noise in lunar seismograms comes from asteroids, but these are for the most part easily identifiable as such.
+Thus, in the case that we can distinguish between asteroids and Macros, the Moon is a nearly ideal location to place constraints via total seismic event rate.
+However, in the case that the Macro impacts are very weak, it may be impossible to distinguish them from asteroids or weak Moonquakes based on a single seismogram.
+In this case, it is necessary to identify correlated events among lunar seismometers which correspond to a propagating source of seismic waves.
+This sort of analysis will be left to future work.
 \section{The Seismic Source}
@@
 \begin{align}
-E = \int\diff^3 x\p{ \rho\abs{\partial_t u}^2+(\lambda+2\mu)\abs{\nabla u}^2}\,,
+E = \f12\int\diff^3 x\p{ \rho\abs{\partial_t u}^2+(\lambda+2\mu)\abs{\nabla u}^2}\,,
 \end{align}
@@
 Taking $\epsilon_\te{melt} = 0$, $\rho = 3.3\times 10^3\,\te{kg m}^{-3}$, $v_X = 2.5\times 10^5\,\te{m s}^{-1}$, $\kappa = 5.5\times 10^{10}\,\te{Pa}$, and $k = 1.5\times 10^{-2}\,\te{m}^{-1}$ \cite{garcia2011very}, we obtain $\Xi<4.5\times 10^4 (\sigma_X/\te{m}^2)$.
-To obtain the figure that Teplitz \textit{et al.} have used, one must take $\sigma_X >10^{-6}\te{m}^2$, which is rather large.
+To obtain the figure that Teplitz \textit{et al.} have used, one must take $\sigma_X >10^{-2}\te{\,cm}^2$, which is rather large.
 
@@
 \end{align}
-\subsection{Isotropic Limit Bound}
-In the case of a homogeneous moon, we obtain the following upper bound.
+\subsection{Homogeneous Limit}
+To obtain an estimate of the size of a detectable Macro, we suppose that one ray from each point source on the Macro Trajectory hits a single pixel.
+In the case that rays don't bend, this is a good approximation for behavior away from the source.
+Note, however, that this does not account for geometric focusing around the entrance and exit of the Macro trajectory.
 \begin{align}
-u\leq\sqrt{\f{\Xi E}{\pi^2\rho k v_p^2 R_\te{Moon}^2}}
+u\leq\sqrt{\f{\Xi E}{\pi^2\rho k v_p^2 R_\te{Moon}^2}}\,.
 \end{align}
-This expression is independent of the choice of $n_\te{side}$. For the triangle wave $\sigma_X\leq 4.4\times 10^{-7}\te{\,cm}^2$ is undetectable in the homogeneous limit.
+This expression is independent of the choice of $n_\te{side}$.
+For the triangle wave, $\sigma_X\leq 4.4\times 10^{-7}\te{\,cm}^2$ is unlikely to be detected unless it enters or exits the Moon adjacent to a seismometer.
 \section{Results}
@@
 \section{Acknowledgements}
-TO BE FINISHED: The author would like to thank SOURCE for supporting this research.
-\section{Summer Reflection}
-My research this summer will be very important when I make my case to graduate schools that I am capable of doing independent research and problem solving.
-This project will likely be developed into my capstone, and we will try to publish this work.
-For next year's students, drink lots of coffee.
+This work made use of the High Performance Computing Resource in the Core Facility for Advanced Research Computing at Case Western Reserve University.
+David Cyncynates would like to thank SOURCE for supporting this research.
 \bibliography{Macro-Impact}{}

### 2016-09-05 DATA/Draft.tex
Big Ol' Update

--- 2016-09-02 Article_Draft.tex
@@
 \title{New seismological constraints on the available parameter space of macroscopic dark matter}
-\author{}
+\author{David Cyncynates, Glenn Starkman, Joshua Chiel, Jagjit Singh Sidhu}
 \affiliation{Physics Department\\ Case Western Reserve University\\ Cleveland, Ohio 44106-7079, USA}
@@
 \begin{align}
-E = \f12\int\diff^3 x\p{ \rho\abs{\partial_t u}^2+(\lambda+2\mu)\abs{\nabla u}^2}\,,
+E = \int\diff^3 x\p{ \rho\abs{\partial_t u}^2+(\lambda+2\mu)\abs{\nabla u}^2}\,,
 \end{align}
@@
 \section{Acknowledgements}
-This work made use of the High Performance Computing Resource in the Core Facility for Advanced Research Computing at Case Western Reserve University.
-David Cyncynates would like to thank SOURCE for supporting this research.
+The author would like to thank SOURCE for supporting this research.
+\section{Summer Reflection}
+My research this summer will be very important when I make my case to graduate schools that I am capable of doing independent research and problem solving.
+This project will likely be developed into my capstone, and we will try to publish this work.
+For next year's students, drink lots of coffee.
 \bibliography{Macro-Impact}{}

### 2016-09-05 LaTeX/Article_Draft.tex
Big Ol' Update

--- 2016-09-02 Article_Draft.tex
@@
 These limits were based on the energy deposition of Macros into low frequency seismic modes being akin to that of a nuclear or chemical bomb.
-We show that this assumption does not hold by considering the mechanism through which Macro impacts generates seismic waves.
+We show that this assumption does not hold by considering the mechanism through which Macro impacts generate seismic waves.
 Our new estimates take into account the effect of seismometer sensitivity and energy distribution across frequencies, anelastic attenuation, geometric effects, internal anisotropy of the Earth or Moon, as well as energy loss due to melting.
@@
 The super-heated rock, held at constant volume, generates a pressure which sources the seismic waves that can be measured at detectors.
-Macro's with velocity insignificantly changed by their encounter with the Moon source a pressure of the form
+Macro's with velocity insignificantly changed by their encounter with the Moon source an overpressure pressure of the form
 \begin{align}
@@
 \end{align}
+*CHANGE $\chi$ TO CASES*
 where $f$ is an analytic function whose range is a subset of $[-1,1]$, and $p_0$ is the maximum differential pressure in this region.
@@
 \begin{align}
-\scr F = \sum_D\f{\scr F_D D}{D}\,.
+\scr F =\f{\sum_D \scr F_D}{\sum_D D}\,.
 \end{align}

### 2016-09-05 Data Analysis Code/DataAnalysis.py

@@ -1,0 +1,95 @@
+#%reset
+import sys
+import scipy.io as sio
+from scipy.stats import mode
+import healpy as hp
+import numpy as np
+import itertools as it
+import math
+
+
+
+nside = int(sys.argv[0]);
+R = 1.731E6; #Radius of Moon
+sigmaX = 4.0E-11 #Cross-sectional area of macro
+vX = 2.5E5 #Velocity of Macro
+p0 = 1.0E8 #Hookean Pressure
+frequencymax = 2.0E0
+DisplacementThreshold = 3.0E-10; #How much does the detector need to be displaced in order to register the ray?
+vsurf = 1.0E3; #Velocity of Rays at Surface
+
+A = hp.nside2pixarea(nside) * R**2 #Area of pixel
+T = ((A/np.pi)**(1/2))/vsurf; #How close in time do two rays have to be in order to be considered hitting together?
+N = hp.nside2npix(nside);
+
+#Loading Data from Matlab
+mat_contents = sio.loadmat('/Users/David/Macro-Impact/Data/PointsTestMat1.mat');
+points = mat_contents['outputmat']; #Points has the format (x,y,z,time,density,REF,ATT,kappa,velocity)
+num_contents = sio.loadmat('/Users/David/Macro-Impact/Data/PointsTestNum1.mat');
+numbers = num_contents['outputnum']; #Points has the format (M,N,L,D)
+length = len(points);
+
+#Assigning each point its HEALPix coordinate
+hppoints = hp.pixelfunc.vec2pix(nside, points[:,0],points[:,1],points[:,2])
+#Mode = mode(hppoints)[1][0]; #Mode is the maximum number of times a pixel is struck by a ray
+
+PixelTimes = np.zeros((N,len(hppoints))); #Each row contains a list of times at which rays struck the nth pixel
+Density = np.zeros((N,len(hppoints))); #This is the corresponding list of energies
+PixelREF = np.zeros((N,len(hppoints))); #Refraction/Reflection Coefficient of each ray
+#PixelATT = np.zeros((N,len(hppoints))); #Quality Factor (ish) of each ray
+Velocity = np.zeros((N,len(hppoints))); #Velocity at source
+kmax = np.zeros((N,len(hppoints))); #Max wavenumber at source
[…]

### 2016-09-06 DataAnalysis.py
Updates for dayyyyys

@@ -1,0 +1,100 @@
+#%reset
+import sys
+import scipy.io as sio
+from scipy.stats import mode
+import healpy as hp
+import numpy as np
+import itertools as it
+import math
+
+a = int(sys.argv[1])  b = int(sys.argv[2])
+
+print a, b
+
+print a+b
+
+nside = sys.argv[1];
+nside = int(nside)
+R = 1.731E6; #Radius of Moon
+sigmaX = 4.0E-11 #Cross-sectional area of macro
+vX = 2.5E5 #Velocity of Macro
+p0 = 1.0E8 #Hookean Pressure
+frequencymax = 2.0E0
+DisplacementThreshold = 3.0E-10; #How much does the detector need to be displaced in order to register the ray?
+vsurf = 1.0E3; #Velocity of Rays at Surface
+
+A = hp.nside2pixarea(nside) * R**2 #Area of pixel
+T = ((A/np.pi)**(1/2))/vsurf; #How close in time do two rays have to be in order to be considered hitting together?
+N = hp.nside2npix(nside);
+
+#Loading Data from Matlab
+mat_contents = sio.loadmat('/Users/David/Macro-Impact/Data/PointsTestMat1.mat');
+points = mat_contents['outputmat']; #Points has the format (x,y,z,time,density,REF,ATT,kappa,velocity)
+num_contents = sio.loadmat('/Users/David/Macro-Impact/Data/PointsTestNum1.mat');
+numbers = num_contents['outputnum']; #Points has the format (M,N,L,D)
+length = len(points);
+
+#Assigning each point its HEALPix coordinate
+hppoints = hp.pixelfunc.vec2pix(nside, points[:,0],points[:,1],points[:,2])
+#Mode = mode(hppoints)[1][0]; #Mode is the maximum number of times a pixel is struck by a ray
+
+PixelTimes = np.zeros((N,len(hppoints))); #Each row contains a list of times at which rays struck the nth pixel
+Density = np.zeros((N,len(hppoints))); #This is the corresponding list of energies
+PixelREF = np.zeros((N,len(hppoints))); #Refraction/Reflection Coefficient of each ray
+#PixelATT = np.zeros((N,len(hppoints))); #Quality Factor (ish) of each ray
+Velocity = np.zeros((N,len(hppoints))); #Velocity at source
[…]

### 2016-09-06 Data_Analysis_Code/DataAnalysis.py

@@ -7,39 +7,25 @@ import numpy as np
 import itertools as it
 import math
 
-
-
-nside = int(sys.argv[0]);
-R = 1.731E6; #Radius of Moon
-sigmaX = 4.0E-11 #Cross-sectional area of macro
-vX = 2.5E5 #Velocity of Macro
-p0 = 1.0E8 #Hookean Pressure
-frequencymax = 2.0E0
-DisplacementThreshold = 3.0E-10; #How much does the detector need to be displaced in order to register the ray?
-vsurf = 1.0E3; #Velocity of Rays at Surface
+nside = int(sys.argv[1]) #EG 4
+R = float(sys.argv[2]); #Radius of Moon EG 1.737E6
+vsurf = float(sys.argv[3]); #Velocity of Rays at Surface EG 1.0E3
+frequencymax = float(sys.argv[4]); #Maximum Detectable Frequency EG 2.0E1
 
 A = hp.nside2pixarea(nside) * R**2 #Area of pixel
 T = ((A/np.pi)**(1/2))/vsurf; #How close in time do two rays have to be in order to be considered hitting together?
 N = hp.nside2npix(nside);
 
 #Loading Data from Matlab
-mat_contents = sio.loadmat('/Users/David/Macro-Impact/Data/PointsTestMat1.mat');
+mat_contents = sio.loadmat('/Users/David/Macro-Impact/Data/PointsTestMat'+sys.argv[5]+'.mat');
 points = mat_contents['outputmat']; #Points has the format (x,y,z,time,density,REF,ATT,kappa,velocity)
-num_contents = sio.loadmat('/Users/David/Macro-Impact/Data/PointsTestNum1.mat');
+num_contents = sio.loadmat('/Users/David/Macro-Impact/Data/PointsTestNum'+sys.argv[5]+'.mat');
 numbers = num_contents['outputnum']; #Points has the format (M,N,L,D)
 length = len(points);
 
-#Assigning each point its HEALPix coordinate
-hppoints = hp.pixelfunc.vec2pix(nside, points[:,0],points[:,1],points[:,2])
-#Mode = mode(hppoints)[1][0]; #Mode is the maximum number of times a pixel is struck by a ray
-
+hppoints = hp.pixelfunc.vec2pix(nside, points[:,0],points[:,1],points[:,2]) #Assigning each point its HEALPix coordinate
[…]

### 2016-09-06 HPC_Data_Generation/Ray-Tracing/Ray_Tracing_Moon_1.m

@@ -17,7 +17,7 @@ vs = 4.4 * 10^3;%AVERAGE SHEAR WAVE VELOCITY THROUGHOUT THE WHOLE MOON m/s
 vp = 7.6 * 10^3;%AVERAGE PRESSURE WAVE VELOCITY THROUGHOUT THE WHOLE MOON m/s
 
 M = 200; %NUMBER OF POINTS ON THE LINE
-N = 192; %NUMBER OF RAYS FROM EACH POINT
+N = 12; %NUMBER OF RAYS FROM EACH POINT
 %{
 %APPROXIMATION TO OUTER LAYERS
 a = [8.26955,8.26955,8.26955,8.26955,145.46].^(1/2);

### 2016-09-06 LaTeX/Article_Draft.tex
Updates for dayyyyys
update
More Update

@@
 \begin{align}
-p = p_0 f(r)\chi_{(r,z)\in [a,b]\times [-\f \ell 2,\f \ell 2]}\,,
+\begin{array}{cc}p = p_0 f(r)&\te{ if }a<r<b,-\f h2<z<\f h2\,,\\ p = 0&\te{ else,}\end{array}
 \end{align}
-*CHANGE $\chi$ TO CASES*
-where $f$ is an analytic function whose range is a subset of $[-1,1]$, and $p_0$ is the maximum differential pressure in this region.
+where $f$ is an analytic function on $[a,b]$ whose range is a subset of $[-1,1]$, and $p_0$ is the maximum differential pressure in this region.
 After a short time, the pressure is still of this form, since the inhomogeneity of the Moon is significant only on large scales.
 
-The seismometers on the moon have a net useful range of up to $20\,\te{Hz}$ and are sensitive to displacements as small as $0.3\,\text{nm}$ \cite{latham1973lunar}.
-Therefore, we only calculate the energy contained in the modes of frequency less than $20\,\te{Hz}$.
+The seismometers on the moon have a net useful range of up to $16\,\te{Hz}$ and are sensitive to displacements as small as $0.3\,\text{nm}$ \cite{latham1973lunar}\cite{nakamura1982apollo}.
+Therefore, we only calculate the energy contained in the modes of frequency less than $20\,\te{Hz}$\cite{nakamura1982apollo}.
 
@@
 \begin{align}
-\abs{u(\vec x,t)}\leq\sqrt{\f{4\te{Ref}\,\Xi E}{\pi k\rho v_p^2 A}}\,.
+\abs{u(\vec x,t)}&\leq\sqrt{\f{4\te{Ref}\,\Xi E}{\pi k\rho v_p^2 A}}\,,\\
+&=\sqrt{\f{9\te{Ref}}{2mn}\f{\kappa\rho\ell}{\pi v_p^3A}}\f{\sqrt{ f_\te{max}}\sigma_Xv_X^2}{p_0}\,.
 \end{align}
+(28 will be deleted, I'm just using it to remember the formula)
 \section{Simulation}

### 2016-09-06 LaTeX/Article_Draft.tex
Update

@@
 The super-heated rock, held at constant volume, generates a pressure which sources the seismic waves that can be measured at detectors.
-Macro's with velocity insignificantly changed by their encounter with the Moon source an overpressure pressure of the form
+Macro's with velocity insignificantly changed by their encounter with the Moon source an overpressure of the form
 \begin{align}
@@
 The seismometers on the moon have a net useful range of up to $16\,\te{Hz}$ and are sensitive to displacements as small as $0.3\,\text{nm}$ \cite{latham1973lunar}\cite{nakamura1982apollo}.
-Therefore, we only calculate the energy contained in the modes of frequency less than $20\,\te{Hz}$\cite{nakamura1982apollo}.
+Therefore, we only calculate the energy contained in the modes of frequency less than $16\,\te{Hz}$.
 
@@
 
+The choice of $p_0 = 10^8\,\te{Pa}$ does significantly impact our result; ultimately the measured displacements we calculate will be inversely proportional to $p_0$.
+Our choice of $p_0$, however, is well below the overpressure corresponding to the boundary between linear and non-linear elasticity in the Moon.
+As the ambient pressure on a sample of rock increases, so too does $p_0$.
+We have taken $p_0$ to be a factor of $3$ below that of granite with a modest $50\te{ MPa}$ overpressure \cite{lockner200232}.
+In reality, $p_0$ is probably, on average, several orders of magnitude larger than we claim it to be because the ambient pressure in the Moon is on the order of $\te{GPa}$ rather than $\te{MPa}$, but no measurements, to our knowledge, probe the elastic behavior of rock at these high pressures.
+It is also important to notice that this choice of $p_0$ corresponds to $r_0$ on the order of $1\te{ km}$, which well exceeds the regime of non-linearity we would have expected based on the solutions to the heat equation.
 \section{Seismic Wave Propagation}
@@
 \section{Seismic Wave Detection}
-Consider a $p$-wave traveling towards positive $x$ and of compact support $S$ in the plane normal to to its motion. Denote $A =\int_S\diff y\diff z$ The displacement field is
+Consider a $p$-wave traveling towards positive $x$ and of compact support $S$ in the plane normal to to its motion.
+Denote $A =\int_S\diff y\diff z$, and let $\chi_S$ be $1$ on $S$ and $0$ elsewhere.
+The displacement field is
 \begin{align}
@@
 If attenuation were important, we may average $\te{Att}$ among the coincident rays and obtain an approximate expression.
-However, since we only wish to consider the lowest frequency modes, $f<20\te{Hz}$, the suppression $\te{Att} k$ is order unity, and does not contribute significantly to $u$.
+However, since we only wish to consider the lowest frequency modes, $f<16\te{Hz}$, the suppression $\te{Att} k$ is order unity, and does not contribute significantly to $u$.
 Taking $\te{Att} = 0$, the displacement caused by the incident $p$-wave is bounded above by
 \begin{align}
-\abs{u(\vec x,t)}&\leq\sqrt{\f{4\te{Ref}\,\Xi E}{\pi k\rho v_p^2 A}}\,,\\
-&=\sqrt{\f{9\te{Ref}}{2mn}\f{\kappa\rho\ell}{\pi v_p^3A}}\f{\sqrt{ f_\te{max}}\sigma_Xv_X^2}{p_0}\,.
+\abs{u(\vec x,t)}&\leq\sqrt{\f{4\te{Ref}\,\Xi E}{\pi k\rho v_p^2 A}}\,.
 \end{align}
-(28 will be deleted, I'm just using it to remember the formula)
+
 \section{Simulation}
@@
 This expression is independent of the choice of $n_\te{side}$.
-For the triangle wave, $\sigma_X\leq 4.4\times 10^{-7}\te{\,cm}^2$ is unlikely to be detected unless it enters or exits the Moon adjacent to a seismometer.
+For the triangle wave, $\sigma_X\leq 1\times 10^{-7}\te{\,cm}^2$ is unlikely to be detected unless it enters or exits the Moon adjacent to a seismometer.
 \section{Results}
@@
 \section{Conclusion}
-For Macros with density sufficient to pass nearly unimpeded through the Moon and sufficiently small cross-section, and in particular nuclear dense objects such as strange quark nuggets with cross-section $\sigma_X\leq 4\times 10^{-7}\te{\, cm}^2$, we have demonstrated that seismological constraints are insufficient to rule them out.
+For Macros with density sufficient to pass nearly unimpeded through the Moon and sufficiently small cross-section, and in particular nuclear dense objects such as strange quark nuggets with cross-section $\sigma_X\leq 1\times 10^{-7}\te{\, cm}^2$, we have demonstrated that seismological constraints are insufficient to rule them out.
 Since the Moon (and Earth) preferentially attenuate higher frequency modes, it is unlikely that measuring high frequencies would greatly improve sensitivity to these types of impacts.

### 2016-09-06 LaTeX/Intro Edit.tex
Update

Dark matter constitutes a large fraction of the Universe today. However, no theory about its composition has yet be theoretically confirmed. Some more prominent candidates are particles which exist outside the Standard Model, such as weakly interacting massive particles (WIMPS) and axions. However, plausible candidates for dark matter still exist inside the current theoretical paradigm. These candidates are dense clumps of matter, including strange quark nuggets (SQNs), small black holes, and so on. In this paper, we consider model independent seismological constraints on the available parameter space of macroscopic dark matter candidates. The theoretical motivation from this stems from the work of Witten (1984), in which

macroscopic clumps of strange matter could be stable and make up the amount

of dark matter needed.

Previous work on this topic has focused on both the moon and the Earth.

Here we consider lunar seismometer limits before returning to the Earth in fu-
ture work. Teplitz et al(2005) have placed some limits on a fraction of the

parameter space of macros by considering the average total seismic energy re-
leased and the average number of seismic events on the moon. These data

were obtained from the Apollo lunar seismometers in the 70?s. In this paper,

we revise these limits based on a computation of the seismic efficiency, which

is the coupling constant representing the fraction of energy deposited by our

macro on its passage through the earth that is available for seismic waves. The

mechanism for this is anelastic damping, which is the preferential damping of

higher frequency components of a signal on passage through an object. Note

that this work also relies on a delta function distribution of the dark matter

nuggets. However, one should expect some extended mass distribution of the

dark matter nuggets.

In addition to that, we also seek to calculate the plasma zone, vapor zone and

melt zone, which are the zones of rock that are converted into plasma, vaporized

and melted respectively due to the extreme temperature of the rapidly expand-
ing shockwave formed by the energy deposited due to the macro. This further

reduces the seismic efficiency. Lastly, we ran computer simulations to determine

if the stratified structure of the moon would focus the energy such that the sig-
nal received could be magnified in amplitude. Prior works neglected reflection

and refraction in modelling the passage of the seismic waves. (However, these

focusing effects proved to be of minimal significance, with the reduction in the

seismic efficiency being orders of magnitude more.)

### 2016-09-06 Data_Analysis_Code/HPCDataAnalysis.py

@@ -1,0 +1,58 @@
+#%reset
+import sys
+import scipy.io as sio
+from scipy.stats import mode
+import healpy as hp
+import numpy as np
+import itertools as it
+import math
+
+nside = int(sys.argv[1]) #EG 4
+R = float(sys.argv[2]); #Radius of Moon EG 1.737E6
+vsurf = float(sys.argv[3]); #Velocity of Rays at Surface EG 1.0E3
+frequencymax = float(sys.argv[4]); #Maximum Detectable Frequency EG 2.0E1
+
+A = hp.nside2pixarea(nside) * R**2 #Area of pixel
+T = ((A/np.pi)**(1/2))/vsurf; #How close in time do two rays have to be in order to be considered hitting together?
+N = hp.nside2npix(nside);
+
+#Loading Data from Matlab
+mat_contents = sio.loadmat('/Users/David/Macro-Impact/Data/PointsTestMat'+sys.argv[5]+'.mat');
+points = mat_contents['outputmat']; #Points has the format (x,y,z,time,density,REF,ATT,kappa,velocity)
+num_contents = sio.loadmat('/Users/David/Macro-Impact/Data/PointsTestNum'+sys.argv[5]+'.mat');
+numbers = num_contents['outputnum']; #Points has the format (M,N,L,D)
+length = len(points);
+
+hppoints = hp.pixelfunc.vec2pix(nside, points[:,0],points[:,1],points[:,2]) #Assigning each point its HEALPix coordinate
+PixelTimes = np.zeros((N,len(hppoints))); #Each row contains a list of times at which rays struck the nth pixel
+PreDisplacementPrime = np.zeros((N,len(hppoints))); #Intermediate array to store ray initial condition dependent information
+PixelDisplacements = np.zeros((N,len(hppoints))); #Maximum Displacements measured in a pixel
+
+m = numbers[0][0]
+n = numbers[0][1]
+L = numbers[0][2]
+D = numbers[0][3]
+
+#Now we assign PixelTimes and PixelEnergies their values
+for i in range(0,N):
+    counter = 0;
+    for j in range(0,length):
+        if hppoints[j] == i:
+            PixelTimes[i][counter] = points[j,3];
+            PreDisplacementPrime[i][counter] = (points[j,5] * points[j,7] * points[j,4])/(points[j,8]**3)
+            counter = counter + 1;
+#New improved code by Prof. Copi
[…]

### 2016-09-06 HPC_Data_Analysis/DataAnalysis.py

@@ -1,100 +1,0 @@
-#%reset
-import sys
-import scipy.io as sio
-from scipy.stats import mode
-import healpy as hp
-import numpy as np
-import itertools as it
-import math
-
-a = int(sys.argv[1])  b = int(sys.argv[2])
-
-print a, b
-
-print a+b
-
-nside = sys.argv[1];
-nside = int(nside)
-R = 1.731E6; #Radius of Moon
-sigmaX = 4.0E-11 #Cross-sectional area of macro
-vX = 2.5E5 #Velocity of Macro
-p0 = 1.0E8 #Hookean Pressure
-frequencymax = 2.0E0
-DisplacementThreshold = 3.0E-10; #How much does the detector need to be displaced in order to register the ray?
-vsurf = 1.0E3; #Velocity of Rays at Surface
-
-A = hp.nside2pixarea(nside) * R**2 #Area of pixel
-T = ((A/np.pi)**(1/2))/vsurf; #How close in time do two rays have to be in order to be considered hitting together?
-N = hp.nside2npix(nside);
-
-#Loading Data from Matlab
-mat_contents = sio.loadmat('/Users/David/Macro-Impact/Data/PointsTestMat1.mat');
-points = mat_contents['outputmat']; #Points has the format (x,y,z,time,density,REF,ATT,kappa,velocity)
-num_contents = sio.loadmat('/Users/David/Macro-Impact/Data/PointsTestNum1.mat');
-numbers = num_contents['outputnum']; #Points has the format (M,N,L,D)
-length = len(points);
-
-#Assigning each point its HEALPix coordinate
-hppoints = hp.pixelfunc.vec2pix(nside, points[:,0],points[:,1],points[:,2])
-#Mode = mode(hppoints)[1][0]; #Mode is the maximum number of times a pixel is struck by a ray
-
-PixelTimes = np.zeros((N,len(hppoints))); #Each row contains a list of times at which rays struck the nth pixel
-Density = np.zeros((N,len(hppoints))); #This is the corresponding list of energies
-PixelREF = np.zeros((N,len(hppoints))); #Refraction/Reflection Coefficient of each ray
-#PixelATT = np.zeros((N,len(hppoints))); #Quality Factor (ish) of each ray
-Velocity = np.zeros((N,len(hppoints))); #Velocity at source
[…]

### 2016-09-06 LaTeX/Article_Draft.tex
update

@@
 Our choice of $p_0$, however, is well below the overpressure corresponding to the boundary between linear and non-linear elasticity in the Moon.
-As the ambient pressure on a sample of rock increases, so too does $p_0$.
+As the ambient pressure on a sample of rock increases, so too does $p_0$ \cite{mair2002influence}\cite{shimada1993lithosphere}\cite{ord1991deformation}.
 We have taken $p_0$ to be a factor of $3$ below that of granite with a modest $50\te{ MPa}$ overpressure \cite{lockner200232}.
@@
 In the case that rays don't bend, this is a good approximation for behavior away from the source.
-Note, however, that this does not account for geometric focusing around the entrance and exit of the Macro trajectory.
+Note, however, that this does not account for geometric focusing e.g.
+around the entrance and exit of the Macro trajectory.
 \begin{align}

### 2016-09-07 LaTeX/Article_Draft.tex
Added Heat equation material
There is a key consistency check that appears to have an issue, that
may alter some of the results -- David and I plan to work on this
together later today.

@@
 It is also important to notice that this choice of $p_0$ corresponds to $r_0$ on the order of $1\te{ km}$, which well exceeds the regime of non-linearity we would have expected based on the solutions to the heat equation.
+
+\subsection{Heat Equation solution analysis}
+We consider only the melting or vaporization that occurs prior to the onset of the deposited energy serving as a source for seismic waves, since the initiation of seismic wave propagation complicates assessing the amount of energy dissipated in melting (and vaporizing) the impacted material and its surroundings.
+To model an instantaneous energy deposition along the z-axis, we use a delta function, and set the solution of the heat equation equal to a fixed temperature (of melting).
+This yields an expression for the radius, as a function of time, of the impacted material and its surroundings that has reached its melting point temperature, $r_\te{melt}(t)$.
+Differentiating $r_\te{melt}(t)$ with respect to time, setting the result equal to the bulk speed of sound and solving for t yields the time at which the propagation of the "melt point temperature zone" falls to the speed of sound.
+Plugging this time into $r_\te{melt}(t)$ yields $r_\te{fast melt}$: the extent of the impacted material and its surroundings that is heated to its melting point more rapidly than bulk sound speed.
+Replacing the melting point temperature with the vaporization point temperature in the above demonstrates that $r_\te{fast melt}$ is essentially equal to $r_\te{fast vaporize}$ for all Macro radii.
+This result indicates that for macros with radii greater than ***$10^{-9} m$***(pending resolution of consistency check issue, and minor additional refinements), $r_\te{fast vaporize}$ is of the same order as $r_\te{Macro}$.
+The extreme temperatures generated by the impact (approximately $10^{15} K$, again pending resolution of consistency check issue that arose in computing this value) will convert the vaporized material to plasma; however, this conversion is a second order phase transition, and so does not require a latent heat input to occur.
+Thus, the energy to transition from vapor to plasma could conceivably transfer back into seismic waves (as the particles slow down, recombine as vapor, condense to liquid, and then solidify).
+Similarly, the energy required to raise the temperature of the impacted material and its surroundings to their melting and vaporization points could subsequently source seismic waves: temperature changes in the column of heated material result in expansions  and contractions that lead to a column of ovepressure/underpressure.
+Hence, to model the energy dissipated both in raising the temperature of the impacted material and its surroundings, and in effecting a transition to plasma are complicated by the concurrent energy transfer to seismic waves.
+
 \section{Seismic Wave Propagation}

### 2016-09-07 LaTeX/Article_Draft.tex
A few more style things
.

@@
 This result indicates that for macros with radii greater than ***$10^{-9} m$***(pending resolution of consistency check issue, and minor additional refinements), $r_\te{fast vaporize}$ is of the same order as $r_\te{Macro}$.
+A simple computation shows that the heat dissipated in sublimating a column of material with radius $r_\te{fast vaporize}$ ranges from less than $1 J$ to $10^2 J$, a negligible amount (note, these details are all found in Macro impacts revised eqs.
+306-322).
 The extreme temperatures generated by the impact (approximately $10^{15} K$, again pending resolution of consistency check issue that arose in computing this value) will convert the vaporized material to plasma; however, this conversion is a second order phase transition, and so does not require a latent heat input to occur.
@@
 Hence, to model the energy dissipated both in raising the temperature of the impacted material and its surroundings, and in effecting a transition to plasma are complicated by the concurrent energy transfer to seismic waves.
+The force of these results are that either much of the melting occurs once the temperature field's expansion is slower than the speed of sound and this slow-down occurs very quickly, or that the material parameters -- especially the thermal diffusion coefficient and the heat capacity of the impacted material -- are far from constant in the case at hand (given the extremes of pressure and temperature involved, it is more likely the latter).
+In addition, the instantaneous energy deposition model de-emphasizes the significance of the parameters of the macro, and appears to (over)emphasize the significance of the parameters of the impacted material.
 

### 2016-09-07 Data_Analysis_Code/HPCDataAnalysis copy.py
update

@@ -13,13 +13,13 @@ vsurf = float(sys.argv[3]); #Velocity of Rays at Surface EG 1.0E3
 frequencymax = float(sys.argv[4]); #Maximum Detectable Frequency EG 2.0E1
 
 A = hp.nside2pixarea(nside) * R**2 #Area of pixel
-T = ((A/np.pi)**.5)/vsurf; #How close in time do two rays have to be in order to be considered hitting together?
+T = ((A/np.pi)**(1/2))/vsurf; #How close in time do two rays have to be in order to be considered hitting together?
 N = hp.nside2npix(nside);
 
 #Loading Data from Matlab
-mat_contents = sio.loadmat('PointsTestMat'+sys.argv[5]+'.mat');
+mat_contents = sio.loadmat('/Users/David/Macro-Impact/Data/PointsTestMat'+sys.argv[5]+'.mat');
 points = mat_contents['outputmat']; #Points has the format (x,y,z,time,density,REF,ATT,kappa,velocity)
-num_contents = sio.loadmat('PointsTestNum'+sys.argv[5]+'.mat');
+num_contents = sio.loadmat('/Users/David/Macro-Impact/Data/PointsTestNum'+sys.argv[5]+'.mat');
 numbers = num_contents['outputnum']; #Points has the format (M,N,L,D)
 length = len(points);
 
@@ -50,8 +50,9 @@ for i in range(0,N):
     d = np.abs(PixelTimes[i,ind[:,0]] - PixelTimes[i,ind[:,1]])
     for ii in np.where((d < T) & (d > 0))[0]:
         PixelDisplacements[i,ind[ii,0]] += PreDisplacementPrime[i,ind[ii,1]]
+
 #Now we find the maximum displacement factor on each pixel
-PreDisplacement = ((np.amax(PixelDisplacements, axis=1))**.5) * (((9 * L) / (2 * np.pi * n * m * A))**.5) #Multiply by fmax**(1/2) * sigmaX * (vX**2) * p0**(-1) to get displacement
-print(PreDisplacement)
+PreDisplacement = np.amax(PixelDisplacements, axis=1)**(1/2) * ((9 * L) / (2 * np.pi * n * m * A))**(1/2); #Multiply by fmax**(1/2) * sigmaX * (vX**2) * p0**(-1) to get displacement
+
[…]

### 2016-09-07 Macros2.tex
Add files via upload

\documentclass[10pt,a4paper]{article}
\usepackage[utf8]{inputenc}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\author{Jagjit}
\title{MACros2}
\begin{document}
\maketitle{Introduction}\par
	Dark matter constitutes a large fraction of the Universe today. However, we are still unclear as to what exactly makes up this constituent. Some more prominent candidates are particles such as WIMPS and axions. In this paper, we consider a class of macroscopic dark matter candidates, which would yield detectable seismological signals if they were to pass through the Earth. The theoretical motivation from this stems from the work of Witten (1984), in which macroscopic clumps of strange matter could be stable and make up the amount of dark matter needed.\par
	 Previous work on this topic has focused on both the moon and the Earth. Here we consider lunar seismometer limits before returning to the Earth in future work. Teplitz et al(2005) have placed some limits on a fraction of the parameter space of macros by considering the average total seismic energy released and the average number of seismic events on the moon. These data were obtained from the Apollo lunar seismometers in the 70's. In this paper, we revise these limits based on a computation of the seismic efficiency, which is the coupling constant representing the fraction of energy deposited by our macro on its passage through the earth that is available for seismic waves. The mechanism for this is anelastic damping, which is the preferential damping of higher frequency components of a signal on passage through an object. Note that this work also relies on a delta function distribution of the dark matter nuggets. However, one should expect some extended mass distribution of the dark matter nuggets.\par
	In addition to that, we also seek to calculate the plasma zone, vapor zone and melt zone, which are the zones of rock that are converted into plasma, vaporized and melted respectively due to the extreme temperature of the rapidly expanding shockwave formed by the energy deposited due to the macro. This further reduces the seismic efficiency. Lastly, we ran computer simulations to determine if the stratified structure of the moon would focus the energy such that the signal received could be magnified in amplitude. Prior works neglected reflection and refraction in modelling the passage of the seismic waves. (However, these focusing effects proved to be of minimal significance, with the reduction in the seismic efficiency being orders of magnitude more.)\par

\end{document}

### 2016-09-07 HPCAnalysis/HPCDataAnalysis.py
Update

@@ -26,8 +26,8 @@ length = len(points);
 hppoints = hp.pixelfunc.vec2pix(nside, points[:,0],points[:,1],points[:,2]) #Assigning each point its HEALPix coordinate
 PixelTimes = np.zeros((N,len(hppoints))); #Each row contains a list of times at which rays struck the nth pixel
 PreDisplacementPrime = np.zeros((N,len(hppoints))); #Intermediate array to store ray initial condition dependent information
-PixelDisplacements = np.zeros((N,len(hppoints))); #Maximum Displacements measured in a pixel
-
+PixelDisplacements = np.zeros(len(hppoints)); #Maximum Displacements measured in a pixel
+PreDisplacement = np.zeros(N)
 m = numbers[0][0]
 n = numbers[0][1]
 L = numbers[0][2]
@@ -49,9 +49,11 @@ for i in range(0,N):
     ind = np.array(list(it.combinations(range(len(nz)),2)))
     d = np.abs(PixelTimes[i,ind[:,0]] - PixelTimes[i,ind[:,1]])
     for ii in np.where((d < T) & (d > 0))[0]:
-        PixelDisplacements[i,ind[ii,0]] += PreDisplacementPrime[i,ind[ii,1]]
-#Now we find the maximum displacement factor on each pixel
-PreDisplacement = ((np.amax(PixelDisplacements, axis=1))**.5) * (((9 * L) / (2 * np.pi * n * m * A))**.5) #Multiply by fmax**(1/2) * sigmaX * (vX**2) * p0**(-1) to get displacement
+        PixelDisplacements[ind[ii,0]] += PreDisplacementPrime[i][ind[ii,1]]
+    #Now we find the maximum displacement factor on each pixel
+    PreDisplacement[i] = (np.amax(PixelDisplacements)**.5) * (((9 * L) / (2 * np.pi * n * m * A))**.5) #Multiply by fmax**(1/2) * sigmaX * (vX**2) * p0**(-1) to get displacement
+    PixelDisplacements = np.zeros(len(hppoints))
+
 print(PreDisplacement)
 #We save the max displacements in each pixel (up to position independent info i.e. fmax**(1/2) * sigmaX * (vX**2) * p0**(-1))
 sio.savemat('PreDisplacement'+sys.argv[5]+'.mat', {'PreDisplacement':PreDisplacement})

### 2016-09-07 HPCAnalysis/HPCDataAnalysis.py
Update

@@ -52,6 +52,7 @@ for i in range(0,N):
         PixelDisplacements[ind[ii,0]] += PreDisplacementPrime[i][ind[ii,1]]
     #Now we find the maximum displacement factor on each pixel
     PreDisplacement[i] = (np.amax(PixelDisplacements)**.5) * (((9 * L) / (2 * np.pi * n * m * A))**.5) #Multiply by fmax**(1/2) * sigmaX * (vX**2) * p0**(-1) to get displacement
+    print(i)
     PixelDisplacements = np.zeros(len(hppoints))
 
 print(PreDisplacement)

### 2016-09-10 LaTeX/Article_Draft_EDITED.tex
Data Complete

--- 2016-09-07 LaTeX/Article_Draft.tex
@@
 The seismometers on the moon have a net useful range of up to $16\,\te{Hz}$ and are sensitive to displacements as small as $0.3\,\text{nm}$ \cite{latham1973lunar}\cite{nakamura1982apollo}.
-Therefore, we only calculate the energy contained in the modes of frequency less than $16\,\te{Hz}$.
+However, they were primarily run in low frequency peaked response mode \cite{eichelman1974apollo}.
+In this mode, the useful range is limited to $2\te{ Hz}$.
+Therefore, we only calculate the energy contained in the modes of frequency less than $2\,\te{Hz}$.
 

### 2016-09-10 HPC/DATA/ParAnalysis17.m

@@ -1,0 +1,65 @@
+clear
+
+format long
+
+R = 1.737 * 10^6; % m
+vsurf = 1000; %m/s
+
+load hppoints1Test.mat hppoints
+load PointsTestMat1Test.mat outputmat
+load PointsTestNum1Test.mat outputnum
+
+hppoints = double(hppoints);
+outputmat = double(outputmat);
+outputnum = double(outputnum);
+
+Data = cat(2,transpose(hppoints),outputmat(:,4),outputmat(:,5),outputmat(:,6),outputmat(:,8),outputmat(:,9)); % t,rho,REF,kappa,vp
+
+m = outputnum(1);
+n = outputnum(2);
+L = outputnum(3);
+
+clear('hppoints','outputmat','outputnum')
+N = n;
+A = 4 * pi * R^2 / N;
+dT = sqrt(A / pi) / vsurf;
+
+Data = sortrows(Data,1);
+IterDataLength = 0;
+Out = zeros(N,1);
+
+SumDisp = zeros(N,1);
+
+Disp = (Data(:,3) .* Data(:,4) .* Data(:,5)) ./ (Data(:,6).^3);
+Time = Data(:,2);
+
+for i = 1 : N
+    IterDataLength = max(IterDataLength,length(Data(Data(:,1) == i)));
+end
+IterDisp = zeros(IterDataLength,N);
+IterTime = zeros(IterDataLength,N);
+for i = 1 : N
+    IterDisp(:,i) = cat(1,Disp(Data(:,1) == i),zeros(IterDataLength-length(Disp(Data(:,1) == i)),1));
+    IterTime(:,i) = cat(1,Data((Data(:,1) == i),2),zeros(IterDataLength-length(Disp(Data(:,1) == i)),1));
+end
+for i = 1 : N
+    Comb = combnk(1 : IterDataLength,2);
+    LID = abs(IterTime(Comb(:,1)) - IterTime(Comb(:,2))) < dT & abs(IterTime(Comb(:,1)) - IterTime(Comb(:,2))) > 0;
+    %CombIterDisp = combnk(IterDisp(:,i),2);
+    for ii = 1 : IterDataLength
+        if LID(ii) == 1
+            IterOut(ii) = IterDisp(comb(ii,1));
+        end
+        PixOut(i) = max(IterOut)
+    end
+end
+
+%parfor i = 1 : N
+%    sum(combnk(IterData(LID),2),1)
[…]

### 2016-09-10 Results/Resultifier.m

@@ -1,12 +1,12 @@
 clear
 
 format long
-SampleSize = 16;
-Threshold = 5E-11;
+SampleSize = 17;
+Threshold = 3E-10;
 
 fmax = 20;
 vX = 2.7E5;
-sX = 1E-12;
+sX = 1E-11;
 p0 = 3.0E8;
 
 C = zeros(SampleSize,1);
@@ -24,4 +24,4 @@ for i = 1 : SampleSize
     Disp = PreDisp .* ((p0 ^ (-1)) * (fmax ^ (1/2)) * sX * (vX ^ 2));
     C(i) = nnz(Disp > Threshold);
 end
-F = (sum(C.*D)/sum(D))
+F = (sum(C.*D)/sum(D))/n

### 2016-09-11 LaTeX/Article_Draft_EDITED.tex
Update

--- 2016-09-07 LaTeX/Article_Draft.tex
@@
 
-The seismometers on the moon have a net useful range of up to $16\,\te{Hz}$ and are sensitive to displacements as small as $0.3\,\text{nm}$ \cite{latham1973lunar}\cite{nakamura1982apollo}.
-Therefore, we only calculate the energy contained in the modes of frequency less than $16\,\te{Hz}$.
+The seismometers on the moon have a net useful range of up to $20\,\te{Hz}$ and are sensitive to displacements as small as $0.3\,\text{nm}$ \cite{latham1973lunar}\cite{nakamura1982apollo}.
+Therefore, we only calculate the energy contained in the modes of frequency less than $20\,\te{Hz}$.
 

### 2016-09-11 Results/Resultifier.m

@@ -2,12 +2,12 @@ clear
 
 format long
 SampleSize = 17;
-Threshold = 3E-10;
+Threshold = 10 * 3E-10;
 
 fmax = 20;
 vX = 2.7E5;
 sX = 1E-11;
-p0 = 3.0E8;
+p0 = 1.0E8;
 
 C = zeros(SampleSize,1);
 D = zeros(SampleSize,1);

### 2016-09-11 LaTeX/Old/Macro Impacts Revised.tex
Updated Organization

--- 2016-08-25 Macro Impacts Revised.tex
@@
 \end{align}
-where $\alpha$ is the thermal diffusivity, and $\alpha=\f{k}{c_p\rho}$. In cylindrical coordinates and for $T = T(r)$, we have
+where $\alpha$ is the thermal diffusivity, and $\alpha=\f{k}{c_p\rho}$ where k, $\rho$ and $c_p$ are the thermal conductivity, density and heat capacity of the impacted material respectively.
+In cylindrical coordinates and for $T = T(r)$, we have
 \begin{align}
@@
 \end{align}
+where $\frac{dE}{dx}$,$r_X$,$\sigma_{X}$ are the energy deposition, radius and scattering cross section of the Macro respectively.
 Note that this model/initial condition is reasonable given that the delta source becomes a Gaussian with the same energy (assuming energy is conserved) an instant after the initial input of the delta source.

### 2016-09-11 HPC/DATA/SlowAnalysis1.m

@@ -33,7 +33,7 @@ for i = 0 : N - 1
     TempData = Data(C : C + I - 1,2 : 6);
     C = C + nnz(Data(:,1) == i);
     for j = 1 : I
-        LID = abs(TempData(j,1) - TempData(:,1)) < dT & abs(TempData(j,1) - TempData(:,1)) > 0;
+        LID = abs(TempData(j,1) - TempData(:,1)) < dT;
         Disp(i+1,1) = max(Disp(i+1,1),sum((TempData(LID,2) .* TempData(LID,3) .* TempData(LID,4)) ./ (TempData(LID,5).^3)));
     end
 end

### 2016-09-11 Results/Resultifier.m

@@ -2,11 +2,11 @@ clear
 
 format long
 SampleSize = 17;
-Threshold = 10 * 3E-10;
+Threshold = 8 * 3E-10;
 
 fmax = 20;
 vX = 2.7E5;
-sX = 1E-11;
+sX = 5E-12;
 p0 = 1.0E8;
 
 C = zeros(SampleSize,1);

### 2016-09-25 Simulation/Current/DataGeneration/Generation.m
Update
Moved files around and did some stuff

@@ -1,0 +1,404 @@
+clear
+
+format long
+
+%INPUTS
+D = 100*10^3; %THE DISTANCE OF CLOSEST APPROACH TO THE CENTER m
+ACO = 5; %IT TAKES 16 ITERATIONS FOR A RAY TO PASS ENTIRELY THROUGH THE MOON FOR UNSIMPLIFIED ATTENUATION. IT TAKES ONLY 8 FOR SIMPLIFIED ATTENUATION.
+M = 200; %NUMBER OF POINTS ON THE LINE
+N = 192; %NUMBER OF RAYS FROM EACH POINT
+
+%VPREMOON MODEL WITH SIMPLIFIED ATTENUATION
+
+%%{
+a = ([8.26955,5.5,3.2,1.0].*10^3).^(1/2); %THESE ARE THE CONSTANT TERMS IN THE PARABOLIC VELOCITY FIELD STRUCTURE, THE FIRST ENTRY CORRESPONDING TO THE CORE km/s
+b = ([2.47697*10^(-7),10^(-11),10^(-11),10^(-11)].*10^(-3)).^(1/2); %THESE ARE THE COEFFICIENTS OF THE QUADRATIC TERM IN THE VELOCITY FIELD 1/(s*km)
+
+as = ([4.66221,3.3,1.8,0.5].*10^3).^(1/2); %SHEAR WAVE VELOCITY CONSTANTS
+bs = ([1.08519*10^(-7),10^(-11),10^(-11),10^(-11)].*10^(-3)).^(1/2); %NOTE THAT b IS ESSENTIALLY SET TO 0 FOR 3 OUTER LAYERS BECAUSE THEY ARE SO THIN
+
+Radii = [0,1709.1,1725.1,1736.1,1737.1].*10^3; %NOTE THAT WE MUST TAKE 0 AS A LAYER FOR TECHNICAL PURPOSES km
+
+Q = [6750,6750,6750,6750].*10^3; %THE QUALITY FACTOR IN THE DIFFERENT REGIONS
+
+AverageV = [8.07936,5.5,3.2,1.0].*10^3; %THE AVERAGE VELOCITY IN EACH OF THESE REGIONS km/s (INTEGRAL r^2 dr v(r) / INTEGRAL r^2 dr), USED TO CALCULATE ATTENUATION, NOT RAY PROPAGATION
+
+rhoBoundaries = [   2.762       ,   2.762               ;...
+                    2.762       ,   2.762               ;...
[…]

### 2016-09-25 Simulation/Old/HPC/Data_Analysis_Code/Correct and Fast/Analysis.m

@@ -4,11 +4,11 @@ format long
 
 R = 1.737 * 10^6; % m
 vsurf = 1000; %m/s
-Res = 100; %Number of subdivisions per dT
+Res = 1000; %Number of subdivisions per dT
 
-load hppoints12.mat hppoints
-load PointsTestMat12.mat outputmat
-load PointsTestNum12.mat outputnum
+load hppoints17.mat hppoints
+load PointsTestMat17.mat outputmat
+load PointsTestNum17.mat outputnum
 
 hppoints = double(hppoints);
 outputmat = double(outputmat);
@@ -28,9 +28,9 @@ Data = sortrows(Data,1);
 C = 1;
 Disp = zeros(N,1);
 
-%NEW DATA ANALYSIS
+%NEW DATA ANALYSIS (MUCH FASTER)
 
-%{
+%%{
 Tmax = max(Data(:,2));
 Tmin = min(Data(:,2));
 
@@ -46,18 +46,28 @@ end
 Data(:,2) = T;
 Data = sortrows(Data,2);
 
+Points = Data(:,1);
+T = Data(:,2);
+
 TempDisp = zeros(N,Bins);
 TempDispMax = zeros(N,1);
 
 tic
+AllTempDisp = (Data(:,3) .* Data(:,4) .* Data(:,5)) ./ (Data(:,6).^3);
+SumTempDisp = zeros(N,Bins);
+parfor j = 0 : N - 1
+    for i = 1 : Bins
+        Id = (T == i) & (Points == j);
+        SumTempDisp(j + 1,i) = sum(AllTempDisp(Id));
+    end
+end
 
-AllTempDisp = sum((Data(:,3) .* Data(Id,4) .* Data(Id,5)) ./ (Data(Id,6).^3))
+Numbers = transpose(1 : Bins);
 
 for j = 0 : N - 1;
-    j
     for i = 1 : Bins
-        Id = Data(:,2) >= i - 1 & Data(:,2) < Res + i & Data(:,1) == j;
-        TempDisp(j + 1,i) = sum((Data(Id,3) .* Data(Id,4) .* Data(Id,5)) ./ (Data(Id,6).^3));
+        Id = Numbers >= i - 1 & Numbers < Res + i;
+        TempDisp(j + 1,i) = sum(SumTempDisp(j + 1,Id));
     end
[…]

### 2016-09-25 Simulation/Old/HPC/HPCGeneration/Ray-Tracing/Amplitude.m

@@ -1,0 +1,7 @@
+function A = Amplitude( k )
+%UNTITLED4 Summary of this function goes here
+%   Detailed explanation goes here
+
+
+end
+

### 2016-09-25 Simulation/Old/HPC/HPCGeneration/Ray-Tracing/GOD.m

@@ -1,0 +1,46 @@
+function output = GOD(s,a,b,AlphaRay,x0,s1,s2,~)
+%UNTITLED6 Summary of this function goes here
+%   Detailed explanation goes here
+output = 16.*(-1).^s2.*a.^3.*b.*exp(1).^(4.*a.*b.*s).*x0.*(a.^2+(-1).* ...
+b.^2.*x0.^2).*(a.^2.*(1+exp(1).^(2.*a.*b.*s)).^2+b.^2.*((-1)+exp( ...
+  1).^(2.*a.*b.*s)).^2.*x0.^2+2.*(-1).^s1.*a.*b.*((-1)+exp(1).^(4.* ...
+  a.*b.*s)).*x0.*cos(AlphaRay)).^(-1/2).*(a.^2.*((-1)+exp(1).^(2.* ...
+  a.*b.*s)).^2+b.^2.*(1+exp(1).^(2.*a.*b.*s)).^2.*x0.^2+2.*(-1) ...
+.^s1.*a.*b.*((-1)+exp(1).^(4.*a.*b.*s)).*x0.*cos(AlphaRay)).^(1/2) ...
+  .*(a.^4+4.*a.^2.*b.^2.*x0.^2+b.^4.*x0.^4+4.*(-1).^s1.*a.*b.*x0.*( ...
+  a.^2+b.^2.*x0.^2).*cos(AlphaRay)+2.*a.^2.*b.^2.*x0.^2.*cos(2.* ...
+ AlphaRay)).*(4.*a.^2.*b.^2.*(1+exp(1).^(4.*a.*b.*s)).*x0.^2+4.*( ...
+  -1).^s1.*a.*b.*exp(1).^(4.*a.*b.*s).*x0.*(a.^2+b.^2.*x0.^2).*cos( ...
+  AlphaRay)+((-1)+exp(1).^(4.*a.*b.*s)).*(a.^4+b.^4.*x0.^4+2.*a.^2.* ...
+  b.^2.*x0.^2.*cos(2.*AlphaRay))).^(-2).*sin(AlphaRay).*(1+16.* ...
+a.^2.*b.^2.*x0.^2.*(a.^2+(-1).*b.^2.*x0.^2).^2.*(4.*a.^2.*b.^2.*( ...
[…]

### 2016-09-25 Simulation/Old/HPC/HPCGeneration/Ray-Tracing/Ray_Tracing_Moon_1.m

@@ -1,0 +1,404 @@
+clear
+
+format long
+
+%INPUTS
+D = 100*10^3; %THE DISTANCE OF CLOSEST APPROACH TO THE CENTER m
+ACO = 5; %IT TAKES 16 ITERATIONS FOR A RAY TO PASS ENTIRELY THROUGH THE MOON
+M = 200; %NUMBER OF POINTS ON THE LINE
+N = 192; %NUMBER OF RAYS FROM EACH POINT
+
+%VPREMOON MODEL WITH SIMPLIFIED ATTENUATION
+
+%%{
+a = ([8.26955,5.5,3.2,1.0].*10^3).^(1/2); %THESE ARE THE CONSTANT TERMS IN THE PARABOLIC VELOCITY FIELD STRUCTURE, THE FIRST ENTRY CORRESPONDING TO THE CORE km/s
+b = ([2.47697*10^(-7),10^(-11),10^(-11),10^(-11)].*10^(-3)).^(1/2); %THESE ARE THE COEFFICIENTS OF THE QUADRATIC TERM IN THE VELOCITY FIELD 1/(s*km)
+
+as = ([4.66221,3.3,1.8,0.5].*10^3).^(1/2); %SHEAR WAVE VELOCITY CONSTANTS
+bs = ([1.08519*10^(-7),10^(-11),10^(-11),10^(-11)].*10^(-3)).^(1/2); %NOTE THAT b IS ESSENTIALLY SET TO 0 FOR 3 OUTER LAYERS BECAUSE THEY ARE SO THIN
+
+Radii = [0,1709.1,1725.1,1736.1,1737.1].*10^3; %NOTE THAT WE MUST TAKE 0 AS A LAYER FOR TECHNICAL PURPOSES km
+
+Q = [6750,6750,6750,6750].*10^3; %THE QUALITY FACTOR IN THE DIFFERENT REGIONS
+
+AverageV = [8.07936,5.5,3.2,1.0].*10^3; %THE AVERAGE VELOCITY IN EACH OF THESE REGIONS km/s (INTEGRAL r^2 dr v(r) / INTEGRAL r^2 dr), USED TO CALCULATE ATTENUATION, NOT RAY PROPAGATION
+
+rhoBoundaries = [   2.762       ,   2.762               ;...
+                    2.762       ,   2.762               ;...
+                    2.762       ,   2.600               ;...
[…]

### 2016-09-25 Simulation/Old/HPC/HPCGeneration/Ray-Tracing/ReflectionCoefficient.m

@@ -1,0 +1,7 @@
+function R = ReflectionCoefficient(LayerId,TempAmp,sinTheta,AlphaRay,v1,v2,rho1,rho2)
+%The fluid in which the wave arrives is labeled 1
+%   Detailed explanation goes here
+    R = 1 - TransmissionCoefficient(LayerId,TempAmp,sinTheta,AlphaRay,v1,v2,rho1,rho2);
+    
+end
+

### 2016-09-25 Simulation/Old/HPC/HPCGeneration/Ray-Tracing/TransmissionCoefficient.m

@@ -1,0 +1,21 @@
+function T = TransmissionCoefficient(LayerId,TempAmp,sinTheta,AlphaRay,v1,v2,rho1,rho2)
+%The fluid in which the wave arrives is labeled 1
+%   Detailed explanation goes here
+    Theta1 = zeros(size(AlphaRay));
+    Id = AlphaRay < pi / 2;
+    Idp = AlphaRay >= pi / 2;
+    Theta1(Id) = AlphaRay(Id);
+    Theta1(Idp) = pi - AlphaRay(Idp);
+    Theta2 = asin(sinTheta);
+    Z1 = rho1.* v1;
+    Z2 = rho2.* v2;
+    Tpre = (2.* Z2.*sec(Theta2))./(Z1.*sec(Theta1)+Z2.*sec(Theta2));
+    Thigh = Tpre > 1;
+    Tlow = Tpre < 0;
+    Tmid = (true(size(Tpre)) & (~ Thigh)) & (~ Tlow);
+    T(Thigh) = TempAmp(Thigh);
+    T(Tlow) = 0;
+    T(Tmid) = Tpre(Tmid).*TempAmp(Tmid);
+    
+end
+

### 2016-09-25 Simulation/Old/Results/Resultifier.m

@@ -1,0 +1,27 @@
+clear
+
+format long
+SampleSize = 17;
+Threshold = 10 * 3E-10;
+
+fmax = 20;
+vX = 2.5E5;
+sX = 1E-11;
+p0 = 1.0E8;
+
+C = zeros(SampleSize,1);
+D = zeros(SampleSize,1);
+
+for i = 1 : SampleSize
+    A = strcat('PreDisp',int2str(i));
+    B = strcat('PointsTestNum',int2str(i));
+    load(A,'PreDisp');
+    load(B,'outputnum');
+    m = outputnum(1);
+    n = outputnum(2);
+    L = outputnum(3);
+    D(i) = outputnum(4);
+    Disp = PreDisp .* ((p0 ^ (-1)) * (fmax ^ (1/2)) * sX * (vX ^ 2));
+    C(i) = nnz(Disp> Threshold);
+end
+F = (sum(C.*D)/sum(D))

### 2016-09-27 Simulation/Current/Pictures/HealpyIntensityMap.py
update

@@ -7,7 +7,11 @@ import itertools as it
 import math
 
 #Loading Data from Matlab
-mat_contents = sio.loadmat('/Users/David/Macro-Impact/Simulation/Current/DataAnalysis/Mat'+ sys.argv[1] +'.mat');
-points = mat_contents['outputmat'];
+mat_contents = sio.loadmat('/Users/David/Macro-Impact/Simulation/Current/Results/Disp'+ sys.argv[1] +'.mat');
+Disp = mat_contents['Disp'];
 
 nside = int(sys.argv[2]);
+
+Intensities = hp.read_map(Disp)
+
+hp.mollview(Intensities, coord['G','E'])

### 2016-09-27 LaTeX/Current/Article_Draft_EDITED.tex
Update
Some new ideas

--- 2016-09-11 LaTeX/Article_Draft_EDITED.tex
@@
 \end{align}
+
+Since it is unlikely that a Macro impact will be detected if it only just exceeds one digital unit of displacement, it is useful to use a weighted sum.
+As the strength of the signal goes to $\infty$, we should always expect impact to be seen, and as the displacement approaches $d = 3\times 10^{-10}\te{ m}$, we should expect no chance of detection.
+Hence, a tile with displacement $\Delta x$ has detection likelihood
+\begin{align}
+1-e^{p(1-\f{\Delta x}{d})}\,,
+\end{align}
+where $p$ describes how the detection probability increases as the strength of signal increases.
 \subsection{Homogeneous Limit}

### 2016-09-27 Simulation/Current/Results/Resultifier.m
More Update

@@ -5,7 +5,7 @@ format long
 Save = 1; %1 = save displacement arrays, 0 = do not save
 SampleSize = 1;
 Threshold = 1* 3E-10;
-p = 1; %Detection Likelihood Scaling
+p = log(sqrt(2)); %Detection Likelihood Scaling
 
 fmax = 20;
 vX = 2.5E5;

### 2016-09-27 LaTeX/Current/Macros2.tex
Add files via upload

--- 2016-09-06 LaTeX/Article_Draft.tex
@@
-\documentclass[prd,reprint,10pt]{revtex4-1}
-
-% Packages
-
-\usepackage{fullpage}
-\usepackage{amsmath, amsthm, amsfonts, amssymb, mathtools, calrsfs, tensor, physics,tikz-cd}
-\usepackage[mathscr]{euscript}
-\usepackage{graphicx}
-\graphicspath{ {images/} }
-\usepackage{enumitem}
-\setlist[description]{font=\normalfont}
-
-% Custom Commands
-
+\documentclass[9pt,twocolumn]{article}
+\usepackage[margin=0.5in]{geometry}
+\usepackage[utf8]{inputenc}
+\usepackage{amsmath}
+\usepackage{amstext}
+\usepackage{amsfonts}
+\usepackage{amssymb}
+\author{Jagjit}
+\title{MACros2}
+\usepackage[parfill]{parskip}
 \newcommand*\diff{\mathop{}\!\mathrm{d}}
@@
 
-% Miscellaneous
+\begin{document}
+\maketitle{Introduction}\par
+	Dark matter constitutes a large fraction of the Universe today.
+However, we are still unclear as to what exactly makes up this constituent.
+Some more prominent candidates are particles such as WIMPS and axions.
+In this paper, we consider a class of macroscopic dark matter candidates, which would yield detectable seismological signals if they were to pass through the moon.
+The theoretical motivation from this stems from the work of Witten (1984), in which macroscopic clumps of strange matter are shown to possibly be stable and contribute to the dark matter content of the Universe.
+The elegance of such a solution is that there is no need to invoke the existence of new particles to explain the observed discrepancy in gravitational masses and luminous masses in galaxies.\par
+	 Previous work on this topic has focused on both the moon and the Earth.
+Here we consider lunar seismometer limits before returning to the Earth in future work.
+The moon is an attractive site to carry out a seismological search for Macro impacts.
+Unlike the Earth, the Moon is nearly dormant.
+Most internal seismological activity in the Moon originates from deep Moonquakes, which are very attenuated by the time they reach the surface.
+Most of the noise in lunar seismograms comes from asteroids, but these are for the most part easily identifiable as such.\par
+	 Teplitz et al(2005) have placed some limits on a fraction of the parameter space of macros by considering the average total seismic energy released and the average number of seismic events on the moon.
+These data were obtained from the Apollo lunar seismometers in the 70's.
+In this paper, we revise these limits based on a computation of the seismic efficiency, which is the coupling constant representing the fraction of energy deposited by our macro on its passage through the earth that is available for seismic waves.
+The mechanism for this is anelastic damping, which is the preferential damping of higher frequency components of a signal on passage through an object.
+Note that this work also relies on a delta function distribution of the dark matter nuggets.
+However, one should expect some extended mass distribution of the dark matter nuggets.\par
+	In addition to that, we also seek to calculate the plasma zone, vapor zone and melt zone, which are the zones of rock that are converted into plasma, vaporized and melted respectively due to the extreme temperature of the rapidly expanding shockwave formed by the energy deposited due to the macro.
+This further reduces the seismic efficiency.
+Lastly, we ran computer simulations to determine if the stratified structure of the moon would focus the energy such that the signal received could be magnified in amplitude.
+Prior works neglected reflection and refraction in modelling the passage of the seismic waves.
+(However, these focusing effects proved to be of minimal significance, with the reduction in the seismic efficiency being orders of magnitude more.)\par
 
-\newtheorem{theorem}{Theorem}
-\usetikzlibrary{matrix,arrows,decorations.pathmorphing}
+	In this paper, we consider macros that would not have stopped in the moon, i.e.
+their energy deposition is not such that they experience a significant reduction in their speed.
+From the equation for the speed of the macro
+\begin{equation}
+v = v_0 exp^{-(x\sigma_x\rho/M_x)},
+\end{equation}
+this places a limit on the masses considered since the stopping length, $\rho\sigma_x/M_x << 1$ is much more than the diameter of the moon
+\begin{equation}
+M_x >> \rho\sigma_x
+\end{equation}\par
 
-% Title
-
-\begin{document}
-
-\title{New seismological constraints on the available parameter space of macroscopic dark matter}
-\author{}
-\affiliation{Physics Department\\ Case Western Reserve University\\ Cleveland, Ohio 44106-7079, USA}
-
-\begin{abstract}
-Limits have been proposed constraining the available parameter space of macroscopic dark matter (Macros).
-These limits were based on the energy deposition of Macros into low frequency seismic modes being akin to that of a nuclear or chemical bomb.
-We show that this assumption does not hold by considering the mechanism through which Macro impacts generate seismic waves.
-Our new estimates take into account the effect of seismometer sensitivity and energy distribution across frequencies, anelastic attenuation, geometric effects, internal anisotropy of the Earth or Moon, as well as energy loss due to melting.
-We produce limits describing the Macro parameter space which can be ruled out by current seismological evidence.
-\end{abstract}
-\maketitle
-\section{Introduction}
-Teplitz \textit{et al.} \cite{banerdt2005seismic} have suggested that the energy deposition into the $1\,\te{Hz}$ range from a nuclearite (Macro) impact should be $0.05$ of the total energy deposition.
-This, as shown in section II A, is a gross overestimate even compared to our own generous overestimation.
 	We produce a more accurate model of the seismic effects of Macro impacts, including in our model the effects of geometric lensing, stratification of the Moon, anelastic attenuation, and geometric attenuation.
@@
 We also include a simple argument which demonstrates that a large portion of the available parameter space cannot be ruled out by seismological constraints.
+Teplitz et al.
+(2005) have suggested that the energy deposition into the 1 Hz range from a nuclearite (Macro) impact should be 0.05 of the total energy deposition.
+This, as shown in section II A, is a gross overestimate even compared to our estimation.\par
 
-The moon is an attractive site to carry out a seismological search for Macro impacts.
-Unlike the Earth, the Moon is nearly dormant.
-Most internal seismological activity in the Moon originates from deep Moonquakes, which are very attenuated by the time they reach the surface.
-Most of the noise in lunar seismograms comes from asteroids, but these are for the most part easily identifiable as such.
-Thus, in the case that we can distinguish between asteroids and Macros, the Moon is a nearly ideal location to place constraints via total seismic event rate.
-However, in the case that the Macro impacts are very weak, it may be impossible to distinguish them from asteroids or weak Moonquakes based on a single seismogram.
-In this case, it is necessary to identify correlated events among lunar seismometers which correspond to a propagating source of seismic waves.
-This sort of analysis will be left to future work.
-\section{The Seismic Source}
-\subsection{Seismic Wave Generation}
+\maketitle{Vapor and melt zones}\par
+	We begin by calculating the fraction of energy deposited by the macro that is irreversibly lost to vaporization and melting and therefore unavailable for seismic propagation.
+We consider only the melting or vaporization that occurs prior to the onset of the deposited energy serving as a source for seismic waves, since the initiation of seismic wave propagation complicates assessing the amount of energy dissipated in melting (and vaporizing) the impacted material and its surroundings.
+To model an instantaneous energy deposition along the z-axis, we use a delta function, and set the solution of the heat equation equal to a fixed temperature (of melting).
+This yields an expression for the radius, as a function of time, of the impacted material and its surroundings that has reached its melting point temperature, $r_{melt(t)}$.\par
+	Differentiating $r_{melt(t)}$ with respect to time, setting the result equal to the bulk speed of sound and solving for t yields the time at which the propagation of the "melt point temperature zone" falls to the speed of sound.
+Plugging this time into $r_{melt(t)}$ yields $r_{fast-melt}$: the extent of the impacted material and its surroundings that is heated to its melting point more rapidly than bulk sound speed.
+Replacing the melting point temperature with the vaporization point temperature in the above demonstrates that $r_{fast melt}$ is essentially equal to $r_{fast}$ vaporize for all Macro radii.
+This result indicates that for macros with radii greater than $10^{(-9)}$ m $r_{fast}$ vaporize is of the same order as $r_x$.
+A simple computation shows that the heat dissipated in sublimating a column of material with radius $r_{fast}$ vaporize ranges from less than 1 J to 100 J, a negligible amount.\par
+	Some difficulties associated with this part of the project was quantifying the shock wave and its effects.
+Most of the literature on the subject involves pressures that are around the Hugoniot elastic limit.
+However initial calculations reveal that the pressures involved are significantly greater than this limit.
+Similarly temperatures involved fare exceed anything that is currently accessible naturally on Earth.
+Most work to determine plastic deformations (and hence energy permanently lost and unavailable for seismic attenuation) involves experimentally obtained material specific Hugoniot curves.
+Thus, experiments are required to accurately model the conditions expected from the passage of one of these macros through the moon or earth.\par
+\maketitle{Anelastic Attenuation}\par
+	Having calculated the minimum fraction of energy that is irreversibly lost to melting and vaporization, we now proceed to calculate the fraction of energy that is unattenuated by the moon.
+The moon acts as a low pass filter by preferentially attenuating the high frequency modes of the seismic signal.
+The relevant quantity is the quality factor, which is the related to the fraction of energy lost in one oscillation.
+\par
 	The energy from the initial impact generates a column of melted rock.
@@
 Macro's with velocity insignificantly changed by their encounter with the Moon source an overpressure of the form
-\begin{align}
+\begin{equation}
 \begin{array}{cc}p = p_0 f(r)&\te{ if }a<r<b,-\f h2<z<\f h2\,,\\ p = 0&\te{ else,}\end{array}
-\end{align}
+\end{equation}
 where $f$ is an analytic function on $[a,b]$ whose range is a subset of $[-1,1]$, and $p_0$ is the maximum differential pressure in this region.
@@
 Therefore, we only calculate the energy contained in the modes of frequency less than $16\,\te{Hz}$.
+(**Can talk about additional/more convoluted detectability criteria here**)
 
 The Fourier transform of $p$ to leading order in $kb$ is
-\begin{align}
-P = \f{4\pi p_0}{k\cos\theta}\sin\p{\f{h k\cos\theta}{2}}F+\scr O((kb)^0)\,,
-\end{align}
+\begin{equation}
+P = \f{4\pi p_0}{k\cos\theta}\sin\p{\f{h k\cos\theta}{2}}F\,
+\end{equation}
 where $\theta,\phi$ are the momentum space polar angles, $k$ is the magnitude of the wave-vector, $F = b^2f_1(b)-a^2f_1(a)$ and
-\begin{align}
+\begin{equation}
 f_1(x) = \sum_{n=0}^\infty\sum_{m=0}^n\binom{n}{m}\f{f^{(n)}(x_0)}{n!}\f{(-x_0)^{n-m}}{2+m}x^{m}\,,
-\end{align}
+\end{equation}
 for some $x_0\in[a,b]$. The energy of a seismic $p$-wave is
-\begin{align}
+\begin{equation}
 E = \f12\int\diff^3 x\p{ \rho\abs{\partial_t u}^2+(\lambda+2\mu)\abs{\nabla u}^2}\,,
-\end{align}
+\end{equation}
 where $u$ is the displacement field, and $\rho,\lambda,\mu$ are the density and Lam\`e coefficients respectively.
@@
 It follows that
-\begin{align}
+\begin{equation}
 E =\f1\kappa\int\f{\diff^3 k}{(2\pi)^3}\abs{P}^2\,.
-\end{align}
-Since a seismometer can only detect lower frequency modes, the detectible energy is
-\begin{align}
-E_k = \f1\kappa\int_0^k\f{\diff k'\diff\theta}{(2\pi)^2}k'^2\sin\theta\abs{P}^2\,.
-\end{align}
+\end{equation}
+Since a seismometer can only detect lower frequency modes, the detectable energy is
+\begin{equation}
+E_k = \f1\kappa\int_0^k\f{\diff k'\diff\theta}{(2\pi)^2}k'^2\sin\theta\abs{P}^2\,
+\end{equation}
 Substituting in our $P$, we find that
-\begin{align}
+\begin{equation}
 \notag E_k&=\f1\kappa 2p_0^2F^2\ell k^2\\\notag&\times\p{\f{\sin(\ell k)+k\ell(\cos(\ell k)-2)}{\ell^2 k^2}+\te{Si}(\ell k)}+\scr O((kb)^4)\,.
-\end{align}
+\end{equation}
 When $\ell k>1$ it is a good approximation to take
-\begin{align}
+\begin{equation}
 E_k&=\f1\kappa \pi\ell p_0^2F^2 k^2:=C_1 k^2\,.
-\end{align}
+\end{equation}
 
@@
 The Macro travels at super-sonic speeds and will generate a shock wave.
-Shock waves typically evolve to pressure fronts resembling a right triangle \cite{forbes2013shock} i.e.
+Shock waves typically evolve to pressure fronts resembling a right triangle i.e.
 $f = \p{r - r_0}/\Delta r$ where $a = r_0$ and $b = r_0 + \Delta r$.
@@
 In this case $f_1(x) = \p{2 x-3r_0}/6\Delta r$ and
-\begin{align}
+\begin{equation}
 E_k = \f{\Delta r^2(3r_0+2\Delta r)^2}{36 \kappa} \pi\ell p_0^2k^2\,.
-\end{align}
+\end{equation}
 The total energy of the pressure wave is
-\begin{align}
+\begin{equation}
 E \notag&= \f{2\pi p_0^2\ell}{\kappa}\int_a^b r\diff r f(r)^2\,,\\
 &=\f{p_0^2}{6\kappa}\pi\Delta r \ell(4r_0 + 3\Delta r)\,.
-\end{align}
+\end{equation}
 The Macro deposits energy
-\begin{align}
+\begin{equation}
 E_\te{initial} = \abs{\td{E}{x}{}}\ell = \rho\sigma_X v_X^2\ell\,,
-\end{align}
+\end{equation}
 and loses some energy from phase changes of its surroundings. Thus, the pressure waves have initial energy
-\begin{align}
+\begin{equation}
 E_\te{propagated} \notag&= E_\te{initial} - E_\te{melt}\,,\\
 &= \p{\rho\sigma_X v_X^2 - \epsilon_\te{melt}}\ell:=\epsilon\ell\,.
-\end{align}
+\end{equation}
 A very unrealistic assumption is that no energy is lost during the non-linear evolution.
@@
 We thus set $E = E_\te{propagated}$ and obtain an expression for $r_0$
-\begin{align}
+\begin{equation}
 r_0 =  \f{3\kappa\epsilon}{2\pi p_0^2\Delta r}-\f{3\Delta r}{4}\,.
-\end{align}
+\end{equation}
 $r_0$ demarcates the end of the non-linear regime.
@@
 A lower bound on $r_0$ is 0, corresponding to entirely linear behavior. This, in turn, imposes an upper bound on the pulse width
-\begin{align}
+\begin{equation}
 \Delta r\leq\sqrt{\f{2\kappa \epsilon}{\pi p_0^2}}\,.
-\end{align}
+\end{equation}
 We now form $\Xi:=E_k/E_\te{propagated}$ representing the fraction of deposited energy detectable to seismometers
-\begin{align}
+\begin{equation}
 \Xi = k^2\f{\p{\pi p_0^2\Delta r^2-18\kappa \epsilon}^2}{576 \pi p_0^2 \kappa \epsilon}\,.
-\end{align}
+\end{equation}
 When $\Delta r$ is restricted to its physical range, $\Xi$ is a monotonic decreasing function in $\Delta r$. Thus
-\begin{align}
+\begin{equation}
 \f{4}{9}\f{\kappa\epsilon k^2}{\pi  p_0^2} \leq \Xi <\f{9}{16}\f{\kappa\epsilon k^2}{\pi  p_0^2}\,.
-\end{align}
+\end{equation}
 It is important to note that these expressions only hold for $k(r_0+\Delta r)\ll 1$, however they will always provide an over-estimate of the fraction of detectable energy.
@@
 It is also important to notice that this choice of $p_0$ corresponds to $r_0$ on the order of $1\te{ km}$, which well exceeds the regime of non-linearity we would have expected based on the solutions to the heat equation.
-\section{Seismic Wave Propagation}
+
+\maketitle{Ray Propagation}\par
+	Due to the stratified nature of the moon, waves that propagate through it are subject to all the phenomena of rays, such as reflection and refraction.
+Depending on the density profile, there might be focusing of rays at certain locations on the surface of the body.
+This could increase the seismic efficiency calculated previously.
+To account for this, we wrote a program to propagate rays through the moon.\par
 	The velocity of $p$-waves as a function of distance from the center $r$ of the Earth and Moon (and presumably other spherical rocky celestial bodies) is of the form $v = a^2 - b^2 r^2$ \cite{garcia2011very}\cite{dziewonski1981preliminary}.
 Using Snell's law, we obtain the differential equations for the trajectory of $p$-wave rays within such bodies
-\begin{align}
+\begin{equation}
 v^2 \notag&= \dot r^2 + \f{p_\te{ray}^2 v^4}{r^2}\,,\\
 0 &=\dot\theta\pm\f{p_\te{ray} v^2}{r^2}\,.
-\end{align}
+\end{equation}
 where $r$ is the radial coordinate of the ray, $\theta$ is the polar angle of the ray measured from the center of the body, and $p_\te{ray}$ is the ray parameter, which is fixed along a ray trajectory.
@@
 In the case that $v = a^2 - b^2 r^2$, we obtain for some constants $q$ and $\theta_0$.
-\begin{align}
+\begin{equation}
 \notag&r(t) = \f{a\sqrt{(q^2e^{2abt}-b)^2 + 4a^2b^4 p_\te{ray}}}{b\sqrt{(qe^{2abt}+b)^2 + 4a^2b^4 p_\te{ray}}}\,,\\
 &\tan(\theta(t) - \theta_0) = \f{qe^{4abt}-b^2}{4ab^3p_\te{ray}}+abp_\te{ray}\,.
-\end{align}
+\end{equation}
 \textit{A priori} these are geodesics on the Poincar\'e disc of radius $\f ab$, which is easily seen from the form of $v$.
@@
 For a given mode, the ratio of final to initial amplitude is
-\begin{align}
+\begin{equation}
 \exp\ps{-k \int_{t_0}^t\diff t'\f{v(r(t))}{2Q(r(t))}}:=\exp\ps{-k \te{Att}}\,.
-\end{align}
+\end{equation}
 The VPREMOON Model \cite{garcia2011very} provides piecewise constant data for $Q$, so it is reasonable to subdivide the moon further into strata of different $Q$.
@@
 Thus, the amplitude of a ray can be computed by knowing the two numbers
-\begin{align}
+\begin{equation}
 \te{Ref} \notag&= \prod_i\te{Ref}_i\,,\\
 \te{Att} &=\sum_i\f{\Delta t_i v_i}{Q_i}\,,
-\end{align}
+\end{equation}
 where $\te{Ref}_i$ are the reflection or transmission coefficients of boundary $i$ on which the ray is incident.
 
-\section{Seismic Wave Detection}
 Consider a $p$-wave traveling towards positive $x$ and of compact support $S$ in the plane normal to to its motion.
@@
 The displacement field is
-\begin{align}
+\begin{equation}
 u(\vec x,t) &= \chi_{\R\times S}\int\f{\diff k}{2\pi}U(k)e^{-\I k(x-v_p t)}\,,\\
 \abs{u(\vec x,t)}&\leq\int\f{\diff k}{2\pi}\abs{U(k)}\,,
-\end{align}
+\end{equation}
 and the energy is
-\begin{align}
+\begin{equation}
 E = \rho v_p^2 A\int\f{\diff k}{2\pi}k^2\abs{U(k)}^2\,.
-\end{align}
+\end{equation}
 As before, we denote the energy in the low frequency spectrum
-\begin{align}
+\begin{equation}
 E_k = \rho v_p^2 A\int_0^k\f{\diff k'}{2\pi}k'^2\abs{U(k')}^2\,.
-\end{align}
+\end{equation}
 It follows that
-\begin{align}
+\begin{equation}
 \abs{U(k)} = \sqrt{\f{2\pi}{\rho v_p^2 A}}\f1k\sqrt{\td{E_k}{k}{}}\,,
-\end{align}
+\end{equation}
 and from the estimate above
-\begin{align}
+\begin{equation}
 \abs{u(\vec x,t)}\leq(2\pi\rho v_p^2 A)^{-1/2}\int_0^k\f{\diff k'}{k'}\sqrt{\td{E_{k'}}{k'}{}}\,.
-\end{align}
+\end{equation}
 In our case $\Xi E= C_1 k^2$ before attenuation. After anelastic attenuation, $E_k =\te{Ref}\,2C_1 k e^{-k\,\te{Att}}$
-\begin{align}
+\begin{equation}
 \abs{u(\vec x,t)}\leq\sqrt{\f{2}{\rho v_p^2 A}}\sqrt{\f{\te{Ref}\,\Xi E}{\te{Att}}}\f1k\te{Erf}\ps{\sqrt{\f{\te{Att}\,k}{2}}}\,.
-\end{align}
+\end{equation}
 (25) is impossible to integrate when $E_k$ consists of the energies of two different rays, each with different attenuation factors.
@@
 Taking $\te{Att} = 0$, the displacement caused by the incident $p$-wave is bounded above by
-\begin{align}
+\begin{equation}
 \abs{u(\vec x,t)}&\leq\sqrt{\f{4\te{Ref}\,\Xi E}{\pi k\rho v_p^2 A}}\,.
-\end{align}
-
-\section{Simulation}
+\end{equation}
+	\par
+	We note that using previous lunar data does not allow for detection of a macro even if it did register signals satisfying the minimum displacement thresholds of the Apollo seismometers because of the low number of detectors sites on the moon, which is 4.
+As Teplitz et al (2003) pointed out, a minimum of 6 seismometers are needed to distinguish an epilinear source from a point source.
+Thus our work here serves to use simulations of macro passages of various cross sections, for macros satisfying equation (1), to determine thresholds for signal detectibility for possible future seismic networks.
 	In previous works, e.g.
@@
 We then convert the intensity maps to displacement maps, and using the sensitivity of the lunar seismometers, we obtain an average event rate that the lunar seismometers would measure.
-\subsection{Data Generation}
+\maketitle{Map Generation}\par
 	We consider a Macro trajectory which passes a distance $D$ from the center of the moon.
@@
 Thus in order to save on computation time, it is reasonable to reduce the number of iterations to 9.
-\subsection{Data Analysis}
 	Analysis begins by converting the position data to HEALPix coordinates for a given $n_\te{side}$.
@@
 This procedure is repeated for 17 values of $D$ spaced evenly by $100\,\te{km}$. The average fraction of detectable surface area is then approximately
-\begin{align}
+\begin{equation}
 \scr F =\f{\sum_D \scr F_D}{\sum_D D}\,.
-\end{align}
+\end{equation}
 If there are $n$ lunar seismometers, we suppose that each occupies its own HEALPix pixel.
@@
 Otherwise, if $\scr M$ Macros impact the moon, the likelihood of any of them being detected is
-\begin{align}
+\begin{equation}
 \scr P &= 1-\ps{\f{(n_\te{pix}-n)!(n_\te{pix}-m)!}{n_\te{pix}!(n_\te{pix}-n-m)!}}^{\scr M}\,.
-\end{align}
-\subsection{Homogeneous Limit}
+\end{equation}
+
 To obtain an estimate of the size of a detectable Macro, we suppose that one ray from each point source on the Macro Trajectory hits a single pixel.
@@
 around the entrance and exit of the Macro trajectory.
-\begin{align}
+\begin{equation}
 u\leq\sqrt{\f{\Xi E}{\pi^2\rho k v_p^2 R_\te{Moon}^2}}\,.
-\end{align}
+\end{equation}
 This expression is independent of the choice of $n_\te{side}$.
-For the triangle wave, $\sigma_X\leq 1\times 10^{-7}\te{\,cm}^2$ is unlikely to be detected unless it enters or exits the Moon adjacent to a seismometer.
-\section{Results}
-Data has been generated but not run through the analysis routine yet. Preliminary results suggest that the computer analysis will not produce results much stronger than (30).
-\section{Conclusion}
+For the triangle wave, $\sigma_X\leq 1\times 10^{-7}\te{\,cm}^2$ is unlikely to be detected unless it enters or exits the Moon adjacent to a seismometer.\par
+
 For Macros with density sufficient to pass nearly unimpeded through the Moon and sufficiently small cross-section, and in particular nuclear dense objects such as strange quark nuggets with cross-section $\sigma_X\leq 1\times 10^{-7}\te{\, cm}^2$, we have demonstrated that seismological constraints are insufficient to rule them out.
 Since the Moon (and Earth) preferentially attenuate higher frequency modes, it is unlikely that measuring high frequencies would greatly improve sensitivity to these types of impacts.
-On the other hand, increasing the lunar seismometer sensitivity to small displacements may allow one to use seismological evidence to rule out high density Macros, although it is uncertain whether seismic noise at such small displacements would make Macro impacts indistinguishable from the background.
+On the other hand, increasing the lunar seismometer sensitivity to small displacements may allow one to use seismological evidence to rule out high density Macros, although it is uncertain whether seismic noise at such small displacements would make Macro impacts indistinguishable from the background.\par
 
@@
 In the future, a more sensitive lunar array will allow for a better understanding of the lunar structure and for a greater volume of Macro parameter space to be considered through seismic means.
-In the case that the lunar seismic background is too loud for extremely small displacements to be distinguished, it will be necessary to reconstruct the seismic response to high density Macros in order to measure an approximate event rate.
-\section{Acknowledgements}
+In the case that the lunar seismic background is too loud for extremely small displacements to be distinguished, it will be necessary to reconstruct the seismic response to high density Macros in order to measure an approximate event rate.\par
+
+\maketitle{Discussion}\par
+	In Teplitz et al (2005), he sets an approximate limit to rule out macros (for a delta function mass distribution) in the range of 10 - 1000 kg making up a significant fraction of the dark matter local density.(not sure why he doesn't say anything about masses below 10kg, should be able to say the same thing about those as well).
+However our re-calculation of just the seismic efficiency alone removes this boundary entirely, as Teplitz et al noted in the same paper, based on possible recalculations of this quantity.
+It is likely the boundary will be even lower if the irreversible energy loss due to melting and vaporization was better quantified.
+\par
+	(noise level discussion?)
+\maketitle{Conclusion}\par
+\maketitle{Acknowledgements}\par
 This work made use of the High Performance Computing Resource in the Core Facility for Advanced Research Computing at Case Western Reserve University.
-David Cyncynates would like to thank SOURCE for supporting this research.
-\bibliography{Macro-Impact}{}
-\bibliographystyle{apsrev4-1}
+David Cyncynates would like to thank SOURCE for supporting this research.\par
+(**sources/references**)
 \end{document}

### 2016-09-27 LaTeX/Current/Article_Draft_EDITED.tex
More Update
Small correction
corrected again
Updated Article_Draft_EDITED.pdf

@@
 We then use HEALPix to create an intensity map of the lunar surface for a representative sample of Macro impacts.
-We then convert the intensity maps to displacement maps, and using the sensitivity of the lunar seismometers, we obtain an average event rate that the lunar seismometers would measure.
+Finally, we convert the intensity maps to displacement maps, and using the sensitivity of the lunar seismometers, we obtain an average event rate that the lunar seismometers would measure.
 \subsection{Data Generation}
 We consider a Macro trajectory which passes a distance $D$ from the center of the moon.
-The Macro trajectory has length $L$, and along its trajectory we consider a set of $M$ points.
+The Macro trajectory has length $L$ within the moon, and along its trajectory we consider a set of $M$ points.
 From each of these points we propagate $N$ randomly oriented rays, each endowed with $E_i = \rho(r_{i})\sigma_Xv_X^2 L/(MN)$ energy, where $i\in\{1,\dots,M\}$ labels the point, and $\rho$ is taken to be a function of the radius.
@@
 Since the moon is stratified, we must halt the propagation at the boundary of each layer to reflect and transmit rays.
-During a ray's propagation through a given stratum, its time spent in that layer $\Delta t_i$ is recorded, the attenuation factor in that layer $\te{Att}_i$ is recorded, and the reflection/refraction coefficient $\te{Ref}_i$ is recorded.
+During a ray's propagation through a given stratum, its time spent in that layer $\Delta t_i$, the attenuation factor in that layer $\te{Att}_i$, and the reflection/refraction coefficient $\te{Ref}_i$ are all recorded.
 Each time a ray makes contact with the surface of the Moon, its position, $\te{Att}$, $\te{Ref}$, and $\Delta t$ are recorded.
-The data produced by the propagation routine is a table of these values and the corresponding surface coordinates, as well as density at the source, $\kappa$ at the source, and $p$-wave velocity at the source.
+The data produced by the propagation routine is a table of these values and the corresponding surface coordinates (i.e.
+we only count the energy of those rays which hit the surface), as well as density at the source, $\kappa$ at the source, and $p$-wave velocity at the source.
 In this model, it takes 16 iterations to propagate a ray from one side of the moon to the other.
-Rays which propagate from one side of the moon to the other only after 16 iterations will be weak from undergoing 16 refractions.
-Thus in order to save on computation time, it is reasonable to reduce the number of iterations to 9.
+However, we simplify the model by assuming constant $Q = 6750$.
+In this case, it takes 8 iterations to propagate entirely through the Moon.
 \subsection{Data Analysis}
-Analysis begins by converting the position data to HEALPix coordinates for a given $n_\te{side}$.
-We pick $n_\te{side} = 4$ since this corresponds to an angular resolution of 7 degrees, which accounts for the effects of diffraction about the strata boundaries.
+Analysis begins by converting the surface-incident ray position data to HEALPix coordinates for a given $n_\te{side}$.
 Define $A_\te{pix} = 4\pi R_\te{moon}^2/n_\te{pix}$ the area of a HEALPix pixel, where $n_\te{pix} = 12\times 2^{n_{\te{side}}}$.
@@
 Rays that contact a pixel within $t_\te{crossing}$ of one another are considered to add constructively.
-Since the integral in section IV is unreasonable to do for more than one ray, we average $\te{Att}$ over the coincident rays.
 We require that each ray distributes its energy evenly over the area of the HEALPix pixel, and thus set $A = A_\te{pix}$.
 This is a good approximation when $N=n_\te{pix}$, since the average angular separation of the rays at the source corresponds to the average angular separation of the HEALPix pixels.
+Note, for the case of the Moon, we omit the effects of anelastic attenuation since its contribution is relatively unimportant, as indicated by several tests in which its average contribution was on the order of $e^{-10^{-2}}$.
 
@@
 
-This procedure is repeated for 17 values of $D$ spaced evenly by $100\,\te{km}$. The average fraction of detectable surface area is then approximately
+Since it is unlikely that a Macro impact will be detected if it only just exceeds one digital unit of displacement, it is useful to use a weighted sum.
+As the strength of the signal goes to $\infty$, we should always expect impact to be seen, and as the displacement approaches $d = 3\times 10^{-10}\te{ m}$, we should expect no chance of detection.
+Hence, a tile with displacement $\Delta x$ has detection likelihood
 \begin{align}
-\scr F =\f{\sum_D \scr F_D}{\sum_D D}\,.
+1-\exp\ps{p\p{1-\f{\Delta x}{d}}}\,,
 \end{align}
-If there are $n$ lunar seismometers, we suppose that each occupies its own HEALPix pixel.
-Define $m = \scr Fn_\te{pix}$, the average number of pixels with detectable frequency.
+where $p$ describes how the detection probability increases as the strength of signal increases.
+Requiring that 4 digital units be $q$ times as detectable as 2 digital unit fixes $p = \ln\sqrt q$.
+Summing over the all the pixels yields the effective number of pixels in which there exists a detectable signal
+\begin{align}
+m_D = \sum_{i = 1}^{n_{\te{pix}}}\pc{1-\exp\ps{p\p{1-\f{\Delta x_i}{d}}}}
+\end{align}
+
+This procedure is repeated for 20 values of $D$ spaced evenly by $85\,\te{km}$. The average number of pixels on which there exists a detectable signal is then
+\begin{align}
+m =\f{\sum_D D m_D}{\sum_D D}\,.
+\end{align}
+If there are $n$ lunar seismometers (or tight clusters thereof), we suppose that each occupies one HEALPix pixel.
 If $n+m\geq n_\te{pix}$, then detection is guaranteed.
@@
 \end{align}
-
-Since it is unlikely that a Macro impact will be detected if it only just exceeds one digital unit of displacement, it is useful to use a weighted sum.
-As the strength of the signal goes to $\infty$, we should always expect impact to be seen, and as the displacement approaches $d = 3\times 10^{-10}\te{ m}$, we should expect no chance of detection.
-Hence, a tile with displacement $\Delta x$ has detection likelihood
-\begin{align}
-1-e^{p(1-\f{\Delta x}{d})}\,,
-\end{align}
-where $p$ describes how the detection probability increases as the strength of signal increases.
 \subsection{Homogeneous Limit}
@@
 \section{Results}
-Data has been generated but not run through the analysis routine yet. Preliminary results suggest that the computer analysis will not produce results much stronger than (30).
+Data has been generated but not run through the analysis routine yet. Preliminary results suggest that the computer analysis will not produce results much stronger than (32).
 \section{Conclusion}

### 2016-09-27 Simulation/HPC/Cart2Hp/Cart2Hp.py
Update

@@ -1,0 +1,19 @@
+#%reset
+import sys
+import scipy.io as sio
+from scipy.stats import mode
+import healpy as hp
+import numpy as np
+import itertools as it
+import math
+
+#Loading Data from Matlab
+mat_contents = sio.loadmat('/Users/David/Macro-Impact/Simulation/Current/DataGeneration/Mat'+ sys.argv[1] +'.mat');
+points = mat_contents['outputmat'];
+
+nside = int(sys.argv[2]);
+
+#Assigning each point its HEALPix coordinate
+hppoints = hp.pixelfunc.vec2pix(nside, points[:,0],points[:,1],points[:,2])
+
+sio.savemat('/Users/David/Macro-Impact/Simulation/Current/Cart2Hp/hppoints' + sys.argv[1] + '.mat', mdict = {'hppoints':hppoints})

### 2016-09-27 Simulation/HPC/DataAnalysis/Analysis.m

@@ -1,0 +1,98 @@
+clear
+
+format long
+
+R = 1.737 * 10^6; % m
+vsurf = 1000; %m/s
+Res = 1000; %Number of subdivisions per dT
+
+load /Users/David/Macro-Impact/Simulation/Current/Cart2Hp/hppoints1.mat hppoints
+load /Users/David/Macro-Impact/Simulation/Current/DataGeneration/Mat1.mat outputmat
+load /Users/David/Macro-Impact/Simulation/Current/DataGeneration/Num1.mat outputnum
+
+hppoints = double(hppoints);
+outputmat = double(outputmat);
+outputnum = double(outputnum);
+
+Data = cat(2,transpose(hppoints),outputmat(:,4),outputmat(:,5),outputmat(:,6),outputmat(:,8),outputmat(:,9)); % t,rho,REF,kappa,vp
+
+m = outputnum(1);
+N = outputnum(2);
+L = outputnum(3);
+
+clear('hppoints','outputmat','outputnum')
+A = 4 * pi * R^2 / N;
+dT = sqrt(A / pi) / vsurf;
+
+Data = sortrows(Data,1);
+C = 1;
+Disp = zeros(N,1);
+
+%NEW DATA ANALYSIS (MUCH FASTER)
+
+%%{
+Tmax = max(Data(:,2));
+Tmin = min(Data(:,2));
+
+Bins = int64(Res * ceil((Tmax-Tmin)/dT));
+
+T = zeros(length(Data(:,2)),1);
+
+for i = 1 : Bins
+    Id = (Data(:,2) > Tmin + (i - 1) * dT / Res) & (Data(:,2) <= Tmin + i * dT / Res);
+    T(Id,1) = i;
+end
+
+Data(:,2) = T;
+Data = sortrows(Data,2);
+
+Points = Data(:,1);
+T = Data(:,2);
+
+TempDisp = zeros(N,Bins);
+TempDispMax = zeros(N,1);
+
+AllTempDisp = (Data(:,3) .* Data(:,4) .* Data(:,5)) ./ (Data(:,6).^3);
+SumTempDisp = zeros(N,Bins);
+parfor j = 0 : N - 1
+    for i = 1 : Bins
+        Id = (T == i) & (Points == j);
+        SumTempDisp(j + 1,i) = sum(AllTempDisp(Id));
+    end
+end
+
+Numbers = transpose(1 : Bins);
+
[…]

### 2016-09-27 Simulation/HPC/DataGeneration/Generation1.m

@@ -1,0 +1,404 @@
+clear
+
+format long
+
+%INPUTS
+D = 1*85*10^3; %THE DISTANCE OF CLOSEST APPROACH TO THE CENTER m
+ACO = 5; %IT TAKES 16 ITERATIONS FOR A RAY TO PASS ENTIRELY THROUGH THE MOON FOR UNSIMPLIFIED ATTENUATION. IT TAKES ONLY 8 FOR SIMPLIFIED ATTENUATION.
+M = 400; %NUMBER OF POINTS ON THE LINE
+N = 12 * 2^8; %NUMBER OF RAYS FROM EACH POINT
+
+%VPREMOON MODEL WITH SIMPLIFIED ATTENUATION
+
+%%{
+a = ([8.26955,5.5,3.2,1.0].*10^3).^(1/2); %THESE ARE THE CONSTANT TERMS IN THE PARABOLIC VELOCITY FIELD STRUCTURE, THE FIRST ENTRY CORRESPONDING TO THE CORE km/s
+b = ([2.47697*10^(-7),10^(-11),10^(-11),10^(-11)].*10^(-3)).^(1/2); %THESE ARE THE COEFFICIENTS OF THE QUADRATIC TERM IN THE VELOCITY FIELD 1/(s*km)
+
+as = ([4.66221,3.3,1.8,0.5].*10^3).^(1/2); %SHEAR WAVE VELOCITY CONSTANTS
+bs = ([1.08519*10^(-7),10^(-11),10^(-11),10^(-11)].*10^(-3)).^(1/2); %NOTE THAT b IS ESSENTIALLY SET TO 0 FOR 3 OUTER LAYERS BECAUSE THEY ARE SO THIN
+
+Radii = [0,1709.1,1725.1,1736.1,1737.1].*10^3; %NOTE THAT WE MUST TAKE 0 AS A LAYER FOR TECHNICAL PURPOSES km
+
+Q = [6750,6750,6750,6750].*10^3; %THE QUALITY FACTOR IN THE DIFFERENT REGIONS
+
+AverageV = [8.07936,5.5,3.2,1.0].*10^3; %THE AVERAGE VELOCITY IN EACH OF THESE REGIONS km/s (INTEGRAL r^2 dr v(r) / INTEGRAL r^2 dr), USED TO CALCULATE ATTENUATION, NOT RAY PROPAGATION
+
+rhoBoundaries = [   2.762       ,   2.762               ;...
+                    2.762       ,   2.762               ;...
[…]

### 2016-09-27 Simulation/HPC/DataGeneration/Generation20.m

@@ -1,0 +1,404 @@
+clear
+
+format long
+
+%INPUTS
+D = 20*85*10^3; %THE DISTANCE OF CLOSEST APPROACH TO THE CENTER m
+ACO = 5; %IT TAKES 16 ITERATIONS FOR A RAY TO PASS ENTIRELY THROUGH THE MOON FOR UNSIMPLIFIED ATTENUATION. IT TAKES ONLY 8 FOR SIMPLIFIED ATTENUATION.
+M = 400; %NUMBER OF POINTS ON THE LINE
+N = 12 * 2^8; %NUMBER OF RAYS FROM EACH POINT
+
+%VPREMOON MODEL WITH SIMPLIFIED ATTENUATION
+
+%%{
+a = ([8.26955,5.5,3.2,1.0].*10^3).^(1/2); %THESE ARE THE CONSTANT TERMS IN THE PARABOLIC VELOCITY FIELD STRUCTURE, THE FIRST ENTRY CORRESPONDING TO THE CORE km/s
+b = ([2.47697*10^(-7),10^(-11),10^(-11),10^(-11)].*10^(-3)).^(1/2); %THESE ARE THE COEFFICIENTS OF THE QUADRATIC TERM IN THE VELOCITY FIELD 1/(s*km)
+
+as = ([4.66221,3.3,1.8,0.5].*10^3).^(1/2); %SHEAR WAVE VELOCITY CONSTANTS
+bs = ([1.08519*10^(-7),10^(-11),10^(-11),10^(-11)].*10^(-3)).^(1/2); %NOTE THAT b IS ESSENTIALLY SET TO 0 FOR 3 OUTER LAYERS BECAUSE THEY ARE SO THIN
+
+Radii = [0,1709.1,1725.1,1736.1,1737.1].*10^3; %NOTE THAT WE MUST TAKE 0 AS A LAYER FOR TECHNICAL PURPOSES km
+
+Q = [6750,6750,6750,6750].*10^3; %THE QUALITY FACTOR IN THE DIFFERENT REGIONS
+
+AverageV = [8.07936,5.5,3.2,1.0].*10^3; %THE AVERAGE VELOCITY IN EACH OF THESE REGIONS km/s (INTEGRAL r^2 dr v(r) / INTEGRAL r^2 dr), USED TO CALCULATE ATTENUATION, NOT RAY PROPAGATION
+
+rhoBoundaries = [   2.762       ,   2.762               ;...
+                    2.762       ,   2.762               ;...
[…]

### 2016-09-27 Simulation/HPC/DataGeneration/QualityFactor.m

@@ -1,0 +1,5 @@
+function output = QualityFactor(LayerId,DeltaTime,AverageV,Q,Suppression)
+%UNTITLED5 Summary of this function goes here
+%   Detailed explanation goes here
+output = Suppression + ((AverageV(LayerId).*DeltaTime)./Q(LayerId));
+end

### 2016-09-27 Simulation/HPC/DataGeneration/SR.m

@@ -1,0 +1,8 @@
+function output = SR(rm,a,b,x0,AlphaRay,s1,~,s3)
+%This function tells us what value of the parameter corresponds to the ray
+%intersecting a surface of radius R. May be incorrectly copied!
+output = (1/2).*a.^(-1).*b.^(-1).*log((a+(-1).*b.*rm).^(-1).*(a+b.*rm).^( ...
+ -1).*(a.^2+b.^2.*x0.^2+2.*(-1).^s1.*a.*b.*x0.*cos(AlphaRay)).^(-1).*(a.^4+(-1).*b.^4.*rm.^2.*x0.^2+a.^2.*b.^2.*(rm+(-1).*x0).*(rm+x0)+ ...
+2.*(-1).^s3.*a.*b.*((rm+(-1).*x0).*(rm+x0).*(a.^4+(-1).*b.^4.* ...
+rm.^2.*x0.^2)+(a.^2+(-1).*b.^2.*rm.^2).^2.*x0.^2.*cos(AlphaRay).^2).^(1/2)));
+end

### 2016-09-27 Simulation/HPC/Pictures/HealpyIntensityMap.py

@@ -1,0 +1,17 @@
+import sys
+import scipy.io as sio
+from scipy.stats import mode
+import healpy as hp
+import numpy as np
+import itertools as it
+import math
+
+#Loading Data from Matlab
+mat_contents = sio.loadmat('/Users/David/Macro-Impact/Simulation/Current/Results/Disp'+ sys.argv[1] +'.mat');
+Disp = mat_contents['Disp'];
+
+nside = int(sys.argv[2]);
+
+Intensities = hp.read_map(Disp)
+
+hp.mollview(Intensities, coord['G','E'])

### 2016-09-27 Simulation/HPC/Results/Resultifier.m

@@ -1,0 +1,41 @@
+clear
+
+format long
+
+Save = 1; %1 = save displacement arrays, 0 = do not save
+SampleSize = 1;
+Threshold = 1* 3E-10;
+p = log(sqrt(2)); %Detection Likelihood Scaling
+
+fmax = 20;
+vX = 2.5E5;
+sX = 1E-11;
+p0 = 1.0E8;
+
+C = zeros(SampleSize,1);
+Cweight = zeros(SampleSize,1);
+D = zeros(SampleSize,1);
+
+for i = 1 : SampleSize
+    A = strcat('/Users/David/Macro-Impact/Simulation/Current/DataAnalysis/PreDisp',int2str(i));
+    B = strcat('/Users/David/Macro-Impact/Simulation/Current/DataGeneration/Num',int2str(i));
+    load(A,'PreDisp');
+    load(B,'outputnum');
+    m = outputnum(1);
+    n = outputnum(2);
+    L = outputnum(3);
+    D(i) = outputnum(4);
+    Disp = PreDisp .* ((p0 ^ (-1)) * (fmax ^ (1/2)) * sX * (vX ^ 2));
+    WeightedDisp = max(1 - exp(p.*(-(Disp-Threshold)./Threshold)),0);
+    C(i) = nnz(Disp> Threshold);
+    Cweight(i) = sum(WeightedDisp);
+    
+    %SAVE DISPLACEMENTS TO MAKE PICTURES
+    
+    if Save == 1;
+        S = strcat('Disp',int2str(i),'.mat');
+        save(S,'Disp');
+    end
+end
+F = (sum(C.*D)/sum(D))
+Fweight = (sum(Cweight.*D)/sum(D))

### 2016-10-09 LaTeX/Current/Heat equation analysis.tex
Heat equation analysis files

\documentclass[prd,reprint,10pt]{revtex4-1}

% Packages

\usepackage{fullpage}
\usepackage{amsmath, amsthm, amsfonts, amssymb, mathtools, calrsfs, tensor, physics,tikz-cd}
\usepackage[mathscr]{euscript}
\usepackage{graphicx}
\graphicspath{ {images/} }
\usepackage{enumitem}
\setlist[description]{font=\normalfont}

% Custom Commands

\newcommand*\diff{\mathop{}\!\mathrm{d}}
\newcommand*\Diff[1]{\mathop{}\!\mathrm{d^#1}}
\newcommand*\nrml{\vartriangleleft}
\newcommand*\scr[1]{\mathscr{#1}}
\newcommand*\bb[1]{\mathbb{#1}}
\newcommand*\la{\langle}
\newcommand*\ra{\rangle}
\newcommand*\gen[1]{\langle #1 \rangle}
\newcommand*\x{\times}
\newcommand*\st{\text{ s.t. }}
\newcommand*\ord[1]{\left\vert#1\right\vert}
\newcommand*\aut{\text{Aut}}
\newcommand*\lcm{\text{lcm}}
\newcommand*\mcal{\mathcal}
\newcommand*\es{\emptyset}
\newcommand*\im{\text{ Im }}
\newcommand*\N{\mathbb N}
\newcommand*\Z{\mathbb Z}
\newcommand*\R{\mathbb R}
\newcommand*\Q{\mathbb Q}
\newcommand*\C{\mathbb C}
\newcommand*\te[1]{\text{#1}}
\newcommand*\en[1]{\begin{enumerate}#1\end{enumerate}}
\newcommand*\e{\varepsilon}
\newcommand*\p[1]{\left(#1\right)}
\newcommand*\ps[1]{\left[#1\right]}
\newcommand*\pc[1]{\left\{#1\right\}}
\newcommand*\f[2]{\frac{#1}{#2}}
\newcommand*\mat[2]{\left(\begin{array}{#1}#2\end{array}\right)}
\newcommand*\ocross{\otimes}
\newcommand*\I{\te{i}}
\newcommand*\pd[3]{\frac{\partial^{#3} #1}{\partial {#2}^{#3}}}
\newcommand*\td[3]{\frac{d^{#3}#1}{d #2^{#3}}}
\newcommand*\m{\te{Mat}}
\newcommand*\End{\te{End}}
\newcommand*\irr{\te{Irr}}
\newcommand*\sgn{\te{sgn}}
\newcommand*\pn[2]{\left\|#1\right\|_{#2}}
\newcommand*\esssup{\te{ess sup}}
\newcommand*\essinf{\te{ess inf}}

% Miscellaneous

\newtheorem{theorem}{Theorem}
\usetikzlibrary{matrix,arrows,decorations.pathmorphing}

% Title

\begin{document}
\subsection{Heat Equation analysis}
As a first approximation for the energy dissipated as heat in a Macro impact, we consider only the melting or vaporization that occurs prior to the onset of the deposited energy serving as a source for seismic waves, since the initiation of seismic wave propagation complicates assessing the amount of energy dissipated in melting (and vaporizing) the impacted material.  To model an instantaneous energy deposition along the z-axis, we use the following initial condition
\begin{align}
T(r,0) = \f{\abs{\frac{dE}{dx}}\sigma_X}{2\pi \rho \sigma_X c_p}\f{\delta(r)}{r} = \f{\sigma_{X} v_X^2}{2\pi c_p}\f{\delta(r)}{r}\,,
\end{align}
where $\abs{\frac{dE}{dx}}$, $\sigma_{X}$, $v_X$ are the energy deposition, scattering cross section and velocity of the Macro respectively, and $c_p$, $\rho$ are the heat capacity and density of the impacted material respectively. This initial condition is reasonable given that the delta source becomes a Gaussian with the same energy (assuming energy is conserved) an instant after the initial energy deposition.
This gives the temperature field
\begin{align}
T(r,t) = \f{\sigma_{X} v_X^2}{4\pi \alpha c_p}\f{e^{-\f{r^2}{4t\alpha}}}{t},\,
\end{align} which is normalized such that $T(r_X,t_{max}) = \frac{\sigma_X v_X^2}{e \pi  c_p r_X^2} \approx 10^7 K$, where $r_X$ is the Macro radius and $t_{max}$ is found by maximizing $T(r_X,t)$.

\par Setting $T(r,t) = T_{melt}$ (the derivation for $T_{vaporization}$ is analogous) yields an expression for the radius, as a function of time, of the impacted material that has reached its melting point temperature,
\begin{align}
r_\te{melt}(t) = \sqrt{4t\alpha\ln\ps{\f{v_X^2\sigma_X}{4 \pi c_p \alpha T_\te{melt} t}}}\,.
\end{align} 
Differentiating $r_\te{melt}(t)$ with respect to time yields
\begin{align}
\dot r_\te{melt}(t) &=\sqrt{\f{\alpha}{t}}\p{\f{\ln\ps{\f{v_X^2\sigma_X}{4 \pi c_p \alpha T_\te{melt} t}} - 1}{\sqrt{\ln\ps{\f{v_X^2\sigma_X}{4 \pi c_p \alpha T_\te{melt} t}}}}}\,.
\end{align}
For the parameters at hand, $\ln\p{\f{v_X^2\sigma_X}{4 \pi c_p \alpha T_\te{melt} t}}$ is of order $10 \gg 1$, when $t < 2.2*10^{-6} s$ for $\sigma_X = 10^{-11} m^2$, and $t < 2.2*10^{-9} s$ for $\sigma_X = 10^{-14} m^2$; these thresholds of validity are significantly greater than the values found for $t_{fast} \approx 10^{-13} s$, where $t_{fast}$ is described below.  Hence, it is a reasonable approximation (as an overestimate) to take
\begin{align}
\dot r_\te{melt}(t) &=\sqrt{\f{\alpha}{t}\ln\ps{\f{v_X^2\sigma_X}{4 \pi c_p \alpha T_\te{melt} t}}}\,.
\end{align}
Setting $\dot r_\te{melt}(t) = v_p$, where $v_p$ is the bulk speed of sound, and solving for $t$ yields $t_{fast}$: the time at which the propagation of the "melt point temperature zone" falls to the speed of sound.  Plugging $t_{fast}$ into $r_\te{melt}(t)$ yields
\begin{align}
r_\te{fast melt} =  \frac{2\alpha}{v_p}W\p{\frac{v_p^2 v_X^2 \sigma_X}{4 \pi c_p \alpha^2 T_\te{melt}}}
\\
= \frac{2\alpha}{v_p}W\p{\frac{v_p^2 v_X^2 r_X^2}{4 c_p \alpha^2 T_\te{melt}}}:
\end{align}the extent of the impacted material heated to its melting point more rapidly than the bulk sound speed.

\par Observe that $ 1.07*10^9 \leq \frac{v_p^2 v_X^2 r_X^2}{4 c_p \alpha^2 T_\te{melt}} \leq 2.03*10^{12}$ for the parameters of limestone (lower bound, with $\sigma =10^{-14} m^2$) and granite (upper bound, with $\sigma = 10^{-11} m^2$) (parameter values are from Thermal properties of rocks report and Deep Geothermal Drilling Using Millimeter Wave Technology).  Hence, we can Taylor expand the Lambert function $W(x)$ around $x\to \infty$, and iterate $r_\te{fast melt}$ to find the macro radii for which $r_\te{fast melt} \approx r_X$.  We find that for limestone, if $r_X \leq 3.12*10^{-9} m$ then $r_\te{fast melt} \approx r_X$ and for granite, if $r_X \leq 3.29*10^{-9} m$, then $r_\te{fast melt} \approx r_X$.

Replacing the melting point temperature with the vaporization point temperature in the derivation above shows that $r_\te{fast melt}$ is essentially the same as $r_\te{fast vaporize}$ for all Macro radii.  Thus, for macros with radii greater than $2.92*10^{-9} m$, $r_\te{fast vaporize} \approx r_X$.

\par These results are notable for a number of reasons. First, $r_\te{fast melt}$ is highly sensitive to $\alpha$ and $v_p$ and relatively insensitive to the Macro's parameters, in contrast to what might be expected physically: for the limiting case which Macro impacts represent, the properties of the impacted material should be relatively unimportant in the physics of the impact (and, in particular, the initial heat transfer dynamics).  The instantaneous energy deposition model de-emphasizes the significance of the parameters of the Macro, and appears to (over)emphasize the significance of the parameters of the impacted material.

At face value, these results indicate that much of the melting occurs once the temperature field's expansion is slower than the speed of sound and that this deceleration occurs quite quickly.  
However, the assumptions of constant material parameters -- particularly $\alpha$ and $c_p$ -- and the applicability of Fourier's law, which assumes that any thermal gradients are small, while reasonable to first order, are suspect for this highly non-linear process.  Strikingly, this model implies a negligible quantity of the macro's energy deposition is rapidly dissipated in either melting or vaporization of the impacted material, since the heat dissipated in sublimating a column of material with radius $r_\te{fast vaporize} \approx r_X$ is given by
\begin{align}
Q_\te{sublimate} = (L_\te{melt} + L_\te{vaporization})\rho \pi h(r_X)^2,
\end{align}
where $L_\te{melt}$, $L_\te{vaporization}$, $\rho$ and $h$ are the latent heats of melting and vaporization, density, and diameter of the impacted material body.  $Q_\te{sublimate}$ ranges from less than $1 J$ to $10^2 J$, a negligible amount in comparison to $\abs{\frac{dE}{dx}}$.  This is of greater note when we recall the overestimation that results from dropping the negative term in $\dot r_\te{melt}(t)$.

The extreme temperatures generated by the impact (approximately $10^7 K$, as noted above) will convert much of the vaporized material to plasma; however, this conversion is a second order phase transition, and so does not require a latent heat input to occur.  Thus, the energy to transition from vapor to plasma could conceivably transfer back into seismic waves (as the particles slow down, recombine as vapor, condense to liquid, and then solidify). Similarly, the energy required to raise the temperature of the impacted material to its melting and vaporization points could subsequently source seismic waves: temperature changes in the column of heated material result in expansions  and contractions that lead to a column of ovepressure/underpressure. Hence, modeling the energy dissipated both in raising the temperature of the impacted material and in effecting a transition to plasma are complicated by the concurrent energy transfer to seismic waves.

\subsection{Heat Equation analysis, take 1}
\par Two approaches that initially present themselves to model the heat transfer due to a Macro impact as a limiting case of models found in impact engineering or astrophysical impact modeling present a number of challenges.  The immense speed of Macros added to their density differences with a target of standard Baryonic matter imply a negligible loss of momentum throughout any impact process.  This poses an obstacle for using momentum balance equations, a standard approach in impact engineering.  Moreover, it is assumed that no erosion nor disintegration will occur to the Macro penetrator, which further complicates applying the models of these two fields.  Additionally, impacts to brittle and ductile materials exhibit velocity thresholds (which are far lower than Macro speeds) at which impacts to these materials show significant alterations in the impact dynamics (e.g. the disappearance of a "cracked region" in the impacted material -- see page 11 of Penetration into dry porous rock; and there are numerous sources for each of the above points in the dropbox.  See especially "Modeling asteroid collisions and impact processes" section 3 where they describe the use of "point source models").  As one example of the failure of these models, consider equation (38) in Hypervelocity penetration modeling- momentum vs. energy and energy transfer mechanisms" which gives the plastic work done by a non-eroding penetrator:
\begin{multline}
W_p = 
\\
\pi  r^2 y \p{\frac{2 \ln(\frac{v_{plastic}
   \sqrt{1-\frac{v_{cavity}^2}{v_{plastic}^2}}}{v_{cavity}}+\frac{{v_{plastic}}}{v_{cavity}})}{\sqrt{1-\frac{\
   v_{cavity}^2}{v_{plastic}^2}}}-1} \geq 0,
\end{multline}
where $y$ is the yield strength of the impacted material, $r$ is the (final) cavity radius, and $v_{cavity}$ is the cavity expansion velocity.  The following assumes that $r \approx r_{macro}$, 
and that $v_{cavity} \approx v_{macro} = 2.5*10^5 m/s$. 
For cavity expansion velocities where $v_{cavity} \geq 0.2v_{sound}$ the elastic-plastic interface velocity is nearly the bulk sound speed: $v_{plastic} \approx v_{sound}$. Plugging $v_{macro}$ into the above amounts to taking $v_{cavity}\to \infty$ which gives $W_p = -\pi r_X y $ which, within the model this equation was derived for is highly suspect as a negative energy.

\par Instead of pursing the above models we consider, as a first approximation for the energy dissipated as heat in a Macro impact, only the melting or vaporization that occurs prior to the onset of the deposited energy serving as a source for seismic waves, since the initiation of seismic wave propagation complicates assessing the amount of energy dissipated in melting (and vaporizing) the impacted material.  To model an instantaneous energy deposition along the z-axis, we use a delta function, and set the solution of the heat equation equal to a fixed temperature (of melting). This yields an expression for the radius, as a function of time, of the impacted material and its surroundings that has reached its melting point temperature, $r_\te{melt}(t)$.  Differentiating $r_\te{melt}(t)$ with respect to time, setting the result equal to the bulk speed of sound and solving for t yields the time at which the propagation of the "melt point temperature zone" falls to the speed of sound.  Plugging this time into $r_\te{melt}(t)$ yields $r_\te{fast melt}$: the extent of the impacted material and its surroundings that is heated to its melting point more rapidly than bulk sound speed. Replacing the melting point temperature with the vaporization point temperature in the above demonstrates that $r_\te{fast melt}$ is essentially equal to $r_\te{fast vaporize}$ for all Macro radii.  This result indicates that for macros with radii greater than $10^{-9} m$, $r_\te{fast vaporize}$ is of the same order as $r_\te{Macro}$.  A simple computation shows that the heat dissipated in sublimating a column of material with radius $r_\te{fast vaporize}$ ranges from less than $1 J$ to $10^2 J$, a negligible amount.
The extreme temperatures generated by the impact (approximately $10^7 K$) will convert the vaporized material to plasma; however, this conversion is a second order phase transition, and so does not require a latent heat input to occur.  Thus, the energy to transition from vapor to plasma could conceivably transfer back into seismic waves (as the particles slow down, recombine as vapor, condense to liquid, and then solidify). Similarly, the energy required to raise the temperature of the impacted material and its surroundings to their melting and vaporization points could subsequently source seismic waves: temperature changes in the column of heated material result in expansions  and contractions that lead to a column of ovepressure/underpressure. Hence, to model the energy dissipated both in raising the temperature of the impacted material and its surroundings, and in effecting a transition to plasma are complicated by the concurrent energy transfer to seismic waves.
The force of these results are that either much of the melting occurs once the temperature field's expansion is slower than the speed of sound and this slow-down occurs very quickly, or that the material parameters -- especially the thermal diffusion coefficient and the heat capacity of the impacted material -- are far from constant in the case at hand (given the extremes of pressure and temperature involved, it is more likely the latter).  In addition, the instantaneous energy deposition model de-emphasizes the significance of the parameters of the macro, and appears to (over)emphasize the significance of the parameters of the impacted material.

\subsection{Heat Equation analysis, take 2}

The equation governing the evolution of the temperature field in 2 dimensions is, with no driving term,
\begin{align}
\partial_t T - \alpha\nabla^2 T = 0
\end{align}
where $\alpha$ is the thermal diffusivity, and $\alpha=\f{k}{c_p\rho}$ where k, $\rho$ and $c_p$ are the thermal conductivity, density and heat capacity of the impacted material respectively. In cylindrical coordinates and for $T = T(r)$, we have
\begin{align}
\partial_t T - \alpha\nabla_r T = 0
\end{align}
We now Fourier transform in $r$ and $\phi$, yielding
\begin{align}
\partial_t\tilde T =-\alpha k_r^2 \tilde T\,,
\end{align}
where
\begin{multline}
\tilde T =  \int_0^\infty r \diff r\int_{0}^{2\pi} T e^{i r(k_x\cos\phi +k_y\sin\phi)}\diff \phi\, 
\\
= 2\pi \int_0^\infty r \diff r  T J_0(k_r r)\,.
\end{multline}
where
\begin{align}
k_r = \sqrt{k_x^2 +k_y^2}
\end{align}
Now, we integrate $\partial_t\tilde T =-\alpha k_r^2 \tilde T\,$ and find that
\begin{align}
\tilde T = C_1e^{-\alpha k_r^2 t}.
\end{align}

Consider the initial condition of a delta source along the z-axis in cylindrical coordinates:
\begin{align}
T(r,0) = \f{\abs{\frac{dE}{dx}}\sigma_X}{2\pi \rho \sigma_X c_p}\f{\delta(r)}{r} = \f{\sigma_{X} v_X^2}{2\pi c_p}\f{\delta(r)}{r}\,,
\end{align}
where $\abs{\frac{dE}{dx}}$, $\sigma_{X}$ are the energy deposition and scattering cross section of the Macro respectively and where $\frac{v_{X}^2}{c_p} =  \frac{\rho \sigma_X v_X^2}{\rho \sigma_X c_p} = \frac{\abs{\frac{dE}{dx}}}{\rho \sigma_X c_p}$.  
Note that this model/initial condition is reasonable given that the delta source becomes a Gaussian with the same energy (assuming energy is conserved) an instant after the initial input of the delta source.

Taking the Fourier transform of this initial condition over r and $\phi$ fixes $C_1$ as 
\begin{align}
C_1 &= \int_0^\infty 2\pi r\diff r J_0 (k_r r) T(r,0) \,,\\
&= \int_0^\infty 2\pi r\diff r J_0 (k_r r) \f{\sigma_{X} v_X^2}{2\pi c_p}\f{\delta(r)}{r} \,,\\
&=\f{\sigma_{X} v_X^2}{c_p}\,.
\end{align}
where the factor of $2 \pi$ comes from the $\phi$ integral.
$T$ in real space is given by inverting the Fourier transform:
\begin{align}
T(r,t) &=\int_0^\infty \f{k_r\diff r}{2\pi} J_0(k_r r) C_1 e^{-\alpha k_r^2 t}\,,\\
&=\int_0^\infty \f{k_r\diff k_r}{2\pi} J_0(k_r r) C_1 e^{-\alpha k_r^2 t}\,,\\
&=\f{C_1 e^{-\f{r^2}{4t\alpha}}}{4\pi t\alpha}\,,\\
&=\f{\sigma_{X} v_X^2}{4\pi \alpha c_p}\f{e^{-\f{r^2}{4t\alpha}}}{t}\,.
\end{align}
Setting $T = T_\te{melt}$, we have
\begin{align}
r_\te{melt} = \sqrt{4t\alpha\ln\ps{\f{v_X^2\sigma_X}{4 \pi c_p \alpha T_\te{melt} t}}}\,.
\end{align}
where the positive branch of the square root has been taken as this is the physical result. Then taking the derivative w.r.t to time gives
\begin{align}
\dot r_\te{melt} &=\sqrt{\f{\alpha}{t}}\p{\f{\ln\ps{\f{v_X^2\sigma_X}{4 \pi c_p \alpha T_\te{melt} t}} - 1}{\sqrt{\ln\ps{\f{v_X^2\sigma_X}{4 \pi c_p \alpha T_\te{melt} t}}}}}\,.
\end{align}
Since, for the parameters at hand, $\ln\ps{\f{v_X^2\sigma_X}{4 \pi c_p \alpha T_\te{melt} t}}$ is at least of order $10 \gg 1$ (for $t < 2.2*10^{-6} s$, which is within the relevant time scale), it is a reasonable approximation (as an overestimate) to take
\begin{align}
\dot r_\te{melt} &=\sqrt{\f{\alpha}{t}\ln\ps{\f{v_X^2\sigma_X}{4 \pi c_p \alpha T_\te{melt} t}}}\,.
\end{align}
Thus, the time at which the velocity of the melt front is that of the speed of sound, $v_p$, is given by using the Lambert W-function (or "ProductLog" in Mathamatica) as
\begin{align}
t_{\te{fast}} = \f{\alpha}{v_p^2}W\p{\frac{v_p^2 v_X^2 \sigma_X}{4 \pi c_p \alpha^2 T_\te{melt}}}
\end{align}
Plugging in $t_{\te{fast}}$ to $r_\te{melt}$, which is a solid approximation for the given case, gives
\begin{multline}
r_\te{fast melt} =  \frac{2\alpha}{v_p}W\p{\frac{v_p^2 v_X^2 \sigma_X}{4 \pi c_p \alpha^2 T_\te{melt}}}
\\
= \frac{2\alpha}{v_p}W\p{\frac{v_p^2 v_X^2 r_X^2}{4 c_p \alpha^2 T_\te{melt}}},
\end{multline}
where $r_X$ is the macro radius.
\\\
Observe that $ 1.07*10^9 \leq \frac{v_p^2 v_X^2 r_X^2}{4 c_p \alpha^2 T_\te{melt}} \leq 2.03*10^{12}$ for $10^{-14} \leq \sigma_X \leq 10^{-11}$ and the parameters of limestone (lower bound, with $\sigma =10^{-14}$) and granite (upper bound, with $\sigma = 10^{-11}$) (parameter values are from Thermal properties of rocks report and Deep Geothermal Drilling Using Millimeter Wave Technology).  Hence, we can Taylor expand the Lambert function $W(x)$ around $x\to \infty$, and iterate $r_\te{fast melt}$ to find the macro radii for which $r_\te{fast melt} \approx r_X$.  We find that for limestone, if $r_X \leq 3.12*10^{-9}$ then $r_\te{fast melt} \approx r_X$ and for granite, if $r_X \leq 3.29*10^{-9}$, then $r_\te{fast melt} \approx r_X$.

These results are notable for a number of reasons. First, $r_\te{fast melt}$ is highly sensitive to $\alpha$ and $v_p$ and relatively insensitive to the macro's parameters, in contrast to what might be expected physically: for the limiting case which macro impacts represent, the properties of the impacted material should be relatively unimportant in the physics of the impact (and, in particular, the heat transfer dynamics).

At face value, these results indicate that much of the melting occurs once the temperature field's expansion is slower than the speed of sound and that this deceleration occurs quite quickly.  However, the assumptions of constant material parameters -- particularly $\alpha$ and $c_p$ -- and the applicability of Fourier's law, which assumes that any thermal gradients are small, while reasonable to first order, are suspect for this highly non-linear process.

As attempt to establish a lower bound for the energy that is unequivocally dissipated that relies on fewer parameters of the impacted material, consider the energy required to vaporize a cylinder of material (with parameters akin to rock) with radius equal to the macro and length h equal to the diameter of the moon, which is given by
\begin{align}
Q_\te{sublimate} = (L_\te{melt} + L_\te{vaporization})\rho \pi h(r_X)^2,
\end{align}

As an example, for $r_X \propto 10^{-6}$, this gives $Q \propto 10^2 J$ which is quite small, and for $r_X < 10^{-9}$ this gives results that are less than 1 J.

\bibliography{Macro-Impact}{}
\bibliographystyle{apsrev4-1}
\end{document}
